### 2016-06-21 R0V0.tex
> Done: First commit after reorganization.

% !TEX encoding = UTF-8 Unicode

\documentclass[10pt,twocolumn,twoside]{IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** FONT AND LANGUAGE PACKAGES ***

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathrsfs}

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

\usepackage[natbib=true,backend=bibtex,style=ieee,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
\addbibresource{../../../Library.bib}
\AtBeginBibliography{\small}

% !!!! IF FILE NOT FOUND DOWNLOAD IT FROM
%https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{xcolor}
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{./imgs}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

  \usepackage{epstopdf} % Must be loaded right after graphicx
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** CROSS-REF PACKAGES ***

\usepackage{hyperref}% backref linktocpage pagebackref
%
\hypersetup{
% Uncomment the line below to remove all links (to references, figures, tables, etc)
%draft, 
colorlinks=true, linktocpage=true, pdfstartpage=1, pdfstartview=FitV,
% Uncomment the line below if you want to have black links (e.g. for printing black and white)
%colorlinks=false, linktocpage=false, pdfborder={0 0 0}, pdfstartpage=3, pdfstartview=FitV, 
breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,
plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,
hypertexnames=true, pdfhighlight=/O, urlcolor=red!50!black, linkcolor=blue!75!black, citecolor=green!50!black,
%
% PDF file meta-information
%
pdftitle={},
pdfauthor={},
pdfsubject={},
pdfkeywords={},
pdfcreator={},
pdfproducer={LaTeX}
}

% *** MATH PACKAGES ***
%
\usepackage{amsmath, amsthm, amssymb, amsfonts}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** THEOREM ENVIRONMENTS ***

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{problem}[theorem]{Problem}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{todonotes}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Humberto~Stein Shiromoto,~\IEEEmembership{Member,~IEEE,}
        Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org.}% <-this % stops a space
}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

For linear systems, the problem of design controllers with a prescribed structure is known to be NP-hard \cite{BlondelTsitsiklis1997}. Consequently, for nonlinear systems, it is \emph{at least} NP-hard.

\paragraph{Overview.} The motivation and background needed for this paper are stated in Section \ref{sec:Background and Motivation}. The problem under consideration is formalized in Section \ref{sec:Problem Formulation}. Section \ref{sec:Results} presents the result of this paper. Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}. The proofs of the results are provided in Section \ref{sec:Proof of the Results}. Section \ref{sec:Conclusion} collects final remarks.

\paragraph{Notation.} Let $N\in\mathbb{N}$ be a constant value. The notation $\mathbb{N}_{[1,N]}$ stands for the set $\{i\in\mathbb{N}:1\leq i\leq N\}$. Let $c\in\mathbb{R}$ be a constant value. The notation $\mathbb{R}_{[1,c]}$ (resp. $\mathbb{R}_{\diamond c}$) stands for the set $\{x\in\mathbb{R}:1\leq x\leq c\}$ (resp.  $\{x\in\mathbb{R}:x\diamond c\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi) definite.

The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded. Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.

\subsection{Problem Formulation and Motivation}\label{sec:Problem Formulation and Motivation}

\noindent{\itshape Class of systems.} Consider the class of systems described by the differential equation
\begin{equation}\label{eq:general system}
	\dot{x}(t)=f(x(t))+B(x(t))u(t),	
\end{equation}
where, for positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively. The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and satisfy $f(0)=0$ and $B(0)=0$. From now on the dependence of on the time $t$ will be omitted.

A function $u^\ast\in\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ is said to be an \emph{input signal or control for \eqref{eq:general system}}. For such a control for \eqref{eq:general system}, and for every \emph{initial condition} $x^\ast$, there exists a unique solution to \eqref{eq:general system} (\cite{Teschl2012}) that is denoted by $X(t,x^\ast,u^\ast)$, when computed at time $t$. This solution is defined over an open interval $(\underline{t},\overline{t})$, and it is said to be \emph{forward complete} if $\overline{t}=+\infty$.

{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
\begin{equation}\label{eq:global exponential uniform stabilizability}
	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
\end{equation}
holds true, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}). Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.

Note that a stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable. This concept is formalized in the following definition recalled from \cite{Manchester2014a}.

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:global exponential uniform stabilizability}.
\end{definition}

Note that Definition \ref{def:US} reduces to the notion of stabilizability of equilibria, when $x^\ast=0$ (for further reading on stabilizability, the reader may address \cite{Bacciotti:1992}).

For each component $i\in\mathbb{N}_{[1,m]}$ of the feedback law $k^\ast=(k_1^\ast,\ldots,k_m^\ast)^\top$, denote the set of indexes
\begin{equation*}
	\mathscr{K}(i)=\left\{j\in\mathbb{N}_{[1,n]}:k_i^\ast\ \text{depends explicitely on}\ x_j \right\}.
\end{equation*}
The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures. For instance, when $m=n$ full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$. This is formalized by letting $\mathscr{K}(i)=\{i\}$. Moreover, at points where $k_i^\ast$ is differentiable, the explicit dependence on $x_i$ means that, for every index $j\in\mathbb{N}_{[1,n]}$ with $j\neq i$, $\partial k_i^\ast/\partial x_j\equiv0$.

Define also the set of feedback laws
\begin{equation*}
	\Xi=\left\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:k_i^\ast\ \text{has the property}\ \mathscr{K}(i)\right\}.
\end{equation*}

At this point, the problem under consideration in this paper can be stated as follows.

\begin{problem}\label{problem formulation}\hfill
	\begin{enumerate}
		\item Find a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$ for system \eqref{eq:general system} that globally exponentially uniformly stabilizes any forward complete solution $X(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system};

		\item The function $k^\ast=(k_1^\ast,\ldots,k_m^\ast)$ belongs to the set $\Xi$.
		\end{enumerate}
\end{problem}

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology) for network systems rendering it universally stabilizable. Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example system:i}
	\dot{x}_i=??
\end{equation}
Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example system:i}.

\subsection{Background}

{\itshape Riemannian metrics and differential formulation.} A Riemannian metric is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$. In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the metric is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function. Consequently, local notions of norm $|\delta_x|_x=\sqrt{\langle\delta_x,\delta_x\rangle_x}$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined. The metric is said to be \emph{bounded} if there exists constant values $\underline{m}>0$ and $\overline{m}>0$ such that, for every $x\in\mathbb{R}^n$, $\underline{m}I_n\leq M(x)\leq \overline{m}I_n$, where $I_n\in\mathbb{R}^{n\times n}$ is the identity matrix.

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{equation*}
	\ell(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}\,ds\ \text{and}\ e(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}^2\,ds.
\end{equation*}
The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem.
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma).
\end{equation}

A suitable framework to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by $A_{jk}(x,u)=\tfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)$
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

The resulting system composed of Equations \eqref{eq:general system} and \eqref{eq:general system:differential} is analyzed on the state space spanned by the vector $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.

Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$ with $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.

Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear parameter-varying systems (LPVS) (see \cite[Ch. 2 and 3]{Briat2015} for more information on LPVS).

The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively. If every solution $|\Delta_x(t,x,\delta_x,u,\delta u)|\to0$ exponentially as $t\to\infty$, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

A sufficient condition for the stability of \eqref{eq:general system:differential} is provided by analyzing the derivative of a particular function along the solutions of systems \eqref{eq:general system} and \eqref{eq:general system:differential}. This function is recalled from \cite{Forni2014} and \cite{Manchester2014a}.

\begin{definition}\label{def:}
		 A smooth function $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ is said to be a \emph{metric for system \eqref{eq:general system}} if there exist constant values $\underline{c}>$ and $\overline{c}>$ such that the inequality
		 \begin{subequations}\label{eq:metric}
		 \begin{equation}
		 	\underline{c}|\delta_x|^2\leq V(x,\delta_x)\leq \overline{c}|\delta_x|^2,
	 	 \end{equation}
	 	 holds, for every $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$. Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively. A metric system \eqref{eq:general system} receives the adjective \emph{contraction} if there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\frac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta x,u,\delta u))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 \end{subequations}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}
Note that a bounded Riemannian metric defined, for every $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$, as $V(x,\delta_x)=|\delta_x|_x^2$ and satisfying the set of inequalities \eqref{eq:metric} is a contraction metric for system \eqref{eq:general system}. With an abuse of concept, from now the bounded Riemannian metric defined above will be called simply as \emph{metric}.

The existence a contraction metric for system \eqref{eq:general system} with $u\equiv0$ implies that every two solutions of this system converge to each other exponentially. The proof of this claim can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.

For the class of systems considered in this paper, the following kind of metric is of interest, since it also allows the design a feedback law for system \eqref{eq:general system:differential}.

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{align}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x\leq\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
		\end{align}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for contraction. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

The following result is recalled from \cite{Manchester2014a} and provides a feedback law for system \eqref{eq:general system} given a feedback law for system \eqref{eq:general system:differential}.

\begin{theorem}\label{prop:CCM Existence}
	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a solution to item 1 of Problem~\ref{problem formulation}.
\end{theorem}

Another important result of Theorem \ref{prop:CCM Existence} the feedback for system \eqref{eq:general system} obtained by integrating a feedback law designed for system \eqref{eq:general system:differential}.

As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem \cite{Rantzer:2001}. The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.

Step 1 (Offline LMI computation). Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$. The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following linear matrix inequality (LMI)
\begin{equation}\label{eq:LMI formulation}
	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\preceq0,
\end{equation}
for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.

Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system} and $K=YW^{-1}$, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them. This implies that the solution $k^\ast$ to the integral equation
\begin{equation}\label{eq:contracting feedback law}
	k^\ast(t,s)=u^\ast(t)+\int_0^s K(\gamma(\sigma),k^\ast(t,\sigma))\gamma'(\sigma)\,d\sigma,
\end{equation}
where $s\in[0,1]$, is a feedback law for system \eqref{eq:general system}.

{\itshape Motivation.} From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.

{\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$. Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the LMI \eqref{eq:contracting feedback law}.

\section{Results}\label{sec:Results}

\begin{definition}\label{def:SSCCM}
	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if $M$ has a block-diagonal structure. 
\end{definition}

Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$. Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i},
	\end{equation*}
for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.

Although the requirement of a control-contraction metric $M$ to have block-diagonal structure may be restrictive, for positive linear time-invariant systems the existence of a matrices $P=P^\top\succ0$ with diagonal structure is not conservative \cite{Tanaka2011}. Thus, the question of how restrictive is the requirement of $M$ to be diagonal is open. The main result of the paper is stated below.

\todo[inline]{Compare SS-CCM with SS-LF from \cite{Dirr2015,Rantzer2013}}

To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the LMI \eqref{eq:LMI formulation}.

For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{equation*}
		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
	\end{equation*}
	and
	\begin{align*}
		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
		\text{has the property}&\ \mathscr{K}_Y(i)\}.
	\end{align*}
\end{subequations}
Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI \eqref{eq:LMI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

The detailed proof of Theorem \ref{thm:main result} is provided in Section \ref{sec:Proof of the Results}.

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the LMI \eqref{eq:LMI formulation} is cannot be done in parallel. The next result provides sufficient conditions to solve each component \eqref{eq:LMI formulation} independently, and according to the structure defined by the set $\Xi$. Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

Consider the smooth function $T:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times n}$ with elements $i,j\in\mathbb{N}_{[1,N]}$ defined as
	\begin{subequations}\label{eq:T}
	\begin{align}
		T_{ii}=-\dot{W}_i+A_{ii}W_i+W_iA_i^\top+B_iY_{ii}+(B_iY_{ii})^\top\nonumber\\
		+2\lambda_i W_i
	\end{align}
	and
	\begin{equation}
		T_{ij}=A_{ij}W_j+W_iA_{ji}+B_iY_{ij}+(B_jY_{ji})^\top.
	\end{equation}
	\end{subequations}

\begin{definition}\label{def:}
	The matrix $T$ is said to be \emph{block-diagonally dominant} if the inequality
	\begin{equation}\label{eq:BDD}
		|T_{ii}^{-1}|^{-1}\geq\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|,
	\end{equation}
	holds, for every index $i\in\mathbb{N}_{[1,N]}$ and for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
\end{definition}

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI
	\begin{equation}\label{eq:LMI formulation:i}
		T_{ii}\preceq 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the LMI \eqref{eq:LMI formulation}.
\end{corollary}

The detailed proof of Corollary \ref{cor:distributed computation} is provided in Section \ref{sec:Proof of the Results}.

\todo[inline]{See the works of Ahmadi (Princeton) on scale-diag. dom.}

\section{Illustration}\label{sec:Illustration}

Consider the network composed of interconnected systems described by the equation
\begin{equation}\label{eq:example}
		\left\{\begin{array}{rcl}
			\dot{x}_i&=&\dfrac{a}{k+z_i}-bx_i+d(x_{i-1}-2x_i+x_{i+1})\\
			\dot{y}_i&=&\alpha x_i-\beta y_i\\
			\dot{z}_i&=&-\dfrac{\delta z_i}{k_M+z_i}+\gamma y_i+u_i\\
		\end{array}\right.
\end{equation}
where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}=x_N$ for convenience.

System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and considered in \cite{Aminzare2014a}. When $d=0$, this system is a generic model describing how persistent oscillations can be generated by an autoinhibitory gene circuit \cite[Section 7.3.1]{Ingalls2013}. The variable $x_i$ is the mRNA is translated into the enzyme $y_i$ which catalyses the production of the metabolite $z$. The metabolite $z$ supresses the transcription of the mRNA. When $d\neq0$, the composed network is interconnected throughout a diffusive term.

As presented in Equation~\eqref{eq:example}, the translation of the mRNA $x_i$ is controlled by acting on the concentration of the metabolite $z_i$ by employing $u_i$.

\section{Proof of the Results}\label{sec:Proof of the Results}

\begin{proof}[Proof of Theorem \ref{thm:main result}]
	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ is a solution to the LMI \eqref{eq:LMI formulation}. Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$. Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi_Y$.

	The LMI \eqref{eq:LMI formulation} implies that the inequality
	\begin{equation*}
		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
	\end{equation*}
	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds. Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system}.

	It now remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds.
	\end{equation}

	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. More precisely, 
	\begin{equation*}
		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}.
	\end{equation*}
	This implies that the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.

	From Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
	\begin{align*}
		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i).
	\end{align*}
	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$.

	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} is given by Equation \eqref{eq:contracting feedback law}.

	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast).
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the smoothness of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, to show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.

	To show that a solution $k^\ast$ is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed. This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then the solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.

	Since the vector field $\overline{K}$ is smooth, it also Lipschitz. This implies that, for every fixed $t\geq0$, and for every $S>0$, there exists a constants $c_1(S)$ and $c_2(S)$ such that the inequality
	\begin{equation*}
		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
	\end{equation*}
	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$. Applying \cite[Theorem 2.12]{Teschl2012} pointwisely on $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.

	Note that, due to the structure of the matrix $K$, the feedback law $k^\ast$ defined in Equation \eqref{eq:contracting feedback law} solves item 2 of Problem~\ref{problem formulation}, i.e., $k^\ast\in\Xi$. Furthermore, the computation of a solution to Equation~\eqref{eq:K ODE} can be partially distributed, because each line of the matrix $K$ will depend only on specific components of the vector $\gamma'$.

	 This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
	By assumption, the pair of matrices $W$ and $Y$ is a solution to the LMI \eqref{eq:LMI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.

	Equation \eqref{eq:BDD} together with the fact that $|I_{n_i}|\leq |T_{ii}||T_{ii}^{-1}|$ implies that the inequality
	\begin{equation}\label{eq:BDD2} 
		\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|\leq |T_{ii}|
	\end{equation}
	holds, for every index $i\in\mathbb{N}_{[1,N]}$.

	For every $\delta_\eta\in\mathbb{R}^n$, consider the product $\delta_\eta^\top T\delta_\eta$. Each line $i\in\mathbb{N}_{[1,N]}$ of this product is given by
	\begin{equation*}
		\delta_{\eta_i}^\top\begin{bmatrix}
			T_{i1}&\cdots&T_{i(i-1)}&T_{ii}&T_{i(i+1)}&\cdots&T_{iN}
		\end{bmatrix}\delta_\eta.
	\end{equation*}
	Inequalities \eqref{eq:BDD2} and \eqref{eq:LMI formulation:i} imply that the inequalities
	\begin{equation*}
		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{x_i}^\top T_{ii}\delta_{\eta_i}\leq 0
	\end{equation*}
	hold, for every $\delta_\eta\in\mathbb{R}^n$. Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$. This later inequality is equivalent to the LMI \eqref{eq:LMI formulation}. This concludes the proof of Corollary~\ref{cor:distributed computation}.
\end{proof}

\section{Conclusion}\label{sec:Conclusion}

\appendices

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\printbibliography

\end{document}

### 2016-06-21 main.m
> Done: First commit after reorganization.

@@ -1,0 +1,90 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Title: Simulation of system (19) from [AS14].                           %
+% Author: H. Stein Shiromoto                                              %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+function main
+
+clear all
+close all
+clc
+
+% Set axis of graphs to LaTeX
+set(groot, 'defaultAxesTickLabelInterpreter','latex');
+set(groot, 'defaultLegendInterpreter','latex');
+
+
+% System Parameters
+
+global a b k km alpha beta gamma delta
+
+a     = 150; % [concentration/s]
+b     = 0.2; % [1/s]
+k     = 1;   % [concentration]
+km    = 1;   % ??
+alpha = 0.2; % [1/s]
+beta  = 0.2; % [1/s]
+gamma = 0.2; % [1/s]
+delta = 15;  % ??
+
+% Input
+global u
+
+u = 0;
+
+
+
+IC = [1,10,100];
+
+time = 0:1e-1:1e2;
+[time,simout] = ode45(@sys,time,IC);
+
+
+% Time Evolution of the Solution components
+figure
+plot(time,simout(:,1),'b-','LineWidth',2);
+hold on
+plot(time,simout(:,2),'r--','LineWidth',2);
+hold on
+plot(time,simout(:,3),'k:','LineWidth',2);
+grid on
+xlabel('Time $t$','interpreter','latex','fontsize',14);
+ylabel('Variables','interpreter','latex','fontsize',14);
+title('Time Evolution of the Components of the Solution','interpreter','latex','fontsize',14);
+legend('mRNA ($x$)','enzyme ($y$)','metabolite ($z$)','Location','Best');
+set(gca, 'FontSize', 14)
+axis tight
+grid on
+
+% 3D plot of the solution
+figure
+plot3(simout(:,1),simout(:,2),simout(:,3),'b-','LineWidth',2);
+hold on
+plot3(simout(1,1),simout(1,2),simout(1,3),'bo','LineWidth',2);
[…]

### 2016-06-22 AS14MultipleSystemsSimulation.m
> Done: added multiple systems simulation

@@ -1,0 +1,241 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Title: Simulation of system (19) from [AS14].                           %
+% Author: H. Stein Shiromoto                                              %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+function main
+
+clear all
+close all
+clc
+
+% Set axis of graphs to LaTeX
+set(groot, 'defaultAxesTickLabelInterpreter','latex');
+set(groot, 'defaultLegendInterpreter','latex');
+
+
+% System Parameters
+
+global a b k km alpha beta gamma delta d
+
+a     = 150; % [concentration/s]
+b     = 0.2; % [1/s]
+k     = 1;   % [concentration]
+km    = 1;   % ??
+alpha = 0.2; % [1/s]
+beta  = 0.2; % [1/s]
+gamma = 0.2; % [1/s]
+delta = 15;  % ??
+d     = 1;
+
+% Input
+global u1 u2 u3 u4 u5 u6
+
+u1 = 0;
+u2 = 0;
+u3 = 0;
+u4 = 0;
+u5 = 0;
+u6 = 0;
+
+
+xIC = rand(6,1)*100;
+yIC = rand(6,1)*100;
+zIC = rand(6,1)*100;
+
+IC = [xIC;yIC;zIC];
+
+time = 0:1e-1:5e1;
+[time,simout] = ode45(@sys,time,IC);
+
+size(simout)
+
+
+% Time Evolution of the Solution components
+figure
+subplot(3,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
+hold on
+subplot(3,1,1),plot(time,simout(:,2),'g-','LineWidth',2);
+hold on
+subplot(3,1,1),plot(time,simout(:,3),'r-','LineWidth',2);
+hold on
+subplot(3,1,1),plot(time,simout(:,4),'c-','LineWidth',2);
+hold on
[…]

### 2016-06-22 Example.m
> Done: Wrote the script to solve the LMI. Still having problems with it.

@@ -1,0 +1,621 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Title: Example for the paper                           %
+% Author: H. Stein Shiromoto                                              %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+function main
+
+clear all
+close all
+clc
+
+% Set axis of graphs to LaTeX
+set(groot, 'defaultAxesTickLabelInterpreter','latex');
+set(groot, 'defaultLegendInterpreter','latex');
+
+
+% System Parameters
+
+global a b k km alpha beta gamma delta d
+
+a     = 150; % [concentration/s]
+b     = 0.2; % [1/s]
+k     = 1;   % [concentration]
+km    = 1;   % ??
+alpha = 0.2; % [1/s]
+beta  = 0.2; % [1/s]
+gamma = 0.2; % [1/s]
+delta = 15;  % ??
+d     = 1;
+
+% Input
+global u1 u2 u3 u4 u5 u6
+
+u1 = 0;
+u2 = 0;
+u3 = 0;
+u4 = 0;
+u5 = 0;
+u6 = 0;
+
+
+xIC = rand(6,1)*100;
+yIC = rand(6,1)*100;
+zIC = rand(6,1)*100;
+
+IC = [xIC;yIC;zIC];
+
+time = 0:1e-1:5e1;
+[time,simout] = ode45(@sys,time,IC);
+
+PlotSimulation(time,simout)
+LMIOptimization
+
+end
+
+function []=PlotSimulation(time,simout)
+
+
+% Time Evolution of the Solution components
+figure
+subplot(3,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
+hold on
[…]

### 2016-06-22 R0V0.tex
> Done: Writing the example.

@@
 \end{equation}
-where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}=x_N$ for convenience.
+where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}:=x_N$ for convenience.
 
-System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and considered in \cite{Aminzare2014a}.
+System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and it is also based on \cite{Aminzare2014a}.
 When $d=0$, this system is a generic model describing how persistent oscillations can be generated by an autoinhibitory gene circuit \cite[Section 7.3.1]{Ingalls2013}.

### 2016-07-05 TheoreticalExample1c/PostProcessedWandDW.m
> Done: Scenarios working fine. Saved the output of each one.

@@ -1,194 +1,194 @@
 % Rewriting the matrix W
-VerifiedW11 = clean(replace(W(1,1), coefList, double(coefList)), 1e-06);
+VerifiedW11 = clean(replace(W(1,1), coefList, double(coefList)), 0.001);
 W11 = sdisplay(VerifiedW11);
 
-VerifiedW12 = clean(replace(W(1,2), coefList, double(coefList)), 1e-06);
+VerifiedW12 = clean(replace(W(1,2), coefList, double(coefList)), 0.001);
 W12 = sdisplay(VerifiedW12);
 
-VerifiedW13 = clean(replace(W(1,3), coefList, double(coefList)), 1e-06);
+VerifiedW13 = clean(replace(W(1,3), coefList, double(coefList)), 0.001);
 W13 = sdisplay(VerifiedW13);
 
-VerifiedW14 = clean(replace(W(1,4), coefList, double(coefList)), 1e-06);
+VerifiedW14 = clean(replace(W(1,4), coefList, double(coefList)), 0.001);
 W14 = sdisplay(VerifiedW14);
 
-VerifiedW15 = clean(replace(W(1,5), coefList, double(coefList)), 1e-06);
+VerifiedW15 = clean(replace(W(1,5), coefList, double(coefList)), 0.001);
 W15 = sdisplay(VerifiedW15);
 
-VerifiedW16 = clean(replace(W(1,6), coefList, double(coefList)), 1e-06);
+VerifiedW16 = clean(replace(W(1,6), coefList, double(coefList)), 0.001);
 W16 = sdisplay(VerifiedW16);
 
-VerifiedW17 = clean(replace(W(1,7), coefList, double(coefList)), 1e-06);
+VerifiedW17 = clean(replace(W(1,7), coefList, double(coefList)), 0.001);
 W17 = sdisplay(VerifiedW17);
 
-VerifiedW18 = clean(replace(W(1,8), coefList, double(coefList)), 1e-06);
+VerifiedW18 = clean(replace(W(1,8), coefList, double(coefList)), 0.001);
 W18 = sdisplay(VerifiedW18);
 
-VerifiedW21 = clean(replace(W(2,1), coefList, double(coefList)), 1e-06);
+VerifiedW21 = clean(replace(W(2,1), coefList, double(coefList)), 0.001);
 W21 = sdisplay(VerifiedW21);
 
[…]

### 2016-07-05 TheoreticalExample1c/PostProcessedY.m

@@ -1,98 +1,98 @@
 % Rewriting the matrix W
-VerifiedY11 = clean(replace(Y(1,1), coefList, double(coefList)), 1e-06);
+VerifiedY11 = clean(replace(Y(1,1), coefList, double(coefList)), 0.001);
 Y11 = sdisplay(VerifiedY11);
 
-VerifiedY12 = clean(replace(Y(1,2), coefList, double(coefList)), 1e-06);
+VerifiedY12 = clean(replace(Y(1,2), coefList, double(coefList)), 0.001);
 Y12 = sdisplay(VerifiedY12);
 
-VerifiedY13 = clean(replace(Y(1,3), coefList, double(coefList)), 1e-06);
+VerifiedY13 = clean(replace(Y(1,3), coefList, double(coefList)), 0.001);
 Y13 = sdisplay(VerifiedY13);
 
-VerifiedY14 = clean(replace(Y(1,4), coefList, double(coefList)), 1e-06);
+VerifiedY14 = clean(replace(Y(1,4), coefList, double(coefList)), 0.001);
 Y14 = sdisplay(VerifiedY14);
 
-VerifiedY15 = clean(replace(Y(1,5), coefList, double(coefList)), 1e-06);
+VerifiedY15 = clean(replace(Y(1,5), coefList, double(coefList)), 0.001);
 Y15 = sdisplay(VerifiedY15);
 
-VerifiedY16 = clean(replace(Y(1,6), coefList, double(coefList)), 1e-06);
+VerifiedY16 = clean(replace(Y(1,6), coefList, double(coefList)), 0.001);
 Y16 = sdisplay(VerifiedY16);
 
-VerifiedY17 = clean(replace(Y(1,7), coefList, double(coefList)), 1e-06);
+VerifiedY17 = clean(replace(Y(1,7), coefList, double(coefList)), 0.001);
 Y17 = sdisplay(VerifiedY17);
 
-VerifiedY18 = clean(replace(Y(1,8), coefList, double(coefList)), 1e-06);
+VerifiedY18 = clean(replace(Y(1,8), coefList, double(coefList)), 0.001);
 Y18 = sdisplay(VerifiedY18);
 
-VerifiedY21 = clean(replace(Y(2,1), coefList, double(coefList)), 1e-06);
+VerifiedY21 = clean(replace(Y(2,1), coefList, double(coefList)), 0.001);
 Y21 = sdisplay(VerifiedY21);
 
[…]

### 2016-07-05 TheoreticalExample1c/PreProcessedY.m

@@ -1,47 +1,47 @@
 
  % Creation of Variable Y1
 
-[Y11,Yc11,Yv11] = polynomial(q1,Ydegree,0);
-[Y12,Yc12,Yv12] = polynomial(q1,Ydegree,0);
-[Y13,Yc13,Yv13] = polynomial(q1,Ydegree,0);
-[Y14,Yc14,Yv14] = polynomial(q1,Ydegree,0);
-[Y15,Yc15,Yv15] = polynomial(q1,Ydegree,0);
-[Y16,Yc16,Yv16] = polynomial(q1,Ydegree,0);
-[Y17,Yc17,Yv17] = polynomial(q1,Ydegree,0);
-[Y18,Yc18,Yv18] = polynomial(q1,Ydegree,0);
+[Y11,Yc11,Yv11] = polynomial(q,Ydegree,0);
+[Y12,Yc12,Yv12] = polynomial(q,Ydegree,0);
+[Y13,Yc13,Yv13] = polynomial(q,Ydegree,0);
+[Y14,Yc14,Yv14] = polynomial(q,Ydegree,0);
+[Y15,Yc15,Yv15] = polynomial(q,Ydegree,0);
+[Y16,Yc16,Yv16] = polynomial(q,Ydegree,0);
+[Y17,Yc17,Yv17] = polynomial(q,Ydegree,0);
+[Y18,Yc18,Yv18] = polynomial(q,Ydegree,0);
 
  % Creation of Variable Y2
 
-[Y21,Yc21,Yv21] = polynomial(q2,Ydegree,0);
-[Y22,Yc22,Yv22] = polynomial(q2,Ydegree,0);
-[Y23,Yc23,Yv23] = polynomial(q2,Ydegree,0);
-[Y24,Yc24,Yv24] = polynomial(q2,Ydegree,0);
-[Y25,Yc25,Yv25] = polynomial(q2,Ydegree,0);
-[Y26,Yc26,Yv26] = polynomial(q2,Ydegree,0);
-[Y27,Yc27,Yv27] = polynomial(q2,Ydegree,0);
-[Y28,Yc28,Yv28] = polynomial(q2,Ydegree,0);
+[Y21,Yc21,Yv21] = polynomial(q,Ydegree,0);
+[Y22,Yc22,Yv22] = polynomial(q,Ydegree,0);
+[Y23,Yc23,Yv23] = polynomial(q,Ydegree,0);
[…]

### 2016-07-05 TheoreticalExample1c/TheoreticalExample1c.m

@@ -147,7 +147,7 @@ Ydegree = 2;
 
 LinesVectorB = size(B,1);
 
-PreProcessingY(LinesVectorB,L,'Decentralized')
+PreProcessingY(LinesVectorB,L,'General')
 PreProcessedY
 
 
@@ -184,7 +184,7 @@ tic
 LMISolvingTime = toc
 % optimize(Constraints,[],options);
 
-prec = 1e-6;
+prec = 1e-3;
 PostProcessingW(NAgents,2,prec)
 PostProcessedWandDW
 

### 2016-07-05 R0V0.tex
> Done: Removed Sontag's Example.

--- 2016-06-21 R0V0.tex
@@
 
-Consider the network composed of interconnected systems described by the equation
-\begin{equation}\label{eq:example}
-		\left\{\begin{array}{rcl}
-			\dot{x}_i&=&\dfrac{a}{k+z_i}-bx_i+d(x_{i-1}-2x_i+x_{i+1})\\
-			\dot{y}_i&=&\alpha x_i-\beta y_i\\
-			\dot{z}_i&=&-\dfrac{\delta z_i}{k_M+z_i}+\gamma y_i+u_i\\
-		\end{array}\right.
-\end{equation}
-where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}=x_N$ for convenience.
-
-System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and considered in \cite{Aminzare2014a}.
-When $d=0$, this system is a generic model describing how persistent oscillations can be generated by an autoinhibitory gene circuit \cite[Section 7.3.1]{Ingalls2013}.
-The variable $x_i$ is the mRNA is translated into the enzyme $y_i$ which catalyses the production of the metabolite $z$.
-The metabolite $z$ supresses the transcription of the mRNA.
-When $d\neq0$, the composed network is interconnected throughout a diffusive term.
-
-As presented in Equation~\eqref{eq:example}, the translation of the mRNA $x_i$ is controlled by acting on the concentration of the metabolite $z_i$ by employing $u_i$.
-
 \section{Proof of the Results}\label{sec:Proof of the Results}

### 2016-07-05 R0V0.tex
> Done: Added Theoretical Example.

@@
 
+Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
+\begin{equation}\label{eq:example}
+	\left\{\begin{array}{rcl}
+		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
+		\dot{y}_i&=&u_i,
+	\end{array}\right.
+\end{equation}
+where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.
+
+For each index $i\in\mathbb{N}_{[1,N]}$, define the vectors $q_i=(x_i,y_i)$, $\breve{q}_i=(x_{i-1},x_{i+1})$ and let $q=(q_1,\ldots,q_N)$. Denote also
+\begin{align*}
+	f_i(q_i,\breve{q}_i)=&\begin{bmatrix}
+		-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
+		0
+	\end{bmatrix}\\
+	B_i=&\begin{bmatrix}
+	0\\ 1
+	\end{bmatrix}.
+\end{align*}
+
+Note that system \eqref{eq:example} is not feedback linearizable in the sense of \cite{Isidori:1995}, because the vector fields
+\begin{align*}
+	B=&\mathbin{\mathtt{diag}}(B_1,\ldots,B_N),\\
+	\dfrac{\partial f}{\partial q}B-\dfrac{\partial B}{\partial q}f=&\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
+	2y_1\\0
+	\end{bmatrix},\ldots,\begin{bmatrix}
+	2y_N\\0
+	\end{bmatrix}\right)
+\end{align*}
+are not linearly independent when $y_1=\cdots=y_N=0$.
+Furthermore, due to the quadratic term on $y$, the only action of the controller on the $x$-subsystem is capable of is to move the $x$-component of solution to \eqref{eq:example} towards the positive semi-axis.
+In other words, the controller cannot reduce the value of the $x$-component.
+
+Employing the method provided in Theorem~\ref{thm:main result}, the LMI \eqref{eq:LMI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$.
+
+In all cases, the matrix $W$ has a diagonal structure as follows
+\begin{equation*}
+ W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),
+\end{equation*}
+the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.
+
+In the first one, no constraints were imposed on the matrix $Y$.
+The parser took 97 seconds to solve the  LMI \eqref{eq:LMI formulation}.
+The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
+\begin{equation*}
+		W_a=\mathbin{\mathtt{diag}}\left(
+ 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
+\end{equation*}
+and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
+\begin{align*}
+ \overline{Y}_{ij}=&-3y_i-0.08x_iy_i\\
+ \underline{Y}_{ij}=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
+\end{align*}
+
+\begin{figure*}
+\begin{equation}\label{eq:example:Y:general}
+		Y=\scalebox{0.75}{$\begin{bmatrix}
+			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1+0.003x_3y_1,&0.005y_1y_3,&-0.007y_1+0.001x_4y_1,&0\\
+			-0.008y_2-0.002x_1y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.007y_2-0.004x_3y_2,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
+			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.004x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.008y_3+0.002x_4y_3,&0\\
+			-0.009y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
+		\end{bmatrix}$}
+\end{equation}
+\end{figure*}
+
+In the second case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
+The time taken by the parser to solve the LMI \eqref{eq:LMI formulation} was 98 seconds.
+The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
+\begin{equation*}
+		W_a=\mathbin{\mathtt{diag}}\left(
+ 1.32,1.59\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.61\right).
+\end{equation*}
+and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
+\begin{align*}
+	Y_{ij}=&-3y_i-0.03x_iy_i&i,j\in\mathbb{N}_{[1,4]}\\
+	Y_{12}=&-4-0.01x_1-y_1^2-y_2^2-2x_1^2-x_2^2\\	
+	Y_{24}=&-3-0.01x_2-y_1^2-y_2^2-y_3^2-x_1^2-x_2^2-x_3^2\\	
+	Y_{36}=&-3-0.01x_3-y_2^2-y_3^2-y_4^2-x_2^2-x_3^2-x_4^2\\	
+	Y_{48}=&-4-0.01x_4-y_4^2-y_3^2-2x_4^2-x_3^2
+\end{align*}
+
+\begin{figure*}
+\begin{equation}\label{eq:example:Y:neighbor}
+	Y=\scalebox{0.75}{$\begin{bmatrix}
+	Y_{11},&Y_{12},&-0.01y_2+0.03x_2y_1,&0,&0,&0,&0,&0\\
+	-0.01y_2-0.002x_1y_2,&0,&Y_{23},&Y_{24},&-0.01y_2+0.03x_3y_2,&0,&0,&0\\
+	0,&0,&-0.01y_3+0.03x_2y_3,&0,&Y_{35},&Y_{36},&-0.01y_3-0.002x_4y_3,&0\\
+	0,&0,&0,&0,&-0.01y_4+0.03x_3y_4,&0,&Y_{47},&Y_{48}
+	\end{bmatrix}$}
+\end{equation}
+\end{figure*}
+
+In the last case, the fully decentralized scenario has been considered.
+The time taken by the parser to solve the LMI \eqref{eq:LMI formulation} was 101 seconds.
+In this case, $\mathscr{K}_Y(i)=\{j\in\mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}$, where $\mathscr{K}(i)=\{i\}$.
+Imposing $Y\in\Xi_Y$ and solving the LMI \eqref{eq:LMI formulation} the following matrices were obtained
+\begin{align*}
+ W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
+ Y=&\mathbin{\mathtt{diag}}\left(Y_1,Y_2,Y_3,Y_4\right)
+\end{align*}
+where
+\begin{equation*}
+		W_a=\mathbin{\mathtt{diag}}\left(
+ 1.43,1.17\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.03,2.17\right)
+\end{equation*}
+and, for each index $i\in\mathbb{N}_{[1,4]}$,
+\begin{align*}
+ Y_i=[-4.33y_i+0.04x_iy_i,\\
+ -7.78-&0.01x_i-2.73y_i^2-2.98x_i^2].
+\end{align*}
+
 \section{Proof of the Results}\label{sec:Proof of the Results}

### 2016-07-15 R0V0.tex
> Done: Must of the introduction.
> Do: Review some parts of the introduction. Maybe emphasize about the distributed integration of the controller and review the conclusion.

@@
 firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
-\addbibresource{../../../Library.bib}
+\addbibresource{../../../../Library.bib}
 \AtBeginBibliography{\small}
@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+\hyphenation{op-tical net-works semi-conduc-tor ORCID}
 
@@
 \thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
-Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org.}% <-this % stops a space
+Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org. ORCID: 0000-0002-0883-0231, }% <-this % stops a space
 }
@@
 \begin{abstract}
-The abstract goes here.
+In this paper, input-affine nonlinear systems are considered.
+The problem under consideration is to design structured (for instance, decentralized or distributed) controllers for this class of systems.
+Although control-Lyapunov functions are the natural candidate to design these feedback laws, in terms of dynamical programming, the search for these functions is non-convex \cite{Rantzer:2001}.
+On the other hand, control-contraction metrics provide controllers that render pairs of solutions exponentially converge to each other.
+Moreover, the search for a structured controller and a suitable metric can be formulated in terms of a convex optimization problem.
+Under block-diagonal dominance conditions, this convex optimization problem can also be distributed.
+An example illustrate the approach for a network system.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-IEEE, IEEEtran, journal, \LaTeX, paper, template.
+Nonlinear Systems, Feedback Design, Contraction Theory, Distributed Control, Network Systems
 \end{IEEEkeywords}
@@
 
-For linear systems, the problem of design controllers with a prescribed structure is known to be NP-hard \cite{BlondelTsitsiklis1997}.
-Consequently, for nonlinear systems, it is \emph{at least} NP-hard.
+Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
+The main concept employed for the control of dynamic systems is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
+In terms of computation, controller design problems are often translated in terms of dynamic programming.
 
-\paragraph{Overview.} The motivation and background needed for this paper are stated in Section \ref{sec:Background and Motivation}.
-The problem under consideration is formalized in Section \ref{sec:Problem Formulation}.
+For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
+The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.
+
+In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
+These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.
+In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.
+
+For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
+However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}).
+In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.
+
+An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
+One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation of the system is considered.
+The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below).
+This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.
+
+The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has several states (large scale), it does not scale well.
+This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
+
+Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
+For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems, i.e., to make the controller scalable.
+In some cases, this property is satisfied by desnigning controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
+
+In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
+Consequently, for nonlinear systems the problem is very challenging.
+
+In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}.
+Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure.
+The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to reduce the number of LMIs to be solved.
+
+For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein).
+However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}.
+The case can be even worse, when structural constraints are considered.
+
+For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs, in this work.
+The systems under consideration are continuously differentiable and affine in the input.
+One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed similarly to Lyapunov functions to measure the exponential convergence of pairs of solutions.
+Employing CCMs, the design of a structured feedback law allowing exponential convergence of solution is obtained in two steps.
+
+The first step consists of an off-line computation.
+The original system is extended with its \emph{differential / variational} formulation.
+The exponential convergence is reformulated in terms of stability of the origin for the extended system.
+This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint.
+The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law.
+
+The second step consists of an on-line integration. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).
+
+\todo[inline]{Highlight the difference between this paper and \cite{Manchester2014a} by saying that this one the integration part is also distributed.}
+
+At this point, the three contributions of this work can be highlighted.
+First, a systematic framework for off-line computation of a structured controller and metric for nonlinear systems is provided.
+This framework is the formulation of a convex optimization problem whose computation can also be distributed, provided that some conditions are met.
+Second, the computation of the online integration phase can distributed, due to the structure imposed on the metric.
+Third, the structure impose on the controller allows to address the scalability issue of CCMs.
+Note that the proposed method provides an explicit formula for the controller, since it is constructive.
+
+Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
+These are mostly related to network systems.
+For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
+This paper contrast with these works mainly in two points: 1) A systematic framework  for structured controller design is proposed; 2) Due the formulation of the stabilization as a convex optimization problem, not only a explicit formula of a structured controller is obtained but also a metric.
+
+\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}.
+The background needed for this paper is stated in Section \ref{sec:background}.
 Section \ref{sec:Results} presents the result of this paper.
@@
 Consider the network composed of systems described by the following equation.
-\begin{equation}\label{eq:example system:i}
-	\dot{x}_i=??
+\begin{equation}\label{eq:example}
+	\left\{\begin{array}{rcl}
+		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
+		\dot{y}_i&=&u_i,
+	\end{array}\right.
 \end{equation}
-Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example system:i}.
+Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example}.
 
-\subsection{Background}
+\subsection{Background}\label{sec:background}
 
@@
 $\mathbb{R}^m$).
-The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by $A_{jk}(x,u)=\tfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)$
+The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by
+\begin{equation*}
+	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
+\end{equation*}
 for indexes $j,k\in\mathbb{N}_{[1,n]}$.
@@
 
-As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem \cite{Rantzer:2001}.
+As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.
 
-Step 1 (Offline LMI computation).
+Step 1 (Offline MI computation).
 Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$.
 The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf.
-\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following linear matrix inequality (LMI)
-\begin{equation}\label{eq:LMI formulation}
+\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
+\begin{equation}\label{eq:MI formulation}
 	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\preceq0,
 \end{equation}
-for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.
+that is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.
 
@@
 {\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
-Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the LMI \eqref{eq:contracting feedback law}.
+Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:contracting feedback law}.
 
@@
 	\begin{equation*}
-		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i},
+		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i),
 	\end{equation*}
@@
 
-Although the requirement of a control-contraction metric $M$ to have block-diagonal structure may be restrictive, for positive linear time-invariant systems the existence of a matrices $P=P^\top\succ0$ with diagonal structure is not conservative \cite{Tanaka2011}.
-Thus, the question of how restrictive is the requirement of $M$ to be diagonal is open.
-The main result of the paper is stated below.
+In other words, a sum-separable metric is the case in which the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these components depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$.
+The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
 
-\todo[inline]{Compare SS-CCM with SS-LF from \cite{Dirr2015,Rantzer2013}}
-
-To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the LMI \eqref{eq:LMI formulation}.
+To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
 
@@
 		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
-		\text{has the property}&\ \mathscr{K}_Y(i)\}.
+		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
 	\end{align*}
@@
 \begin{theorem}\label{thm:main result}
-	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI \eqref{eq:LMI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 
-Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the LMI \eqref{eq:LMI formulation} is cannot be done in parallel.
-The next result provides sufficient conditions to solve each component \eqref{eq:LMI formulation} independently, and according to the structure defined by the set $\Xi$.
+Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel.
+The next result provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$.
 Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.
@@
 \begin{corollary}\label{cor:distributed computation}
-	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the LMI
-	\begin{equation}\label{eq:LMI formulation:i}
+	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
+	\begin{equation}\label{eq:MI formulation:i}
 		T_{ii}\preceq 0
 	\end{equation}
-	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the LMI \eqref{eq:LMI formulation}.
+	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
 \end{corollary}
@@
 
+\subsection{Discussion}
+
+Although the requirement of a sum-separable structure seems to be restrictive, for some classes of systems this structure is equivalent to the (possibly local) stability of the origin.
+
+For monotone systems (i.e., systems for which the some order of initial conditions is preserved along the flow of the vector field) described by a vector field that is continuously differentiable and whose gradient matrix is Hurwitz at the origin, there exists a sum-separable Lyapunov function in a neighborhood of the origin \cite[Theorem 3.4]{Dirr2015}.
+
+For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.
+
+Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure is open.
+As mentioned before, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
+
 \section{Illustration}\label{sec:Illustration}
 
+A case where structured controller design is important is on distributed design for network systems.
+
 Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
-\begin{equation}\label{eq:example}
+\begin{equation}\tag{\ref{eq:example}}
 	\left\{\begin{array}{rcl}
@@
 	B_i=&\begin{bmatrix}
-	0\\ 1
-	\end{bmatrix}.
+	0, 1
+	\end{bmatrix}^\top.
 \end{align*}
@@
 
-Employing the method provided in Theorem~\ref{thm:main result}, the LMI \eqref{eq:LMI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$.
+Employing the method provided in Theorem~\ref{thm:main result}, the MI \eqref{eq:MI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$.
+The hardware on which the software ran is an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
 
@@
 In the first one, no constraints were imposed on the matrix $Y$.
-The parser took 97 seconds to solve the  LMI \eqref{eq:LMI formulation}.
-The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
+The parser took  seconds to solve the  MI \eqref{eq:MI formulation}.
+The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
 \begin{equation*}
@@
 \begin{equation}\label{eq:example:Y:general}
-		Y=\scalebox{0.75}{$\begin{bmatrix}
+		Y(q)=\scalebox{0.75}{$\begin{bmatrix}
 			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1+0.003x_3y_1,&0.005y_1y_3,&-0.007y_1+0.001x_4y_1,&0\\
@@
 In the second case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
-The time taken by the parser to solve the LMI \eqref{eq:LMI formulation} was 98 seconds.
-The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:LMI formulation} are
+The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
+Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience $q_0=q_1$ and $q_5=q_4$).
+
+The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 98 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
 \begin{equation*}
@@
 and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
+\begin{equation*}
+	Y_{ij}=-3y_i-0.03x_iy_i
+\end{equation*}
+for pair of indexes $(i,j)$ given as $(1,1)$, $(2,3)$, $(3,5)$ and $(4,6)$. Also, 
 \begin{align*}
-	Y_{ij}=&-3y_i-0.03x_iy_i&i,j\in\mathbb{N}_{[1,4]}\\
 	Y_{12}=&-4-0.01x_1-y_1^2-y_2^2-2x_1^2-x_2^2\\	
@@
 \begin{equation}\label{eq:example:Y:neighbor}
-	Y=\scalebox{0.75}{$\begin{bmatrix}
+	Y(q)=\scalebox{0.85}{$\begin{bmatrix}
 	Y_{11},&Y_{12},&-0.01y_2+0.03x_2y_1,&0,&0,&0,&0,&0\\
@@
 In the last case, the fully decentralized scenario has been considered.
-The time taken by the parser to solve the LMI \eqref{eq:LMI formulation} was 101 seconds.
+The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 101 seconds.
 In this case, $\mathscr{K}_Y(i)=\{j\in\mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}$, where $\mathscr{K}(i)=\{i\}$.
-Imposing $Y\in\Xi_Y$ and solving the LMI \eqref{eq:LMI formulation} the following matrices were obtained
+Imposing $Y\in\Xi_Y$ and solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
 \begin{align*}
@@
 
+Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents doubled each time.
+
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
+	\caption{Time take by the parser to solve the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents double each time. Axis are on log scale.}
+	\label{fig:time graph}
+\end{figure}
+
 \section{Proof of the Results}\label{sec:Proof of the Results}
@@
 \begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ is a solution to the LMI \eqref{eq:LMI formulation}.
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ is a solution to the MI \eqref{eq:MI formulation}.
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
@@
 
-	The LMI \eqref{eq:LMI formulation} implies that the inequality
+	The MI \eqref{eq:MI formulation} implies that the inequality
 	\begin{equation*}
@@
 \begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
-	By assumption, the pair of matrices $W$ and $Y$ is a solution to the LMI \eqref{eq:LMI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.
+	By assumption, the pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.
 
@@
 	\end{equation*}
-	Inequalities \eqref{eq:BDD2} and \eqref{eq:LMI formulation:i} imply that the inequalities
+	Inequalities \eqref{eq:BDD2} and \eqref{eq:MI formulation:i} imply that the inequalities
 	\begin{equation*}
@@
 Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$.
-This later inequality is equivalent to the LMI \eqref{eq:LMI formulation}.
+This later inequality is equivalent to the MI \eqref{eq:MI formulation}.
 This concludes the proof of Corollary~\ref{cor:distributed computation}.
@@
 \section{Conclusion}\label{sec:Conclusion}
+
+In this work, input-affine nonlinear systems were considered.
+The considered problem was the design of structured feedback laws.
+The methodology employed for synthesis was based on control-contraction metrics which provides a controller ensuring exponential convergence of pairs of solutions.
+
+In terms of dynamic programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
+This is one of its main advantages in comparison to the search of control-Lyapunov functions, as its dynamic programming formulation leads to a non-convex problem.
+
+The main contribution of this paper is the synthesis of a feedback law with a prescribed structure.
+More precisely, since the matrix describing the metric has a block-diagonal structure, the on-line integration phase can be done in parallel, i.e.,  each block defines a metric to the corresponding component of the state space where the geodesic is computed by optimization.
+
+The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances like time delays.
+
+{\itshape Acknowledgments.} The authors thank the anonymous reviewers.
 

### 2016-07-15 TheoreticalExample1FinalVersion/PostProcessedW.m
> Do: Simulate the Neighbor case for 128 agents
> Done: The neighbor case preserves the structure of the MI matrix. Thus I wrote the MI similarly to the diagonal case. I have also proved the conditions for which the smaller matrices imply that MI matrix is PD.

@@ -17,24 +17,6 @@ W15 = sdisplay(VerifiedW15);
 VerifiedW16 = clean(replace(W(1,6), coefList, double(coefList)), 0.001);
 W16 = sdisplay(VerifiedW16);
 
-VerifiedW17 = clean(replace(W(1,7), coefList, double(coefList)), 0.001);
-W17 = sdisplay(VerifiedW17);
-
-VerifiedW18 = clean(replace(W(1,8), coefList, double(coefList)), 0.001);
-W18 = sdisplay(VerifiedW18);
-
-VerifiedW19 = clean(replace(W(1,9), coefList, double(coefList)), 0.001);
-W19 = sdisplay(VerifiedW19);
-
-VerifiedW110 = clean(replace(W(1,10), coefList, double(coefList)), 0.001);
-W110 = sdisplay(VerifiedW110);
-
-VerifiedW111 = clean(replace(W(1,11), coefList, double(coefList)), 0.001);
-W111 = sdisplay(VerifiedW111);
-
-VerifiedW112 = clean(replace(W(1,12), coefList, double(coefList)), 0.001);
-W112 = sdisplay(VerifiedW112);
-
 VerifiedW21 = clean(replace(W(2,1), coefList, double(coefList)), 0.001);
 W21 = sdisplay(VerifiedW21);
 
@@ -52,24 +34,6 @@ W25 = sdisplay(VerifiedW25);
 
 VerifiedW26 = clean(replace(W(2,6), coefList, double(coefList)), 0.001);
 W26 = sdisplay(VerifiedW26);
-
-VerifiedW27 = clean(replace(W(2,7), coefList, double(coefList)), 0.001);
-W27 = sdisplay(VerifiedW27);
-
-VerifiedW28 = clean(replace(W(2,8), coefList, double(coefList)), 0.001);
-W28 = sdisplay(VerifiedW28);
-
-VerifiedW29 = clean(replace(W(2,9), coefList, double(coefList)), 0.001);
-W29 = sdisplay(VerifiedW29);
-
-VerifiedW210 = clean(replace(W(2,10), coefList, double(coefList)), 0.001);
-W210 = sdisplay(VerifiedW210);
-
-VerifiedW211 = clean(replace(W(2,11), coefList, double(coefList)), 0.001);
-W211 = sdisplay(VerifiedW211);
-
-VerifiedW212 = clean(replace(W(2,12), coefList, double(coefList)), 0.001);
[…]

### 2016-07-15 TheoreticalExample1FinalVersion/PostProcessedY.m

@@ -17,24 +17,6 @@ Y15 = sdisplay(VerifiedY15);
 VerifiedY16 = clean(replace(Y(1,6), coefList, double(coefList)), 0.001);
 Y16 = sdisplay(VerifiedY16);
 
-VerifiedY17 = clean(replace(Y(1,7), coefList, double(coefList)), 0.001);
-Y17 = sdisplay(VerifiedY17);
-
-VerifiedY18 = clean(replace(Y(1,8), coefList, double(coefList)), 0.001);
-Y18 = sdisplay(VerifiedY18);
-
-VerifiedY19 = clean(replace(Y(1,9), coefList, double(coefList)), 0.001);
-Y19 = sdisplay(VerifiedY19);
-
-VerifiedY110 = clean(replace(Y(1,10), coefList, double(coefList)), 0.001);
-Y110 = sdisplay(VerifiedY110);
-
-VerifiedY111 = clean(replace(Y(1,11), coefList, double(coefList)), 0.001);
-Y111 = sdisplay(VerifiedY111);
-
-VerifiedY112 = clean(replace(Y(1,12), coefList, double(coefList)), 0.001);
-Y112 = sdisplay(VerifiedY112);
-
 VerifiedY21 = clean(replace(Y(2,1), coefList, double(coefList)), 0.001);
 Y21 = sdisplay(VerifiedY21);
 
@@ -52,24 +34,6 @@ Y25 = sdisplay(VerifiedY25);
 
 VerifiedY26 = clean(replace(Y(2,6), coefList, double(coefList)), 0.001);
 Y26 = sdisplay(VerifiedY26);
-
-VerifiedY27 = clean(replace(Y(2,7), coefList, double(coefList)), 0.001);
-Y27 = sdisplay(VerifiedY27);
-
-VerifiedY28 = clean(replace(Y(2,8), coefList, double(coefList)), 0.001);
-Y28 = sdisplay(VerifiedY28);
-
-VerifiedY29 = clean(replace(Y(2,9), coefList, double(coefList)), 0.001);
-Y29 = sdisplay(VerifiedY29);
-
-VerifiedY210 = clean(replace(Y(2,10), coefList, double(coefList)), 0.001);
-Y210 = sdisplay(VerifiedY210);
-
-VerifiedY211 = clean(replace(Y(2,11), coefList, double(coefList)), 0.001);
-Y211 = sdisplay(VerifiedY211);
-
[…]

### 2016-07-15 TheoreticalExample1FinalVersion/PreProcessedSys.m

@@ -1,41 +1,34 @@
 x1 = sdpvar(1);
 x2 = sdpvar(1);
 x3 = sdpvar(1);
-x4 = sdpvar(1);
 
 y1 = sdpvar(1);
 y2 = sdpvar(1);
 y3 = sdpvar(1);
-y4 = sdpvar(1);
 
 u1 = sdpvar(1);
 u2 = sdpvar(1);
 u3 = sdpvar(1);
-u4 = sdpvar(1);
-u = [u1; u2; u3; u4]; 
+u = [u1; u2; u3]; 
 
 q1 = [x1;y1];
 q2 = [x2;y2];
 q3 = [x3;y3];
-q4 = [x4;y4];
 
-q = [q1; q2; q3; q4];
+q = [q1; q2; q3];
  
-x1dot = -x1 - x1^3 + y1^2 -0.010000*(+1*x1^3 -1*x2^3 +0*x3^3 +0*x4^3);
-x2dot = -x2 - x2^3 + y2^2 -0.010000*(-1*x1^3 +2*x2^3 -1*x3^3 +0*x4^3);
-x3dot = -x3 - x3^3 + y3^2 -0.010000*(+0*x1^3 -1*x2^3 +2*x3^3 -1*x4^3);
-x4dot = -x4 - x4^3 + y4^2 -0.010000*(+0*x1^3 +0*x2^3 -1*x3^3 +1*x4^3);
+x1dot = -x1 - x1^3 + y1^2 -0.010000*(+1*x1^3 -1*x2^3 +0*x3^3);
+x2dot = -x2 - x2^3 + y2^2 -0.010000*(-1*x1^3 +2*x2^3 -1*x3^3);
+x3dot = -x3 - x3^3 + y3^2 -0.010000*(+0*x1^3 -1*x2^3 +1*x3^3);
 
 y1dot = u1;
 y2dot = u2;
 y3dot = u3;
-y4dot = u4;
 
 f1 = [x1dot;y1dot];
 f2 = [x2dot;y2dot];
 f3 = [x3dot;y3dot];
-f4 = [x4dot;y4dot];
-f = [f1; f2; f3; f4]; 
+f = [f1; f2; f3]; 
 
 A11 = jacobian(f1,q1);
 A12 = jacobian(f1,q2);
@@ -48,10 +41,5 @@ B2  = jacobian(f2,u2);
 
 A32 = jacobian(f3,q2);
 A33 = jacobian(f3,q3);
[…]

### 2016-07-15 TheoreticalExample1FinalVersion/PreProcessedW.m

@@ -52,25 +52,7 @@ DW3 = [DWTemp(1,:)/2*f3, DWTemp(2,:)*f3;
 DW3 = DW3 + transpose(DW3);
 
 
-% Creation of W4 and DW4
-[Wp411,Wc411,Wv411] = polynomial(q4,2.000000,0);
-[Wp412,Wc412,Wv412] = polynomial(q4,2.000000,0);
-[Wp422,Wc422,Wv422] = polynomial(q4,2.000000,0);
-% Creation of W4
-W4 = [Wp411, Wp412;
-      Wp412, Wp422];
-
-Wc4 = [Wc411;Wc412;Wc422];
-Wp4 = [Wp411;Wp412;Wp422];
-
-% Creation of DW4
-DWTemp = jacobian(Wp4,q4);
-DW4 = [DWTemp(1,:)/2*f4, DWTemp(2,:)*f4;
-       0,                DWTemp(3,:)/2*f4];
-DW4 = DW4 + transpose(DW4);
-
-
-W = blkdiag(W1,W2,W3,W4);
-WConstraints = [sos(W1-eye(2)*1.000000);sos(W2-eye(2)*1.000000);sos(W3-eye(2)*1.000000);sos(W4-eye(2)*1.000000)];
-DW = blkdiag(DW1,DW2,DW3,DW4);
-Wc = [Wc1;Wc2;Wc3;Wc4];
+W = blkdiag(W1,W2,W3);
+WConstraints = [sos(W1-eye(2)*1.000000);sos(W2-eye(2)*1.000000);sos(W3-eye(2)*1.000000)];
+DW = blkdiag(DW1,DW2,DW3);
+Wc = [Wc1;Wc2;Wc3];

### 2016-07-15 TheoreticalExample1FinalVersion/PreProcessedY.m

@@ -1,32 +1,38 @@
 
  % Creation of Variable Y1
 
-[Y11,Yc11,Yv11] = polynomial(q1,Ydegree,0);
-[Y12,Yc12,Yv12] = polynomial(q1,Ydegree,0);
+[Y11,Yc11,Yv11] = polynomial(q,Ydegree,0);
+[Y12,Yc12,Yv12] = polynomial(q,Ydegree,0);
+[Y13,Yc13,Yv13] = polynomial(q,Ydegree,0);
+[Y14,Yc14,Yv14] = polynomial(q,Ydegree,0);
+[Y15,Yc15,Yv15] = polynomial(q,Ydegree,0);
+[Y16,Yc16,Yv16] = polynomial(q,Ydegree,0);
 
  % Creation of Variable Y2
 
-[Y23,Yc23,Yv23] = polynomial(q2,Ydegree,0);
-[Y24,Yc24,Yv24] = polynomial(q2,Ydegree,0);
+[Y21,Yc21,Yv21] = polynomial(q,Ydegree,0);
+[Y22,Yc22,Yv22] = polynomial(q,Ydegree,0);
+[Y23,Yc23,Yv23] = polynomial(q,Ydegree,0);
+[Y24,Yc24,Yv24] = polynomial(q,Ydegree,0);
+[Y25,Yc25,Yv25] = polynomial(q,Ydegree,0);
+[Y26,Yc26,Yv26] = polynomial(q,Ydegree,0);
 
  % Creation of Variable Y3
 
-[Y35,Yc35,Yv35] = polynomial(q3,Ydegree,0);
-[Y36,Yc36,Yv36] = polynomial(q3,Ydegree,0);
-
- % Creation of Variable Y4
-
-[Y47,Yc47,Yv47] = polynomial(q4,Ydegree,0);
-[Y48,Yc48,Yv48] = polynomial(q4,Ydegree,0);
+[Y31,Yc31,Yv31] = polynomial(q,Ydegree,0);
+[Y32,Yc32,Yv32] = polynomial(q,Ydegree,0);
+[Y33,Yc33,Yv33] = polynomial(q,Ydegree,0);
+[Y34,Yc34,Yv34] = polynomial(q,Ydegree,0);
+[Y35,Yc35,Yv35] = polynomial(q,Ydegree,0);
+[Y36,Yc36,Yv36] = polynomial(q,Ydegree,0);
 
[…]

### 2016-07-15 TheoreticalExample1FinalVersion/TheoreticalExample1c.m

@@ -28,7 +28,7 @@ d = 1e-2;
 % d = 0
 
 % Possible choices are: General, Decentralized and Neighbor
-Option  = 'Decentralized';
+Option  = 'General';
 
 if strcmp(Option,'General') + strcmp(Option,'Decentralized') ...
         + strcmp(Option,'Neighbor') == 0
@@ -38,7 +38,7 @@ if strcmp(Option,'General') + strcmp(Option,'Decentralized') ...
     
 end
 
-NAgents = 4;
+NAgents = 3;
 u = zeros(NAgents,1);
 
 L = LinearLaplacianGenerator(NAgents);

### 2016-07-15 TheoreticalExample1Version2/AnalysisW.m

@@ -1,0 +1,45 @@
+function AnalysisW(SystemStates,LaplacianMatrix,Precision)
+
+fid = fopen('PostProcessedW.m','w');
+
+NumberOfAgents = size(LaplacianMatrix,1);
+NumberOfStates = length(SystemStates);
+
+for RowCounter = 1:NumberOfStates*NumberOfAgents
+    for ColumnCounter = 1:NumberOfStates*NumberOfAgents
+        fprintf(fid, 'VerifiedW%s%s = ', num2str(RowCounter),num2str(ColumnCounter));
+        fprintf(fid, 'clean(replace(W(%s,%s), coefList, double(coefList)), %s);\n', num2str(RowCounter),num2str(ColumnCounter),num2str(Precision));
+        fprintf(fid, 'W%s%s = ', num2str(RowCounter),num2str(ColumnCounter));
+        fprintf(fid, 'sdisplay(VerifiedW%s%s);\n\n', num2str(RowCounter),num2str(ColumnCounter));
+        fprintf(fid, 'clear VerifiedW%s%s;\n', num2str(RowCounter),num2str(ColumnCounter));
+    end
+end
+
+fprintf(fid, 'W = [');
+
+for RowCounter = 1:NumberOfStates*NumberOfAgents
+    
+    for ColumnCounter = 1:NumberOfStates*NumberOfAgents
+        
+             if ColumnCounter == NumberOfStates*NumberOfAgents && RowCounter == NumberOfStates*NumberOfAgents
+                 
+                 fprintf(fid, 'W%s%s];\n', num2str(RowCounter),num2str(ColumnCounter));
+                 
+             elseif ColumnCounter == NumberOfStates*NumberOfAgents
+            
+                 fprintf(fid, 'W%s%s;\n', num2str(RowCounter),num2str(ColumnCounter));
+                 fprintf(fid, '     ');
+                 
+             else
+                 
+                 fprintf(fid, 'W%s%s, ', num2str(RowCounter),num2str(ColumnCounter));
+                 
+             end
+            
+        
+    end
+end
+
+fclose(fid);
+
+end

### 2016-07-15 TheoreticalExample1Version2/LMIOptmisation.m

@@ -1,0 +1,78 @@
+function test
+clear all
+close all
+clc
+warning off
+
+global Simulation SystemStates SystemInputs 
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2;
+lambda = 1;
+Option       = 'Neighbor';
+NumberOfAgents = 64
+
+fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
+diary(fname)
+diary on
+
+if NumberOfAgents > 4 && strcmp(Option,'Diagonal') + strcmp(Option,'Neighbor') == 0
+    
+    disp('This option requires lots of RAM memory for more than 4 agents.')
+    disp('Chose Option = Diagonal and run it with more than 4 agents or')
+    disp('Chose another option and run with less than 4 agents')
+    return
+    
+end
+
+LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
+LMIOptimisation1(LaplacianMatrix,Option,lambda)
+
+diary off
+
+end
+
+function LMIOptimisation1(LaplacianMatrix,Option,lambda)
+
+%     function LMIOptmisation(LaplacianMatrix,Option,lambda)
+
+global Simulation SystemStates SystemInputs SystemParameters
+
+WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+PreProcessedSys
+
+Wdegree = 2;
+ScalingFactor = 1;
+WriterW(SystemStates,LaplacianMatrix,Wdegree,ScalingFactor)
+PreProcessedW
+
+Ydegree = 2;
+WriterY(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+PreProcessedY
+
+WriterMI(SystemStates,LaplacianMatrix,ScalingFactor,lambda,Option)
+PreProcessedMI
+
+Constraints = [WConstraints;MIConstraints];
+checkset(Constraints)
+coefList = [Wc;Yc];
+options = sdpsettings('solver','mosek','verbose',1);
+tic
+[sol, q, Q, res] = solvesos(Constraints,[],options,coefList);
+SolverTime = toc;
+
+Precision = 1e-3;
+AnalysisW(SystemStates,LaplacianMatrix,Precision)
+PostProcessedW
+
[…]

### 2016-07-15 TheoreticalExample1Version2/LinearLaplacianGenerator.m

@@ -1,0 +1,38 @@
+function L=LinearLaplacianGenerator(NAgents)
+
+L = zeros(NAgents,NAgents);
+
+for RowCounter = 1:NAgents
+    
+    for ColumnCounter = 1:NAgents
+        
+        if ColumnCounter >= RowCounter
+            
+            if ColumnCounter == RowCounter
+                
+                if RowCounter == 1 || RowCounter == NAgents
+                    
+                    L(RowCounter,ColumnCounter) = 1/2;
+                    
+                else
+                    
+                    L(RowCounter,ColumnCounter) = 1;
+                    
+                end
+                
+            elseif ColumnCounter == RowCounter - 1 || ColumnCounter == RowCounter + 1
+                
+                L(RowCounter,ColumnCounter) = -1;
+                
+            end
+            
+        end
+        
+    end
+    
+end
+
+L = L + transpose(L);
+
+
+end

### 2016-07-15 TheoreticalExample1Version2/PreProcessedMI.m

@@ -1,0 +1,192 @@
+MI = -DW + A*W + transpose(A*W) + B*Y + transpose(B*Y) + 2*1.000000*W;
+
+Block1 = MI(1:4,1:4);
+Block1(2,2) = Block1(2,2)/2;
+
+Block2 = MI(3:6,3:6);
+Block2(2,2) = Block2(2,2)/2;
+
+Block3 = MI(5:8,5:8);
+Block3(2,2) = Block3(2,2)/2;
+
+Block4 = MI(7:10,7:10);
+Block4(2,2) = Block4(2,2)/2;
+
+Block5 = MI(9:12,9:12);
+Block5(2,2) = Block5(2,2)/2;
+
+Block6 = MI(11:14,11:14);
+Block6(2,2) = Block6(2,2)/2;
+
+Block7 = MI(13:16,13:16);
+Block7(2,2) = Block7(2,2)/2;
+
+Block8 = MI(15:18,15:18);
+Block8(2,2) = Block8(2,2)/2;
+
+Block9 = MI(17:20,17:20);
+Block9(2,2) = Block9(2,2)/2;
+
+Block10 = MI(19:22,19:22);
+Block10(2,2) = Block10(2,2)/2;
+
+Block11 = MI(21:24,21:24);
+Block11(2,2) = Block11(2,2)/2;
+
+Block12 = MI(23:26,23:26);
+Block12(2,2) = Block12(2,2)/2;
+
+Block13 = MI(25:28,25:28);
+Block13(2,2) = Block13(2,2)/2;
+
+Block14 = MI(27:30,27:30);
+Block14(2,2) = Block14(2,2)/2;
+
+Block15 = MI(29:32,29:32);
+Block15(2,2) = Block15(2,2)/2;
+
+Block16 = MI(31:34,31:34);
+Block16(2,2) = Block16(2,2)/2;
+
+Block17 = MI(33:36,33:36);
+Block17(2,2) = Block17(2,2)/2;
+
+Block18 = MI(35:38,35:38);
+Block18(2,2) = Block18(2,2)/2;
+
+Block19 = MI(37:40,37:40);
+Block19(2,2) = Block19(2,2)/2;
+
+Block20 = MI(39:42,39:42);
+Block20(2,2) = Block20(2,2)/2;
+
+Block21 = MI(41:44,41:44);
+Block21(2,2) = Block21(2,2)/2;
+
+Block22 = MI(43:46,43:46);
[…]

### 2016-07-15 TheoreticalExample1Version2/PreProcessedSys.m

@@ -1,0 +1,924 @@
+% System Parameters: d
+
+global d 
+
+% Writing System States: xy
+
+x1 = sdpvar(1);
+x2 = sdpvar(1);
+x3 = sdpvar(1);
+x4 = sdpvar(1);
+x5 = sdpvar(1);
+x6 = sdpvar(1);
+x7 = sdpvar(1);
+x8 = sdpvar(1);
+x9 = sdpvar(1);
+x10 = sdpvar(1);
+x11 = sdpvar(1);
+x12 = sdpvar(1);
+x13 = sdpvar(1);
+x14 = sdpvar(1);
+x15 = sdpvar(1);
+x16 = sdpvar(1);
+x17 = sdpvar(1);
+x18 = sdpvar(1);
+x19 = sdpvar(1);
+x20 = sdpvar(1);
+x21 = sdpvar(1);
+x22 = sdpvar(1);
+x23 = sdpvar(1);
+x24 = sdpvar(1);
+x25 = sdpvar(1);
+x26 = sdpvar(1);
+x27 = sdpvar(1);
+x28 = sdpvar(1);
+x29 = sdpvar(1);
+x30 = sdpvar(1);
+x31 = sdpvar(1);
+x32 = sdpvar(1);
+x33 = sdpvar(1);
+x34 = sdpvar(1);
+x35 = sdpvar(1);
+x36 = sdpvar(1);
+x37 = sdpvar(1);
+x38 = sdpvar(1);
+x39 = sdpvar(1);
+x40 = sdpvar(1);
+x41 = sdpvar(1);
+x42 = sdpvar(1);
+x43 = sdpvar(1);
+x44 = sdpvar(1);
+x45 = sdpvar(1);
+x46 = sdpvar(1);
+x47 = sdpvar(1);
+x48 = sdpvar(1);
+x49 = sdpvar(1);
+x50 = sdpvar(1);
+x51 = sdpvar(1);
+x52 = sdpvar(1);
+x53 = sdpvar(1);
+x54 = sdpvar(1);
+x55 = sdpvar(1);
+x56 = sdpvar(1);
+x57 = sdpvar(1);
+x58 = sdpvar(1);
+x59 = sdpvar(1);
+x60 = sdpvar(1);
+x61 = sdpvar(1);
+x62 = sdpvar(1);
+x63 = sdpvar(1);
+x64 = sdpvar(1);
+
+y1 = sdpvar(1);
[…]

### 2016-07-15 TheoreticalExample1Version2/PreProcessedW.m

@@ -1,0 +1,1156 @@
+% Creation of W1 and DW1
+[Wp111,Wc111,Wv111] = polynomial(q1,2,0);
+[Wp112,Wc112,Wv112] = polynomial(q1,2,0);
+[Wp122,Wc122,Wv122] = polynomial(q1,2,0);
+% Creation of W1
+W1 = [Wp111, Wp112;
+      Wp112, Wp122];
+
+Wc1 = [Wc111;Wc112;Wc122];
+Wp1 = [Wp111;Wp112;Wp122];
+
+% Creation of DW1
+DWTemp = jacobian(Wp1,q1);
+DW1 = [DWTemp(1,:)*f1/2, DWTemp(2,:)*f1;
+       0,                DWTemp(3,:)*f1/2];
+DW1 = DW1 + transpose(DW1);
+
+
+% Creation of W2 and DW2
+[Wp211,Wc211,Wv211] = polynomial(q2,2,0);
+[Wp212,Wc212,Wv212] = polynomial(q2,2,0);
+[Wp222,Wc222,Wv222] = polynomial(q2,2,0);
+% Creation of W2
+W2 = [Wp211, Wp212;
+      Wp212, Wp222];
+
+Wc2 = [Wc211;Wc212;Wc222];
+Wp2 = [Wp211;Wp212;Wp222];
+
+% Creation of DW2
+DWTemp = jacobian(Wp2,q2);
+DW2 = [DWTemp(1,:)*f2/2, DWTemp(2,:)*f2;
+       0,                DWTemp(3,:)*f2/2];
+DW2 = DW2 + transpose(DW2);
+
+
+% Creation of W3 and DW3
+[Wp311,Wc311,Wv311] = polynomial(q3,2,0);
+[Wp312,Wc312,Wv312] = polynomial(q3,2,0);
+[Wp322,Wc322,Wv322] = polynomial(q3,2,0);
+% Creation of W3
+W3 = [Wp311, Wp312;
+      Wp312, Wp322];
+
+Wc3 = [Wc311;Wc312;Wc322];
+Wp3 = [Wp311;Wp312;Wp322];
+
+% Creation of DW3
+DWTemp = jacobian(Wp3,q3);
+DW3 = [DWTemp(1,:)*f3/2, DWTemp(2,:)*f3;
+       0,                DWTemp(3,:)*f3/2];
+DW3 = DW3 + transpose(DW3);
+
+
+% Creation of W4 and DW4
[…]

### 2016-07-15 TheoreticalExample1Version2/TimerPlot.m

@@ -1,0 +1,39 @@
+function TimerPlot
+
+close all
+clear all
+clc;
+
+set(groot, 'defaultAxesTickLabelInterpreter','latex');
+set(groot, 'defaultLegendInterpreter','latex');
+
+Option = 'Diagonal'
+
+if strcmp(Option,'Diagonal')
+    
+    Time(1) = 1.224428609719290;
+    Time(2) = 1.561498248693083;
+    Time(3) = 2.754560839016742;
+    Time(4) = 5.57600135162288;
+    Time(5) = 10.910490511994272;
+    Time(6) = 22.1421868579150;
+    Time(7) = 47.584998880884680;
+    Time(8) = 1.074516828633032e+02;
+    Time(9) = 2.677553198628477e+02;
+    Time(10) = 8.784112856174025e+02;
+    
+    NumberOfAgents = 0:1:9;
+    
+end
+
+figure
+scatter(2.^(NumberOfAgents),Time,'filled');
+set(gca,'yscale','log','FontSize', 14,'FontWeight','bold')
+set(gca,'xscale','log','FontSize', 14,'FontWeight','bold')
+grid on
+% axis tight
+xlabel('Number of Agents','interpreter','latex','fontsize',14);
+ylabel('Time [s]','interpreter','latex','fontsize',14);
+title('Time Taken by the Parser to solve the Matrix Inequality','interpreter','latex','fontsize',14);
+
+end

### 2016-07-15 TheoreticalExample1Version2/WriterMI.m

@@ -1,0 +1,63 @@
+% function test
+% 
+% SystemStates = ['x','y'];
+% ScalingFactor = 1e-2;
+% LaplacianMatrix = LinearLaplacianGenerator(5)
+% WriterMI1(SystemStates,LaplacianMatrix,ScalingFactor)
+% 
+% end
+% 
+% function WriterMI1(SystemStates,LaplacianMatrix,ScalingFactor)
+
+function WriterMI(SystemStates,LaplacianMatrix,ScalingFactor,lambda,Option)
+
+fid = fopen('PreProcessedMI.m','w');
+
+NumberOfAgents = size(LaplacianMatrix,1);
+NumberOfStates = length(SystemStates);
+
+% for AgentsCounter = 1:NumberOfAgents
+%     
+%     for NeighborCounter = 1:NumberOfAgents
+%             
+%             if LaplacianMatrix(AgentsCounter,NeighborCounter) ~= 0
+%                 
+%                 fprintf(fid, 'Component%s%s = A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentsCounter),num2str(NeighborCounter),num2str(AgentsCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentsCounter),num2str(AgentsCounter));
+%                 fprintf(fid, 'B%s*Y%s%s + transpose(B%s*Y%s%s);\n',num2str(AgentsCounter),num2str(AgentsCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentsCounter));
+%                 
+%             else
+%                 
+%                 fprintf(fid, 'Component%s%s = %d;\n',num2str(AgentsCounter),num2str(NeighborCounter),0);
+%                 
+%             end
+%         
+%     end
+%     fprintf(fid, '\n');
+% end
+
+fprintf(fid, 'MI = -DW + A*W + transpose(A*W) + B*Y + transpose(B*Y) + 2*%f*W;\n\n',lambda);
+
+if strcmp(Option,'Diagonal') || strcmp(Option,'Neighbor')
+    
+    for AgentsCounter = 1:NumberOfAgents - 1
+        fprintf(fid, 'Block%s = ',num2str(AgentsCounter));
[…]

### 2016-07-15 TheoreticalExample1Version2/WriterY.m

@@ -1,0 +1,300 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Title: Pre Processing Y                                                 %
+% Description: Creates the matrix Y for the LMI optmization               %
+% Inputs: nr. Integer, Scalar, Number of Rows                            %
+%         nc. Integer, Scalar, Number of Columns   %
+% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
+% Author: Humberto Stein Shiromoto                                        %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 
+% function test
+% 
+% SystemStates = ['w','x','y','z'];
+% SystemInputs = ['u','v'];
+% LaplacianMatrix = RandomLaplacianGenerator(3)
+% Option = 'Neighbor';
+% Ydegree = 2;
+% WriterY1(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+% 
+% 
+% end
+% 
+% function WriterY1(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+
+function WriterY(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+
+fid = fopen('PreProcessedY.m','w');
+
+NumberOfAgents = size(LaplacianMatrix,1);
+NumberOfInputs = length(SystemInputs);
+NumberOfStates = length(SystemStates);
+
+fprintf(fid, '%% NumberOfAgents = %d,\n%% NumberOfInputs = %d,\n%% NumberOfStates = %d,\n',NumberOfAgents,NumberOfInputs,NumberOfStates);
+
+if strcmp(Option,'Diagonal')
+    
+    fprintf(fid, '\n%% Option = %s\n',Option);
+    
+    for AgentsCounter = 1:NumberOfAgents
+        fprintf(fid, '\n\n%% Starting Agent %d\n',AgentsCounter);
+        for RowCounter = 1:NumberOfInputs
+            fprintf(fid, '\n%% Writing Line %d\n',RowCounter);
+            for ColumnCounter = 1:NumberOfStates
+                
+                fprintf(fid, '[');
[…]

### 2016-07-15 TheoreticalExample1e/PostProcessedWandDW.m

@@ -1,6 +1,0 @@
-VerifiedW1 = clean(replace(W1, coefList, double(coefList)), 1e-06);
-W1 = sdisplay(VerifiedW1);
-
-VerifiedW2 = clean(replace(W2, coefList, double(coefList)), 1e-06);
-W2 = sdisplay(VerifiedW2);
-

### 2016-07-15 TheoreticalExample1e/PostProcessedY.m

@@ -1,6 +1,0 @@
-VerifiedY1 = clean(replace(Y1, coefList, double(coefList)), 1e-06);
-Y1 = sdisplay(VerifiedY1);
-
-VerifiedY2 = clean(replace(Y2, coefList, double(coefList)), 1e-06);
-Y2 = sdisplay(VerifiedY2);
-

### 2016-07-15 TheoreticalExample1e/PostProcessingY.m

@@ -1,15 +1,0 @@
-function PostProcessingY(NumberOfAgents,prec)
-
-fid = fopen('PostProcessedY.m','w');
-
-for nr = 1:NumberOfAgents
-        
-        fprintf(fid, 'VerifiedY%s = ', num2str(nr));
-        fprintf(fid, 'clean(replace(Y%s, coefList, double(coefList)), %s);\n', num2str(nr),num2str(prec));
-        fprintf(fid, 'Y%s = ', num2str(nr));
-        fprintf(fid, 'sdisplay(VerifiedY%s);\n\n', num2str(nr));
-        
-end
-    
-fclose(fid);
-end

### 2016-07-15 TheoreticalExample1e/PreProcessedLfW.m

@@ -1,4 +1,0 @@
-LfW1 = -DW1 + A11*W1 + transpose(A11*W1) + A12*W2 + transpose(A21*W1) + B1*Y1 + transpose(B1*Y1) + 2*1.000000*W1;
-LfW2 = -DW2 + A21*W1 + transpose(A12*W2) + A22*W2 + transpose(A22*W2) + B2*Y2 + transpose(B2*Y2) + 2*1.000000*W2;
-
-Constraints = [ sos(W1-eye(2)*0.010000); sos(-LfW1+eye(2)*0.010000); sos(W2-eye(2)*0.010000); sos(-LfW2+eye(2)*0.010000)]; 

### 2016-07-15 TheoreticalExample1e/PreProcessedSys.m

@@ -1,33 +1,0 @@
-x1 = sdpvar(1);
-x2 = sdpvar(1);
-
-y1 = sdpvar(1);
-y2 = sdpvar(1);
-
-u1 = sdpvar(1);
-u2 = sdpvar(1);
-u = [u1; u2]; 
-
-q1 = [x1;y1];
-q2 = [x2;y2];
-
-q = [q1; q2];
- 
-x1dot = -x1 - x1^3 + y1^2 -0.000100*(+1*x1^3 -1*x2^3);
-x2dot = -x2 - x2^3 + y2^2 -0.000100*(-1*x1^3 +1*x2^3);
-
-y1dot = u1;
-y2dot = u2;
-
-f1 = [x1dot;y1dot];
-f2 = [x2dot;y2dot];
-f = [f1; f2]; 
-
-A11 = jacobian(f1,q1);
-A12 = jacobian(f1,q2);
-B1  = jacobian(f1,u1);
-
-A21 = jacobian(f2,q1);
-A22 = jacobian(f2,q2);
-B2  = jacobian(f2,u2);
-

### 2016-07-15 TheoreticalExample1e/PreProcessedWandDW.m

@@ -1,41 +1,0 @@
-% Creation of W1 and DW1
-[Wp111,Wc111,Wv111] = polynomial(q,2.000000,0);
-[Wp112,Wc112,Wv112] = polynomial(q,2.000000,0);
-[Wp122,Wc122,Wv122] = polynomial(q,2.000000,0);
-% Creation of W1
-W1 = [Wp111, Wp112;
-      Wp112, Wp122];
-
-Wc1 = [Wc111;Wc112;Wc122];
-Wp1 = [Wp111;Wp112;Wp122];
-
-% Creation of DW1
-DWTemp = jacobian(Wp1,q);
-v = f;
-
-DW1 = [DWTemp(1,:)/2*v, DWTemp(2,:)*v;
-       0,                DWTemp(3,:)/2*v];
-DW1 = DW1 + transpose(DW1);
-
-
-% Creation of W2 and DW2
-[Wp211,Wc211,Wv211] = polynomial(q,2.000000,0);
-[Wp212,Wc212,Wv212] = polynomial(q,2.000000,0);
-[Wp222,Wc222,Wv222] = polynomial(q,2.000000,0);
-% Creation of W2
-W2 = [Wp211, Wp212;
-      Wp212, Wp222];
-
-Wc2 = [Wc211;Wc212;Wc222];
-Wp2 = [Wp211;Wp212;Wp222];
-
-% Creation of DW2
-DWTemp = jacobian(Wp2,q);
-v = f;
-
-DW2 = [DWTemp(1,:)/2*v, DWTemp(2,:)*v;
-       0,                DWTemp(3,:)/2*v];
-DW2 = DW2 + transpose(DW2);
-
-
-Wc = [Wc1;Wc2];

### 2016-07-15 TheoreticalExample1e/PreProcessedY.m

@@ -1,12 +1,0 @@
-
-[Yp11,Yc11,Yv11] = polynomial(q,2.000000,0);
-[Yp12,Yc12,Yv12] = polynomial(q,2.000000,0);
-
-[Yp21,Yc21,Yv21] = polynomial(q,2.000000,0);
-[Yp22,Yc22,Yv22] = polynomial(q,2.000000,0);
-
-
-Y1 = [Yp11, Yp12];
-Y2 = [Yp21, Yp22];
-
-Yc = [Yc11; Yc12; Yc21; Yc22];

### 2016-07-15 TheoreticalExample1e/PreProcessingLfW.m

@@ -1,59 +1,0 @@
-function PreProcessingLfW(NumberOfAgents,lambda,ScalingFactor)
-
-fid = fopen('PreProcessedLfW.m','w');
-
-for AgentCounter = 1:NumberOfAgents
-    
-    fprintf(fid, 'LfW%s = -DW%s + ', num2str(AgentCounter),num2str(AgentCounter));
-    
-    if AgentCounter == 1
-        
-        for NeighborCounter = 1:min(2,NumberOfAgents)
-        
-        fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    elseif AgentCounter == NumberOfAgents
-        
-        for NeighborCounter = AgentCounter-1:NumberOfAgents
-        
-            fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    else
-        
-        for NeighborCounter = AgentCounter-1:AgentCounter+1
-        
-            fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    end
-    
-    fprintf(fid, 'B%s*Y%s + transpose(B%s*Y%s) + 2*%f*W%s;\n', num2str(AgentCounter),num2str(AgentCounter),num2str(AgentCounter),num2str(AgentCounter),lambda,num2str(AgentCounter));
-    
-end
-
-fprintf(fid,'\n');
-
-fprintf(fid,'Constraints = [ ');
-
-for AgentCounter = 1:NumberOfAgents
-    
-    if AgentCounter < NumberOfAgents
-        
-        fprintf(fid,'sos(W%s-eye(2)*%f); sos(-LfW%s+eye(2)*%f); ',num2str(AgentCounter),ScalingFactor,num2str(AgentCounter),ScalingFactor);
-        
-    else
-        
[…]

### 2016-07-15 TheoreticalExample1e/PreProcessingY.m

@@ -1,107 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing Y                                                 %
-% Description: Creates the matrix Y for the LMI optmization               %
-% Inputs: nr. Integer, Scalar, Number of Rows                            %
-%         nc. Integer, Scalar, Number of Columns   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Note: Works only for Linear Graphs!
-
-function PreProcessingY(NumberOfAgents,NumberOfLinesBi,Ydegree,Option)
-
-fid = fopen('PreProcessedY.m','w');
-
-for AgentCounter = 1:NumberOfAgents
-    
-    fprintf(fid, '\n');
-    
-    for ComponentCounter = 1:NumberOfLinesBi
-            
-            fprintf(fid, '[Yp%s%s,Yc%s%s,Yv%s%s] = polynomial', num2str(AgentCounter),num2str(ComponentCounter), num2str(AgentCounter),num2str(ComponentCounter), num2str(AgentCounter),num2str(ComponentCounter));
-            
-            if strcmp(Option,'General')
-                
-                fprintf(fid, '(q,%f,0);\n', Ydegree);
-                
-            elseif strcmp(Option,'Decentralized')
-                
-                fprintf(fid, '(q%s,%f,0);\n', num2str(AgentCounter),Ydegree);
-                
-            else 
-                
-                if AgentCounter == 1
-                    
-                    fprintf(fid, '([q%s;q%s],%f,0);\n', num2str(AgentCounter),num2str(AgentCounter+1),Ydegree);
-                    
-                elseif AgentCounter == NumberOfAgents
-                    
-                    fprintf(fid, '([q%s;q%s],%f,0);\n', num2str(AgentCounter-1),num2str(AgentCounter),Ydegree);
-                    
-                else
-                    
[…]

### 2016-07-15 TheoreticalExample1e/TheoreticalExample1e.m

@@ -1,210 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Simulation of system (19) from [AS14].                           %
-% Author: H. Stein Shiromoto                                              %
-% Notes: DIfference: Nonlinear diffusion works with d<=1e-2               %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function main
-
-clear all
-close all
-clc
-yalmip('clear')
-warning off
-
-% System Parameters
-
-global u d NAgents nr nc Option Simulation L
-
-Simulation = 0;
-
-% Possible choices are: General, Decentralized and Neighbor
-Option  = 'General';
-
-if strcmp(Option,'General') + strcmp(Option,'Decentralized') + strcmp(Option,'Neighbor') == 0
-    
-    disp('Chose an option: General, Decentralized or Neighbor');
-    return
-    
-end
-
-NAgents = 2^1
-d = 1e-4; % Max value for feasibility of the LMI optimization
-
-
-if Simulation == 0
-    
-    L = LinearLaplacianGenerator(NAgents);
-    LMIOptimization;
-    
-else
-    
-    xIC = rand(NAgents,1)*100;
-    yIC = rand(NAgents,1)*100;
-    u = zeros(NAgents,1);
-    
-    IC = [xIC;yIC];
-    
-    time = 0:1e-1:5e1;
-    [time,simout] = ode45(@sys,time,IC);
-    
-    fname = sprintf('Simulation%dAgents%s',NAgents,Option);
-    save(fname,'time','simout')
-    
-    load(fname)
-    PlotSimulation(time,simout)
-    
-end
-
-end
-
-function []=PlotSimulation(time,simout)
-
-% Set axis of graphs to LaTeX
-set(groot, 'defaultAxesTickLabelInterpreter','latex');
-set(groot, 'defaultLegendInterpreter','latex');
-
-% Time Evolution of the Solution components
-figure
-subplot(2,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
-hold on
[…]

### 2016-07-19 TheoreticalExample1Version2/LMIOptmisation.m
> Done: Generate more cases. Started to save the outputs with diary command. It is finished.

@@ -13,26 +13,39 @@ SystemInputs = ['u'];
 SystemParameters = ['d'];
 d = 1e-2;
 lambda = 1;
-Option       = 'Neighbor';
-NumberOfAgents = 64
+Option       = 'General';
+
+NumberOfAgents = 5
 
 fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
 diary(fname)
 diary on
 
-if NumberOfAgents > 4 && strcmp(Option,'Diagonal') + strcmp(Option,'Neighbor') == 0
+if NumberOfAgents > 5 && strcmp(Option,'Diagonal') + strcmp(Option,'Neighbor') == 0
     
-    disp('This option requires lots of RAM memory for more than 4 agents.')
-    disp('Chose Option = Diagonal and run it with more than 4 agents or')
-    disp('Chose another option and run with less than 4 agents')
+    disp('This option requires lots of RAM memory for more than 5 agents.')
+    disp('Chose Option = Diagonal or Neighbor to run with more than 5 agents or')
     return
     
+end
+
+if NumberOfAgents > 256 && strcmp(Option,'Neighbor')
+    disp('This option requires lots of RAM memory for more than 256 agents.')
+    disp('Chose Option = Diagonal and run it with more than 256 agents or')
+    return
+end
+
+if NumberOfAgents > 512 && strcmp(Option,'Diagonal')
+    disp('This option requires lots of RAM memory for more than 512 agents.')
+    return
 end
 
 LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
 LMIOptimisation1(LaplacianMatrix,Option,lambda)
 
 diary off
+
+pause(60)
 
 end
 

### 2016-07-19 TheoreticalExample1Version2/PreProcessedMI.m

@@ -1,192 +1,3 @@
 MI = -DW + A*W + transpose(A*W) + B*Y + transpose(B*Y) + 2*1.000000*W;
 
-Block1 = MI(1:4,1:4);
-Block1(2,2) = Block1(2,2)/2;
-
-Block2 = MI(3:6,3:6);
-Block2(2,2) = Block2(2,2)/2;
-
-Block3 = MI(5:8,5:8);
-Block3(2,2) = Block3(2,2)/2;
-
-Block4 = MI(7:10,7:10);
-Block4(2,2) = Block4(2,2)/2;
-
-Block5 = MI(9:12,9:12);
-Block5(2,2) = Block5(2,2)/2;
-
-Block6 = MI(11:14,11:14);
-Block6(2,2) = Block6(2,2)/2;
-
-Block7 = MI(13:16,13:16);
-Block7(2,2) = Block7(2,2)/2;
-
-Block8 = MI(15:18,15:18);
-Block8(2,2) = Block8(2,2)/2;
-
-Block9 = MI(17:20,17:20);
-Block9(2,2) = Block9(2,2)/2;
-
-Block10 = MI(19:22,19:22);
-Block10(2,2) = Block10(2,2)/2;
-
-Block11 = MI(21:24,21:24);
-Block11(2,2) = Block11(2,2)/2;
-
-Block12 = MI(23:26,23:26);
-Block12(2,2) = Block12(2,2)/2;
-
-Block13 = MI(25:28,25:28);
-Block13(2,2) = Block13(2,2)/2;
-
-Block14 = MI(27:30,27:30);
-Block14(2,2) = Block14(2,2)/2;
-
-Block15 = MI(29:32,29:32);
-Block15(2,2) = Block15(2,2)/2;
-
-Block16 = MI(31:34,31:34);
-Block16(2,2) = Block16(2,2)/2;
-
-Block17 = MI(33:36,33:36);
-Block17(2,2) = Block17(2,2)/2;
-
-Block18 = MI(35:38,35:38);
-Block18(2,2) = Block18(2,2)/2;
-
-Block19 = MI(37:40,37:40);
-Block19(2,2) = Block19(2,2)/2;
-
-Block20 = MI(39:42,39:42);
-Block20(2,2) = Block20(2,2)/2;
-
-Block21 = MI(41:44,41:44);
-Block21(2,2) = Block21(2,2)/2;
-
-Block22 = MI(43:46,43:46);
[…]

### 2016-07-19 TheoreticalExample1Version2/PreProcessedSys.m

@@ -9,130 +9,12 @@ x2 = sdpvar(1);
 x3 = sdpvar(1);
 x4 = sdpvar(1);
 x5 = sdpvar(1);
-x6 = sdpvar(1);
-x7 = sdpvar(1);
-x8 = sdpvar(1);
-x9 = sdpvar(1);
-x10 = sdpvar(1);
-x11 = sdpvar(1);
-x12 = sdpvar(1);
-x13 = sdpvar(1);
-x14 = sdpvar(1);
-x15 = sdpvar(1);
-x16 = sdpvar(1);
-x17 = sdpvar(1);
-x18 = sdpvar(1);
-x19 = sdpvar(1);
-x20 = sdpvar(1);
-x21 = sdpvar(1);
-x22 = sdpvar(1);
-x23 = sdpvar(1);
-x24 = sdpvar(1);
-x25 = sdpvar(1);
-x26 = sdpvar(1);
-x27 = sdpvar(1);
-x28 = sdpvar(1);
-x29 = sdpvar(1);
-x30 = sdpvar(1);
-x31 = sdpvar(1);
-x32 = sdpvar(1);
-x33 = sdpvar(1);
-x34 = sdpvar(1);
-x35 = sdpvar(1);
-x36 = sdpvar(1);
-x37 = sdpvar(1);
-x38 = sdpvar(1);
-x39 = sdpvar(1);
-x40 = sdpvar(1);
-x41 = sdpvar(1);
-x42 = sdpvar(1);
-x43 = sdpvar(1);
-x44 = sdpvar(1);
-x45 = sdpvar(1);
-x46 = sdpvar(1);
-x47 = sdpvar(1);
-x48 = sdpvar(1);
-x49 = sdpvar(1);
-x50 = sdpvar(1);
-x51 = sdpvar(1);
-x52 = sdpvar(1);
-x53 = sdpvar(1);
-x54 = sdpvar(1);
-x55 = sdpvar(1);
-x56 = sdpvar(1);
-x57 = sdpvar(1);
-x58 = sdpvar(1);
-x59 = sdpvar(1);
-x60 = sdpvar(1);
-x61 = sdpvar(1);
-x62 = sdpvar(1);
-x63 = sdpvar(1);
-x64 = sdpvar(1);
 
 y1 = sdpvar(1);
 y2 = sdpvar(1);
 y3 = sdpvar(1);
 y4 = sdpvar(1);
 y5 = sdpvar(1);
-y6 = sdpvar(1);
[…]

### 2016-07-19 TheoreticalExample1Version2/PreProcessedW.m

@@ -88,1069 +88,7 @@ DW5 = [DWTemp(1,:)*f5/2, DWTemp(2,:)*f5;
 DW5 = DW5 + transpose(DW5);
 
 
-% Creation of W6 and DW6
-[Wp611,Wc611,Wv611] = polynomial(q6,2,0);
-[Wp612,Wc612,Wv612] = polynomial(q6,2,0);
-[Wp622,Wc622,Wv622] = polynomial(q6,2,0);
-% Creation of W6
-W6 = [Wp611, Wp612;
-      Wp612, Wp622];
-
-Wc6 = [Wc611;Wc612;Wc622];
-Wp6 = [Wp611;Wp612;Wp622];
-
-% Creation of DW6
-DWTemp = jacobian(Wp6,q6);
-DW6 = [DWTemp(1,:)*f6/2, DWTemp(2,:)*f6;
-       0,                DWTemp(3,:)*f6/2];
-DW6 = DW6 + transpose(DW6);
-
-
-% Creation of W7 and DW7
-[Wp711,Wc711,Wv711] = polynomial(q7,2,0);
-[Wp712,Wc712,Wv712] = polynomial(q7,2,0);
-[Wp722,Wc722,Wv722] = polynomial(q7,2,0);
-% Creation of W7
-W7 = [Wp711, Wp712;
-      Wp712, Wp722];
-
-Wc7 = [Wc711;Wc712;Wc722];
-Wp7 = [Wp711;Wp712;Wp722];
-
-% Creation of DW7
-DWTemp = jacobian(Wp7,q7);
-DW7 = [DWTemp(1,:)*f7/2, DWTemp(2,:)*f7;
-       0,                DWTemp(3,:)*f7/2];
-DW7 = DW7 + transpose(DW7);
-
-
-% Creation of W8 and DW8
-[Wp811,Wc811,Wv811] = polynomial(q8,2,0);
-[Wp812,Wc812,Wv812] = polynomial(q8,2,0);
-[Wp822,Wc822,Wv822] = polynomial(q8,2,0);
-% Creation of W8
-W8 = [Wp811, Wp812;
-      Wp812, Wp822];
-
-Wc8 = [Wc811;Wc812;Wc822];
-Wp8 = [Wp811;Wp812;Wp822];
-
-% Creation of DW8
-DWTemp = jacobian(Wp8,q8);
-DW8 = [DWTemp(1,:)*f8/2, DWTemp(2,:)*f8;
-       0,                DWTemp(3,:)*f8/2];
[…]

### 2016-07-19 TheoreticalExample1Version2/TimerPlot.m

@@ -6,28 +6,49 @@ clc;
 
 set(groot, 'defaultAxesTickLabelInterpreter','latex');
 set(groot, 'defaultLegendInterpreter','latex');
-
-Option = 'Diagonal'
-
-if strcmp(Option,'Diagonal')
     
-    Time(1) = 1.224428609719290;
-    Time(2) = 1.561498248693083;
-    Time(3) = 2.754560839016742;
-    Time(4) = 5.57600135162288;
-    Time(5) = 10.910490511994272;
-    Time(6) = 22.1421868579150;
-    Time(7) = 47.584998880884680;
-    Time(8) = 1.074516828633032e+02;
-    Time(9) = 2.677553198628477e+02;
-    Time(10) = 8.784112856174025e+02;
+    TimeDiagonal(1) = 1.224428609719290;
+    TimeDiagonal(2) = 1.561498248693083;
+    TimeDiagonal(3) = 2.754560839016742;
+    TimeDiagonal(4) = 5.57600135162288;
+    TimeDiagonal(5) = 10.910490511994272;
+    TimeDiagonal(6) = 22.1421868579150;
+    TimeDiagonal(7) = 47.584998880884680;
+    TimeDiagonal(8) = 1.074516828633032e+02;
+    TimeDiagonal(9) = 2.677553198628477e+02;
+    TimeDiagonal(10) = 8.784112856174025e+02;
+    
+    
+    TimeNeighbor(1) = 1.4669574118103108;
+    TimeNeighbor(2) = 1.534924490309093;
+    TimeNeighbor(3) = 3.531500826408437;
+    TimeNeighbor(4) = 8.130443844688111;
+    TimeNeighbor(5) = 17.69292659906184;
+    TimeNeighbor(6) = 37.699186934101675;
+    TimeNeighbor(7) = 81.59612608462406;
+    TimeNeighbor(8) = 159.61856998294263;
+    TimeNeighbor(9) = 444.1379786425903;
+    TimeNeighbor(10) = 0;
+    
+    TimeGeneral(1) = 1.37392396598692;
+    TimeGeneral(2) = 1.5140840205569028;
+    TimeGeneral(3) = 98.62643367580364;
+    TimeGeneral(4) = 0;
+    TimeGeneral(5) = 0;
+    TimeGeneral(6) = 0;
+    TimeGeneral(7) = 0;
+    TimeGeneral(8) = 0;
+    TimeGeneral(9) = 0;
[…]

### 2016-07-19 R0V0 (DESKTOP-K3D88KL's conflicted copy 2016-07-16).tex
> Done: Paper finished. Need to review it.

--- 2016-07-15 R0V0.tex
@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor ORCID}
+\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 \thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
-Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org. ORCID: 0000-0002-0883-0231, }% <-this % stops a space
+Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org.}% <-this % stops a space
 }
@@
 \begin{abstract}
-In this paper, input-affine nonlinear systems are considered.
-The problem under consideration is to design structured (for instance, decentralized or distributed) controllers for this class of systems.
-Although control-Lyapunov functions are the natural candidate to design these feedback laws, in terms of dynamical programming, the search for these functions is non-convex \cite{Rantzer:2001}.
-On the other hand, control-contraction metrics provide controllers that render pairs of solutions exponentially converge to each other.
-Moreover, the search for a structured controller and a suitable metric can be formulated in terms of a convex optimization problem.
-Under block-diagonal dominance conditions, this convex optimization problem can also be distributed.
-An example illustrate the approach for a network system.
+The abstract goes here.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Nonlinear Systems, Feedback Design, Contraction Theory, Distributed Control, Network Systems
+IEEE, IEEEtran, journal, \LaTeX, paper, template.
 \end{IEEEkeywords}
@@
 Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
-The main concept employed for the control of dynamic systems is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
-In terms of computation, controller design problems are often translated in terms of dynamic programming.
+In terms of computation, controller design problem are often translated in terms of dynamic programming
 
@@
 
-In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
-These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.
-In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.
+In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995,SteinShiromoto2013a}, and forwarding \cite{MazencPraly96}.
+In terms of numerical computation, techniques employed include sum-of-squares (SOS) optimization \cite{Parrilo2003}.
 
-For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
+For those system described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
 However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}).
-In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.
+In addition to the lack of a general systematic approach, the formulation of the CLF search in terms of numerical optimization leads to a problem that is not necessarily convex and not connected, in general \cite{Rantzer:2001}.
 
 An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
-One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation of the system is considered.
+In this methodology the feedback law is the solution of a convex optimization problem \cite{Manchester2014a}.
 The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below).
-This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.
 
 The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has several states (large scale), it does not scale well.
-This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
+This is due to the fact that the stability verification of a system with $n$ states may require an appropriate function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
 
 Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
-For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems, i.e., to make the controller scalable.
-In some cases, this property is satisfied by desnigning controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
-
+For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems of the network, i.e., to make the controller scalable.
+This property can be satisfied with decentralized controllers \cite{Siljak1991}.
 In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
@@
 Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure.
-The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to reduce the number of LMIs to be solved.
+The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where a structured synthesis of a controller is shown.
 
-For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein).
-However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}.
-The case can be even worse, when structural constraints are considered.
+For nonlinear systems in which some order of initial conditions is preserved along the flow of the vector field (monotone systems),
 
-For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs, in this work.
-The systems under consideration are continuously differentiable and affine in the input.
-One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed similarly to Lyapunov functions to measure the exponential convergence of pairs of solutions.
-Employing CCMs, the design of a structured feedback law allowing exponential convergence of solution is obtained in two steps.
-
-The first step consists of an off-line computation.
-The original system is extended with its \emph{differential / variational} formulation.
-The exponential convergence is reformulated in terms of stability of the origin for the extended system.
-This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint.
-The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law.
-
-The second step consists of an on-line integration. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).
-
-\todo[inline]{Highlight the difference between this paper and \cite{Manchester2014a} by saying that this one the integration part is also distributed.}
-
-At this point, the three contributions of this work can be highlighted.
-First, a systematic framework for off-line computation of a structured controller and metric for nonlinear systems is provided.
-This framework is the formulation of a convex optimization problem whose computation can also be distributed, provided that some conditions are met.
-Second, the computation of the online integration phase can distributed, due to the structure imposed on the metric.
-Third, the structure impose on the controller allows to address the scalability issue of CCMs.
-Note that the proposed method provides an explicit formula for the controller, since it is constructive.
-
-Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
-These are mostly related to network systems.
-For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
-This paper contrast with these works mainly in two points: 1) A systematic framework  for structured controller design is proposed; 2) Due the formulation of the stabilization as a convex optimization problem, not only a explicit formula of a structured controller is obtained but also a metric.
-
-\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}.
-The background needed for this paper is stated in Section \ref{sec:background}.
+\paragraph{Overview.} The motivation and background needed for this paper are stated in Section \ref{sec:Background and Motivation}.
+The problem under consideration is formalized in Section \ref{sec:Problem Formulation}.
 Section \ref{sec:Results} presents the result of this paper.
@@
 Consider the network composed of systems described by the following equation.
-\begin{equation}\label{eq:example}
-	\left\{\begin{array}{rcl}
-		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
-		\dot{y}_i&=&u_i,
-	\end{array}\right.
+\begin{equation}\label{eq:example system:i}
+	\dot{x}_i=??
 \end{equation}
-Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example}.
+Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example system:i}.
 
-\subsection{Background}\label{sec:background}
+\subsection{Background}
 
@@
 Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
-\begin{equation}\tag{\ref{eq:example}}
+\begin{equation}\label{eq:example}
 	\left\{\begin{array}{rcl}
@@
 In the first one, no constraints were imposed on the matrix $Y$.
-The parser took  seconds to solve the  MI \eqref{eq:MI formulation}.
+The parser took 97 seconds to solve the  MI \eqref{eq:MI formulation}.
 The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
@@
 \end{align*}
-
-Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents doubled each time.
-
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
-	\caption{Time take by the parser to solve the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents double each time. Axis are on log scale.}
-	\label{fig:time graph}
-\end{figure}
 
@@
 
-In this work, input-affine nonlinear systems were considered.
-The considered problem was the design of structured feedback laws.
-The methodology employed for synthesis was based on control-contraction metrics which provides a controller ensuring exponential convergence of pairs of solutions.
-
-In terms of dynamic programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
-This is one of its main advantages in comparison to the search of control-Lyapunov functions, as its dynamic programming formulation leads to a non-convex problem.
-
-The main contribution of this paper is the synthesis of a feedback law with a prescribed structure.
-More precisely, since the matrix describing the metric has a block-diagonal structure, the on-line integration phase can be done in parallel, i.e.,  each block defines a metric to the corresponding component of the state space where the geodesic is computed by optimization.
-
-The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances like time delays.
-
-{\itshape Acknowledgments.} The authors thank the anonymous reviewers.
-
 \appendices

### 2016-07-19 TheoreticalExample2/LMIOptmisation.m
> Done: Renamed the folder and uploaded to Github

@@ -1,4 +1,4 @@
-function test
+function caller
 clear all
 close all
 clc
@@ -41,7 +41,7 @@ if NumberOfAgents > 512 && strcmp(Option,'Diagonal')
 end
 
 LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
-LMIOptimisation1(LaplacianMatrix,Option,lambda)
+LMIOptimisation(LaplacianMatrix,Option,lambda)
 
 diary off
 
@@ -49,9 +49,7 @@ pause(60)
 
 end
 
-function LMIOptimisation1(LaplacianMatrix,Option,lambda)
-
-%     function LMIOptmisation(LaplacianMatrix,Option,lambda)
+function LMIOptimisation(LaplacianMatrix,Option,lambda)
 
 global Simulation SystemStates SystemInputs SystemParameters
 

### 2016-07-19 R0V0.tex
> Done: Finished to review. Need to send to Ian.

@@
   % declare the path(s) where your graphic files are
-  \graphicspath{{./imgs}}
+  \graphicspath{{./imgs/}}
   % and their extensions so you won't have to specify these with
@@
 In this paper, input-affine nonlinear systems are considered.
-The problem under consideration is to design structured (for instance, decentralized or distributed) controllers for this class of systems.
-Although control-Lyapunov functions are the natural candidate to design these feedback laws, in terms of dynamical programming, the search for these functions is non-convex \cite{Rantzer:2001}.
-On the other hand, control-contraction metrics provide controllers that render pairs of solutions exponentially converge to each other.
-Moreover, the search for a structured controller and a suitable metric can be formulated in terms of a convex optimization problem.
-Under block-diagonal dominance conditions, this convex optimization problem can also be distributed.
-An example illustrate the approach for a network system.
+The problem under consideration is the design of structured (for instance, decentralized or distributed) controllers for this class of systems.
+Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, the search for these functions is non-convex \cite{Rantzer:2001}.
+On the other hand, control-contraction metrics can provide controllers through a convex optimization problem.
+The drawback is that it may require the a function with $n^2$ elements.
+By exploiting sparsity, this number of verification can be decreased and the convex optimization problem can also be distributed.
+An example illustrates the approach for a network system.
 \end{abstract}
@@
 Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
-The main concept employed for the control of dynamic systems is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
+The main underlying concept employed for the synthesis of feedback laws is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
 In terms of computation, controller design problems are often translated in terms of dynamic programming.
@@
 The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.
-
-In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
+In the case of nonlinear systems, design approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
 These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.
@@
 An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
-One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation of the system is considered.
+One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered.
 The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below).
@@
 Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
-For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems, i.e., to make the controller scalable.
-In some cases, this property is satisfied by desnigning controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
+For such systems, a property often desired is the ability to synthetize controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
 
@@
 
-For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs, in this work.
+For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work.
 The systems under consideration are continuously differentiable and affine in the input.
-One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed similarly to Lyapunov functions to measure the exponential convergence of pairs of solutions.
-Employing CCMs, the design of a structured feedback law allowing exponential convergence of solution is obtained in two steps.
+One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions.
+Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.
 
@@
 The original system is extended with its \emph{differential / variational} formulation.
-The exponential convergence is reformulated in terms of stability of the origin for the extended system.
+The exponential convergence problem is reformulated in terms of stability of the origin for the extended system.
 This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint.
 The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law.
-
-The second step consists of an on-line integration. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).
-
-\todo[inline]{Highlight the difference between this paper and \cite{Manchester2014a} by saying that this one the integration part is also distributed.}
+The second step consists of an on-line optimization.
+The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).
 
 At this point, the three contributions of this work can be highlighted.
-First, a systematic framework for off-line computation of a structured controller and metric for nonlinear systems is provided.
-This framework is the formulation of a convex optimization problem whose computation can also be distributed, provided that some conditions are met.
-Second, the computation of the online integration phase can distributed, due to the structure imposed on the metric.
-Third, the structure impose on the controller allows to address the scalability issue of CCMs.
+First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structure constraint, a feedback law with prescribed structure is obtained for nonlinear systems.
+Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is distributed.
+Third, when the system is described a non-strongly connected graph, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability.
 Note that the proposed method provides an explicit formula for the controller, since it is constructive.
@@
 Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
-These are mostly related to network systems.
 For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
-This paper contrast with these works mainly in two points: 1) A systematic framework  for structured controller design is proposed; 2) Due the formulation of the stabilization as a convex optimization problem, not only a explicit formula of a structured controller is obtained but also a metric.
+This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained.
 
@@
 The background needed for this paper is stated in Section \ref{sec:background}.
-Section \ref{sec:Results} presents the result of this paper.
+Section \ref{sec:Results} presents the main result of this paper.
 Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}.
@@
 $M\succeq 0$) stands for $M$ being positive (resp.
-semi) definite.
+semi)definite.
 
@@
 Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.
+The notation $f'$ stands for the total derivative of $f$.
 
@@
 where, for positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively.
-The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and satisfy $f(0)=0$ and $B(0)=0$.
-From now on the dependence of on the time $t$ will be omitted.
+The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and to satisfy $f(0)=0$ and $B(0)=0$.
+From now on the dependence on the time $t$ will be omitted.
 
@@
 \end{equation}
-holds true, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
+holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
 Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.
 
-Note that a stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable.
+A stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable.
 This concept is formalized in the following definition recalled from \cite{Manchester2014a}.
@@
 \begin{definition}\label{def:US}
-	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:global exponential uniform stabilizability}.
+	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}.
 \end{definition}
@@
 The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures.
-For instance, when $m=n$ full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$.
+For instance when $m=n$, full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$.
 This is formalized by letting $\mathscr{K}(i)=\{i\}$.
@@
 	\begin{enumerate}
-		\item Find a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$ for system \eqref{eq:general system} that globally exponentially uniformly stabilizes any forward complete solution $X(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system};
-
-		\item The function $k^\ast=(k_1^\ast,\ldots,k_m^\ast)$ belongs to the set $\Xi$.
+		\item Find a feedback law rendering system \eqref{eq:general system} universally stable;
+
+		\item The function $k^\ast$ belongs to the set $\Xi$.
 		\end{enumerate}
@@
 
-The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology) for network systems rendering it universally stabilizable.
+The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
 Consider the network composed of systems described by the following equation.
@@
 		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
-		\dot{y}_i&=&u_i,
+		\dot{y}_i&=&u_i.
 	\end{array}\right.
 \end{equation}
-Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example}.
+As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach cannot compute a unconstrained controller on a standard desktop machine, due to the number of variables.
+However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.
 
@@
 
-A suitable framework to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
+A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
 \begin{equation}\label{eq:general system:differential}
@@
 \end{definition}
-The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for contraction.
+The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for exponential convergence of solutions.
 Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
@@
 \begin{theorem}\label{prop:CCM Existence}
-	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a solution to item 1 of Problem~\ref{problem formulation}.
+	If there exists a control-contraction metric for system \eqref{eq:general system}, then a feedback law for system~\eqref{eq:general system} is obtained by integrating the feedback law for system~\eqref{eq:general system:differential}.
 \end{theorem}
 
-Another important result of Theorem \ref{prop:CCM Existence} the feedback for system \eqref{eq:general system} obtained by integrating a feedback law designed for system \eqref{eq:general system:differential}.
-
-As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
+Theorem~\ref{prop:CCM Existence} provides the result needed to solve item 1 of Problem~\ref{problem formulation}.
+
+As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.
@@
 
-{\itshape Motivation.} From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
+From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
 This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.
 
-{\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
-Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:contracting feedback law}.
+In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
+Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:MI formulation}.
 
@@
 for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.
-
-In other words, a sum-separable metric is the case in which the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these components depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$.
+In other words, the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$.
 The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
@@
 \begin{theorem}\label{thm:main result}
-	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 \begin{corollary}\label{cor:distributed computation}
-	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
+	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
 	\begin{equation}\label{eq:MI formulation:i}
@@
 
-\todo[inline]{See the works of Ahmadi (Princeton) on scale-diag. dom.}
-
 \subsection{Discussion}
 
-Although the requirement of a sum-separable structure seems to be restrictive, for some classes of systems this structure is equivalent to the (possibly local) stability of the origin.
+Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
 
@@
 
-Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure is open.
-As mentioned before, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
+Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open.
+As mentioned before, the main advantage to look for control-contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems.
+This is illustrated in the next section.
 
@@
 
-A case where structured controller design is important is on distributed design for network systems.
-
-Let $N>0$ be a constant integer, for each index $i\in\mathbb{N}_{[1,N]}$, consider the system given by
+A case where structured controller design is relevant is on distributed design for network systems.
+Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
+\begin{figure}[htpb!]
+	\centering
+	\input{./imgs/GraphStructure.pdf_tex}
+	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
+	\label{fig:graph}
+\end{figure}
+For each index $i\in\mathbb{N}_{[1,N]}$, the agents dynamics is described by the system
 \begin{equation}\tag{\ref{eq:example}}
@@
 are not linearly independent when $y_1=\cdots=y_N=0$.
-Furthermore, due to the quadratic term on $y$, the only action of the controller on the $x$-subsystem is capable of is to move the $x$-component of solution to \eqref{eq:example} towards the positive semi-axis.
+Furthermore, due to the quadratic term on $y$, the only possible action by the controller on the $x$-subsystem is to move the $x$-component of solution to \eqref{eq:example} towards the positive semi-axis.
 In other words, the controller cannot reduce the value of the $x$-component.
 
-Employing the method provided in Theorem~\ref{thm:main result}, the MI \eqref{eq:MI formulation} has been solved with optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek for a network composed of four systems (i.e., $N=4$) and for three different constraints on the matrix $Y$.
-The hardware on which the software ran is an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
-
-In all cases, the matrix $W$ has a diagonal structure as follows
+When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
+A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
+Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite.
+When no structural constraints are imposed on $Y$, this verification can lead $n^2$ equations to be solved.
+This motivates the approach proposed in this paper.
+
+To show the advantages of the method proposed in this paper, a benchmark was run for a network composes by $N=4$ systems and in three scenarios, according to the constraints imposed on the matrix $Y$.
+Namely, the unconstrained case, the ``neighbor case'', and the fully decentralized (diagonal) case.
+For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor case'' and up to $N=512$ systems for the fully decentralized (diagonal) case.
+
+In all cases, the matrix $W$ was required to have a block-diagonal structure as follows
 \begin{equation*}
@@
 
-In the first one, no constraints were imposed on the matrix $Y$.
-The parser took  seconds to solve the  MI \eqref{eq:MI formulation}.
-The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
+In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix).
+The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.
+The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
 \begin{equation*}
@@
 \begin{align*}
- \overline{Y}_{ij}=&-3y_i-0.08x_iy_i\\
- \underline{Y}_{ij}=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
+ \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
+ \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
 \end{align*}
@@
 		Y(q)=\scalebox{0.75}{$\begin{bmatrix}
-			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1+0.003x_3y_1,&0.005y_1y_3,&-0.007y_1+0.001x_4y_1,&0\\
-			-0.008y_2-0.002x_1y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.007y_2-0.004x_3y_2,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
-			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.004x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.008y_3+0.002x_4y_3,&0\\
-			-0.009y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
+			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1-0.003x_3y_1,&0.005y_1y_3,&-0.006y_1+0.001x_4y_1,&0\\
+			-0.006y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.009y_2-0.001x_3y_21,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
+			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.001x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.006y_3,&0\\
+			-0.006y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
 		\end{bmatrix}$}
@@
 
-In the second case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
+For the remaining cases, the constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
+\begin{equation*}
+	\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
+		T_{11}&T_{12}\\
+		T_{12}^\top&T_{22}
+	\end{bmatrix},\cdots,\begin{bmatrix}
+		T_{(N-1)(N-1)}&T_{(N-1)N}\\
+		T_{(N-1)N}^\top&T_{NN}
+	\end{bmatrix}\right).
+\end{equation*}
+This implies that sparsity can be exploited to decrease the number of equations needed to verify the MI \eqref{eq:MI formulation}.
+
+In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
 The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
-Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience $q_0=q_1$ and $q_5=q_4$).
-
-The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 98 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
+Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).
+
+The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds.
+The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
 \begin{equation*}
 		W_a=\mathbin{\mathtt{diag}}\left(
- 1.32,1.59\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.61\right).
+ 1.32,1.7\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
 \end{equation*}
@@
 \begin{equation*}
-	Y_{ij}=-3y_i-0.03x_iy_i
+	Y_{ij}(q_i,\breve{q}_i)=-3.3y_i-0.09x_iy_i
 \end{equation*}
@@
 \begin{align*}
-	Y_{12}=&-4-0.01x_1-y_1^2-y_2^2-2x_1^2-x_2^2\\	
-	Y_{24}=&-3-0.01x_2-y_1^2-y_2^2-y_3^2-x_1^2-x_2^2-x_3^2\\	
-	Y_{36}=&-3-0.01x_3-y_2^2-y_3^2-y_4^2-x_2^2-x_3^2-x_4^2\\	
-	Y_{48}=&-4-0.01x_4-y_4^2-y_3^2-2x_4^2-x_3^2
+	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\\	
+	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\\	
+	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\\	
+	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)
 \end{align*}
@@
 	Y(q)=\scalebox{0.85}{$\begin{bmatrix}
-	Y_{11},&Y_{12},&-0.01y_2+0.03x_2y_1,&0,&0,&0,&0,&0\\
-	-0.01y_2-0.002x_1y_2,&0,&Y_{23},&Y_{24},&-0.01y_2+0.03x_3y_2,&0,&0,&0\\
-	0,&0,&-0.01y_3+0.03x_2y_3,&0,&Y_{35},&Y_{36},&-0.01y_3-0.002x_4y_3,&0\\
-	0,&0,&0,&0,&-0.01y_4+0.03x_3y_4,&0,&Y_{47},&Y_{48}
+	Y_{11}(q_1,\breve{q}_1),&Y_{12}(q_1,\breve{q}_1),&-0.001y_1,&0,&0,&0,&0,&0\\
+	-0.001(y_2+x_1y_2),&0,&Y_{23}(q_2,\breve{q}_2),&Y_{24}(q_2,\breve{q}_2),&-0.003y_2,&0,&0,&0\\
+	0,&0,&-0.002y_3,&0,&Y_{35}(q_3,\breve{q}_3),&Y_{36}(q_3,\breve{q}_3),&-0.002y_3,&0\\
+	0,&0,&0,&0,&-0.003y_4,&0,&Y_{47}(q_4,\breve{q}_4),&Y_{48}(q_4,\breve{q}_4)
 	\end{bmatrix}$}
@@
 In the last case, the fully decentralized scenario has been considered.
-The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 101 seconds.
+The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 2.6 seconds.
 In this case, $\mathscr{K}_Y(i)=\{j\in\mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}$, where $\mathscr{K}(i)=\{i\}$.
-Imposing $Y\in\Xi_Y$ and solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
+Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
 \begin{align*}
@@
 		W_a=\mathbin{\mathtt{diag}}\left(
- 1.43,1.17\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.03,2.17\right)
-\end{equation*}
-and, for each index $i\in\mathbb{N}_{[1,4]}$,
+ 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
+\end{equation*}
+and, for each index $i=1,4$,
 \begin{align*}
- Y_i=[-4.33y_i+0.04x_iy_i,\\
- -7.78-&0.01x_i-2.73y_i^2-2.98x_i^2].
+ Y_i(q_i)=[-3.1y_i+0.06x_iy_i,-3.6-0.02x_i-2.3y_i^2-2.4x_i^2]
 \end{align*}
-
-Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents doubled each time.
+and, for each index $i=2,3$,
+\begin{align*}
+ Y_i(q_i)=[-3.1y_i,-3.8-2.1y_i^2-2.2x_i^2].
+\end{align*}
+
+Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this illustration: unconstrained, ``neighbor'' and fully decentralized.
 
@@
 	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
-	\caption{Time take by the parser to solve the MI \eqref{eq:MI formulation} for the case of full decentralization, when the number of agents double each time. Axis are on log scale.}
+	\caption{Time take by the parser to solve the MI \eqref{eq:MI formulation} for the three cases under consideration.
+The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).
+Axes are on log scale.}
 	\label{fig:time graph}
@@
 
+According to the graph shown in Figure \ref{fig:time graph}, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} was of the same order of magnitude for the three cases.
+However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor''-constrained case which, in turn, takes more time than the fully decentralized-constrained case.
+The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case.
+In addition to this, in the former case, each element is defined as a polynomial of second degree on the variables $q_i$ and $\breve{q}_i$, while for the latter, they are defined on the variable $q_i$ only.
+
+Regarding the on-line integration phase, since the matrices $W$ computed in each case is  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$.
+For each case, and for each index $i\in\mathbb{N}_{[1,4]}$, the feedback law is  given by the formula
+\begin{equation*}
+	k= \int_0^1Y(sq)W^{-1}q\,ds.
+\end{equation*}
+Given the structure of the matrices $Y$ and $W$, each line $i\in\mathbb{N}_{[1,4]}$ is given by
+\begin{equation*}
+k_i=\begin{cases}
+	\displaystyle\int_0^1Y_i(sq)W_i^{-1}q_i\,ds,&\text{if unconstrained}\\
+	\displaystyle\int_0^1Y_i(sq_i,s\breve{q}_i)W_i^{-1}q_i\,ds,&\text{if ``neighbor''}\\
+	\displaystyle\int_0^1Y_i(sq_i)W_i^{-1}q_i\,ds,&\text{if fully decentralized.}
+\end{cases}
+\end{equation*}
+Moreover, from Theorem~\ref{thm:main result}, the feedback law $k$ solves Problem~\ref{problem formulation} for the network resulting from the interconnection of systems \eqref{eq:example}.
+
 \section{Proof of the Results}\label{sec:Proof of the Results}
@@
 \begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ is a solution to the MI \eqref{eq:MI formulation}.
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}.
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
@@
 	\end{equation*}
-	This implies that the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.
+	Consequently, the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.
 
@@
 	\end{align*}
-	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$.
+	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.
 
@@
 It remains to show that this interval of existence can be extended on $[0,1]$.
-In other words, to show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.
+In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.
 
@@
 
-	Since the vector field $\overline{K}$ is smooth, it also Lipschitz.
-This implies that, for every fixed $t\geq0$, and for every $S>0$, there exists a constants $c_1(S)$ and $c_2(S)$ such that the inequality
+	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
+This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
 	\begin{equation*}
@@
 	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
-Applying \cite[Theorem 2.12]{Teschl2012} pointwisely on $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
+Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
 
 	Note that, due to the structure of the matrix $K$, the feedback law $k^\ast$ defined in Equation \eqref{eq:contracting feedback law} solves item 2 of Problem~\ref{problem formulation}, i.e., $k^\ast\in\Xi$.
-Furthermore, the computation of a solution to Equation~\eqref{eq:K ODE} can be partially distributed, because each line of the matrix $K$ will depend only on specific components of the vector $\gamma'$.
-
 This concludes the proof of Theorem \ref{thm:main result}.
@@
 	\begin{equation*}
-		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{x_i}^\top T_{ii}\delta_{\eta_i}\leq 0
+		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}\leq 0
 	\end{equation*}
@@
 In this work, input-affine nonlinear systems were considered.
-The considered problem was the design of structured feedback laws.
+The problem was the design of structured feedback laws.
 The methodology employed for synthesis was based on control-contraction metrics which provides a controller ensuring exponential convergence of pairs of solutions.
@@
 In terms of dynamic programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
-This is one of its main advantages in comparison to the search of control-Lyapunov functions, as its dynamic programming formulation leads to a non-convex problem.
-
-The main contribution of this paper is the synthesis of a feedback law with a prescribed structure.
-More precisely, since the matrix describing the metric has a block-diagonal structure, the on-line integration phase can be done in parallel, i.e.,  each block defines a metric to the corresponding component of the state space where the geodesic is computed by optimization.
-
-The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances like time delays.
+Although this is one of its main advantages over the search of control-Lyapunov functions, it does not scale well.
+
+For systems described by a non-fully connected graph, the approach presented in this paper exploits sparsity to design feedback laws with a prescribed structure.
+More precisely, by imposing a block-diagonal structure on the matrix describing the metric, a controller with a prescribed structure can be synthesized.
+Moreover, the on-line integration phase computation can be in parallel, because each block defines a metric to the corresponding component of the state space where the geodesic is computed by optimization.
+
+The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances such as time delays.
 

### 2016-07-25 R0V0.tex
> Done: Started to remove all files that are not the TeX file. Add information about graphs.

@@
 
+Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$.
+A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$.
+Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
+A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them.
+It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise.
+
 \subsection{Problem Formulation and Motivation}\label{sec:Problem Formulation and Motivation}
@@
 holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
-Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.
 
@@
 \begin{definition}\label{def:US}
-	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}.
+	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes it.
 \end{definition}
@@
 
-The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances such as time delays.
-
-{\itshape Acknowledgments.} The authors thank the anonymous reviewers.
-
 \appendices

### 2016-07-25 R0V0.tex
> Removed the Reviews from Commit.

@@
 holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
+Equivalently, if inequality \eqref{eq:global exponential uniform stabilizability} hold, then the solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be \emph{globally exponentially uniformly stable} for system \eqref{eq:general system} in closed loop with $k^\ast$
 
@@
 \begin{definition}\label{def:US}
-	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes it.
+	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} rendering $X^\ast(\cdot,\cdot,u^\ast)$ globally exponentially uniformly stable with rate $\lambda$.
 \end{definition}
-
-Note that Definition \ref{def:US} reduces to the notion of stabilizability of equilibria, when $x^\ast=0$ (for further reading on stabilizability, the reader may address \cite{Bacciotti:1992}).
 
@@
 \end{equation}
-As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach cannot compute a unconstrained controller on a standard desktop machine, due to the number of variables.
+As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to the number of variables.
 However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.
@@
 Note that a bounded Riemannian metric defined, for every $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$, as $V(x,\delta_x)=|\delta_x|_x^2$ and satisfying the set of inequalities \eqref{eq:metric} is a contraction metric for system \eqref{eq:general system}.
-With an abuse of concept, from now the bounded Riemannian metric defined above will be called simply as \emph{metric}.
-
-The existence a contraction metric for system \eqref{eq:general system} with $u\equiv0$ implies that every two solutions of this system converge to each other exponentially.
-The proof of this claim can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
+For brevity, from now the bounded Riemannian metric defined above will be called simply as \emph{metric}.
+
+The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially.
+The proof of this claim, for the case in which $u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
 
@@
 		\begin{equation}\label{eq:}
-			\delta_x^\top M(x)B(x)=0
+			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
 		\end{equation}
@@
 		\begin{align}
-			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x\leq\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
+			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
 		\end{align}
@@
 \begin{equation}\label{eq:MI formulation}
-	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\preceq0,
+	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0,
 \end{equation}
@@
 	\begin{equation}\label{eq:MI formulation:i}
-		T_{ii}\preceq 0
+		T_{ii}\prec 0
 	\end{equation}
@@
 Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite.
-When no structural constraints are imposed on $Y$, this verification can lead $n^2$ equations to be solved.
-This motivates the approach proposed in this paper.
+When no structural constraints are imposed on $Y$, this verification can lead to
+\begin{equation*}
+\left(\sum_{i=1}^N\begin{pmatrix}
+n_i+d\\ d
+\end{pmatrix}\right)^2
+\end{equation*}
+equations to be solved. This motivates the approach proposed in this paper.
 
@@
 	\begin{equation*}
-		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}\leq 0
+		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}< 0
 	\end{equation*}

### 2016-08-25 R0V0.tex
changed the gitignore
Change notation of ordered sets.

@@
 \thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
-Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: humberto.shiromoto@ieee.org. ORCID: 0000-0002-0883-0231, }% <-this % stops a space
+Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt humberto.shiromoto@ieee.org}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
 }
@@
 
-\paragraph{Notation.} Let $N\in\mathbb{N}$ be a constant value.
-The notation $\mathbb{N}_{[1,N]}$ stands for the set $\{i\in\mathbb{N}:1\leq i\leq N\}$.
-Let $c\in\mathbb{R}$ be a constant value.
-The notation $\mathbb{R}_{[1,c]}$ (resp.
-$\mathbb{R}_{\diamond c}$) stands for the set $\{x\in\mathbb{R}:1\leq x\leq c\}$ (resp.
-$\{x\in\mathbb{R}:x\diamond c\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$).
+\paragraph{Notation.} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$.
+The notation $\mathbb{S}_{[s_1,s_2)}$ (resp.
+$\mathbb{S}_{\diamond s_3}$) stands for the set $\{s\in\mathbb{S}:s_1\leq s< s_2\}$ (resp.
+$\{s\in\mathbb{S}:s\diamond s_3\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$).
 A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$.

### 2016-09-22 R0V0.tex
Add header
Change header
Restructure the paper into design of decentralized controllers and decentralized design of decentralized controllers.
Move proofs from the Proofs section

@@
 % !TEX encoding = UTF-8 Unicode
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 																			   %
+% Git Branch: Manchester20160725											   %
+% 																			   %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Results}\label{sec:Results}
+\section{Design of Decentralized Controllers}\label{sec:Design of Decentralized Controllers}
 
@@
 
-The detailed proof of Theorem \ref{thm:main result} is provided in Section \ref{sec:Proof of the Results}.
+\begin{proof}[Proof of Theorem \ref{thm:main result}]
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}.
+Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
+Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi_Y$.
+
+	The MI \eqref{eq:MI formulation} implies that the inequality
+	\begin{equation*}
+		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
+	\end{equation*}
+	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$.
+Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
+Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system}.
+
+	It now remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
+Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
+	\begin{equation}\label{eq:geodesic sum}
+		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds.
+	\end{equation}
+
+	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. More precisely, 
+	\begin{equation*}
+		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}.
+	\end{equation*}
+	Consequently, the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.
+
+	From Hopf-Rinow theorem (cf.
+\cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
+	\begin{align*}
+		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i).
+	\end{align*}
+	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.
+
+	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} is given by Equation \eqref{eq:contracting feedback law}.
+
+	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
+	\begin{equation}\label{eq:K ODE}
+		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast).
+	\end{equation}
+	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the smoothness of the functions $K$ and $\gamma$.
+It remains to show that this interval of existence can be extended on $[0,1]$.
+In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.
+
+	To show that a solution $k^\ast$ is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
+This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then the solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
+
+	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
+This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
+	\begin{equation*}
+		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
+	\end{equation*}
+	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
+Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
+
+	Note that, due to the structure of the matrix $K$, the feedback law $k^\ast$ defined in Equation \eqref{eq:contracting feedback law} solves item 2 of Problem~\ref{problem formulation}, i.e., $k^\ast\in\Xi$.
+This concludes the proof of Theorem \ref{thm:main result}.
+\end{proof}
 
 Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel.
-The next result provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$.
+The next section provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$.
 Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.
+
+\section{Distributed Design of Decentralized Controllers}
 
@@
 
-The detailed proof of Corollary \ref{cor:distributed computation} is provided in Section \ref{sec:Proof of the Results}.
+\begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
+	By assumption, the pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.
+
+	Equation \eqref{eq:BDD} together with the fact that $|I_{n_i}|\leq |T_{ii}||T_{ii}^{-1}|$ implies that the inequality
+	\begin{equation}\label{eq:BDD2} 
+		\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|\leq |T_{ii}|
+	\end{equation}
+	holds, for every index $i\in\mathbb{N}_{[1,N]}$.
+
+	For every $\delta_\eta\in\mathbb{R}^n$, consider the product $\delta_\eta^\top T\delta_\eta$. Each line $i\in\mathbb{N}_{[1,N]}$ of this product is given by
+	\begin{equation*}
+		\delta_{\eta_i}^\top\begin{bmatrix}
+			T_{i1}&\cdots&T_{i(i-1)}&T_{ii}&T_{i(i+1)}&\cdots&T_{iN}
+		\end{bmatrix}\delta_\eta.
+	\end{equation*}
+	Inequalities \eqref{eq:BDD2} and \eqref{eq:MI formulation:i} imply that the inequalities
+	\begin{equation*}
+		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}< 0
+	\end{equation*}
+	hold, for every $\delta_\eta\in\mathbb{R}^n$.
+Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$.
+This later inequality is equivalent to the MI \eqref{eq:MI formulation}.
+This concludes the proof of Corollary~\ref{cor:distributed computation}.
+\end{proof}
 
@@
 
-\section{Proof of the Results}\label{sec:Proof of the Results}
-
-\begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}.
-Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
-Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi_Y$.
-
-	The MI \eqref{eq:MI formulation} implies that the inequality
-	\begin{equation*}
-		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
-	\end{equation*}
-	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$.
-Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
-Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system}.
-
-	It now remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
-Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
-	\begin{equation}\label{eq:geodesic sum}
-		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds.
-	\end{equation}
-
-	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. More precisely, 
-	\begin{equation*}
-		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}.
-	\end{equation*}
-	Consequently, the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.
-
-	From Hopf-Rinow theorem (cf.
-\cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
-	\begin{align*}
-		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i).
-	\end{align*}
-	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.
-
-	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} is given by Equation \eqref{eq:contracting feedback law}.
-
-	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
-	\begin{equation}\label{eq:K ODE}
-		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast).
-	\end{equation}
-	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the smoothness of the functions $K$ and $\gamma$.
-It remains to show that this interval of existence can be extended on $[0,1]$.
-In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.
-
-	To show that a solution $k^\ast$ is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
-This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then the solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
-
-	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
-This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
-	\begin{equation*}
-		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
-	\end{equation*}
-	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
-Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
-
-	Note that, due to the structure of the matrix $K$, the feedback law $k^\ast$ defined in Equation \eqref{eq:contracting feedback law} solves item 2 of Problem~\ref{problem formulation}, i.e., $k^\ast\in\Xi$.
-This concludes the proof of Theorem \ref{thm:main result}.
-\end{proof}
-
-\begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
-	By assumption, the pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.
-
-	Equation \eqref{eq:BDD} together with the fact that $|I_{n_i}|\leq |T_{ii}||T_{ii}^{-1}|$ implies that the inequality
-	\begin{equation}\label{eq:BDD2} 
-		\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|\leq |T_{ii}|
-	\end{equation}
-	holds, for every index $i\in\mathbb{N}_{[1,N]}$.
-
-	For every $\delta_\eta\in\mathbb{R}^n$, consider the product $\delta_\eta^\top T\delta_\eta$. Each line $i\in\mathbb{N}_{[1,N]}$ of this product is given by
-	\begin{equation*}
-		\delta_{\eta_i}^\top\begin{bmatrix}
-			T_{i1}&\cdots&T_{i(i-1)}&T_{ii}&T_{i(i+1)}&\cdots&T_{iN}
-		\end{bmatrix}\delta_\eta.
-	\end{equation*}
-	Inequalities \eqref{eq:BDD2} and \eqref{eq:MI formulation:i} imply that the inequalities
-	\begin{equation*}
-		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}< 0
-	\end{equation*}
-	hold, for every $\delta_\eta\in\mathbb{R}^n$.
-Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$.
-This later inequality is equivalent to the MI \eqref{eq:MI formulation}.
-This concludes the proof of Corollary~\ref{cor:distributed computation}.
-\end{proof}
-
 \section{Conclusion}\label{sec:Conclusion}

### 2016-09-22 R0V0.tex
Small changes on the outline paragraph
Correct from LPV systems and LTI systems

--- 2016-08-25 R0V0.tex
@@
 % !TEX encoding = UTF-8 Unicode
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 																			   %
+% Git Branch: Master	 													   %
+% 																			   %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\usepackage[natbib=true,backend=bibtex,style=ieee,
+\usepackage[natbib=true,backend=biber,style=ieee,
 firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
-\addbibresource{../../../../Library.bib}
+\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
 \AtBeginBibliography{\small}
@@
 
-Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear parameter-varying systems (LPVS) (see \cite[Ch.
-2 and 3]{Briat2015} for more information on LPVS).
+Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTIS) (see \cite{Hespanha:2009} for more information on LTIS).
 

### 2016-09-22 R0V0.tex
Correct from LPV systems and LTI systems

--- 2016-09-22 R0V0.tex
@@
 The background needed for this paper is stated in Section \ref{sec:background}.
-Section \ref{sec:Results} presents the main result of this paper.
 Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}.
-The proofs of the results are provided in Section \ref{sec:Proof of the Results}.
 Section \ref{sec:Conclusion} collects final remarks.

### 2016-09-22 R0V0.tex
Better explanation to the number of monomials to be optimized

--- 2016-09-22 R0V0.tex
@@
 Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite.
-When no structural constraints are imposed on $Y$, this verification can lead to
-\begin{equation*}
-\left(\sum_{i=1}^N\begin{pmatrix}
-n_i+d\\ d
-\end{pmatrix}\right)^2
+For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
+\begin{equation*}
+		\begin{pmatrix}
+n+d\\ d
+\end{pmatrix}\;.
+\end{equation*}
+Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
+\begin{equation*}
+N^2\begin{pmatrix}
+n+d\\ d
+\end{pmatrix}^2
 \end{equation*}

### 2016-10-06 R0V0.tex
Add a reference for the number of monomials
Reduce the size of the equation describing the dynamical system of the example to fit in the page. Start to write about distributed design.

@@
 \begin{equation}\label{eq:example}
-	\left\{\begin{array}{rcl}
+	\scalebox{0.95}{$\left\{\begin{array}{rcl}
 		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
 		\dot{y}_i&=&u_i.
-	\end{array}\right.
+	\end{array}\right.$}
 \end{equation}
@@
 
+Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015}.
+
+Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.
+A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
+A \emph{clique tree} is a tree that has cliques as its nodes.
+An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.
+
 Consider the smooth function $T:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times n}$ with elements $i,j\in\mathbb{N}_{[1,N]}$ defined as
@@
 
-\section{Illustration}\label{sec:Illustration}
+\section{Numerical Experiment}\label{sec:Illustration}
 
@@
 \begin{equation}\tag{\ref{eq:example}}
-	\left\{\begin{array}{rcl}
+	\scalebox{0.95}{$\left\{\begin{array}{rcl}
 		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
 		\dot{y}_i&=&u_i,
-	\end{array}\right.
+	\end{array}\right.$}
 \end{equation}
@@
 n+d\\ d
-\end{pmatrix}\;.
-\end{equation*}
-Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
+\end{pmatrix}
+\end{equation*}
+\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
 \begin{equation*}

### 2016-10-10 R0V0.tex
Start to review the notation of the sets describing the feedback law
small change on notation

@@
 Define also the set of feedback laws
-\begin{equation*}
-	\Xi=\left\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:k_i^\ast\ \text{has the property}\ \mathscr{K}(i)\right\}.
-\end{equation*}
+\begin{align*}
+	\Xi=\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:\forall i\in\mathbb{N}_{[1,m]},k_i^\ast\ \text{depends on}\\
+	 \text{the components of}\ x\ \text{with indexes given by}\ \mathscr{K}(i)\}.
+\end{align*}
 
@@
 \begin{theorem}\label{thm:main result}
-	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 
-Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.
+Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}.
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.

### 2016-10-10 R0V0.tex
Change counters, erase the fomulation of the set \mathscr{K} and reformulate the statement of the problem in consideration

@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{claim}{Claim}
+\newtheorem{corollary}{Corollary}
 
 \theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{assumption}[theorem]{Assumption}
-\newtheorem{problem}[theorem]{Problem}
+\newtheorem{definition}{Definition}
+\newtheorem{assumption}{Assumption}
+\newtheorem{problem}{Problem}
 
 \theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
+\newtheorem{remark}{Remark}
+\newtheorem{example}{Example}
 
@@
 \begin{definition}\label{def:US}
-	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} rendering $X^\ast(\cdot,\cdot,u^\ast)$ globally exponentially uniformly stable with rate $\lambda$.
+	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} rendering $X^\ast(\cdot,x^\ast,u^\ast)$ globally exponentially uniformly stable with rate $\lambda$.
 \end{definition}
 
-For each component $i\in\mathbb{N}_{[1,m]}$ of the feedback law $k^\ast=(k_1^\ast,\ldots,k_m^\ast)^\top$, denote the set of indexes
-\begin{equation*}
-	\mathscr{K}(i)=\left\{j\in\mathbb{N}_{[1,n]}:k_i^\ast\ \text{depends explicitely on}\ x_j \right\}.
-\end{equation*}
-The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures.
-For instance when $m=n$, full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$.
-This is formalized by letting $\mathscr{K}(i)=\{i\}$.
-Moreover, at points where $k_i^\ast$ is differentiable, the explicit dependence on $x_i$ means that, for every index $j\in\mathbb{N}_{[1,n]}$ with $j\neq i$, $\partial k_i^\ast/\partial x_j\equiv0$.
-
-Define also the set of feedback laws
-\begin{align*}
-	\Xi=\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:\forall i\in\mathbb{N}_{[1,m]},k_i^\ast\ \text{depends on}\\
-	 \text{the components of}\ x\ \text{with indexes given by}\ \mathscr{K}(i)\}.
-\end{align*}
-
 At this point, the problem under consideration in this paper can be stated as follows.
 
-\begin{problem}\label{problem formulation}\hfill
-	\begin{enumerate}
-		\item Find a feedback law rendering system \eqref{eq:general system} universally stable;
-
-		\item The function $k^\ast$ belongs to the set $\Xi$.
-		\end{enumerate}
+\begin{problem}\label{problem formulation}
+	For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
+Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into the set $\mathscr{K}(i)\subset\mathbb{N}_{[1,N]}$.
 \end{problem}

### 2016-10-10 R0V0.tex
Small change regarding the old items 1 and 2 of old problem formulation

@@
 
-The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
+The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
 Consider the network composed of systems described by the following equation.
@@
 
-To solve item 2 of Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
+To address the constraint on the component of $k^\ast$ described in Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
 

### 2016-10-10 R0V0.tex
Change the set \Xi, introduce new set Y_i and X_i

@@
 % 																			   %
-% Git Branch: Manchester20160725											   %
+% Git Branch: Master	 													   %
 % 																			   %
@@
 
-For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
+Following the notation introduced in \cite{Tanaka2011}, For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
 \begin{subequations}
-	\begin{equation*}
-		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
-	\end{equation*}
-	and
 	\begin{align*}
-		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
-		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
+		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
+		&\ \forall j\in\mathbb{N}_{[1,N]}\}\;,
 	\end{align*}
 \end{subequations}
+where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, and the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$.
+The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential}.
+
+It remains to specify the dependence of each component of the matrix $Y$ on the elements of the state-space variable. To that end, let the set
+\begin{align*}
+		\mathbf{Y}_i=\{Y_{ij}:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ | \arg(Y_{ij})\in\mathbf{X}_i\}\;,
+\end{align*}
+where the set $\mathbf{X}_i$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(i)$.
+
 Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero.

### 2016-10-11 R0V0.tex
Modified notation of Xi set

--- 2016-10-10 R0V0.tex
@@
 
-For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
+Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
 \begin{subequations}
-	\begin{equation*}
-		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
-	\end{equation*}
-	and
 	\begin{align*}
-		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
-		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
+		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
+		&\ \arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},\\
+		&\ k\in\mathbb{N}_{[1,N]}\}\;,
 	\end{align*}
 \end{subequations}
-Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero.
-By definition, this set is the complement of $\mathscr{K}(i)$.
-Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$.
-As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.
+where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.
+
+The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
+Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and the set $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.
+
+In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}_i=\{x_i\}$.
 
 \begin{theorem}\label{thm:main result}
-	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
-Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi_Y$.
+Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi$.
 
@@
 
-Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}.
+Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}.
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
 A \emph{clique tree} is a tree that has cliques as its nodes.
+
+\begin{proposition}\label{prop:}
+	Let $p\in\mathbb{N}_{>0}$ be the number of cliques of the graph $\mathscr{G}$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
+\end{proposition}
+
 An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.

### 2016-10-11 R0V0.tex
Start the proof of decomposition of the MI

@@
 
-An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.
+\begin{proof}
+	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}.
+The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.
+
+	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
+For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}(\mathscr{C}_k)\times n}$ as
+	\begin{equation*}
+		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\mathbin{\mathtt{card}}(\mathscr{C}_k)]}\;,
+	\end{equation*}	
+	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.
+
+\end{proof}
 

### 2016-10-11 R0V0.tex
Finish first round of proof of clique decomposition
Erase the result regarding diagonal dominance

@@
 	\begin{align*}
-		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
-		&\ \arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},\\
-		&\ k\in\mathbb{N}_{[1,N]}\}\;,
+		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
+		\arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
 	\end{align*}
@@
 
-\end{proof}
-
-Consider the smooth function $T:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times n}$ with elements $i,j\in\mathbb{N}_{[1,N]}$ defined as
-	\begin{subequations}\label{eq:T}
-	\begin{align}
-		T_{ii}=-\dot{W}_i+A_{ii}W_i+W_iA_i^\top+B_iY_{ii}+(B_iY_{ii})^\top\nonumber\\
-		+2\lambda_i W_i
-	\end{align}
-	and
-	\begin{equation}
-		T_{ij}=A_{ij}W_j+W_iA_{ji}+B_iY_{ij}+(B_jY_{ji})^\top.
-	\end{equation}
-	\end{subequations}
-
-\begin{definition}\label{def:}
-	The matrix $T$ is said to be \emph{block-diagonally dominant} if the inequality
-	\begin{equation}\label{eq:BDD}
-		|T_{ii}^{-1}|^{-1}\geq\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|,
-	\end{equation}
-	holds, for every index $i\in\mathbb{N}_{[1,N]}$ and for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
-\end{definition}
-
-\begin{corollary}\label{cor:distributed computation}
-	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
-	\begin{equation}\label{eq:MI formulation:i}
-		T_{ii}\prec 0
-	\end{equation}
-	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
-\end{corollary}
-
-\begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
-	By assumption, the pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.
-
-	Equation \eqref{eq:BDD} together with the fact that $|I_{n_i}|\leq |T_{ii}||T_{ii}^{-1}|$ implies that the inequality
-	\begin{equation}\label{eq:BDD2} 
-		\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|\leq |T_{ii}|
-	\end{equation}
-	holds, for every index $i\in\mathbb{N}_{[1,N]}$.
-
-	For every $\delta_\eta\in\mathbb{R}^n$, consider the product $\delta_\eta^\top T\delta_\eta$. Each line $i\in\mathbb{N}_{[1,N]}$ of this product is given by
-	\begin{equation*}
-		\delta_{\eta_i}^\top\begin{bmatrix}
-			T_{i1}&\cdots&T_{i(i-1)}&T_{ii}&T_{i(i+1)}&\cdots&T_{iN}
-		\end{bmatrix}\delta_\eta.
-	\end{equation*}
-	Inequalities \eqref{eq:BDD2} and \eqref{eq:MI formulation:i} imply that the inequalities
-	\begin{equation*}
-		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}< 0
-	\end{equation*}
-	hold, for every $\delta_\eta\in\mathbb{R}^n$.
-Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$.
-This later inequality is equivalent to the MI \eqref{eq:MI formulation}.
-This concludes the proof of Corollary~\ref{cor:distributed computation}.
+   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$. The existence of $p$ cliques implies that there exist matrices $F_1,\ldots,F_p$ such that the equation
+   \begin{equation*}
+   	 T=\sum_{k=1}^p E_k^\top F_k E_k
+  	\end{equation*}
+  	holds.
+
+  	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
+  	\begin{equation*}
+  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
+	\end{equation*}
+	This concludes the proof.
 \end{proof}

### 2016-10-11 R0V0.tex
Add a comment on integrability

@@
 One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered.
-The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below).
+The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed solution (see a precise definition below).
+In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system.
 This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

### 2016-10-13 R0V0.tex
Changes on the definition of the set Xi and and the Proof of Proposition 1

@@
 		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
-		\arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
+		\arg(Y_{ij})\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
 	\end{align*}
 \end{subequations}
-where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.
+where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.
 
@@
 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
-For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}(\mathscr{C}_k)\times n}$ as
-	\begin{equation*}
-		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\mathbin{\mathtt{card}}(\mathscr{C}_k)]}\;,
+For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathbin{\mathtt{card}}(\mathscr{C}_k))$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ as
+	\begin{equation*}
+		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\dim_k]}\;,
 	\end{equation*}	
@@
 
-   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$. The existence of $p$ cliques implies that there exist matrices $F_1,\ldots,F_p$ such that the equation
+   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$.
+The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, such that the equation
    \begin{equation*}

### 2016-10-13 R0V0.tex
Changed the proof of Proposition 1. Especially, the definition of the sets E_k to be more precise with [Pak+15].

@@
 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
-For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathbin{\mathtt{card}}(\mathscr{C}_k))$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ as
-	\begin{equation*}
-		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\dim_k]}\;,
-	\end{equation*}	
-	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.
+For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 

### 2016-10-17 R0V0.tex
Add comment regarding the local property of considering a diagonal-structured metric
Start to apply modifications of review 20161017

@@
 
-\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}.
+\paragraph{Overview} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}.
 The background needed for this paper is stated in Section \ref{sec:background}.
@@
 
-\paragraph{Notation.} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$.
+\paragraph{Notation} Let $\mathbb{S}$ be a totally ordered set and $s_1,s_2,s_3\in\mathbb{S}$.
 The notation $\mathbb{S}_{[s_1,s_2)}$ (resp.
@@
 $\{s\in\mathbb{S}:s\diamond s_3\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$).
+Let $n>0$ be any integer, the vector $e_i$ denotes the vector with zeros in all rows except the $i$-th where it is 1.
 A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$.
@@
 
-\noindent{\itshape Class of systems.} Consider the class of systems described by the differential equation
+Consider the class of systems described by the differential equation
 \begin{equation}\label{eq:general system}
@@
 \end{equation}
-where, for positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively.
+where, for every positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively.
 The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and to satisfy $f(0)=0$ and $B(0)=0$.
@@
 
-{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
+A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\times\{X^\ast\}\times\{u^\ast\}\to\mathbb{R}^m$, denoted as $k^\ast$, such that the inequality
 \begin{equation}\label{eq:global exponential uniform stabilizability}
@@
 \end{equation}
-holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
-Equivalently, if inequality \eqref{eq:global exponential uniform stabilizability} hold, then the solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be \emph{globally exponentially uniformly stable} for system \eqref{eq:general system} in closed loop with $k^\ast$
-
-A stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable.
+holds, for every $t\geq0$, and for every initial condition $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).
+Equivalently, if inequality~\eqref{eq:global exponential uniform stabilizability} holds, then the solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be \emph{globally exponentially uniformly stable} for system \eqref{eq:general system} in closed loop with $k^\ast$
+
+A stronger condition than the global exponential stabilizability of a particular solution is the requirement for every forward complete solution to be globally exponentially stabilizable.
 This concept is formalized in the following definition recalled from \cite{Manchester2014a}.
@@
 
-{\itshape Riemannian metrics and differential formulation.} A Riemannian metric is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
-In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the metric is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function.
-Consequently, local notions of norm $|\delta_x|_x=\sqrt{\langle\delta_x,\delta_x\rangle_x}$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined.
+A \emph{Riemannian metric} is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
+In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function.
+Consequently, local notions of norm $|\delta_0|_x=\sqrt{\langle\delta_0,\delta_0\rangle_x}$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined.
 The metric is said to be \emph{bounded} if there exists constant values $\underline{m}>0$ and $\overline{m}>0$ such that, for every $x\in\mathbb{R}^n$, $\underline{m}I_n\leq M(x)\leq \overline{m}I_n$, where $I_n\in\mathbb{R}^{n\times n}$ is the identity matrix.
@@
 \begin{equation*}
-	\ell(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}\,ds\ \text{and}\ e(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}^2\,ds.
+	\ell(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}\,ds\ \text{and}\ e(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}^2\,ds\;.
 \end{equation*}
 The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them.
-This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem.
+This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
 \begin{equation}\label{eq:geodesic formulation}
-	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma).
+	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
 \end{equation}
@@
 
-Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$ with $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
+Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
 
@@
 The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially.
-The proof of this claim, for the case in which $u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
+The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
 
@@
 \end{definition}
-The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for exponential convergence of solutions.
+The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the  exponential convergence of solutions.
 Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
@@
 \begin{theorem}\label{prop:CCM Existence}
-	If there exists a control-contraction metric for system \eqref{eq:general system}, then a feedback law for system~\eqref{eq:general system} is obtained by integrating the feedback law for system~\eqref{eq:general system:differential}.
+	If there exists a control-contraction metric for system \eqref{eq:general system}, then a feedback law for system~\eqref{eq:general system} is obtained by integrating the feedback law for system~\eqref{eq:general system:differential} along geodesics.
 \end{theorem}
 
-Theorem~\ref{prop:CCM Existence} provides the result needed to solve item 1 of Problem~\ref{problem formulation}.
-
-As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
-The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.
+As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
+The steps to obtain a control to system~\eqref{eq:general system} are recalled below.
 
@@
 \begin{equation}\label{eq:MI formulation}
-	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0,
-\end{equation}
-that is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, $M=W^{-1}$ is a control-contraction metric for system \eqref{eq:general system}.
+	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0\;.
+\end{equation}
+Note that \eqref{eq:MI formulation} is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
+Consequently, the MI~\eqref{eq:MI formulation} can be solved with positive semidefinite programming techniques.
 
@@
 \begin{equation}\label{eq:contracting feedback law}
-	k^\ast(t,s)=u^\ast(t)+\int_0^s K(\gamma(\sigma),k^\ast(t,\sigma))\gamma'(\sigma)\,d\sigma,
+	k^\ast(t,s)=u^\ast(t)+\int_0^s K(\gamma(\sigma),k^\ast(t,\sigma))\gamma'(\sigma)\,d\sigma\;,
 \end{equation}
@@
 In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
-Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:MI formulation}.
 
@@
 
-Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$.
+Definition~\ref{def:SSCCM} implies that there exist $N>1$ integers $n_i>0$ such that $n_1+\ldots+n_N=n$.
 Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
@@
 
-To address the constraint on the component of $k^\ast$ described in Problem~\ref{problem formulation}, the structure on the feedback defined in Equation \eqref{eq:contracting feedback law} is obtained by imposing a a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
+To address the constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation}, the structure of the feedback defined by Equation~\eqref{eq:contracting feedback law} is obtained by imposing a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
 
@@
 \end{subequations}
-where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.
+where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ indexed by the set $\mathscr{K}(k)$.
 
 The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
-Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and the set $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.
+Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.
 
@@
 \begin{theorem}\label{thm:main result}
-	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exist smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 \begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}.
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ are a solution to the MI \eqref{eq:MI formulation}.
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
@@
 
-	It now remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
+	It remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
 Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
@@
 	\end{equation*}
-	Consequently, the minimization of Equation \eqref{eq:geodesic sum} can be computed separately.
+	Consequently, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
 
@@
 	To show that a solution $k^\ast$ is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
-This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then the solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
+This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
 
@@
 
-Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel.
+Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel.
 The next section provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$.
-Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.
+Before presenting it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.
 
@@
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
-A \emph{clique tree} is a tree that has cliques as its nodes.
 
@@
    Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$.
-The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, such that the equation
-   \begin{equation*}
-   	 T=\sum_{k=1}^p E_k^\top F_k E_k
-  	\end{equation*}
-  	holds.
+The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
+   \begin{equation*}
+   	 T=\sum_{k=1}^p E_k^\top F_k E_k\;.
+  	\end{equation*}
 
@@
 For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.
+Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
 

### 2016-10-17 R0V0.tex
Typo
Finish the modification of the proof of Theorem 2

@@
 \begin{equation}\label{eq:general system}
-	\dot{x}(t)=f(x(t))+B(x(t))u(t),	
+	\dot{x}(t)=f(x(t))+B(x(t))u(t)\;,	
 \end{equation}
@@
 \begin{equation}\label{eq:global exponential uniform stabilizability}
-	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
+	\left|X^\ast(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
 \end{equation}
@@
 		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
-		\dot{y}_i&=&u_i.
+		\dot{y}_i&=&u_i\;.
 	\end{array}\right.$}
@@
 \begin{equation}\label{eq:general system:differential}
-	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
+	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u\;,
 \end{equation}
@@
 Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively.
-If every solution $|\Delta_x(t,x,\delta_x,u,\delta u)|\to0$ exponentially as $t\to\infty$, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
+If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
 The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.
@@
 		 \begin{equation}
-		 	\underline{c}|\delta_x|^2\leq V(x,\delta_x)\leq \overline{c}|\delta_x|^2,
+		 	\underline{c}|\delta_x|^2\leq V(x,\delta_x)\leq \overline{c}|\delta_x|^2\;,
 	 	 \end{equation}
@@
 
-The following result is recalled from \cite{Manchester2014a} and provides a feedback law for system \eqref{eq:general system} given a feedback law for system \eqref{eq:general system:differential}.
+The following result is recalled from \cite{Manchester2014a} and provides a feedback law for system~\eqref{eq:general system} given a feedback law for system~\eqref{eq:general system:differential}.
 
 \begin{theorem}\label{prop:CCM Existence}
-	If there exists a control-contraction metric for system \eqref{eq:general system}, then a feedback law for system~\eqref{eq:general system} is obtained by integrating the feedback law for system~\eqref{eq:general system:differential} along geodesics.
+	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a differential feedback law for system~\eqref{eq:general system:differential} rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
+Moreover, a stabilizing feedback law for system~\eqref{eq:general system} is obtained by integrating the differential feedback law for system~\eqref{eq:general system:differential} along geodesics.
 \end{theorem}
@@
 
+Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
+	\begin{equation}\label{eq:differential feedback law}
+		\delta_k=Y(x,u)W^{-1}(x)\delta_x:=K(x,u)\delta_x
+	\end{equation}
+	is a differential feedback law that renders the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop with $\delta_k$.
+
 Step 2 (Online controller integration).
 The feedback law for system \eqref{eq:general system} can be obtained by integration as follows.
-Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system} and $K=YW^{-1}$, from Hopf-Rinow theorem (cf.
+Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf.
 \cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them.
@@
 \end{equation}
-where $s\in[0,1]$, is a feedback law for system \eqref{eq:general system}.
+where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.
 
@@
 	\begin{equation*}
-		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i),
+		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i)\;,
 	\end{equation*}
@@
 Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
-Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system}.
-
-	It remains to integrate $K\delta_x$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
+Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
+
+	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
 Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
 	\begin{equation}\label{eq:geodesic sum}
-		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds.
+		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds\;.
 	\end{equation}
@@
 	\begin{equation*}
-		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}.
+		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
 	\end{equation*}
@@
 	\begin{align*}
-		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i).
+		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i)\;.
 	\end{align*}
@@
 
-	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} is given by Equation \eqref{eq:contracting feedback law}.
+	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system~\eqref{eq:general system} is given by Equation~\eqref{eq:contracting feedback law}.
 
@@
 	\begin{equation}\label{eq:K ODE}
-		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast).
-	\end{equation}
-	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the smoothness of the functions $K$ and $\gamma$.
+		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast)\;.
+	\end{equation}
+	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$.
 It remains to show that this interval of existence can be extended on $[0,1]$.
-In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)\to\infty$, as $s\to\bar{s}$.
-
-	To show that a solution $k^\ast$ is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
+In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.
+
+	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
 This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
@@
 
-	Note that, due to the structure of the matrix $K$, the feedback law $k^\ast$ defined in Equation \eqref{eq:contracting feedback law} solves item 2 of Problem~\ref{problem formulation}, i.e., $k^\ast\in\Xi$.
-This concludes the proof of Theorem \ref{thm:main result}.
+	Note that, due to the structure of the matrix $K$, for each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$ defined by  Equation~\eqref{eq:contracting feedback law} is given by
+	\begin{equation*}
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\widetilde{\gamma}_i'(\sigma)\,d\sigma\;,
+	\end{equation*}
+	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
+
+	Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
 \end{proof}

### 2016-10-19 R0V0.tex
Finish proof of THeorem 2

@@
 
-In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}_i=\{x_i\}$.
+In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}(\mathscr{K}(i))=\{x_i\}$.
 
@@
 
-	Note that, due to the structure of the matrix $K$, for each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$ defined by  Equation~\eqref{eq:contracting feedback law} is given by
+	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
 	\begin{equation*}
@@
 	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
-
-	Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
+	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
 \end{proof}

### 2016-10-21 R0V0.tex
Start to change the example
Waiting for quality check of sets \mathscr{K} and \Xi
change header
Change abstract

@@
 % 																			   %
-% Git Branch: Master	 													   %
+% Git Branch: Manchester20161020											   %
 % 																			   %
@@
 In this paper, input-affine nonlinear systems are considered.
-The problem under consideration is the design of structured (for instance, decentralized or distributed) controllers for this class of systems.
-Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, the search for these functions is non-convex \cite{Rantzer:2001}.
-On the other hand, control-contraction metrics can provide controllers through a convex optimization problem.
-The drawback is that it may require the a function with $n^2$ elements.
-By exploiting sparsity, this number of verification can be decreased and the convex optimization problem can also be distributed.
+The problem is the design of structured (for instance, decentralized or distributed) controllers for this class of systems.
+Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, numerical methods employed to construct for these functions usually leads to a non-convex optimization problem.
+Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements.
+In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable topological (distributed) structures.
+By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
 An example illustrates the approach for a network system.
@@
 \section{Numerical Experiment}\label{sec:Illustration}
+
+\todo[inline]{Waiting for quality check of the definition of the sets $\mathscr{K}$ and $\Xi$.}
 
@@
 In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix).
+More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and for each $i$ $\mathbf{X}(\mathscr{K}(k))=\{x\}$.
 The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.

### 2016-10-21 R0V0.tex
Change introduction,
Definition 4

Start to change the notation of total derivative

@@
 
-The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has several states (large scale), it does not scale well.
+The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well.
 This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
@@
 Third, when the system is described a non-strongly connected graph, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability.
-Note that the proposed method provides an explicit formula for the controller, since it is constructive.
+Note that the proposed method provides an explicit algorithm to design the controller which makes this approach constructive.
 
@@
 Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.
-The notation $f'$ stands for the total derivative of $f$.
+The notation $\dot{f}$ stands for the total derivative of $f$.
 
@@
 where, for every positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively.
-The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and to satisfy $f(0)=0$ and $B(0)=0$.
+The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable.
 From now on the dependence on the time $t$ will be omitted.
@@
 
-A \emph{Riemannian metric} is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
+A \emph{Riemannian metric on $\mathbb{R}^n$} is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
 In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function.
-Consequently, local notions of norm $|\delta_0|_x=\sqrt{\langle\delta_0,\delta_0\rangle_x}$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined.
+Consequently, local notions of norm $|\delta_0|_x^2=\langle\delta_0,\delta_0\rangle_x=:V(x,\delta_0)$ and orthogonality $\langle\delta_0,\delta_1\rangle_x=0$ can be defined.
 The metric is said to be \emph{bounded} if there exists constant values $\underline{m}>0$ and $\overline{m}>0$ such that, for every $x\in\mathbb{R}^n$, $\underline{m}I_n\leq M(x)\leq \overline{m}I_n$, where $I_n\in\mathbb{R}^{n\times n}$ is the identity matrix.
+From now, metric stands for a bounded Riemannian metric.
 
@@
 
-Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTIS) (see \cite{Hespanha:2009} for more information on LTIS).
+Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTVS) (see \cite{Hespanha:2009} for more information on LTVS).
 
@@
 \begin{definition}\label{def:}
-		 A smooth function $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ is said to be a \emph{metric for system \eqref{eq:general system}} if there exist constant values $\underline{c}>$ and $\overline{c}>$ such that the inequality
-		 \begin{subequations}\label{eq:metric}
-		 \begin{equation}
-		 	\underline{c}|\delta_x|^2\leq V(x,\delta_x)\leq \overline{c}|\delta_x|^2\;,
-	 	 \end{equation}
-	 	 holds, for every $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
-Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively.
-A metric system \eqref{eq:general system} receives the adjective \emph{contraction} if there exists a value $\lambda>0$ such that the inequality
+		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if for fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively, there exists a value $\lambda>0$ such that the inequality
 	 	 \begin{equation}
@@
  	 	 \end{equation}
- 	 	 \end{subequations}
  	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
 \end{definition}
-Note that a bounded Riemannian metric defined, for every $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$, as $V(x,\delta_x)=|\delta_x|_x^2$ and satisfying the set of inequalities \eqref{eq:metric} is a contraction metric for system \eqref{eq:general system}.
-For brevity, from now the bounded Riemannian metric defined above will be called simply as \emph{metric}.
 
@@
 
-As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}.
+As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system~\eqref{eq:general system} are recalled below.
@@
 \begin{definition}\label{def:SSCCM}
-	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if $M$ has a block-diagonal structure. 
+	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if it can be decomposed into the following sum
+	\begin{equation*}
+		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
+	\end{equation*}
+	where, for each index $i\in\mathbb{N}_{[1,N]}$, and for every $(x_i,\delta_{x_i})\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$, the function $V_i(x_i,\delta_{x_i}):=\delta_{x_i}^\top M_i(x_i)\delta_{x_i}$ is a metric on $\mathbb{R}^{n_i}$.
 \end{definition}
 
-Definition~\ref{def:SSCCM} implies that there exist $N>1$ integers $n_i>0$ such that $n_1+\ldots+n_N=n$.
-Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
-	\begin{equation*}
-		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i)\;,
-	\end{equation*}
-for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.
-In other words, the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$.
+In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
 The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).

### 2016-10-21 R0V0.tex
Changes on the notation of the metric and the derivative of the geodesic

@@
 The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
-\begin{equation*}
-	\ell(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}\,ds\ \text{and}\ e(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}^2\,ds\;.
-\end{equation*}
+\begin{align*}
+	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
+	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;.
+\end{align*}
 The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them.
@@
 \begin{equation}\label{eq:contracting feedback law}
-	k^\ast(t,s)=u^\ast(t)+\int_0^s K(\gamma(\sigma),k^\ast(t,\sigma))\gamma'(\sigma)\,d\sigma\;,
+	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(s),k^\ast(t,s))\gamma_s(s)\,ds\;,
 \end{equation}
@@
 \begin{theorem}\label{thm:main result}
-	If there exist smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system:differential}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
@@
 	\begin{equation}\label{eq:geodesic sum}
-		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds\;.
+		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)}\,ds\;.
 	\end{equation}
@@
 	\begin{equation}\label{eq:K ODE}
-		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast)\;.
+		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma_s(s)=:\overline{K}(t,s,k^\ast)\;.
 	\end{equation}

### 2016-10-21 R0V0.tex
Changes on the proof of Theorem 2, regarding the minimization of the energy instead of the minimization of the length

@@
 	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
-Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
+Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
 	\begin{equation}\label{eq:geodesic sum}
-		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)}\,ds\;.
-	\end{equation}
-
-	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. More precisely, 
-	\begin{equation*}
-		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
-	\end{equation*}
-	Consequently, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
+		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
+	\end{equation}
+
+	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
+Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$.
+Consequently,
+	\begin{equation*}
+		\gamma_i=\arg\inf e(\varphi_i)\Leftrightarrow\gamma=\arg\inf\ell(\varphi),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+	\end{equation*}
+	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
 

### 2016-10-25 R0V0.tex
Minor changes on notation.
Change notation for the derivative of \gamma

@@
 
-A \emph{Riemannian metric on $\mathbb{R}^n$} is a positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
+A \emph{Riemannian metric on $\mathbb{R}^n$} is a symmetric positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
 In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function.
@@
 	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
-	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;.
+	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;,
 \end{align*}
+where the notation $\gamma_s$ stands for the derivative $\tfrac{\partial\gamma}{\partial s}$.
 The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them.
@@
 	\begin{equation}\label{eq:geodesic sum}
-		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
+		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\frac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
 	\end{equation}
@@
 	\begin{equation*}
-		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\widetilde{\gamma}_i'(\sigma)\,d\sigma\;,
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\frac{\partial\widetilde{\gamma}_i}{\partial \sigma}(\sigma)\,d\sigma\;,
 	\end{equation*}
@@
 
-Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015}.
-
-Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}.
+Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
+
+Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
+Let $k\in\mathbb{N}_{[1,N]}$ be a constant value and $\{1,\ldots,k\}$ be a path.
+A \emph{chord} of a path is any edge joining two nonconsecutive nodes.
+
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.

### 2016-10-28 R0V0.tex
Start to write about chordal graphs
Add concepts of tree, leaves and cycles

@@
 Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
+A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct.
 A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them.
 It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise.
+A graph is said to be a \emph{tree} if it is connected and does not contain cycles.
+A \emph{leaf} is a node that is adjacent to only one node.
 
@@
 Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
-Let $k\in\mathbb{N}_{[1,N]}$ be a constant value and $\{1,\ldots,k\}$ be a path.
+A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
 A \emph{chord} of a path is any edge joining two nonconsecutive nodes.
-
-A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
+A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
+The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005}.
 

### 2016-10-28 R0V0.tex
Edit section about distributed synthesis

@@
 A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
-The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005}.
+The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.
 
 \begin{proposition}\label{prop:}
-	Let $p\in\mathbb{N}_{>0}$ be the number of cliques of the graph $\mathscr{G}$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
+	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
+Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
 \end{proposition}
@@
 \begin{proof}
+\todo[inline]{Continue with the proof}
+
 	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}.

### 2016-10-31 R0V0.tex
Formalized first paragraph of the section and review theorem statement and proof

@@
 \begin{proof}
-\todo[inline]{Continue with the proof}
-
-	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}.
+	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$.
+Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$.
 The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.
 
-	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
+	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
 For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
@@
 \end{proof}
+
+Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph.
+The obtained graph is said to be a \emph{chordal embedding}.
+The above procedure can be applied for the chordal embedded graphs.
 

### 2016-10-31 R0V0.tex
Start to write about diagonal dominance and the search for appropriate basis

@@
 
+Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation.
+There is no reason for the dimension of these components (matrices) to be small enough.
+However, by employing an appropriate choice of the basis, the dimension of the matrix can be smaller \cite{AhmadiHall2016}.
+
 \subsection{Discussion}

### 2016-10-31 R0V0.tex
Add cholesky factor definition on notation

--- 2016-10-31 R0V0.tex
@@
 
+% *** ALGORITHM PACKAGES ***
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
 % correct bad hyphenation here
@@
 semi)definite.
+For a matrix $M\succ0$, the notation $\mathbin{\mathtt{chol}}(M)$ stands for the \emph{upper-triangular Cholesky factor $U$} satisfying $A=U^\top U$.
 
@@
 
-Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel.
-The next section provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$.
-Before presenting it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.
+Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
+The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.
 
@@
 
-Before showing how the MI \eqref{eq:MI formulation} can be computed in parallel, some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
+For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}.
+This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
+For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done parallel.
+To this end some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
 
@@
 A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
-The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.
+The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.
 
@@
 The above procedure can be applied for the chordal embedded graphs.
+
+Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation.
+These components (matrices) may still have a large dimension.
+However, by employing an appropriate choice for the basis of squared polynomials, the dimension of the matrix can be smaller \cite{AhmadiHall2016}.
+To that end, the following class of matrices is recalled from \cite{AhmadiHall2016}.
+
+\begin{definition}\label{def:}
+	a
+\end{definition}
+
+\begin{algorithm}
+        \caption{Some alg}
+        \begin{algorithmic}[1]	
+            \REQUIRE $U_0=I$
+            \STATE d = a + b + c
+            \STATE d = d/2
+            \STATE d = d/3
+            \RETURN d
+        \end{algorithmic}
+    \end{algorithm}
 

### 2016-10-31 R0V0.tex
small changes. Add todo

@@
 
+\todo[inline]{Scalable diagonal dominance}
+
 Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation.
@@
 
-\begin{definition}\label{def:}
-	a
+\begin{definition}
+	A matrix $M\in\mathbb{R}^{n\times n}$ is said to be \emph{diagonally dominant} if, for every index $i\in\mathbb{N}_{[1,n]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^n |a_{ij}|$ holds.
+It is said to be \emph{scalable diagonally dominant} if there exists a diagonal matrix $D$ such that $DAD$ is diagonally dominant.
 \end{definition}

### 2016-11-01 R0V0.tex
Improve the part regarding the scalable diagonal optimization. What I need to show is that, if F is sdd than the algorithm provides a basis of monomials to show that F is negative definite

--- 2016-10-31 R0V0.tex
@@
 
-\begin{proposition}\label{prop:}
+\begin{proposition}\label{prop:clique tree decomposition}
 	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
@@
   	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
-  	\begin{equation*}
+  	\begin{equation}\label{eq:MIF}
   		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
-	\end{equation*}
+	\end{equation}
 	This concludes the proof.
@@
 
-Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation.
-These components (matrices) may still have a large dimension.
-However, by employing an appropriate choice for the basis of squared polynomials, the dimension of the matrix can be smaller \cite{AhmadiHall2016}.
-To that end, the following class of matrices is recalled from \cite{AhmadiHall2016}.
-
-\begin{definition}\label{def:}
-	a
+\todo[inline]{Scalable diagonal dominance}
+
+Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
+The negative definiteness of the $F$ can be shown using sum-of-squares optimization.
+To this end, a vector of monomials $z$ such that $-z^\top F z>0$ need to be found.
+This the objective of the remainder of this section.
+
+\begin{definition}\label{def:SDD}
+	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^h |a_{ij}|$ holds.
+It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
 \end{definition}
+
+The set of dd (resp.
+sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD$ (resp.
+$SDD$).
+Let $z$ be a vector of all monomials on the variable $x$ of degree exactly $d$.
+
+\begin{definition}\label{def:sdsos}
+	A form $p:\mathbb{R}^h\to\mathbb{R}_{\geq0}$ is said to be a (resp.
+\emph{scaled-})\emph{diagonally-dominant-sum-of-squares} (dsos) (resp.
+(sdsos)) if there exists a (resp.
+scalable) diagonally dominant matrix $D$ such that $p=z^\top Dz$.
+\end{definition}
+
+Consider the class of polynomials $p$ defined by $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)=\{p:p = zU^\top DUz, \text{ for some sdd matrix } D\}$.
+The feasibility verification of the MI~\ref{eq:MI formulation} over $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)$
 

### 2016-11-02 R0V0.tex
Further modifications on the scalable diagonal matrices

@@
 Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
-The negative definiteness of the $F$ can be shown using sum-of-squares optimization.
-To this end, a vector of monomials $z$ such that $-z^\top F z>0$ need to be found.
-This the objective of the remainder of this section.
+If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using a the optimization method proposed in \cite{AhmadiHall2016}.
 
@@
 	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^h |a_{ij}|$ holds.
-It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
+It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
 \end{definition}
@@
 The set of dd (resp.
-sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD$ (resp.
-$SDD$).
-Let $z$ be a vector of all monomials on the variable $x$ of degree exactly $d$.
-
-\begin{definition}\label{def:sdsos}
-	A form $p:\mathbb{R}^h\to\mathbb{R}_{\geq0}$ is said to be a (resp.
-\emph{scaled-})\emph{diagonally-dominant-sum-of-squares} (dsos) (resp.
-(sdsos)) if there exists a (resp.
-scalable) diagonally dominant matrix $D$ such that $p=z^\top Dz$.
-\end{definition}
-
-Consider the class of polynomials $p$ defined by $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)=\{p:p = zU^\top DUz, \text{ for some sdd matrix } D\}$.
-The feasibility verification of the MI~\ref{eq:MI formulation} over $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)$
+sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD_h$ (resp.
+$SDD_h$).
+Denote the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$, i.e.,
+\begin{subequations}
+		\begin{equation}\label{eq:}
+			\mathbf{DD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in DD_h\}
+		\end{equation}
+		\begin{equation}\label{eq:}
+			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in SDD_h\}
+		\end{equation}
+\end{subequations}
+
+The MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
+\begin{subequations}
+\begin{equation}\label{eq:DSOS}
+\begin{array}{rl}
+SDSOS_l:=\underset{}{\min} & t \\
+\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)\;,
+\end{array}
+\end{equation}
+which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
+\begin{equation}
+\begin{array}{rcl}
+	U_0&=&\ I_h\\
+	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
+\end{array}
+\end{equation}
+\end{subequations}
+
+As shown in \cite{AhmadiHall2016} if there exists a solution to \eqref{eq:DSOS} with $l=0$, then
 

### 2016-11-07 R0V0.tex
Erased the diagonal dominant class of matrices. Investigate weak coupling for diagonal dominant matrices.

@@
 Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
-If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using a the optimization method proposed in \cite{AhmadiHall2016}.
+If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
 
@@
 
-The set of dd (resp.
-sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD_h$ (resp.
-$SDD_h$).
-Denote the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$, i.e.,
-\begin{subequations}
-		\begin{equation}\label{eq:}
-			\mathbf{DD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in DD_h\}
-		\end{equation}
+The set of scalable diagonally dominant matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $SDD_h$. Let
 		\begin{equation}\label{eq:}
@@
 		\end{equation}
-\end{subequations}
-
-The MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
+be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$. If the MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
 \begin{subequations}

### 2016-11-08 R0V0.tex
Change notation of the curves from \gamma to c.
Write a small paragraph on how the energy function is a CLF.

Write a paragraph about SDD matrices

@@
 
-Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$.
-The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
+Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $c:[0,1]\to\mathbb{R}^n$ connecting $x_0=c(0)$ to $x_1=c(1)$.
+The \emph{length} and \emph{energy} of $c$ are, respectively, defined by the values
 \begin{align*}
-	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
-	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;,
+	\ell(\gamma)=&\ \int_0^1\left|c_s(s)\right|_{c(s)}\,ds\\
+	e(\gamma)=&\ \int_0^1V\left(c(s),c_s(s)\right)\,ds\;,
 \end{align*}
-where the notation $\gamma_s$ stands for the derivative $\tfrac{\partial\gamma}{\partial s}$.
+where the notation $c_s$ stands for the derivative $\tfrac{\partial c}{\partial s}$.
 The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them.
@@
 \begin{equation}\label{eq:geodesic formulation}
-	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
+	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{c\in\Gamma(x_0,x_1)}\ell(c)\;.
 \end{equation}
@@
 Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf.
-\cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them.
+\cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them.
 This implies that the solution $k^\ast$ to the integral equation
 \begin{equation}\label{eq:contracting feedback law}
-	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(s),k^\ast(t,s))\gamma_s(s)\,ds\;,
+	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)\,ds\;,
 \end{equation}
@@
 	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
-Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
+Because $M$ is a block-diagonal matrix, the energy of any curve $c:[0,1]\to\mathbb{R}^n$ satisfies the following equation
 	\begin{equation}\label{eq:geodesic sum}
-		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\frac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
+		e(c)=\int_0^1\sum_{i=1}^N V_i\left(c_i(s_i),\frac{\partial c_i}{\partial s_i}(s_i)\right)\,ds\;.
 	\end{equation}
@@
 	\begin{equation*}
-		\gamma_i=\arg\inf e(\varphi_i)\Leftrightarrow\gamma=\arg\inf\ell(\varphi),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+		\gamma_i=\arg\inf e(c_i)\Leftrightarrow\gamma=\arg\inf\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
 	\end{equation*}
@@
 	\begin{align*}
-		\gamma_i=\arg\inf_{\varphi_i\in\Gamma(x_i^\ast,x_i)} e(\varphi_i)\;.
+		\gamma_i=\arg\inf_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
 	\end{align*}
@@
 	\begin{equation}\label{eq:K ODE}
-		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma_s(s)=:\overline{K}(t,s,k^\ast)\;.
+		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
 	\end{equation}
@@
 	\begin{equation*}
-		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\frac{\partial\widetilde{\gamma}_i}{\partial \sigma}(\sigma)\,d\sigma\;,
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
 	\end{equation*}
@@
 
-Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
+Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} which can be employed to design a distributed controller for system~\eqref{eq:general system}.
+
+Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
 The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.
@@
 
-\todo[inline]{Scalable diagonal dominance}
-
 Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
-If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
+If the search for the matrix $F$ is restricted to have some structure on the diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
 
 \begin{definition}\label{def:SDD}
-	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^h |a_{ij}|$ holds.
+	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds.
 It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
@@
 
-The set of scalable diagonally dominant matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $SDD_h$. Let
-		\begin{equation}\label{eq:}
-			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in SDD_h\}
-		\end{equation}
-be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$. If the MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
+The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
+		\begin{align*}
+			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=U^\top DU,\\
+			 D\in SDD_h\}
+		\end{align*}
+be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$.
+
+Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be cast into the following programming
 \begin{subequations}
@@
 \begin{array}{rl}
-SDSOS_l:=\underset{}{\min} & t \\
-\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)\;,
+SDSOS_l:=\underset{}{\min} & t^2 \\
+\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)
 \end{array}
@@
 \end{subequations}
-
-As shown in \cite{AhmadiHall2016} if there exists a solution to \eqref{eq:DSOS} with $l=0$, then
-
-\begin{algorithm}
-        \caption{Some alg}
-        \begin{algorithmic}[1]	
-            \REQUIRE $U_0=I$
-            \STATE d = a + b + c
-            \STATE d = d/2
-            \STATE d = d/3
-            \RETURN d
-        \end{algorithmic}
-    \end{algorithm}
+Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.
 

### 2016-11-08 R0V0.tex
Added condition to upload to arXiv

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\pdfoutput=1 % to upload to arXiv with the hyperref package
 
@@
 
-\usepackage{hyperref}% backref linktocpage pagebackref
+\usepackage[hyperindex,breaklinks]{hyperref}% backref linktocpage pagebackref
 %
@@
 plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,
-hypertexnames=true, pdfhighlight=/O, urlcolor=red!50!black, linkcolor=blue!75!black, citecolor=green!50!black,
+hypertexnames=true, pdfhighlight=/O, urlcolor=red!50!black, linkcolor=green!50!black, citecolor=green!50!black,
 %

### 2016-11-08 R0V0.tex
Start to change the example to take into account the changes on the set \Xi

@@
 \begin{equation*}
-N^2\begin{pmatrix}
+N\dfrac{N+1}{2}\begin{pmatrix}
 n+d\\ d
@@
 
-In all cases, the matrix $W$ was required to have a block-diagonal structure as follows
+In all cases, the computed matrix $W$ has a block-diagonal structure as follows
 \begin{equation*}
@@
 
-In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix).
-More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and for each $i$ $\mathbf{X}(\mathscr{K}(k))=\{x\}$.
+In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
+More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$.
 The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.
@@
 
-For the remaining cases, the constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
+For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}.
+More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.
+
+The constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
 \begin{equation*}
@@
 \end{equation*}
-This implies that sparsity can be exploited to decrease the number of equations needed to verify the MI \eqref{eq:MI formulation}.
 
@@
 The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
+
+\todo[inline]{From here}
+
+For each $j\in\mathbb{N}$, $\mathbf{C}_j$
+
 Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).

### 2016-11-09 R0V0.tex
Remove the need for the definition of SDD matrices. Add condition for the vector fields to be polynomials

@@
 Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
-If the search for the matrix $F$ is restricted to have some structure on the diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
-
-\begin{definition}\label{def:SDD}
+If the vector fields $f$ and $B$ are polynomials and the search for the matrix $F$ is restricted to have appropriate diagonal structure, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
+
 A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds.
 It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
-\end{definition}
 
@@
 
-Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be cast into the following programming
+Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
 \begin{subequations}
 \begin{equation}\label{eq:DSOS}
-\begin{array}{rl}
-SDSOS_l:=\underset{}{\min} & t^2 \\
-\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)
+\begin{array}{rcl}
+-F_l&\in&\mathbf{SDD}(U_l)\;,
 \end{array}
 \end{equation}
-which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
+where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
 \begin{equation}
@@
 \end{equation*}
-equations to be solved. This motivates the approach proposed in this paper.
+monomials to be computed. This motivates the approach proposed in this paper.
 
@@
 The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
+The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
+\begin{equation*}
+	\begin{array}{rcl}
+		\mathbf{C}_1=\mathbf{C}_2=\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top
+	\end{array} 
+\end{equation*}
 
@@
 
-For each $j\in\mathbb{N}$, $\mathbf{C}_j$
+For each
 

### 2016-11-09 R0V0.tex
Rewrite the neighbor case in the example

@@
 \begin{equation*}
-	\begin{array}{rcl}
-		\mathbf{C}_1=\mathbf{C}_2=\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top
+	\begin{array}{rl}
+		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}1, 1, 1, 0\end{bmatrix}^\top\right\},\\
+		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0, 1, 1, 1\end{bmatrix}^\top\right\},&		    \mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0, 0, 1, 1\end{bmatrix}^\top\right\}\;.
 	\end{array} 
@@
 
-\todo[inline]{From here}
-
-For each
-
-Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).
+The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.
 

### 2016-11-09 R0V0.tex
Remove the paragraph explaining the notation of the set Xi for the fully decentralized case. Start to explain the decomposition of the MI (8) into cliques.
Finish explaining clique decomposition. Start to change decentralized case in example.

@@
 
-In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}(\mathscr{K}(i))=\{x_i\}$.
-
 \begin{theorem}\label{thm:main result}
@@
 More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.
-
-The constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
-\begin{equation*}
-	\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
-		T_{11}&T_{12}\\
-		T_{12}^\top&T_{22}
-	\end{bmatrix},\cdots,\begin{bmatrix}
-		T_{(N-1)(N-1)}&T_{(N-1)N}\\
-		T_{(N-1)N}^\top&T_{NN}
-	\end{bmatrix}\right).
+Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into $N-1$ cliques  described by the matrix
+\begin{equation*}
+	F_k=\begin{bmatrix}
+		F_{11}&F_{12}\\
+		F_{12}^\top&F_{22}
+	\end{bmatrix}\;.
 \end{equation*}
@@
 
-In the last case, the fully decentralized scenario has been considered.
-The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 2.6 seconds.
-In this case, $\mathscr{K}_Y(i)=\{j\in\mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}$, where $\mathscr{K}(i)=\{i\}$.
+In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(i)=\{i\}$, 
+\begin{equation*}
+	\begin{array}{rl}
+		\mathbf{C}_1=\mathbf{C}_2=\{e_1\},&\mathbf{C}_3=\mathbf{C}_4=\{e_2\},\\
+		\mathbf{C}_5=\mathbf{C}_6=\{e_3\},&\mathbf{C}_7=\mathbf{C}_8=\{e_4\}
+	\end{array}
+\end{equation*}
 Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained

### 2016-11-11 R0V0.tex
Start to work on ADMM

@@
 
+The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in parallel \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
+To use this framework, define the sets $\mathbf{Y}^n=\{Y\in\mathbb{R}^{m\times n}\}$, $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{(W_1,\ldots,W_N,Y)\in \mathbb{R}^{n_i\times n_i}\times \mathbb{R}^{m\times n}:\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),T\prec0\}$.
+For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
+\begin{equation*}
+	H(\mathbf{G},g)=\begin{cases}
+									0,&g\in \mathbf{G}\\
+									\infty,&\text{Otherwise.}
+								\end{cases}
+\end{equation*}
+
+The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
+\begin{equation*}
+	\begin{array}{rl}
+		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N,Z_{N+1}))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
+		\text{subject to}&W_i-Z_i=0,\quad \forall i\in\mathbb{N}_{[1,N]}\\
+		&Y-Z_{N+1}=0
+	\end{array}
+\end{equation*}
+
 \subsection{Discussion}
@@
 \section{Numerical Experiment}\label{sec:Illustration}
-
-\todo[inline]{Waiting for quality check of the definition of the sets $\mathscr{K}$ and $\Xi$.}
 
@@
 \begin{equation*}
- W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),
+ W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right)\;.
 \end{equation*}
@@
 \begin{align*}
- \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
- \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
+ \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\;,\\
+ \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2\;.
 \end{align*}
@@
 \begin{align*}
-	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\\	
-	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\\	
-	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\\	
-	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)
+	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\;,\\	
+	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\;,\\	
+	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\;,\\	
+	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)\;.
 \end{align*}
@@
 
-In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(i)=\{i\}$, 
+In the last case, the fully decentralized scenario has been considered.
+The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds.
+In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$.
+Moreover,
 \begin{equation*}
 	\begin{array}{rl}
-		\mathbf{C}_1=\mathbf{C}_2=\{e_1\},&\mathbf{C}_3=\mathbf{C}_4=\{e_2\},\\
-		\mathbf{C}_5=\mathbf{C}_6=\{e_3\},&\mathbf{C}_7=\mathbf{C}_8=\{e_4\}
+		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
+		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
 	\end{array}
@@
  W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
- Y=&\mathbin{\mathtt{diag}}\left(Y_1,Y_2,Y_3,Y_4\right)
+ Y=&\begin{bmatrix}
+ 	Y_{11}&Y_{12}&0&0&0&0&0&0\\
+ 	0&0&Y_{23}&Y_{24}&0&0&0&0\\
+ 	0&0&0&0&Y_{35}&Y_{36}&0&0\\
+ 	0&0&0&0&0&0&Y_{47}&Y_{48}
+ \end{bmatrix}
 \end{align*}
@@
 \end{equation*}
-and, for each index $i=1,4$,
+and
 \begin{align*}
- Y_i(q_i)=[-3.1y_i+0.06x_iy_i,-3.6-0.02x_i-2.3y_i^2-2.4x_i^2]
-\end{align*}
-and, for each index $i=2,3$,
-\begin{align*}
- Y_i(q_i)=[-3.1y_i,-3.8-2.1y_i^2-2.2x_i^2].
+ Y_{11}(q_i)=Y_{47}(q_i)=&\ -3.1y_i+0.06x_iy_i\;,\\
+ Y_{12}(q_i)=Y_{48}(q_i)=&\ -3.6-0.02x_i-2.3y_i^2-2.4x_i^2\;,\\
+ Y_{23}(q_i)=Y_{35}(q_i)=&\ -3.1y_i\;,\\
+ Y_{24}(q_i)=Y_{26}(q_i)=&\ -3.8-2.1y_i^2-2.2x_i^2\;.
 \end{align*}

### 2016-11-14 R0V0.tex
Add the single system expression and expand the paragraph on CLFs. Continue with ADMM formulation.

@@
 
+Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
+\begin{equation}\label{eq:subsystem}
+	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
+\end{equation}
+where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
+
 At this point, the problem under consideration in this paper can be stated as follows.
@@
 Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively.
-If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
+If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta_u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
 The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.
@@
 	 	 \begin{equation}
-	 	 	\frac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta x,u,\delta u))\leq -\lambda V(x,\delta_x)
+	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,u,\delta_u))\leq -\lambda V(x,\delta_x)
  	 	 \end{equation}
@@
 
-Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} which can be employed to design a distributed controller for system~\eqref{eq:general system}.
+Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} that can be employed to design a distributed controller for system~\eqref{eq:general system}.
+More precisely, from the first variation of the energy function, the time derivative of $e$ yields the equation
+\begin{align}
+	\dfrac{1}{2}De^+(X^\ast,X)=\langle \gamma_s(t,0),\dot{X}^\ast\rangle_{X^\ast}-\langle \gamma_s(t,1),f(x)\rangle_{X}\nonumber\\
+	-\langle \gamma_s(t,1),B(x)u\rangle_{X}\,\label{eq:CLF derivative}
+\end{align}
+where $De^+$ stands for the Dini's upper right-hand time derivative of the energy $e$ along the solutions $X$ and $X^\ast$.
+A distributed controller can be obtained by finding the appropriate feedback law for system~\eqref{eq:general system} rendering \eqref{eq:CLF derivative} negative definite.
+This can be achieved by noticing that \eqref{eq:CLF derivative} is the sum of $N$ terms of the form
+\begin{align*}
+	\tfrac{\partial \gamma_i}{\partial s_i}(t,0)M_i(X_i^\ast)X_i^\ast-\tfrac{\partial \gamma_i}{\partial s_i}(t,1)M_i(X_i)f_i(X_i,\breve{X}_i)\\
+	-\tfrac{\partial \gamma_i}{\partial s_i}(t,1)M_i(X_i)B_i(X_i)u_i\;.
+\end{align*}
 
@@
 
-The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in parallel \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
-To use this framework, define the sets $\mathbf{Y}^n=\{Y\in\mathbb{R}^{m\times n}\}$, $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{(W_1,\ldots,W_N,Y)\in \mathbb{R}^{n_i\times n_i}\times \mathbb{R}^{m\times n}:\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),T\prec0\}$.
+The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
+To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{Z\in D^{n\times n}:\exists Y\in\mathbb{R}^{m\times n}, T\prec0\}$.
 For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
@@
 	\begin{array}{rl}
-		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N,Z_{N+1}))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
-		\text{subject to}&W_i-Z_i=0,\quad \forall i\in\mathbb{N}_{[1,N]}\\
-		&Y-Z_{N+1}=0
+		\text{minimize}&\displaystyle H(\mathbf{T},Z)+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
+		\text{subject to}&\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)-Z=0\;.
+	\end{array}
+\end{equation*}
+The ADMM algorithm can be written as
+\begin{equation*}
+	\begin{array}{rl}
+		W_i^{k+1}:=&\mathbin{\mathtt{argmin}}_{W_i}\left(H(\mathbf{S}_{\succ0}^{n_i},W_i))\right)
 	\end{array}

### 2016-11-15 R0V0.tex
Finish ADMM paragraph

@@
 
-The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
-To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{Z\in D^{n\times n}:\exists Y\in\mathbb{R}^{m\times n}, T\prec0\}$.
+The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
+To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{W_1,\ldots,W_N:\exists Y\in\Xi,(\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),Y)\text{ is a solution to \eqref{eq:MI formulation}}\}$.
 For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
@@
 	\begin{array}{rl}
-		\text{minimize}&\displaystyle H(\mathbf{T},Z)+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
-		\text{subject to}&\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)-Z=0\;.
+		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
+		\text{subject to}&W_i-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;.
 	\end{array}
@@
 The ADMM algorithm can be written as
-\begin{equation*}
-	\begin{array}{rl}
-		W_i^{k+1}:=&\mathbin{\mathtt{argmin}}_{W_i}\left(H(\mathbf{S}_{\succ0}^{n_i},W_i))\right)
+\begin{enumerate}
+	\item For each $i\in\mathbb{N}_{[1,N]}$, update the matrix $W_i$ as follows.
+	\begin{equation*}
+	\begin{array}{rcl}
+		W_i^{k+1}&=&\mathbin{\mathtt{argmin}}_{W_i\in\mathbf{S}_{\succ0}^{n_i}}\left|\left|W_i^k-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
 	\end{array}
 \end{equation*}
+	where $||\cdot||_F$ stands for the Frobenius norm;
+
+	\item If the matrices $W_1,\ldots,W_N$ belong to $T$, then a solution has been found and the algorithm can be stopped. Otherwise, solve the global problem
+	\begin{equation*}
+		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|W_i^{k+1}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;;
+	\end{equation*}
+	\item Update $\Lambda$ and return to step 1
+	\begin{equation*}
+		\Lambda_i^{k+1}=X_i^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
+	\end{equation*}
+\end{enumerate}
+Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $W_i$ and the values $\Lambda_i$.
 

### 2016-11-15 TheoreticalExample2/ADMM.m
[ADMM.m] Add new file

@@ -1,0 +1,8 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Author: Humberto Stein Shiromoto                                        %
+% Title: ADMM                                                             %
+% Git Branch: master                                                      %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+

### 2016-11-15 TheoreticalExample1FinalVersion/PostProcessedWandDW.m
[*.m] Remove Older Versions

@@ -1,115 +1,0 @@
-% Rewriting the matrix W
-VerifiedW11 = clean(replace(W(1,1), coefList, double(coefList)), 0.001);
-W11 = sdisplay(VerifiedW11);
-
-VerifiedW12 = clean(replace(W(1,2), coefList, double(coefList)), 0.001);
-W12 = sdisplay(VerifiedW12);
-
-VerifiedW13 = clean(replace(W(1,3), coefList, double(coefList)), 0.001);
-W13 = sdisplay(VerifiedW13);
-
-VerifiedW14 = clean(replace(W(1,4), coefList, double(coefList)), 0.001);
-W14 = sdisplay(VerifiedW14);
-
-VerifiedW15 = clean(replace(W(1,5), coefList, double(coefList)), 0.001);
-W15 = sdisplay(VerifiedW15);
-
-VerifiedW16 = clean(replace(W(1,6), coefList, double(coefList)), 0.001);
-W16 = sdisplay(VerifiedW16);
-
-VerifiedW21 = clean(replace(W(2,1), coefList, double(coefList)), 0.001);
-W21 = sdisplay(VerifiedW21);
-
-VerifiedW22 = clean(replace(W(2,2), coefList, double(coefList)), 0.001);
-W22 = sdisplay(VerifiedW22);
-
-VerifiedW23 = clean(replace(W(2,3), coefList, double(coefList)), 0.001);
-W23 = sdisplay(VerifiedW23);
-
-VerifiedW24 = clean(replace(W(2,4), coefList, double(coefList)), 0.001);
-W24 = sdisplay(VerifiedW24);
-
-VerifiedW25 = clean(replace(W(2,5), coefList, double(coefList)), 0.001);
-W25 = sdisplay(VerifiedW25);
-
-VerifiedW26 = clean(replace(W(2,6), coefList, double(coefList)), 0.001);
-W26 = sdisplay(VerifiedW26);
-
-VerifiedW31 = clean(replace(W(3,1), coefList, double(coefList)), 0.001);
-W31 = sdisplay(VerifiedW31);
-
-VerifiedW32 = clean(replace(W(3,2), coefList, double(coefList)), 0.001);
-W32 = sdisplay(VerifiedW32);
-
-VerifiedW33 = clean(replace(W(3,3), coefList, double(coefList)), 0.001);
-W33 = sdisplay(VerifiedW33);
-
[…]

### 2016-11-15 TheoreticalExample1FinalVersion/PostProcessingW.m

@@ -1,51 +1,0 @@
-function PostProcessingW(NumberOfAgents,SystemDimension,prec,Option)
-
-fid = fopen('PostProcessedW.m','w');
-
-SysDim = SystemDimension;
-
-fprintf(fid, '%% Rewriting the matrix W\n');
-
-for nr = 1:NumberOfAgents*SysDim
-    
-    for nc = 1:NumberOfAgents*SysDim
-        
-        fprintf(fid, 'VerifiedW%s%s = ', num2str(nr),num2str(nc));
-        fprintf(fid, 'clean(replace(W(%s,%s), coefList, double(coefList)), %s);\n', num2str(nr),num2str(nc),num2str(prec));
-        fprintf(fid, 'W%s%s = ', num2str(nr),num2str(nc));
-        fprintf(fid, 'sdisplay(VerifiedW%s%s);\n\n', num2str(nr),num2str(nc));
-        
-        
-    end
-end
-
-
-fprintf(fid, 'W = [');
-
-for nr = 1:NumberOfAgents*SysDim
-    
-    for nc = 1:NumberOfAgents*SysDim
-        
-             if nc == NumberOfAgents*SysDim && nr == NumberOfAgents*SysDim
-                 
-                 fprintf(fid, 'W%s%s];\n', num2str(nr),num2str(nc));
-                 
-             elseif nc == NumberOfAgents*SysDim
-            
-                 fprintf(fid, 'W%s%s;\n', num2str(nr),num2str(nc));
-                 fprintf(fid, '     ');
-                 
-             else
-                 
-                 fprintf(fid, 'W%s%s, ', num2str(nr),num2str(nc));
-                 
-             end
-            
-        
-    end
-end
-
-fclose(fid);
-    
-
-end

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessedSys.m

@@ -1,45 +1,0 @@
-x1 = sdpvar(1);
-x2 = sdpvar(1);
-x3 = sdpvar(1);
-
-y1 = sdpvar(1);
-y2 = sdpvar(1);
-y3 = sdpvar(1);
-
-u1 = sdpvar(1);
-u2 = sdpvar(1);
-u3 = sdpvar(1);
-u = [u1; u2; u3]; 
-
-q1 = [x1;y1];
-q2 = [x2;y2];
-q3 = [x3;y3];
-
-q = [q1; q2; q3];
- 
-x1dot = -x1 - x1^3 + y1^2 -0.010000*(+1*x1^3 -1*x2^3 +0*x3^3);
-x2dot = -x2 - x2^3 + y2^2 -0.010000*(-1*x1^3 +2*x2^3 -1*x3^3);
-x3dot = -x3 - x3^3 + y3^2 -0.010000*(+0*x1^3 -1*x2^3 +1*x3^3);
-
-y1dot = u1;
-y2dot = u2;
-y3dot = u3;
-
-f1 = [x1dot;y1dot];
-f2 = [x2dot;y2dot];
-f3 = [x3dot;y3dot];
-f = [f1; f2; f3]; 
-
-A11 = jacobian(f1,q1);
-A12 = jacobian(f1,q2);
-B1  = jacobian(f1,u1);
-
-A21 = jacobian(f2,q1);
-A22 = jacobian(f2,q2);
-A23 = jacobian(f2,q3);
-B2  = jacobian(f2,u2);
-
-A32 = jacobian(f3,q2);
-A33 = jacobian(f3,q3);
-B3  = jacobian(f3,u3);
-

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessedW.m

@@ -1,58 +1,0 @@
-% Creation of W1 and DW1
-[Wp111,Wc111,Wv111] = polynomial(q1,2.000000,0);
-[Wp112,Wc112,Wv112] = polynomial(q1,2.000000,0);
-[Wp122,Wc122,Wv122] = polynomial(q1,2.000000,0);
-% Creation of W1
-W1 = [Wp111, Wp112;
-      Wp112, Wp122];
-
-Wc1 = [Wc111;Wc112;Wc122];
-Wp1 = [Wp111;Wp112;Wp122];
-
-% Creation of DW1
-DWTemp = jacobian(Wp1,q1);
-DW1 = [DWTemp(1,:)/2*f1, DWTemp(2,:)*f1;
-       0,                DWTemp(3,:)/2*f1];
-DW1 = DW1 + transpose(DW1);
-
-
-% Creation of W2 and DW2
-[Wp211,Wc211,Wv211] = polynomial(q2,2.000000,0);
-[Wp212,Wc212,Wv212] = polynomial(q2,2.000000,0);
-[Wp222,Wc222,Wv222] = polynomial(q2,2.000000,0);
-% Creation of W2
-W2 = [Wp211, Wp212;
-      Wp212, Wp222];
-
-Wc2 = [Wc211;Wc212;Wc222];
-Wp2 = [Wp211;Wp212;Wp222];
-
-% Creation of DW2
-DWTemp = jacobian(Wp2,q2);
-DW2 = [DWTemp(1,:)/2*f2, DWTemp(2,:)*f2;
-       0,                DWTemp(3,:)/2*f2];
-DW2 = DW2 + transpose(DW2);
-
-
-% Creation of W3 and DW3
-[Wp311,Wc311,Wv311] = polynomial(q3,2.000000,0);
-[Wp312,Wc312,Wv312] = polynomial(q3,2.000000,0);
-[Wp322,Wc322,Wv322] = polynomial(q3,2.000000,0);
-% Creation of W3
-W3 = [Wp311, Wp312;
-      Wp312, Wp322];
-
-Wc3 = [Wc311;Wc312;Wc322];
-Wp3 = [Wp311;Wp312;Wp322];
-
-% Creation of DW3
-DWTemp = jacobian(Wp3,q3);
-DW3 = [DWTemp(1,:)/2*f3, DWTemp(2,:)*f3;
-       0,                DWTemp(3,:)/2*f3];
[…]

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessedY.m

@@ -1,38 +1,0 @@
-
- % Creation of Variable Y1
-
-[Y11,Yc11,Yv11] = polynomial(q,Ydegree,0);
-[Y12,Yc12,Yv12] = polynomial(q,Ydegree,0);
-[Y13,Yc13,Yv13] = polynomial(q,Ydegree,0);
-[Y14,Yc14,Yv14] = polynomial(q,Ydegree,0);
-[Y15,Yc15,Yv15] = polynomial(q,Ydegree,0);
-[Y16,Yc16,Yv16] = polynomial(q,Ydegree,0);
-
- % Creation of Variable Y2
-
-[Y21,Yc21,Yv21] = polynomial(q,Ydegree,0);
-[Y22,Yc22,Yv22] = polynomial(q,Ydegree,0);
-[Y23,Yc23,Yv23] = polynomial(q,Ydegree,0);
-[Y24,Yc24,Yv24] = polynomial(q,Ydegree,0);
-[Y25,Yc25,Yv25] = polynomial(q,Ydegree,0);
-[Y26,Yc26,Yv26] = polynomial(q,Ydegree,0);
-
- % Creation of Variable Y3
-
-[Y31,Yc31,Yv31] = polynomial(q,Ydegree,0);
-[Y32,Yc32,Yv32] = polynomial(q,Ydegree,0);
-[Y33,Yc33,Yv33] = polynomial(q,Ydegree,0);
-[Y34,Yc34,Yv34] = polynomial(q,Ydegree,0);
-[Y35,Yc35,Yv35] = polynomial(q,Ydegree,0);
-[Y36,Yc36,Yv36] = polynomial(q,Ydegree,0);
-
- % Creation of Vector Yc
-
-
-Yc = [Yc11; Yc12; Yc13; Yc14; Yc15; Yc16; Yc21; Yc22; Yc23; Yc24; Yc25; Yc26; Yc31; Yc32; Yc33; Yc34; Yc35; Yc36];
- % Creation of Matrix Y
-
-
-Y = [Y11, Y12, Y13, Y14, Y15, Y16;
-     Y21, Y22, Y23, Y24, Y25, Y26;
-     Y31, Y32, Y33, Y34, Y35, Y36];

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessingSys.m

@@ -1,245 +1,0 @@
-function PreProcessingSys(L,Simulation,d)
-
-fid = fopen('PreProcessedSys.m','w');
-
-NAgen  = size(L,1);
-
-Counter = 1;
-for RowCounter=1:NAgen
-    
-    if Simulation == 0
-        
-        fprintf(fid, 'x%s = sdpvar(1);\n', num2str(RowCounter));
-        
-    else
-        
-        fprintf(fid, 'x%s = input(%s);\n', num2str(RowCounter),num2str(Counter));
-        Counter = Counter + 1;
-        
-    end
-    
-end
-
-fprintf(fid, '\n');
-
-for RowCounter=1:NAgen
-    
-    if Simulation == 0
-        
-        fprintf(fid, 'y%s = sdpvar(1);\n', num2str(RowCounter));
-        
-    else
-        
-        fprintf(fid, 'y%s = input(%s);\n', num2str(RowCounter),num2str(Counter));
-        Counter = Counter + 1;
-        
-    end
-    
-end
-
-fprintf(fid, '\n');
-Counter = 1;
-for RowCounter=1:NAgen
-    
-    if Simulation == 0
-        
-        fprintf(fid, 'u%s = sdpvar(1);\n', num2str(RowCounter));
-        
-    else
-        
-        fprintf(fid, 'u%s = u(%s);\n', num2str(RowCounter),num2str(RowCounter));
-        
-    end
-    
-end
-
-if Simulation == 0
-    
-    fprintf(fid, 'u = [');
-    
-    for RowCounter=1:NAgen
-        
-        if RowCounter < NAgen
-            
-            fprintf(fid, 'u%s; ', num2str(RowCounter));
-            
-        else
-            
-            fprintf(fid, 'u%s]; ', num2str(RowCounter));
-            
-        end
-        
-    end
-    
-    fprintf(fid, '\n\n');
-    
-    for RowCounter=1:NAgen
-        
-        fprintf(fid, 'q%s = [x%s;y%s];\n', num2str(RowCounter), num2str(RowCounter), num2str(RowCounter));
-        
-    end
-    
-    fprintf(fid, '\n');
-    fprintf(fid, 'q = [');
-    
-    
-    for RowCounter=1:NAgen
-        
-        if RowCounter < NAgen
-            
-            fprintf(fid, 'q%s; ', num2str(RowCounter));
-            
-        else
-            
[…]

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessingW.m

@@ -1,261 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing W                                                 %
-% Description: Creates the matrices W and DW for the LMI optmization      %
-% Inputs: N. Integer, Scalar, Number of Agents                            %
-%         SystemDimension. Integer, Scalar, Dimension of Each Subsystem   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% function test
-% 
-% PreProcessingW1(3,2,2,1e-1)
-% 
-% end
-% 
-% function PreProcessingW1(N,SystemDimension,Wdegree,ScalingFactor)
-
-function PreProcessingW(N,SystemDimension,Wdegree,ScalingFactor)
-
-fid = fopen('PreProcessedW.m','w');
-
-% Writing the matrix W
-
-Variable_Wp = 'Wp';
-Variable_Wc = 'Wc';
-Variable_Wv = 'Wv';
-Variable_W = 'W';
-Variable_DWTemp = 'DWTemp';
-Variable_DW = 'DW';
-
-dimW = SystemDimension;
-
-for n = 1:N
-    
-    % Writes the line of code
-    % [Wpn11,Wcn11,Wvn11] = polynomial(qn,Wdegree,0);
-    % Note W is written as a polynomial in the variable q
-    fprintf(fid, '%% Creation of W%s and DW%s\n',num2str(n),num2str(n));
-    
-    for nr = 1:dimW
-        
-        for nc = 1:dimW
-            
-            if nc >= nr
-                
-                fprintf(fid, '[');
-                fprintf(fid, [Variable_Wp '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wc '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wv '%s%s%s]'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, ' = polynomial(');
[…]

### 2016-11-15 TheoreticalExample1FinalVersion/PreProcessingY.m

@@ -1,273 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing Y                                                 %
-% Description: Creates the matrix Y for the LMI optmization               %
-% Inputs: nr. Integer, Scalar, Number of Rows                            %
-%         nc. Integer, Scalar, Number of Columns   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Note: Works only for Linear Graphs!
- 
-% function test
-% 
-% L = eye(5);
-% NAgents = size(L,1);
-% Option = 'Neighbor';
-% PreProcessingY1(2*NAgents,L,Option)
-% 
-% end
-
-function PreProcessingY(LinesVectorB,L,Option)
-
-fid = fopen('PreProcessedY.m','w');
-
-NAgents = size(L,1);
-LinesVectorBi = LinesVectorB/NAgents; % Number of lines of each vector Bi
-
-for RowCounter = 1:NAgents
-    
-    fprintf(fid, '\n %% Creation of Variable Y%s\n\n',num2str(RowCounter));
-    
-    for ColumnCounter = 1:LinesVectorB
-        
-        % size(B') variables
-        if strcmp(Option,'General') 
-            
-            fprintf(fid, '[Y%s%s,Yc%s%s,Yv%s%s] = polynomial(',  num2str(RowCounter),num2str(ColumnCounter),num2str(RowCounter),num2str(ColumnCounter),num2str(RowCounter),num2str(ColumnCounter));
-            fprintf(fid, 'q,');
-            fprintf(fid, 'Ydegree,0);\n');
-        
-        % Each variable Y depends on the system i and its neighbor
-        elseif strcmp(Option,'Neighbor')
-                
-                if RowCounter > 1 && RowCounter < NAgents
-                    
-                    if ColumnCounter >= (RowCounter - 1)*LinesVectorBi -1 && ColumnCounter <= (RowCounter - 1)*LinesVectorBi + 4
[…]

### 2016-11-15 TheoreticalExample1FinalVersion/TheoreticalExample1c.m

@@ -1,248 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Simulation of system (19) from [AS14].                           %
-% Author: H. Stein Shiromoto                                              %
-% Notes: DIfference: Nonlinear diffusion works with d<=1e-2               %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function main
-
-clear all
-close all
-clc
-yalmip('clear')
-
-% Set axis of graphs to LaTeX
-set(groot, 'defaultAxesTickLabelInterpreter','latex');
-set(groot, 'defaultLegendInterpreter','latex');
-
-
-% System Parameters
-
-global u d NAgents nr nc Option Simulation L
-
-Simulation = 0;
-
-d = 1e-2;
-% d = 0
-
-% Possible choices are: General, Decentralized and Neighbor
-Option  = 'General';
-
-if strcmp(Option,'General') + strcmp(Option,'Decentralized') ...
-        + strcmp(Option,'Neighbor') == 0
-    
-    disp('Chose an option: General, Decentralized or Neighbor');
-    return
-    
-end
-
-NAgents = 3;
-u = zeros(NAgents,1);
-
-L = LinearLaplacianGenerator(NAgents);
-
-if Simulation == 0
-    LMIOptimization;
-    fname = sprintf('Output%dAgents%s',NAgents,Option);
-    load(fname)
-    W
-    Y
-else
-    
-    xIC = rand(NAgents,1)*100;
-    yIC = rand(NAgents,1)*100;
-    
-    IC = [xIC;yIC];
-    
-    time = 0:1e-1:5e1;
-    [time,simout] = ode45(@sys,time,IC);
-    
-    fname = sprintf('Simulation%dAgents%s',NAgents,Option);
-    save(fname,'time','simout')
-    
-    load(fname)
-    PlotSimulation(time,simout)
-    
-end
-end
-
-function []=PlotSimulation(time,simout)
-% Time Evolution of the Solution components
-figure
[…]

### 2016-11-15 TheoreticalExample1a/PostProcessedWandDW.m

@@ -1,991 +1,0 @@
-% Rewriting the matrix W
-VerifiedW11 = clean(replace(W(1,1), coefList, double(coefList)), eps);
-W11 = sdisplay(VerifiedW11);
-
-VerifiedW12 = clean(replace(W(1,2), coefList, double(coefList)), eps);
-W12 = sdisplay(VerifiedW12);
-
-VerifiedW13 = clean(replace(W(1,3), coefList, double(coefList)), eps);
-W13 = sdisplay(VerifiedW13);
-
-VerifiedW14 = clean(replace(W(1,4), coefList, double(coefList)), eps);
-W14 = sdisplay(VerifiedW14);
-
-VerifiedW15 = clean(replace(W(1,5), coefList, double(coefList)), eps);
-W15 = sdisplay(VerifiedW15);
-
-VerifiedW16 = clean(replace(W(1,6), coefList, double(coefList)), eps);
-W16 = sdisplay(VerifiedW16);
-
-VerifiedW17 = clean(replace(W(1,7), coefList, double(coefList)), eps);
-W17 = sdisplay(VerifiedW17);
-
-VerifiedW18 = clean(replace(W(1,8), coefList, double(coefList)), eps);
-W18 = sdisplay(VerifiedW18);
-
-VerifiedW19 = clean(replace(W(1,9), coefList, double(coefList)), eps);
-W19 = sdisplay(VerifiedW19);
-
-VerifiedW110 = clean(replace(W(1,10), coefList, double(coefList)), eps);
-W110 = sdisplay(VerifiedW110);
-
-VerifiedW111 = clean(replace(W(1,11), coefList, double(coefList)), eps);
-W111 = sdisplay(VerifiedW111);
-
-VerifiedW112 = clean(replace(W(1,12), coefList, double(coefList)), eps);
-W112 = sdisplay(VerifiedW112);
-
-VerifiedW113 = clean(replace(W(1,13), coefList, double(coefList)), eps);
-W113 = sdisplay(VerifiedW113);
-
-VerifiedW114 = clean(replace(W(1,14), coefList, double(coefList)), eps);
-W114 = sdisplay(VerifiedW114);
-
-VerifiedW115 = clean(replace(W(1,15), coefList, double(coefList)), eps);
-W115 = sdisplay(VerifiedW115);
-
-VerifiedW116 = clean(replace(W(1,16), coefList, double(coefList)), eps);
-W116 = sdisplay(VerifiedW116);
-
[…]

### 2016-11-15 TheoreticalExample1a/PostProcessedY.m

@@ -1,58 +1,0 @@
-% Rewriting the matrix W
-VerifiedY11 = clean(replace(Y(1,1), coefList, double(coefList)), eps);
-Y11 = sdisplay(VerifiedY11);
-
-VerifiedY12 = clean(replace(Y(1,2), coefList, double(coefList)), eps);
-Y12 = sdisplay(VerifiedY12);
-
-VerifiedY13 = clean(replace(Y(1,3), coefList, double(coefList)), eps);
-Y13 = sdisplay(VerifiedY13);
-
-VerifiedY14 = clean(replace(Y(1,4), coefList, double(coefList)), eps);
-Y14 = sdisplay(VerifiedY14);
-
-VerifiedY15 = clean(replace(Y(1,5), coefList, double(coefList)), eps);
-Y15 = sdisplay(VerifiedY15);
-
-VerifiedY16 = clean(replace(Y(1,6), coefList, double(coefList)), eps);
-Y16 = sdisplay(VerifiedY16);
-
-VerifiedY21 = clean(replace(Y(2,1), coefList, double(coefList)), eps);
-Y21 = sdisplay(VerifiedY21);
-
-VerifiedY22 = clean(replace(Y(2,2), coefList, double(coefList)), eps);
-Y22 = sdisplay(VerifiedY22);
-
-VerifiedY23 = clean(replace(Y(2,3), coefList, double(coefList)), eps);
-Y23 = sdisplay(VerifiedY23);
-
-VerifiedY24 = clean(replace(Y(2,4), coefList, double(coefList)), eps);
-Y24 = sdisplay(VerifiedY24);
-
-VerifiedY25 = clean(replace(Y(2,5), coefList, double(coefList)), eps);
-Y25 = sdisplay(VerifiedY25);
-
-VerifiedY26 = clean(replace(Y(2,6), coefList, double(coefList)), eps);
-Y26 = sdisplay(VerifiedY26);
-
-VerifiedY31 = clean(replace(Y(3,1), coefList, double(coefList)), eps);
-Y31 = sdisplay(VerifiedY31);
-
-VerifiedY32 = clean(replace(Y(3,2), coefList, double(coefList)), eps);
-Y32 = sdisplay(VerifiedY32);
-
-VerifiedY33 = clean(replace(Y(3,3), coefList, double(coefList)), eps);
-Y33 = sdisplay(VerifiedY33);
-
[…]

### 2016-11-15 TheoreticalExample1a/PreProcessedWandDW.m

@@ -1,57 +1,0 @@
-% Creation of W1 and DW1
-[Wp111,Wc111,Wv111] = polynomial(q1,Wdegree,0);
-[Wp112,Wc112,Wv112] = polynomial(q1,Wdegree,0);
-[Wp122,Wc122,Wv122] = polynomial(q1,Wdegree,0);
-% Creation of W1
-W1 = [Wp111, Wp112;
-      Wp112, Wp122];
-
-Wc1 = [Wc111;Wc112;Wc122];
-Wp1 = [Wp111;Wp112;Wp122];
-
-% Creation of DW1
-DWTemp = jacobian(Wp1,q1);
-DW1 = [DWTemp(1)/2, DWTemp(2);
-       0,           DWTemp(4)/2];
-DW1 = DW1 + transpose(DW1);
-
-
-% Creation of W2 and DW2
-[Wp211,Wc211,Wv211] = polynomial(q2,Wdegree,0);
-[Wp212,Wc212,Wv212] = polynomial(q2,Wdegree,0);
-[Wp222,Wc222,Wv222] = polynomial(q2,Wdegree,0);
-% Creation of W2
-W2 = [Wp211, Wp212;
-      Wp212, Wp222];
-
-Wc2 = [Wc211;Wc212;Wc222];
-Wp2 = [Wp211;Wp212;Wp222];
-
-% Creation of DW2
-DWTemp = jacobian(Wp2,q2);
-DW2 = [DWTemp(1)/2, DWTemp(2);
-       0,           DWTemp(4)/2];
-DW2 = DW2 + transpose(DW2);
-
-
-% Creation of W3 and DW3
-[Wp311,Wc311,Wv311] = polynomial(q3,Wdegree,0);
-[Wp312,Wc312,Wv312] = polynomial(q3,Wdegree,0);
-[Wp322,Wc322,Wv322] = polynomial(q3,Wdegree,0);
-% Creation of W3
-W3 = [Wp311, Wp312;
-      Wp312, Wp322];
-
-Wc3 = [Wc311;Wc312;Wc322];
-Wp3 = [Wp311;Wp312;Wp322];
-
-% Creation of DW3
-DWTemp = jacobian(Wp3,q3);
-DW3 = [DWTemp(1)/2, DWTemp(2);
-       0,           DWTemp(4)/2];
-DW3 = DW3 + transpose(DW3);
-
-
[…]

### 2016-11-15 TheoreticalExample1a/PreProcessedY.m

@@ -1,29 +1,0 @@
-
-[Y11,Yc11,Yv11] = polynomial(q1,Ydegree,0);
-[Y12,Yc12,Yv12] = polynomial(q1,Ydegree,0);
-[Y13,Yc13,Yv13] = polynomial(q1,Ydegree,0);
-[Y14,Yc14,Yv14] = polynomial(q1,Ydegree,0);
-[Y15,Yc15,Yv15] = polynomial(q1,Ydegree,0);
-[Y16,Yc16,Yv16] = polynomial(q1,Ydegree,0);
-
-[Y21,Yc21,Yv21] = polynomial(q2,Ydegree,0);
-[Y22,Yc22,Yv22] = polynomial(q2,Ydegree,0);
-[Y23,Yc23,Yv23] = polynomial(q2,Ydegree,0);
-[Y24,Yc24,Yv24] = polynomial(q2,Ydegree,0);
-[Y25,Yc25,Yv25] = polynomial(q2,Ydegree,0);
-[Y26,Yc26,Yv26] = polynomial(q2,Ydegree,0);
-
-[Y31,Yc31,Yv31] = polynomial(q3,Ydegree,0);
-[Y32,Yc32,Yv32] = polynomial(q3,Ydegree,0);
-[Y33,Yc33,Yv33] = polynomial(q3,Ydegree,0);
-[Y34,Yc34,Yv34] = polynomial(q3,Ydegree,0);
-[Y35,Yc35,Yv35] = polynomial(q3,Ydegree,0);
-[Y36,Yc36,Yv36] = polynomial(q3,Ydegree,0);
-
-Yc = [Yc11; Yc12; Yc13; Yc14; Yc15; Yc16;
-      Yc21; Yc22; Yc23; Yc24; Yc25; Yc26;
-      Yc31; Yc32; Yc33; Yc34; Yc35; Yc36];
-
-Y = [Y11, Y12, Y13, Y14, Y15, Y16;
-     Y21, Y22, Y23, Y24, Y25, Y26;
-     Y31, Y32, Y33, Y34, Y35, Y36];

### 2016-11-15 TheoreticalExample1a/PreProcessingY.m

@@ -1,114 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing Y                                                 %
-% Description: Creates the matrix Y for the LMI optmization               %
-% Inputs: nr. Integer, Scalar, Number of Rows                            %
-%         nc. Integer, Scalar, Number of Columns   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Note: input should be size(B')
-
-function PreProcessingY(nr,nc)
-
-fid = fopen('PreProcessedY.m','w');
-
-Variable_Y = 'Y';
-Variable_Yc = 'Yc';
-
-% Writes the line of code
-% [Yij,Ycij,Yvij] = polynomial(qn,Wdegree,0);
-% Note Y is written as a polynomial in the variable q
-
-for i = 1:nr
-    
-    fprintf(fid, '\n');
-    
-    for j = 1:nc
-        
-        fprintf(fid, '[');
-        fprintf(fid, [Variable_Y '%s%s,'],  num2str(i),num2str(j));
-        fprintf(fid, [Variable_Yc '%s%s,'], num2str(i),num2str(j));
-        fprintf(fid, 'Yv%s%s]',              num2str(i),num2str(j));
-        fprintf(fid, ' = polynomial(');
-        fprintf(fid, 'q%s,', num2str(i));
-        fprintf(fid, 'Ydegree,0);\n');
-        
-    end
-    
-end
-
-% Writes the vector Yc = [Ycij];
-
-fprintf(fid, '\n');
-fprintf(fid, 'Yc = [');
-for i = 1:nr
-    
-    if i > 1
-        
-        fprintf(fid,'      ');
-    end
-    
-    for j = 1:nc
-        
-        if j < nc
-            
-            fprintf(fid, [Variable_Yc '%s%s; '], num2str(i),num2str(j));
-            
-        else
-            
-            if i == nr
-                
-                 fprintf(fid, [Variable_Yc '%s%s];\n'], num2str(i),num2str(j));
-            
-            else
-                
[…]

### 2016-11-15 TheoreticalExample1a/TheoreticalExample1a.m

@@ -1,215 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Simulation of system (19) from [AS14].                           %
-% Author: H. Stein Shiromoto                                              %
-% Notes: Is working fine                                                  %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function main
-
-clear all
-close all
-clc
-yalmip clear
-
-% Set axis of graphs to LaTeX
-set(groot, 'defaultAxesTickLabelInterpreter','latex');
-set(groot, 'defaultLegendInterpreter','latex');
-
-
-% System Parameters
-
-global u d
-
-u = 0;
-d = 1e-2;
-
-xIC = rand(3,1)*100;
-yIC = rand(3,1)*100;
-
-IC = [xIC;yIC];
-
-time = 0:1e-1:5e1;
-% [time,simout] = ode45(@sys,time,IC);
-% PlotSimulation(time,simout)
-
-[W,Y,coefList] = LMIOptimization;
-[W,Y] = postprocessing(W,Y,coefList)
-
-save('TheoreticalExample1aOutput','W','Y')
-
-end
-
-function []=PlotSimulation(time,simout)
-% Time Evolution of the Solution components
-figure
-subplot(2,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
-hold on
-subplot(2,1,1),plot(time,simout(:,2),'g-','LineWidth',2);
-hold on
-subplot(2,1,1),plot(time,simout(:,3),'r-','LineWidth',2);
-xlabel('Time $t$','interpreter','latex','fontsize',14);
-ylabel('$x_i(t)$','interpreter','latex','fontsize',14);
-title('Time Evolution of the mRNA','interpreter','latex','fontsize',14);
[…]

### 2016-11-15 TheoreticalExample1b/PostProcessingW.m

@@ -1,54 +1,0 @@
-function PostProcessingW(NumberOfAgents,SystemDimension)
-
-fid = fopen('PostProcessedWandDW.m','w');
-
-SysDim = SystemDimension;
-NAgen  = NumberOfAgents;
-
-Variable_W = 'W';
-Variable_VerifiedW = 'VerifiedW';
-
-
-fprintf(fid, '%% Rewriting the matrix W\n');
-
-for nr = 1:NAgen*SysDim
-    
-    for nc = 1:NAgen*SysDim
-        
-            
-            fprintf(fid, 'VerifiedW%s%s = ', num2str(nr),num2str(nc));
-            fprintf(fid, 'clean(replace(W(%s,%s), coefList, double(coefList)), eps);\n', num2str(nr),num2str(nc));
-            fprintf(fid, 'W%s%s = ', num2str(nr),num2str(nc));
-            fprintf(fid, 'sdisplay(VerifiedW%s%s);\n\n', num2str(nr),num2str(nc));
-            
-        
-    end
-end
-
-fprintf(fid, 'W = [');
-
-for nr = 1:NAgen*SysDim
-    
-    for nc = 1:NAgen*SysDim
-        
-             if nc == NAgen*SysDim && nr == NAgen*SysDim
-                 
-                 fprintf(fid, 'W%s%s];\n', num2str(nr),num2str(nc));
-                 
-             elseif nc == NAgen*SysDim
-            
-                 fprintf(fid, 'W%s%s;\n', num2str(nr),num2str(nc));
-                 fprintf(fid, '     ');
-                 
-             else
-                 
-                 fprintf(fid, 'W%s%s, ', num2str(nr),num2str(nc));
-                 
-             end
-            
-        
-    end
-end
-    
-
-end

### 2016-11-15 TheoreticalExample1b/PostProcessingY.m

@@ -1,46 +1,0 @@
-function PostProcessingY(NumberOfRows,NumberOfColumns)
-
-fid = fopen('PostProcessedY.m','w');
-
-fprintf(fid, '%% Rewriting the matrix W\n');
-
-for nr = 1:NumberOfRows
-    
-    for nc = 1:NumberOfColumns
-        
-            
-            fprintf(fid, 'VerifiedY%s%s = ', num2str(nr),num2str(nc));
-            fprintf(fid, 'clean(replace(Y(%s,%s), coefList, double(coefList)), eps);\n', num2str(nr),num2str(nc));
-            fprintf(fid, 'Y%s%s = ', num2str(nr),num2str(nc));
-            fprintf(fid, 'sdisplay(VerifiedY%s%s);\n\n', num2str(nr),num2str(nc));
-            
-        
-    end
-end
-
-fprintf(fid, 'Y = [');
-
-for nr = 1:NumberOfRows
-    
-    for nc = 1:NumberOfColumns
-        
-             if nc == NumberOfColumns && nr == NumberOfRows
-                 
-                 fprintf(fid, 'Y%s%s];\n', num2str(nr),num2str(nc));
-                 
-             elseif nc == NumberOfColumns
-            
-                 fprintf(fid, 'Y%s%s;\n', num2str(nr),num2str(nc));
-                 fprintf(fid, '     ');
-                 
-             else
-                 
-                 fprintf(fid, 'Y%s%s, ', num2str(nr),num2str(nc));
-                 
-             end
-            
-    end
-end
-    
-
-end

### 2016-11-15 TheoreticalExample1b/PreProcessingW.m

@@ -1,245 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing W                                                 %
-% Description: Creates the matrices W and DW for the LMI optmization      %
-% Inputs: N. Integer, Scalar, Number of Agents                            %
-%         SystemDimension. Integer, Scalar, Dimension of Each Subsystem   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function PreProcessingW(N,SystemDimension)
-
-fid = fopen('PreProcessedWandDW.m','w');
-
-% Writing the matrix W
-
-Variable_Wp = 'Wp';
-Variable_Wc = 'Wc';
-Variable_Wv = 'Wv';
-Variable_W = 'W';
-Variable_DWTemp = 'DWTemp';
-Variable_DW = 'DW';
-
-dimW = SystemDimension;
-
-for n = 1:N
-    
-    % Writes the line of code
-    % [Wpn11,Wcn11,Wvn11] = polynomial(qn,Wdegree,0);
-    % Note W is written as a polynomial in the variable q
-    fprintf(fid, '%% Creation of W%s and DW%s\n',num2str(n),num2str(n));
-    
-    for nr = 1:dimW
-        
-        for nc = 1:dimW
-            
-            if nc >= nr
-                
-                fprintf(fid, '[');
-                fprintf(fid, [Variable_Wp '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wc '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wv '%s%s%s]'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, ' = polynomial(');
-                fprintf(fid, 'q%s,', num2str(n));
-                fprintf(fid, 'Wdegree,0);\n');
-            
-            end
-            
-        end
-    end
-    
[…]

### 2016-11-15 TheoreticalExample1b/TheoreticalExample1b.m

@@ -1,215 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Simulation of system (19) from [AS14].                           %
-% Author: H. Stein Shiromoto                                              %
-% Notes: DIfference: Nonlinear diffusion works with d<=1e-2               %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function main
-
-clear all
-close all
-clc
-yalmip clear
-
-% Set axis of graphs to LaTeX
-set(groot, 'defaultAxesTickLabelInterpreter','latex');
-set(groot, 'defaultLegendInterpreter','latex');
-
-
-% System Parameters
-
-global u d
-
-u = 0;
-d = 1e-2;
-
-xIC = rand(3,1)*100;
-yIC = rand(3,1)*100;
-
-IC = [xIC;yIC];
-
-time = 0:1e-1:5e1;
-% [time,simout] = ode45(@sys,time,IC);
-% PlotSimulation(time,simout)
-
-[W,Y,coefList] = LMIOptimization;
-[W,Y] = postprocessing(W,Y,coefList)
-
-save('TheoreticalExample1aOutput','W','Y')
-
-end
-
-function []=PlotSimulation(time,simout)
-% Time Evolution of the Solution components
-figure
-subplot(2,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
-hold on
-subplot(2,1,1),plot(time,simout(:,2),'g-','LineWidth',2);
-hold on
-subplot(2,1,1),plot(time,simout(:,3),'r-','LineWidth',2);
-xlabel('Time $t$','interpreter','latex','fontsize',14);
-ylabel('$x_i(t)$','interpreter','latex','fontsize',14);
[…]

### 2016-11-15 TheoreticalExample1d/PostProcessedWandDW.m

@@ -1,3072 +1,0 @@
-VerifiedW1 = clean(replace(W1, coefList, double(coefList)), 1e-06);
-W1 = sdisplay(VerifiedW1);
-
-VerifiedW2 = clean(replace(W2, coefList, double(coefList)), 1e-06);
-W2 = sdisplay(VerifiedW2);
-
-VerifiedW3 = clean(replace(W3, coefList, double(coefList)), 1e-06);
-W3 = sdisplay(VerifiedW3);
-
-VerifiedW4 = clean(replace(W4, coefList, double(coefList)), 1e-06);
-W4 = sdisplay(VerifiedW4);
-
-VerifiedW5 = clean(replace(W5, coefList, double(coefList)), 1e-06);
-W5 = sdisplay(VerifiedW5);
-
-VerifiedW6 = clean(replace(W6, coefList, double(coefList)), 1e-06);
-W6 = sdisplay(VerifiedW6);
-
-VerifiedW7 = clean(replace(W7, coefList, double(coefList)), 1e-06);
-W7 = sdisplay(VerifiedW7);
-
-VerifiedW8 = clean(replace(W8, coefList, double(coefList)), 1e-06);
-W8 = sdisplay(VerifiedW8);
-
-VerifiedW9 = clean(replace(W9, coefList, double(coefList)), 1e-06);
-W9 = sdisplay(VerifiedW9);
-
-VerifiedW10 = clean(replace(W10, coefList, double(coefList)), 1e-06);
-W10 = sdisplay(VerifiedW10);
-
-VerifiedW11 = clean(replace(W11, coefList, double(coefList)), 1e-06);
-W11 = sdisplay(VerifiedW11);
-
-VerifiedW12 = clean(replace(W12, coefList, double(coefList)), 1e-06);
-W12 = sdisplay(VerifiedW12);
-
-VerifiedW13 = clean(replace(W13, coefList, double(coefList)), 1e-06);
-W13 = sdisplay(VerifiedW13);
-
-VerifiedW14 = clean(replace(W14, coefList, double(coefList)), 1e-06);
-W14 = sdisplay(VerifiedW14);
-
-VerifiedW15 = clean(replace(W15, coefList, double(coefList)), 1e-06);
-W15 = sdisplay(VerifiedW15);
-
-VerifiedW16 = clean(replace(W16, coefList, double(coefList)), 1e-06);
-W16 = sdisplay(VerifiedW16);
-
[…]

### 2016-11-15 TheoreticalExample1d/PostProcessedY.m

@@ -1,384 +1,0 @@
-VerifiedY1 = clean(replace(Y1, coefList, double(coefList)), 1e-06);
-Y1 = sdisplay(VerifiedY1);
-
-VerifiedY2 = clean(replace(Y2, coefList, double(coefList)), 1e-06);
-Y2 = sdisplay(VerifiedY2);
-
-VerifiedY3 = clean(replace(Y3, coefList, double(coefList)), 1e-06);
-Y3 = sdisplay(VerifiedY3);
-
-VerifiedY4 = clean(replace(Y4, coefList, double(coefList)), 1e-06);
-Y4 = sdisplay(VerifiedY4);
-
-VerifiedY5 = clean(replace(Y5, coefList, double(coefList)), 1e-06);
-Y5 = sdisplay(VerifiedY5);
-
-VerifiedY6 = clean(replace(Y6, coefList, double(coefList)), 1e-06);
-Y6 = sdisplay(VerifiedY6);
-
-VerifiedY7 = clean(replace(Y7, coefList, double(coefList)), 1e-06);
-Y7 = sdisplay(VerifiedY7);
-
-VerifiedY8 = clean(replace(Y8, coefList, double(coefList)), 1e-06);
-Y8 = sdisplay(VerifiedY8);
-
-VerifiedY9 = clean(replace(Y9, coefList, double(coefList)), 1e-06);
-Y9 = sdisplay(VerifiedY9);
-
-VerifiedY10 = clean(replace(Y10, coefList, double(coefList)), 1e-06);
-Y10 = sdisplay(VerifiedY10);
-
-VerifiedY11 = clean(replace(Y11, coefList, double(coefList)), 1e-06);
-Y11 = sdisplay(VerifiedY11);
-
-VerifiedY12 = clean(replace(Y12, coefList, double(coefList)), 1e-06);
-Y12 = sdisplay(VerifiedY12);
-
-VerifiedY13 = clean(replace(Y13, coefList, double(coefList)), 1e-06);
-Y13 = sdisplay(VerifiedY13);
-
-VerifiedY14 = clean(replace(Y14, coefList, double(coefList)), 1e-06);
-Y14 = sdisplay(VerifiedY14);
-
-VerifiedY15 = clean(replace(Y15, coefList, double(coefList)), 1e-06);
-Y15 = sdisplay(VerifiedY15);
-
-VerifiedY16 = clean(replace(Y16, coefList, double(coefList)), 1e-06);
-Y16 = sdisplay(VerifiedY16);
-
[…]

### 2016-11-15 TheoreticalExample1d/PostProcessingW.m

@@ -1,17 +1,0 @@
-function PostProcessingW(NumberOfAgents,prec)
-
-fid = fopen('PostProcessedWandDW.m','w');
-
-for nr = 1:NumberOfAgents
-        
-        fprintf(fid, 'VerifiedW%s = ', num2str(nr));
-        fprintf(fid, 'clean(replace(W%s, coefList, double(coefList)), %s);\n', num2str(nr),num2str(prec));
-        fprintf(fid, 'W%s = ', num2str(nr));
-        fprintf(fid, 'sdisplay(VerifiedW%s);\n\n', num2str(nr));
-        
-end
-
-fclose(fid);
-    
-
-end

### 2016-11-15 TheoreticalExample1d/PreProcessedLfW.m

@@ -1,130 +1,0 @@
-LfW1 = -DW1 + A11*W1 + transpose(A11*W1) + A12*W2 + transpose(A21*W1) + B1*Y1 + transpose(B1*Y1) + 2*1*W1;
-LfW2 = -DW2 + A21*W1 + transpose(A12*W2) + A22*W2 + transpose(A22*W2) + A23*W3 + transpose(A32*W2) + B2*Y2 + transpose(B2*Y2) + 2*1*W2;
-LfW3 = -DW3 + A32*W2 + transpose(A23*W3) + A33*W3 + transpose(A33*W3) + A34*W4 + transpose(A43*W3) + B3*Y3 + transpose(B3*Y3) + 2*1*W3;
-LfW4 = -DW4 + A43*W3 + transpose(A34*W4) + A44*W4 + transpose(A44*W4) + A45*W5 + transpose(A54*W4) + B4*Y4 + transpose(B4*Y4) + 2*1*W4;
-LfW5 = -DW5 + A54*W4 + transpose(A45*W5) + A55*W5 + transpose(A55*W5) + A56*W6 + transpose(A65*W5) + B5*Y5 + transpose(B5*Y5) + 2*1*W5;
-LfW6 = -DW6 + A65*W5 + transpose(A56*W6) + A66*W6 + transpose(A66*W6) + A67*W7 + transpose(A76*W6) + B6*Y6 + transpose(B6*Y6) + 2*1*W6;
-LfW7 = -DW7 + A76*W6 + transpose(A67*W7) + A77*W7 + transpose(A77*W7) + A78*W8 + transpose(A87*W7) + B7*Y7 + transpose(B7*Y7) + 2*1*W7;
-LfW8 = -DW8 + A87*W7 + transpose(A78*W8) + A88*W8 + transpose(A88*W8) + A89*W9 + transpose(A98*W8) + B8*Y8 + transpose(B8*Y8) + 2*1*W8;
-LfW9 = -DW9 + A98*W8 + transpose(A89*W9) + A99*W9 + transpose(A99*W9) + A910*W10 + transpose(A109*W9) + B9*Y9 + transpose(B9*Y9) + 2*1*W9;
-LfW10 = -DW10 + A109*W9 + transpose(A910*W10) + A1010*W10 + transpose(A1010*W10) + A1011*W11 + transpose(A1110*W10) + B10*Y10 + transpose(B10*Y10) + 2*1*W10;
[…]

### 2016-11-15 TheoreticalExample1d/PreProcessedSys.m

@@ -1,1545 +1,0 @@
-x1 = sdpvar(1);
-x2 = sdpvar(1);
-x3 = sdpvar(1);
-x4 = sdpvar(1);
-x5 = sdpvar(1);
-x6 = sdpvar(1);
-x7 = sdpvar(1);
-x8 = sdpvar(1);
-x9 = sdpvar(1);
-x10 = sdpvar(1);
-x11 = sdpvar(1);
-x12 = sdpvar(1);
-x13 = sdpvar(1);
-x14 = sdpvar(1);
-x15 = sdpvar(1);
-x16 = sdpvar(1);
-x17 = sdpvar(1);
-x18 = sdpvar(1);
-x19 = sdpvar(1);
-x20 = sdpvar(1);
-x21 = sdpvar(1);
-x22 = sdpvar(1);
-x23 = sdpvar(1);
-x24 = sdpvar(1);
-x25 = sdpvar(1);
-x26 = sdpvar(1);
-x27 = sdpvar(1);
-x28 = sdpvar(1);
-x29 = sdpvar(1);
-x30 = sdpvar(1);
-x31 = sdpvar(1);
-x32 = sdpvar(1);
-x33 = sdpvar(1);
-x34 = sdpvar(1);
-x35 = sdpvar(1);
-x36 = sdpvar(1);
-x37 = sdpvar(1);
-x38 = sdpvar(1);
-x39 = sdpvar(1);
-x40 = sdpvar(1);
-x41 = sdpvar(1);
-x42 = sdpvar(1);
-x43 = sdpvar(1);
-x44 = sdpvar(1);
-x45 = sdpvar(1);
-x46 = sdpvar(1);
-x47 = sdpvar(1);
-x48 = sdpvar(1);
-x49 = sdpvar(1);
-x50 = sdpvar(1);
-x51 = sdpvar(1);
-x52 = sdpvar(1);
-x53 = sdpvar(1);
-x54 = sdpvar(1);
-x55 = sdpvar(1);
-x56 = sdpvar(1);
-x57 = sdpvar(1);
-x58 = sdpvar(1);
-x59 = sdpvar(1);
-x60 = sdpvar(1);
-x61 = sdpvar(1);
-x62 = sdpvar(1);
-x63 = sdpvar(1);
-x64 = sdpvar(1);
-x65 = sdpvar(1);
-x66 = sdpvar(1);
-x67 = sdpvar(1);
-x68 = sdpvar(1);
[…]

### 2016-11-15 TheoreticalExample1d/PreProcessedWandDW.m

@@ -1,2561 +1,0 @@
-% Creation of W1 and DW1
-[Wp111,Wc111,Wv111] = polynomial(q1,2.000000,0);
-[Wp112,Wc112,Wv112] = polynomial(q1,2.000000,0);
-[Wp122,Wc122,Wv122] = polynomial(q1,2.000000,0);
-% Creation of W1
-W1 = [Wp111, Wp112;
-      Wp112, Wp122];
-
-Wc1 = [Wc111;Wc112;Wc122];
-Wp1 = [Wp111;Wp112;Wp122];
-
-% Creation of DW1
-DWTemp = jacobian(Wp1,q1);
-v = f1;
-
-DW1 = [DWTemp(1,:)/2*v, DWTemp(2,:)*v;
-       0,                DWTemp(3,:)/2*v];
-DW1 = DW1 + transpose(DW1);
-
-
-% Creation of W2 and DW2
-[Wp211,Wc211,Wv211] = polynomial(q2,2.000000,0);
-[Wp212,Wc212,Wv212] = polynomial(q2,2.000000,0);
-[Wp222,Wc222,Wv222] = polynomial(q2,2.000000,0);
-% Creation of W2
-W2 = [Wp211, Wp212;
-      Wp212, Wp222];
-
-Wc2 = [Wc211;Wc212;Wc222];
-Wp2 = [Wp211;Wp212;Wp222];
-
-% Creation of DW2
-DWTemp = jacobian(Wp2,q2);
-v = f2;
-
-DW2 = [DWTemp(1,:)/2*v, DWTemp(2,:)*v;
-       0,                DWTemp(3,:)/2*v];
-DW2 = DW2 + transpose(DW2);
-
-
-% Creation of W3 and DW3
-[Wp311,Wc311,Wv311] = polynomial(q3,2.000000,0);
-[Wp312,Wc312,Wv312] = polynomial(q3,2.000000,0);
-[Wp322,Wc322,Wv322] = polynomial(q3,2.000000,0);
-% Creation of W3
-W3 = [Wp311, Wp312;
-      Wp312, Wp322];
-
-Wc3 = [Wc311;Wc312;Wc322];
-Wp3 = [Wp311;Wp312;Wp322];
-
-% Creation of DW3
-DWTemp = jacobian(Wp3,q3);
-v = f3;
-
-DW3 = [DWTemp(1,:)/2*v, DWTemp(2,:)*v;
-       0,                DWTemp(3,:)/2*v];
[…]

### 2016-11-15 TheoreticalExample1d/PreProcessedY.m

@@ -1,516 +1,0 @@
-
-[Yp11,Yc11,Yv11] = polynomial(q1,2.000000,0);
-[Yp12,Yc12,Yv12] = polynomial(q1,2.000000,0);
-
-[Yp21,Yc21,Yv21] = polynomial(q2,2.000000,0);
-[Yp22,Yc22,Yv22] = polynomial(q2,2.000000,0);
-
-[Yp31,Yc31,Yv31] = polynomial(q3,2.000000,0);
-[Yp32,Yc32,Yv32] = polynomial(q3,2.000000,0);
-
-[Yp41,Yc41,Yv41] = polynomial(q4,2.000000,0);
-[Yp42,Yc42,Yv42] = polynomial(q4,2.000000,0);
-
-[Yp51,Yc51,Yv51] = polynomial(q5,2.000000,0);
-[Yp52,Yc52,Yv52] = polynomial(q5,2.000000,0);
-
-[Yp61,Yc61,Yv61] = polynomial(q6,2.000000,0);
-[Yp62,Yc62,Yv62] = polynomial(q6,2.000000,0);
-
-[Yp71,Yc71,Yv71] = polynomial(q7,2.000000,0);
-[Yp72,Yc72,Yv72] = polynomial(q7,2.000000,0);
-
-[Yp81,Yc81,Yv81] = polynomial(q8,2.000000,0);
-[Yp82,Yc82,Yv82] = polynomial(q8,2.000000,0);
-
-[Yp91,Yc91,Yv91] = polynomial(q9,2.000000,0);
-[Yp92,Yc92,Yv92] = polynomial(q9,2.000000,0);
-
-[Yp101,Yc101,Yv101] = polynomial(q10,2.000000,0);
-[Yp102,Yc102,Yv102] = polynomial(q10,2.000000,0);
-
-[Yp111,Yc111,Yv111] = polynomial(q11,2.000000,0);
-[Yp112,Yc112,Yv112] = polynomial(q11,2.000000,0);
-
-[Yp121,Yc121,Yv121] = polynomial(q12,2.000000,0);
-[Yp122,Yc122,Yv122] = polynomial(q12,2.000000,0);
-
-[Yp131,Yc131,Yv131] = polynomial(q13,2.000000,0);
-[Yp132,Yc132,Yv132] = polynomial(q13,2.000000,0);
-
-[Yp141,Yc141,Yv141] = polynomial(q14,2.000000,0);
-[Yp142,Yc142,Yv142] = polynomial(q14,2.000000,0);
-
[…]

### 2016-11-15 TheoreticalExample1d/PreProcessingLfW.m

@@ -1,59 +1,0 @@
-function PreProcessingLfW(NumberOfAgents,lambda)
-
-fid = fopen('PreProcessedLfW.m','w');
-
-for AgentCounter = 1:NumberOfAgents
-    
-    fprintf(fid, 'LfW%s = -DW%s + ', num2str(AgentCounter),num2str(AgentCounter));
-    
-    if AgentCounter == 1
-        
-        for NeighborCounter = 1:min(2,NumberOfAgents)
-        
-        fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    elseif AgentCounter == NumberOfAgents
-        
-        for NeighborCounter = AgentCounter-1:NumberOfAgents
-        
-            fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    else
-        
-        for NeighborCounter = AgentCounter-1:AgentCounter+1
-        
-            fprintf(fid, 'A%s%s*W%s + transpose(A%s%s*W%s) + ',num2str(AgentCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(NeighborCounter),num2str(AgentCounter),num2str(AgentCounter));
-    
-        end
-        
-    end
-    
-    fprintf(fid, 'B%s*Y%s + transpose(B%s*Y%s) + 2*%d*W%s;\n', num2str(AgentCounter),num2str(AgentCounter),num2str(AgentCounter),num2str(AgentCounter),lambda,num2str(AgentCounter));
-    
-end
-
-fprintf(fid,'\n');
-
-fprintf(fid,'Constraints = [ ');
-
-for AgentCounter = 1:NumberOfAgents
-    
-    if AgentCounter < NumberOfAgents
-        
-        fprintf(fid,'sos(W%s-eye(2)); sos(-LfW%s+eye(2)); ',num2str(AgentCounter),num2str(AgentCounter));
-        
-    else
-        
[…]

### 2016-11-15 TheoreticalExample1d/PreProcessingW.m

@@ -1,295 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Pre Processing W                                                 %
-% Description: Creates the matrices W and DW for the LMI optmization      %
-% Inputs: N. Integer, Scalar, Number of Agents                            %
-%         SystemDimension. Integer, Scalar, Dimension of Each Subsystem   %
-% Output: File 'CreatorWandDW.m' with the code definifn W and DW          %
-% Author: Humberto Stein Shiromoto                                        %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function PreProcessingW(NumberOfAgents,SystemDimension,Wdegree,Option)
-
-fid = fopen('PreProcessedWandDW.m','w');
-
-% Writing the matrix W
-
-Variable_Wp = 'Wp';
-Variable_Wc = 'Wc';
-Variable_Wv = 'Wv';
-Variable_W = 'W';
-Variable_DWTemp = 'DWTemp';
-Variable_DW = 'DW';
-
-dimW = SystemDimension;
-
-for n = 1:NumberOfAgents
-    
-    % Writes the line of code
-    % [Wpn11,Wcn11,Wvn11] = polynomial(qn,Wdegree,0);
-    % Note W is written as a polynomial in the variable q
-    fprintf(fid, '%% Creation of W%s and DW%s\n',num2str(n),num2str(n));
-    
-    for nr = 1:dimW
-        
-        for nc = 1:dimW
-            
-            if nc >= nr
-                
-                fprintf(fid, '[');
-                fprintf(fid, [Variable_Wp '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wc '%s%s%s,'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, [Variable_Wv '%s%s%s]'], num2str(n),num2str(nr),num2str(nc));
-                fprintf(fid, ' = polynomial(');
-                
-                if strcmp(Option,'General')
-                    
-                    fprintf(fid, 'q,');
-                    
-                elseif strcmp(Option,'Decentralized')
-                    
-                    fprintf(fid, 'q%s,', num2str(n));
[…]

### 2016-11-15 TheoreticalExample1d/TheoreticalExample1d.m

@@ -1,208 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                         %
-% Title: Simulation of system (19) from [AS14].                           %
-% Author: H. Stein Shiromoto                                              %
-% Notes: DIfference: Nonlinear diffusion works with d<=1e-2               %
-%                                                                         %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-function main
-
-clear all
-close all
-clc
-yalmip('clear')
-warning off
-
-% System Parameters
-
-global u d NAgents nr nc Option Simulation L
-
-Simulation = 0;
-
-% Possible choices are: General, Decentralized and Neighbor
-Option  = 'Decentralized';
-
-if strcmp(Option,'General') + strcmp(Option,'Decentralized') + strcmp(Option,'Neighbor') == 0
-    
-    disp('Chose an option: General, Decentralized or Neighbor');
-    return
-    
-end
-
-NAgents = 2^1
-d = 1e-4; % Max value for feasibility of the LMI optimization
-
-
-if Simulation == 0
-    
-    L = LinearLaplacianGenerator(NAgents);
-    LMIOptimization;
-    
-else
-    
-    xIC = rand(NAgents,1)*100;
-    yIC = rand(NAgents,1)*100;
-    u = zeros(NAgents,1);
-    
-    IC = [xIC;yIC];
-    
-    time = 0:1e-1:5e1;
-    [time,simout] = ode45(@sys,time,IC);
-    
-    fname = sprintf('Simulation%dAgents%s',NAgents,Option);
-    save(fname,'time','simout')
-    
-    load(fname)
-    PlotSimulation(time,simout)
-    
-end
-
-end
-
-function []=PlotSimulation(time,simout)
-
-% Set axis of graphs to LaTeX
-set(groot, 'defaultAxesTickLabelInterpreter','latex');
-set(groot, 'defaultLegendInterpreter','latex');
-
-% Time Evolution of the Solution components
-figure
-subplot(2,1,1),plot(time,simout(:,1),'b-','LineWidth',2);
-hold on
[…]

### 2016-11-15 TheoreticalExample2/ADMM.m
Start the algorithm

@@ -6,3 +6,49 @@
 %                                                                         %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+clear all;
+close all;
+clc;
+
+W = sdpvar(2,2);
+Z = rand(2,2)
+Lambda = rand(2,2);
+
+
+
+Constraints = [W>=0];
+Objective   = norm(W-Z+Lambda,'fro');
+
+optimize(Constraints,Objective);
+NextW(1,1) = value(W(1,1));
+NextW(1,2) = value(W(1,2));
+NextW(2,1) = value(W(2,1));
+NextW(2,2) = value(W(2,2));
+
+[~,NotPositiveDefinite] = chol(NextW);
+if NotPositiveDefinite ~= 0
+    display('W is not PD')
+end
+
+
+Z = sdpvar(2,2);
+Constraints = [Z>=0];
+Objective   = norm(NextW-Z+Lambda,'fro');
+optimize(Constraints,Objective);
+NextZ(1,1) = value(Z(1,1));
+NextZ(1,2) = value(Z(1,2));
+NextZ(2,1) = value(Z(2,1));
+NextZ(2,2) = value(Z(2,2));
+[~,NotPositiveDefinite] = chol(NextZ);
+if NotPositiveDefinite ~= 0
+    display('Z is not PD')
+end
+
+
+Objective   = norm(NextW-NextZ+Lambda,'fro');
+optimize([],Objective);
+NextLambda(1,1) = value(Lambda(1,1));
+NextLambda(1,2) = value(Lambda(1,2));
+NextLambda(2,1) = value(Lambda(2,1));
+NextLambda(2,2) = value(Lambda(2,2));
+

### 2016-11-16 TheoreticalExample2/ADMM.m
add a while condition and stopping criterion

@@ -10,12 +10,15 @@ clear all;
 close all;
 clc;
 
-W = sdpvar(2,2);
+
 Z = rand(2,2)
-Lambda = rand(2,2);
+W = rand(2,2)
+Lambda = 10*rand(2,2);
+n = 0;
 
+while norm(W-Z,'fro') > 1e-6 && n <= 20
 
-
+W = sdpvar(2,2);
 Constraints = [W>=0];
 Objective   = norm(W-Z+Lambda,'fro');
 
@@ -24,31 +27,36 @@ NextW(1,1) = value(W(1,1));
 NextW(1,2) = value(W(1,2));
 NextW(2,1) = value(W(2,1));
 NextW(2,2) = value(W(2,2));
-
-[~,NotPositiveDefinite] = chol(NextW);
-if NotPositiveDefinite ~= 0
-    display('W is not PD')
-end
+W = NextW;
 
 
 Z = sdpvar(2,2);
 Constraints = [Z>=0];
-Objective   = norm(NextW-Z+Lambda,'fro');
+Objective   = norm(W-Z+Lambda,'fro');
 optimize(Constraints,Objective);
 NextZ(1,1) = value(Z(1,1));
 NextZ(1,2) = value(Z(1,2));
 NextZ(2,1) = value(Z(2,1));
 NextZ(2,2) = value(Z(2,2));
-[~,NotPositiveDefinite] = chol(NextZ);
-if NotPositiveDefinite ~= 0
+Z = NextZ;
+
+Lambda = W - Z + Lambda;
+
+n = n+1;
+
+end
+
+[~,NotPositiveDefiniteW] = chol(W);
+[~,NotPositiveDefiniteZ] = chol(Z);
+if NotPositiveDefiniteW ~= 0
+    display('W is not PD')
+    return;
+elseif NotPositiveDefiniteZ ~= 0
     display('Z is not PD')
+    return;
 end
 
 
-Objective   = norm(NextW-NextZ+Lambda,'fro');
-optimize([],Objective);
-NextLambda(1,1) = value(Lambda(1,1));
-NextLambda(1,2) = value(Lambda(1,2));
-NextLambda(2,1) = value(Lambda(2,1));
-NextLambda(2,2) = value(Lambda(2,2));
-
+W
+Z
+Lambda

### 2016-11-16 TheoreticalExample2/ADMM.m
Start to write a higher dimensional case

@@ -6,44 +6,110 @@
 %                                                                         %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+function ADMM
+
 clear all;
 close all;
 clc;
 
 
+%Think on the fully distributed case
+
 Z = rand(2,2)
 W = rand(2,2)
 Lambda = 10*rand(2,2);
-n = 0;
+NumberOfIterations = 0;
 
-while norm(W-Z,'fro') > 1e-6 && n <= 20
+while norm(W-Z,'fro') > 1e-6 && NumberOfIterations <= 20
+    
+    W1 = sdpvar(2,2);
+    Constraints = [W1>=0];
+    Objective   = norm(W1-Z1+Lambda1,'fro');
+    
+    optimize(Constraints,Objective);
+    NextW1(1,1) = value(W1(1,1));
+    NextW1(1,2) = value(W1(1,2));
+    NextW1(2,1) = value(W1(2,1));
+    NextW1(2,2) = value(W1(2,2));
+    W1 = NextW1;
+    
+    W2 = sdpvar(2,2);
+    Constraints = [W2>=0];
+    Objective   = norm(W2-Z2+Lambda2,'fro');
+    
+    optimize(Constraints,Objective);
+    NextW2(1,1) = value(W2(1,1));
+    NextW2(1,2) = value(W2(1,2));
+    NextW2(2,1) = value(W2(2,1));
+    NextW2(2,2) = value(W2(2,2));
+    W2 = NextW2;
+    
+    W = blk(diag);
+    Lambda = blkdiag(Lambda1,Lambda2);
+    
+    Z1 = sdpvar(2,2);
+    Z2 = sdpvar(2,2);
+    Z = blkdiag(Z1,Z2);
+    A*Z + transpose(A*Z) + B*Y + transpose(B*Y) + 2*1.000000*Z;
+    Constraints = [Z1>=0,Z2>=0,-MI>=0];
+    Objective   = norm(W-Z+Lambda,'fro');
+    optimize(Constraints,Objective);
+    NextZ(1,1) = value(Z(1,1))/2;
+    NextZ(1,2) = value(Z(1,2));
+    NextZ(1,3) = value(Z(1,3));
+    NextZ(1,4) = value(Z(1,4));
+    NextZ(2,2) = value(Z(2,2))/2;
[…]

### 2016-11-16 TheoreticalExample2/ADMM.m
Start to formulate a case with 2 agents.

@@ -12,19 +12,44 @@ clear all;
 close all;
 clc;
 
+FullAdMM
+
+% SimpleADMMProgram
+end
+
+function FullAdMM
+global Simulation SystemStates SystemInputs 
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2;
+NumberOfAgents = 2
+
+LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
+WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+PreProcessedSys
+
 
 %Think on the fully distributed case
 
-Z = rand(2,2)
-W = rand(2,2)
-Lambda = 10*rand(2,2);
+Z1 = rand(2,2)
+Z2 = rand(2,2)
+Z = blkdiag(Z1,Z2);
+W1 = rand(2,2)
+W2 = rand(2,2)
+W = blkdiag(W1,W2);
+Lambda1 = rand(2,2);
+Lambda2 = rand(2,2);
 NumberOfIterations = 0;
 
 while norm(W-Z,'fro') > 1e-6 && NumberOfIterations <= 20
     
     W1 = sdpvar(2,2);
-    Constraints = [W1>=0];
-    Objective   = norm(W1-Z1+Lambda1,'fro');
+    Constraints = [W1-1e-6*eye(2)>=0];
+    Objective   = norm(W1-Z1+Lambda1,'fro')^2;
     
     optimize(Constraints,Objective);
     NextW1(1,1) = value(W1(1,1));
@@ -34,8 +59,8 @@ while norm(W-Z,'fro') > 1e-6 && NumberOfIterations <= 20
     W1 = NextW1;
     
     W2 = sdpvar(2,2);
-    Constraints = [W2>=0];
-    Objective   = norm(W2-Z2+Lambda2,'fro');
+    Constraints = [W2-1e-6*eye(2)>=0];
+    Objective   = norm(W2-Z2+Lambda2,'fro')^2;
     
     optimize(Constraints,Objective);
     NextW2(1,1) = value(W2(1,1));
@@ -44,33 +69,58 @@ while norm(W-Z,'fro') > 1e-6 && NumberOfIterations <= 20
     NextW2(2,2) = value(W2(2,2));
     W2 = NextW2;
     
-    W = blk(diag);
[…]

### 2016-11-17 R0V0.tex
minpr changes
Change paper title

@@
 % Do not put math or special symbols in the title.
-\title{Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics}
+\title{Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics}
 %
@@
 To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{W_1,\ldots,W_N:\exists Y\in\Xi,(\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),Y)\text{ is a solution to \eqref{eq:MI formulation}}\}$.
-For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
+For a set $\mathbf{G}$ define the indicator/barrier function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
 \begin{equation*}
@@
 	\begin{array}{rcl}
-		W_i^{k+1}&=&\mathbin{\mathtt{argmin}}_{W_i\in\mathbf{S}_{\succ0}^{n_i}}\left|\left|W_i^k-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
+		W_i^{k+1}&=&\mathbin{\mathtt{argmin}}_{W_i\in\mathbf{S}_{\succ0}^{n_i}}\left|\left|W_i-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
 	\end{array}
@@
 	\begin{equation*}
-		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|W_i^{k+1}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;;
+		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|W_i^{k+1}-Z_i+\Lambda_i^k\right|\right|_F^2\;;
 	\end{equation*}

### 2016-11-21 R0V0.tex
Add paragraph numbering

@@
 % 																			   %
-% Git Branch: Manchester20161020											   %
+% Git Branch: master														   %
 % 																			   %
@@
 % have to be run twice to clear warning/error messages.
+
+% Defines a paragraph counter ----------------------------------------------
+
+\usepackage{chngcntr} % To reset counter at each section
+
+% Paragraph counter 
+\newcounter{para}
+\newcommand\mypara{\par \thesection.\refstepcounter{para}\thepara.\space}
+
+\counterwithin*{para}{section} % Resets counter at each section
 
@@
 
-Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
+\mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
 The main underlying concept employed for the synthesis of feedback laws is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
@@
 
-For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
+\mypara For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
 The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.
@@
 
-For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
+\mypara For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
 However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}).
@@
 
-An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
+\mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
 One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered.
@@
 
-The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well.
+\mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well.
 This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
 
-Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
+\mypara Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
 For such systems, a property often desired is the ability to synthetize controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
 
-In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
+\mypara In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
 Consequently, for nonlinear systems the problem is very challenging.
 
-In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}.
+\mypara In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}.
 Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure.
@@
 
-For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein).
+\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein).
 However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}.
@@
 
-For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work.
+\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work.
 The systems under consideration are continuously differentiable and affine in the input.
@@
 
-The first step consists of an off-line computation.
+\mypara The first step consists of an off-line computation.
 The original system is extended with its \emph{differential / variational} formulation.
@@
 
-At this point, the three contributions of this work can be highlighted.
+\mypara At this point, the three contributions of this work can be highlighted.
 First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structure constraint, a feedback law with prescribed structure is obtained for nonlinear systems.
@@
 
-Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
+\mypara Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
 For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
@@
 
-The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded.
+\mypara The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded.
 Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.
@@
 
-Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$.
+\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$.
 A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$.
@@
 
-Consider the class of systems described by the differential equation
+\mypara Consider the class of systems described by the differential equation
 \begin{equation}\label{eq:general system}
@@
 
-A function $u^\ast\in\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ is said to be an \emph{input signal or control for \eqref{eq:general system}}.
+\mypara A function $u^\ast\in\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ is said to be an \emph{input signal or control for \eqref{eq:general system}}.
 For such a control for \eqref{eq:general system}, and for every \emph{initial condition} $x^\ast$, there exists a unique solution to \eqref{eq:general system} (\cite{Teschl2012}) that is denoted by $X(t,x^\ast,u^\ast)$, when computed at time $t$.
@@
 
-A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\times\{X^\ast\}\times\{u^\ast\}\to\mathbb{R}^m$, denoted as $k^\ast$, such that the inequality
+\mypara A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\times\{X^\ast\}\times\{u^\ast\}\to\mathbb{R}^m$, denoted as $k^\ast$, such that the inequality
 \begin{equation}\label{eq:global exponential uniform stabilizability}
@@
 
-A stronger condition than the global exponential stabilizability of a particular solution is the requirement for every forward complete solution to be globally exponentially stabilizable.
+\mypara A stronger condition than the global exponential stabilizability of a particular solution is the requirement for every forward complete solution to be globally exponentially stabilizable.
 This concept is formalized in the following definition recalled from \cite{Manchester2014a}.
@@
 
-Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
+\mypara Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
 \begin{equation}\label{eq:subsystem}
@@
 
-At this point, the problem under consideration in this paper can be stated as follows.
+\mypara At this point, the problem under consideration in this paper can be stated as follows.
 
@@
 
-The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
+\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
 Consider the network composed of systems described by the following equation.
@@
 
-A \emph{Riemannian metric on $\mathbb{R}^n$} is a symmetric positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
+\mypara A \emph{Riemannian metric on $\mathbb{R}^n$} is a symmetric positive-definite bilinear form that depends smoothly on $x\in\mathbb{R}^n$.
 In a particular coordinate system, for any pair of vectors $\delta_0,\delta_1$ of $\mathbb{R}^n$ the \emph{metric} is defined as the inner product $\langle\delta_0,\delta_{ 1}\rangle_x=\delta_0^\top M(x)\delta_1$, where $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ is a smooth function.
@@
 
-Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $c:[0,1]\to\mathbb{R}^n$ connecting $x_0=c(0)$ to $x_1=c(1)$.
+\mypara Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $c:[0,1]\to\mathbb{R}^n$ connecting $x_0=c(0)$ to $x_1=c(1)$.
 The \emph{length} and \emph{energy} of $c$ are, respectively, defined by the values
@@
 
-A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
+\mypara A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
 \begin{equation}\label{eq:general system:differential}
@@
 
-The resulting system composed of Equations \eqref{eq:general system} and \eqref{eq:general system:differential} is analyzed on the state space spanned by the vector $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
-
-Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
-
-Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTVS) (see \cite{Hespanha:2009} for more information on LTVS).
-
-The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows.
+\mypara The resulting system composed of Equations \eqref{eq:general system} and \eqref{eq:general system:differential} is analyzed on the state space spanned by the vector $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
+
+\mypara Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
+
+\mypara Lyapunov stability notions of solutions to \eqref{eq:general system:differential} are similar to those of linear time-varying systems (LTVS) (see \cite{Hespanha:2009} for more information on LTVS).
+
+\mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows.
 Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively.
@@
 
-A sufficient condition for the stability of \eqref{eq:general system:differential} is provided by analyzing the derivative of a particular function along the solutions of systems \eqref{eq:general system} and \eqref{eq:general system:differential}.
+\mypara A sufficient condition for the stability of \eqref{eq:general system:differential} is provided by analyzing the derivative of a particular function along the solutions of systems \eqref{eq:general system} and \eqref{eq:general system:differential}.
 This function is recalled from \cite{Forni2014} and \cite{Manchester2014a}.
@@
 
-The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially.
+\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially.
 The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
 
-For the class of systems considered in this paper, the following kind of metric is of interest, since it also allows the design a feedback law for system \eqref{eq:general system:differential}.
+\mypara For the class of systems considered in this paper, the following kind of metric is of interest, since it also allows the design a feedback law for system \eqref{eq:general system:differential}.
 
@@
 \end{definition}
-The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the  exponential convergence of solutions.
+\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the  exponential convergence of solutions.
 Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
@@
 
-The following result is recalled from \cite{Manchester2014a} and provides a feedback law for system~\eqref{eq:general system} given a feedback law for system~\eqref{eq:general system:differential}.
+\mypara The following result is recalled from \cite{Manchester2014a} and provides a feedback law for system~\eqref{eq:general system} given a feedback law for system~\eqref{eq:general system:differential}.
 
@@
 
-As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
+\mypara As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system~\eqref{eq:general system} are recalled below.
 
-Step 1 (Offline MI computation).
+\mypara Step 1 (Offline MI computation).
 Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$.
@@
 
-Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
+\mypara Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
 	\begin{equation}\label{eq:differential feedback law}
@@
 
-Step 2 (Online controller integration).
+\mypara Step 2 (Online controller integration).
 The feedback law for system \eqref{eq:general system} can be obtained by integration as follows.
@@
 
-From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
+\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
 This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.
 
-In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
+\mypara In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
 
@@
 
-In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
+\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
 The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
 
-To address the constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation}, the structure of the feedback defined by Equation~\eqref{eq:contracting feedback law} is obtained by imposing a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
-
-Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
+\mypara To address the constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation}, the structure of the feedback defined by Equation~\eqref{eq:contracting feedback law} is obtained by imposing a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
+
+\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
 \begin{subequations}
@@
 
-The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
+\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
 Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.
@@
 
-	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
+\mypara 	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
 Because $M$ is a block-diagonal matrix, the energy of any curve $c:[0,1]\to\mathbb{R}^n$ satisfies the following equation
@@
 
-	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
+\mypara 	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
 Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$.
@@
 
-	From Hopf-Rinow theorem (cf.
+\mypara 	From Hopf-Rinow theorem (cf.
 \cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
@@
 
-	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system~\eqref{eq:general system} is given by Equation~\eqref{eq:contracting feedback law}.
-
-	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
+\mypara 	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system~\eqref{eq:general system} is given by Equation~\eqref{eq:contracting feedback law}.
+
+\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
 	\begin{equation}\label{eq:K ODE}
@@
 
-	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
+\mypara 	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
 This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
 
-	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
+\mypara 	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
 This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
@@
 
-	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
+\mypara 	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
 	\begin{equation*}
@@
 
-Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} that can be employed to design a distributed controller for system~\eqref{eq:general system}.
+\mypara Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} that can be employed to design a distributed controller for system~\eqref{eq:general system}.
 More precisely, from the first variation of the energy function, the time derivative of $e$ yields the equation
@@
 
-Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
+\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
 The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.
@@
 
-For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}.
+\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}.
 This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
@@
 
-Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
+\mypara Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
@@
 
-	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
+\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
 For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 
-   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$.
+\mypara    Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$.
 The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
@@
 
-  	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
+\mypara   	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
   	\begin{equation}\label{eq:MIF}
@@
 
-Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph.
+\mypara Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph.
 The obtained graph is said to be a \emph{chordal embedding}.
@@
 
-Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
+\mypara Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
 If the vector fields $f$ and $B$ are polynomials and the search for the matrix $F$ is restricted to have appropriate diagonal structure, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
 
-A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds.
+\mypara A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds.
 It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
 
-The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
+\mypara The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
 		\begin{align*}
@@
 
-Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
+\mypara Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
 \begin{subequations}
@@
 
-The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
+\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
 To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{W_1,\ldots,W_N:\exists Y\in\Xi,(\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),Y)\text{ is a solution to \eqref{eq:MI formulation}}\}$.
@@
 
-The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
+\mypara The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
 \begin{equation*}
@@
 
-Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
-
-For monotone systems (i.e., systems for which the some order of initial conditions is preserved along the flow of the vector field) described by a vector field that is continuously differentiable and whose gradient matrix is Hurwitz at the origin, there exists a sum-separable Lyapunov function in a neighborhood of the origin \cite[Theorem 3.4]{Dirr2015}.
-
-For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.
+\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
+
+\mypara For monotone systems (i.e., systems for which the some order of initial conditions is preserved along the flow of the vector field) described by a vector field that is continuously differentiable and whose gradient matrix is Hurwitz at the origin, there exists a sum-separable Lyapunov function in a neighborhood of the origin \cite[Theorem 3.4]{Dirr2015}.
+
+\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.
 Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
 
-Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open.
+\mypara Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open.
 As mentioned before, the main advantage to look for control-contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems.
@@
 
-A case where structured controller design is relevant is on distributed design for network systems.
+\mypara A case where structured controller design is relevant is on distributed design for network systems.
 Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
@@
 
-For each index $i\in\mathbb{N}_{[1,N]}$, define the vectors $q_i=(x_i,y_i)$, $\breve{q}_i=(x_{i-1},x_{i+1})$ and let $q=(q_1,\ldots,q_N)$. Denote also
+\mypara For each index $i\in\mathbb{N}_{[1,N]}$, define the vectors $q_i=(x_i,y_i)$, $\breve{q}_i=(x_{i-1},x_{i+1})$ and let $q=(q_1,\ldots,q_N)$. Denote also
 \begin{align*}
@@
 
-Note that system \eqref{eq:example} is not feedback linearizable in the sense of \cite{Isidori:1995}, because the vector fields
+\mypara Note that system \eqref{eq:example} is not feedback linearizable in the sense of \cite{Isidori:1995}, because the vector fields
 \begin{align*}
@@
 
-When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
+\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
@@
 
-To show the advantages of the method proposed in this paper, a benchmark was run for a network composes by $N=4$ systems and in three scenarios, according to the constraints imposed on the matrix $Y$.
+\mypara To show the advantages of the method proposed in this paper, a benchmark was run for a network composes by $N=4$ systems and in three scenarios, according to the constraints imposed on the matrix $Y$.
 Namely, the unconstrained case, the ``neighbor case'', and the fully decentralized (diagonal) case.
@@
 
-In all cases, the computed matrix $W$ has a block-diagonal structure as follows
+\mypara In all cases, the computed matrix $W$ has a block-diagonal structure as follows
 \begin{equation*}
@@
 
-In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
+\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
 More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$.
@@
 
-For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}.
+\mypara For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}.
 More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.
@@
 
-In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
+\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
 The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
@@
 
-The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.
-
-The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds.
+\mypara The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.
+
+\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds.
 The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
@@
 
-In the last case, the fully decentralized scenario has been considered.
+\mypara In the last case, the fully decentralized scenario has been considered.
 The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds.
@@
 
-Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this illustration: unconstrained, ``neighbor'' and fully decentralized.
+\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this illustration: unconstrained, ``neighbor'' and fully decentralized.
 
@@
 
-According to the graph shown in Figure \ref{fig:time graph}, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} was of the same order of magnitude for the three cases.
+\mypara According to the graph shown in Figure \ref{fig:time graph}, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} was of the same order of magnitude for the three cases.
 However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor''-constrained case which, in turn, takes more time than the fully decentralized-constrained case.
@@
 
-Regarding the on-line integration phase, since the matrices $W$ computed in each case is  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$.
+\mypara Regarding the on-line integration phase, since the matrices $W$ computed in each case is  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$.
 For each case, and for each index $i\in\mathbb{N}_{[1,4]}$, the feedback law is  given by the formula
@@
 
-In this work, input-affine nonlinear systems were considered.
+\mypara In this work, input-affine nonlinear systems were considered.
 The problem was the design of structured feedback laws.
@@
 
-In terms of dynamic programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
+\mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
 Although this is one of its main advantages over the search of control-Lyapunov functions, it does not scale well.
 
-For systems described by a non-fully connected graph, the approach presented in this paper exploits sparsity to design feedback laws with a prescribed structure.
+\mypara For systems described by a non-fully connected graph, the approach presented in this paper exploits sparsity to design feedback laws with a prescribed structure.
 More precisely, by imposing a block-diagonal structure on the matrix describing the metric, a controller with a prescribed structure can be synthesized.

### 2016-11-21 R0V0.tex
Change the formulation of Problem 1. Add pargraph I.22 to explain that the controller can have a different topology than then plant.

@@
 \usepackage{mathrsfs}
+
+\usepackage{enumerate}
 
@@
 where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
+Using this decomposition, the interconnection of system~\eqref{eq:general system} is described by the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.
 
@@
 \begin{problem}\label{problem formulation}
-	For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
-Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into the set $\mathscr{K}(i)\subset\mathbb{N}_{[1,N]}$.
+	\begin{enumerate}[{P}$_1$.]\hfill
+		\item For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
+Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;
+
+		\item Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among the components of the controller, the set $\mathscr{K}(i)$ is composed of elements from $\mathscr{E}_c$.
+	\end{enumerate}
 \end{problem}
+
+\mypara In other words, item P$_1$ of Problem~\ref{problem formulation} states that the controller is decomposed into smaller components.
+Each of these depends on the states  prescribed by the set $\mathscr{K}$.
+Item P$_2$ of Problem~\ref{problem formulation} states that this set may not necessarily correspond to the states which system~\eqref{eq:subsystem} depends on.
+This item addresses the case in which there exists a difference between the communication topology of the network represented by Equation~\eqref{eq:general system} and the communication topology of the distributed controller.
 
@@
 \begin{definition}\label{def:}
-		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if for fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively, there exists a value $\lambda>0$ such that the inequality
+		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for fixed controls $u\equiv0$ and $\delta_u\equiv0$ for systems~\eqref{eq:general system} and \eqref{eq:general system:differential}, there exists a value $\lambda>0$ such that the inequality
 	 	 \begin{equation}
-	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,u,\delta_u))\leq -\lambda V(x,\delta_x)
+	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,0,0))\leq -\lambda V(x,\delta_x)
  	 	 \end{equation}
@@
 
-\section{Distributed Design of Decentralized Controllers}
+\section{Distributed Design of Distributed Controllers}
 
@@
 
-\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
+\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stabilizability of the origin, for some classes of systems.
 

### 2016-12-02 R0V0.tex
minor change
First formulation of the ADMM paragraph using the Gramians

@@
 $M\succeq 0$) stands for $M$ being positive (resp.
-semi)definite.
+semi)definite such a class of matrices is denoted as $\mathbf{S}_{\star0}^n=\{M\in\mathbb{R}^{n\times n}:M\star0,M=M^\top\}$, where $\star\in\{\succ,\succeq,\prec,\preceq\}$.
 For a matrix $M\succ0$, the notation $\mathbin{\mathtt{chol}}(M)$ stands for the \emph{upper-triangular Cholesky factor $U$} satisfying $A=U^\top U$.
@@
 		implies that the inequality
-		\begin{align}
-			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
-		\end{align}
+		\begin{equation}\label{eq:Artstein-Sontag:inequality}
+			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
+		\end{equation}
 		holds, where $\dot{M}:=\partial_{f+Bu}M$.
@@
 
-\section{Design of Decentralized Controllers}\label{sec:Design of Decentralized Controllers}
+\section{Design of Distributed Controllers}\label{sec:Design of Decentralized Controllers}
 
@@
 \mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
-To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{W_1,\ldots,W_N:\exists Y\in\Xi,(\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),Y)\text{ is a solution to \eqref{eq:MI formulation}}\}$.
-For a set $\mathbf{G}$ define the indicator/barrier function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
+To use this methodology, define the set of (resp.
+sum-of-squares (SOS)) polynomials $\mathbb{R}[x]$ (resp.
+$\mathbb{SOS}[x]$), and denote the degree of a polynomial $p\in\mathbb{R}[x]$ as $\deg(p)$.
+
+\mypara By applying the change of coordinates $\eta=M\delta$ and defining the matrix $W=M^{-1}$, inequality~\eqref{eq:Artstein-Sontag:inequality} is satisfied, whenever the matrix inequality
+\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
+ 	-\dot{W}+AW + WA^\top+2\lambda W\prec0
+\end{equation} 
+holds.
+
+\mypara The search the function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ can be relaxed to a semidefinite program.
+Whenever $f$ and $B$ are polynomials, this program is cast in terms of the sum-of-squares (SOS) feasibility program \cite{Parrilo2000}.
+To that end, introduce the vector $v\in\mathbb{R}^n$ and define the polynomials
+\begin{align*}
+	p_W=&\ v^\top W v\;,\\
+	p_{MI}=&\ -v^\top(-\dot{W}+AW + WA^\top+2\lambda W)v\;.
+\end{align*}
+The feasibility program consists of finding symmetric $Q_W\succeq0$ and $Q_{MI}\succeq0$, called \emph{Gramians}, with appropriate dimensions and such that $p_W=\bar{v}^\top Q_W\bar{v}$ and $p_{MI}=\bar{v}^\top Q_{MI}\bar{v}$ belong to $\mathbb{R}[x,v]$, where $\bar{v}$ is vector of monomials on the variables $x_i,\ldots,x_N$ and $v_1,\ldots,v_N$.
+
+\mypara Once $Q$ has been computed, employing Finsler's lemma \cite[Lemma~11.1]{CalafioreGhaoui2014} pointwisely, the existence of a function $Y:\mathbb{R}^n\to\mathbb{R}^{n\times m}$ satisfying MI~\eqref{eq:MI formulation} is ensured.
+
+\mypara Now that the computation of a positive definite $W$ satisfying inequality~\eqref{eq:Artstein-Sontag:inequality:dual} in terms of SOS polynomials has been explained, the next step is to solve the SOS feasibility using ADMM.
+
+\mypara Define the set $\mathbf{T}=\{Z_1,\ldots,Z_N:Z_W=\mathbin{\mathtt{diag}}(Z_1,\ldots,Z_N)\succeq0,p_{MI}=\bar{v}^\top Z_W\bar{v}\in\mathbb{R}[x,v]\}$.
+For a set $\mathbf{G}$ define the indicator (also known as barrier) function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
 \begin{equation*}
@@
 	\begin{array}{rl}
-		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
-		\text{subject to}&W_i-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{\alpha_i},Q_{W_i})\\
+		\text{subject to}&Q_{W_i}-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;,
 	\end{array}
 \end{equation*}
+where $\alpha_i=(2n_i+d_i)!/(d_i!(2n_i)!)$, $d_i=\deg(v_i^\top W_iv_i)$ and $v_i\in\mathbb{R}^{n_i}$.
+
 The ADMM algorithm can be written as
@@
 	\begin{array}{rcl}
-		W_i^{k+1}&=&\mathbin{\mathtt{argmin}}_{W_i\in\mathbf{S}_{\succ0}^{n_i}}\left|\left|W_i-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
+		Q_{W_i}^{k+1}&=&\mathbin{\mathtt{argmin}}_{Q_{W_i}\in\mathbf{S}_{\succ0}^{\alpha_i}}\left|\left|Q_{W_i}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
 	\end{array}
@@
 	\begin{equation*}
-		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|W_i^{k+1}-Z_i+\Lambda_i^k\right|\right|_F^2\;;
+		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i+\Lambda_i^k\right|\right|_F^2\;;
 	\end{equation*}
@@
 	\begin{equation*}
-		\Lambda_i^{k+1}=X_i^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
+		\Lambda_i^{k+1}=Q_{W_i}^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
 	\end{equation*}
 \end{enumerate}
-Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $W_i$ and the values $\Lambda_i$.
+Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $Q_{W_i}$ and the values $\Lambda_i$.
 

### 2016-12-02 R0V0.tex
Remove .ps file

@@
 
-\mypara Define the set $\mathbf{T}=\{Z_1,\ldots,Z_N:Z_W=\mathbin{\mathtt{diag}}(Z_1,\ldots,Z_N)\succeq0,p_{MI}=\bar{v}^\top Z_W\bar{v}\in\mathbb{R}[x,v]\}$.
+\mypara Define the set $\mathbf{T}=\{Z_1,\ldots,Z_N:Z=\mathbin{\mathtt{diag}}(Z_1,\ldots,Z_N),p_{MI}=\bar{v}^\top Z\bar{v}\in\mathbb{R}[x,v]\}$.
 For a set $\mathbf{G}$ define the indicator (also known as barrier) function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
@@
 	\begin{array}{rl}
-		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{\alpha_i},Q_{W_i})\\
+		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succeq0}^{\alpha_i},Q_{W_i})\\
 		\text{subject to}&Q_{W_i}-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;,
@@
 
-The ADMM algorithm can be written as
+\mypara The ADMM algorithm can be written as
 \begin{enumerate}
@@
 	\begin{array}{rcl}
-		Q_{W_i}^{k+1}&=&\mathbin{\mathtt{argmin}}_{Q_{W_i}\in\mathbf{S}_{\succ0}^{\alpha_i}}\left|\left|Q_{W_i}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
+		Q_{W_i}^{k+1}&=&\mathbin{\mathtt{argmin}}_{Q_{W_i}\in\mathbf{S}_{\succeq0}^{\alpha_i}}\left|\left|Q_{W_i}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
 	\end{array}
@@
 Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $Q_{W_i}$ and the values $\Lambda_i$.
+
+\mypara As $k\to\infty$, for each index $i\in\mathbb{N}_{[1,N]}$, the Gramians $Q_{W_i}$ will coincide with the matrices $Z_i$.
+Consequently, the block-diagonal matrix $Z$ is symmetric and positive definite.
+Thus, $p_{MI}\in\mathbb{SOS}[x,v]$ and, for each index $i\in\mathbb{N}_{[1,N]}$, $v_i^\top W_iv_i\in\mathbb{SOS}[x_i,v_i]$.
+Hence, $M=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)^{-1}$ is a separable control contraction metric for system \eqref{eq:general system}.
 

### 2016-12-02 TheoreticalExample2/ADMMdraft3.m
Minor change

@@ -63,8 +63,8 @@ InputVector = [input1; input2];
 x1dot = -x1 - x1^3 + y1^2 -d*(+1*x1^3 -1*x2^3);
 x2dot = -x2 - x2^3 + y2^2 -d*(-1*x1^3 +1*x2^3);
 
-y1dot = -y1;
-y2dot = -y2;
+y1dot = 0;
+y2dot = 0;
 
 
 % Writing Vector Fields and Jacobian Matrices 

### 2016-12-02 TheoreticalExample2/ADMMdraft4.m
Start a new file to verify is the ADMM solver is correct.

@@ -1,0 +1,136 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Title: Solving LMI with SOS                                             %
+% Description: Write the LMIs as polynomials and then solve with optimize %
+% 2 agents are considered                                                 %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function ADMMdraft3
+
+clear all
+clc
+close all
+
+% System Definition -------------------------------------------------------
+
+global Simulation SystemStates SystemInputs 
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2;
+NumberOfAgents = 2
+
+LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
+% WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+% PreProcessedSys
+
+% System Defintion --------------------------------------------------------
+
+% Writing System States: xy
+
+x1 = sdpvar(1);
+x2 = sdpvar(1);
+
+y1 = sdpvar(1);
+y2 = sdpvar(1);
+
+
+% Writing System Inputs: u
+
+u1 = sdpvar(1);
+u2 = sdpvar(1);
+
+
+% Definition of the Variables q and inputs 
+
+q1 = [x1; y1];
+input1 = [u1];
+
+q2 = [x2; y2];
+input2 = [u2];
+
+q = [q1; q2];
+
+InputVector = [input1; input2];
+
+
+% Writing System Equations 
+
+x1dot = -x1 - x1^3 + y1^2 -d*(+1*x1^3 -1*x2^3);
+x2dot = -x2 - x2^3 + y2^2 -d*(-1*x1^3 +1*x2^3);
+
+y1dot = 0;
+y2dot = 0;
+
+
+% Writing Vector Fields and Jacobian Matrices 
+
[…]

### 2016-12-02 TheoreticalExample2/ADMM.m
Reformulate for the 4 agents case

@@ -24,7 +24,7 @@ SystemInputs = ['u'];
 SystemParameters = ['d'];
 d = 1e-2; %Maximum value to avoid numerical problems
 % d = 0;
-NumberOfAgents = 2
+NumberOfAgents = 4
 NumberOfStates = length(SystemStates);
 
 LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
@@ -42,8 +42,12 @@ ErrorVector = zeros(MaxNumberOfIterations,1);
 
 Gramian_MI1 = rand(NumberOfMonomials);
 Gramian_MI2 = rand(NumberOfMonomials);
+Gramian_MI3 = rand(NumberOfMonomials);
+Gramian_MI4 = rand(NumberOfMonomials);
 Lambda1     = rand(NumberOfMonomials);
 Lambda2     = rand(NumberOfMonomials);
+Lambda3     = rand(NumberOfMonomials);
+Lambda4     = rand(NumberOfMonomials);
 
 %% System Definition ======================================================
 
@@ -51,15 +55,20 @@ Lambda2     = rand(NumberOfMonomials);
 
 x1 = sdpvar(1);
 x2 = sdpvar(1);
+x3 = sdpvar(1);
+x4 = sdpvar(1);
 
 y1 = sdpvar(1);
 y2 = sdpvar(1);
-
+y3 = sdpvar(1);
+y4 = sdpvar(1);
 
 % Writing System Inputs: u
 
 u1 = sdpvar(1);
 u2 = sdpvar(1);
+u3 = sdpvar(1);
+u4 = sdpvar(1);
 
 
 % Definition of the Variables q and inputs
@@ -70,19 +79,28 @@ input1 = [u1];
 q2 = [x2; y2];
 input2 = [u2];
 
-q = [q1; q2];
+q3 = [x3; y3];
+input3 = [u3];
 
-InputVector = [input1; input2];
+q4 = [x4; y4];
+input4 = [u4];
+
+q = [q1; q2; q3; q4];
+
+InputVector = [input1; input2; input3; input4];
 
 
 % Writing System Equations
 
-x1dot = -x1 - x1^3 + y1^2 -d*(+1*x1^3 -1*x2^3);
-x2dot = -x2 - x2^3 + y2^2 -d*(-1*x1^3 +1*x2^3);
[…]

### 2016-12-02 R0V0.tex
Address the comment on the last Ian's review.
Write the matrix W computed for the example

@@
 \begin{theorem}\label{thm:main result}
-	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system:differential}, then there exists a solution to Problem~\ref{problem formulation}.
+	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
 \end{theorem}
+
+\mypara The existence of a control contraction metric for system~\eqref{eq:general system} implies that there exist matrices $(W,Y)$ that are a solution to the MI~\eqref{eq:MI formulation} with structure prescribed by the set $\Xi$.
 
@@
 
-	The MI \eqref{eq:MI formulation} implies that the inequality
+\mypara	The MI \eqref{eq:MI formulation} implies that the inequality
 	\begin{equation*}
@@
 	\begin{equation*}
-		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i+\Lambda_i^k\right|\right|_F^2\;;
+		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i-\Lambda_i^k\right|\right|_F^2\;;
 	\end{equation*}
@@
 \mypara As $k\to\infty$, for each index $i\in\mathbb{N}_{[1,N]}$, the Gramians $Q_{W_i}$ will coincide with the matrices $Z_i$.
-Consequently, the block-diagonal matrix $Z$ is symmetric and positive definite.
+Consequently, the block-diagonal matrix $Z$ is symmetric and positive semidefinite.
 Thus, $p_{MI}\in\mathbb{SOS}[x,v]$ and, for each index $i\in\mathbb{N}_{[1,N]}$, $v_i^\top W_iv_i\in\mathbb{SOS}[x_i,v_i]$.
@@
 
+\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} leads to the following components of the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
+
+\begin{figure*}
+\begin{align*}
+	W_1(q_1)=1\times10^{-7}\begin{bmatrix}
+	18-15x_1-28y_1+11.2y_1^2+3.2x_1^2+1.2x_1y_2&9.3+35x_1-43y_1+28y_1^2-16x_1^2-16x_1y_1\\
+	*&4.9+40x_1-37y_1+72y_1^2+84x_1^2-155x_1y_1
+	\end{bmatrix}\;,\\
+	W_2(q_2)=1\times10^{-7}\begin{bmatrix}1-3.7x_2+2.3y_2+1.3y_2^2+3.5x_2^2-4.3x_2y_2&
+	-0.6-0.6x_2+y_2+2y_2^2+3.5x_2^2-5.5x_2y_2\\
+	*&0.4+2.3x_2-2.3y_2+3.3y_2^2+3.4x_2^2-6.7x_2y_2
+	\end{bmatrix}\;,\\
+	W_3(q_3)=1\times10^{-7}\begin{bmatrix}
+		127-248x_3+18y_3+y_3^2+122x_3^2-18x_3y_3&
+		-98+146x_3+19y_3+1.9y_3^2-50x_3^2-22x_3y_3\\
+		*&76-78x_3-42y_3+6.4y3^2+21x_3^2+20x_3y_3
+	\end{bmatrix}\;,\\
+	W_4(q_4)=1\times10^{-6}\begin{bmatrix}
+	22+4x_4-17y_4+8.8y_4^2+9.4x_4^2+12x_4y_4&
+	-8.6-5.9x_4+1.8y_4-4.2y_4^2-9.7x_4^2-12x_4y_4\\
+	*&4.3+7.5x_4+2.8y_4+3.2y_4^2+10x_4^2+11x_4y_4
+	\end{bmatrix}\;.
+\end{align*}
+\end{figure*}
+
 \section{Conclusion}\label{sec:Conclusion}

### 2016-12-07 R0V0.tex
Minor change

@@
 		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
-		\arg(Y_{ij})\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
+		\arg(Y_{ij}(\cdot,u))\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
 	\end{align*}
@@
 \begin{equation*}
-N\dfrac{N+1}{2}\begin{pmatrix}
+n\dfrac{n+1}{2}\begin{pmatrix}
 n+d\\ d
-\end{pmatrix}^2
+\end{pmatrix}
 \end{equation*}
@@
 
-\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} leads to the following components of the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
+\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
 

### 2016-12-16 IanComments_15th_Dec.tex
Ian add a documento with comments to be addressed.

\documentclass[11pt]{article}
\usepackage{IRM}
\begin{document}

\begin{enumerate}
\section{Introduction}
	\item Overall, this introduction is very focused on "nonlinear" and not much about "distrbuted" until paragraph 5/6. This needs to be fundamentally rethought: right from the start we want to be talking about large-scale networked dynamic systems and the challenges they pose, not getting into the weeds of nonlinear control theory.
	\item I.1 Typo: "the Lyapunov's" should be "Lyapunov's". More broadly, is this claim defensible? Almost all controllers in practice are PID or MPC, neither of which is (explicitly) based on Lyapunov's theory. What does it mean for a design problem to be translated in terms of dynamic programming? I don't understand this at all
	\item I.2: LQR is not defined. Why do you say SOS is often employed for feedback synthesis? As far as I know CCM is the first case in which this is possible.
	\item I.3: Why "by the time this paper was submitted"? That implies that general results came after. 
	\item I.5: "may require a function with $n^2$ terms. Is this supposed to be restricted to linear systems? For nonlinear, how can you even set a finite dimension?
	\item I.7, what has this statement got to do with dynamic programming?
	\item I.8 Isn't the idea of [23] that actually NO LMIs are solved, not just a reduced number? (Instead one can solve LPs)
	\item I.9 Shouldn't we be talking about CLFs here? We are doing synthesis, not just analysis.
	\item I.20: is the graph $\mathcal G$ defined? Shouldn't we define the graph first, and then define $\u x$ in terms of it?
	\item I.21: what is the difference between problems P1 and P2? How does $\mathcal V_c$ differ from $\mathcal K(i)$? Are these actually defined anywhere?
	\item I.22 How do you know it was due to the number of variables, and not, e.g., the number of constraints? Shouldn't we just say due to memory constraints?
	\item I.25: Shouldn't this be something like
	\[
`	\pder{x_k}\left(f_j+\sum_iB_{ji}u_i\right)
	\]
	for the multi-input case? Otherwise you are mixing index of $\dot x$ with index of $u$.
	\item I.30: why fixed $u$ and $\delta_u$? If $u$ is fixed, then $\delta_u=0$ and we are just looking at autonomous systems, right? What is meant be "the norm" here? A metric defines a (possibly state-varying) norm for the differential dynamics. Is this norm in this paragraph the Euclidean norm, or the norm from the metric?
	\item I.31, again Why $u=0$ here? The right hand side of (7) should have $X$ and $\Delta$ as arguments, not $x$ and $\delta_x$. Why not just write
	\[
	ddt V(x(t),\delta_x(t))\le -\lambda V(x(t)\delta_x(t))
	\]
	where $x(t)=X..., \delta_x(t) = \Delta(...$
	\item I.34. Do you mean Artstein-Sontag condition applied to the differential dynamics?
	\item I.36-I.39 Here we should give the alternative CLF construction, as it will generally be more tractable in practice.
	\item I.40: distributely is not a word. Replace with "cannot generally be computed in a distributed manner".
	\item I.41: not block-diagonal but separable.
\section{Design of Distributed Controllers}
\item This section includes a theorem about Problem 1. But actually it seems to me it is not correctly stated. If there exists a SSCCM, then there is a solution to the distributed control problem where the control dependency is defined by $\u x$. This follows from the CLF result. But for arbitrary control dependency, we need also conditions on the sparsity patterns and dependency of $Y$ explicitly stated in the theorem.
\item II.3: I think we need to clean up the definition of $\Xi$. I still can't understand what this is supposed to mean! It should be much simpler.
\item II.8: Why does this follow from $M$ being positive-definite? Don't you mean "since $M$ is separable"? This should be clarified. (13) can be split explicitly into $N$ separate optimization problems depending on different decision variables. Should we use $\arg\min$ rather than $\arg\inf$? If an $\arg$ exists, then a $\min$ exists as well.
\section{Distributed Design of Distributed Controllers}
\item This section looks very-much "first draft". It's not clear who the methods of chordal graphs, scaled diagonal dominance, and ADMM are used together, or whether they are different approaches with different strengths.
\item How is scaled-diagonal-dominance related to networked small gain conditions?
\item III.12: why is this change of variables introduced here? We use it all through the paper. The inequality (18) is just for analysis, not synthesis. Why is it introduced here? Should it be over the kernel of $B$?
\item III.14 pointwisely is not a word. I don't see what Finsler's theorem has to do with this section.
\section{Numerical Experiment}
\item Can we do, in addition, a more interesting graph than a line (like the one you made a figure for with 4 nodes)? Or a randomly-generated scale-free network?
\item What is the results of SDD and ADMM for the example?
\item Can we show results of the systems stabilizing? E.g. time-graphs of convergence? How do we compare performance of the unconstrained, neighbour, and decentralized cases?
\section{Conclusion}
\item Why is the first sentence here "In this work, input-affine nonlinear systems were considered". Is that really a strong claim of what we aim to do?? Think carefully about opening sentences in abstract, intro, and conclusion as these define the reviewer's frame of mind, and the ultimate impact on readers.

	\end{enumerate}

\end{document}

### 2016-12-16 R0V0.tex
Addressed comment 9 from introduction

@@
 
-\mypara Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
+\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$.
+For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
 \begin{equation}\label{eq:subsystem}
@@
 where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
-Using this decomposition, the interconnection of system~\eqref{eq:general system} is described by the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.
 

### 2016-12-16 R0V0.tex
Item 2

@@
 \mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
-The main underlying concept employed for the synthesis of feedback laws is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
-In terms of computation, controller design problems are often translated in terms of dynamic programming.
+One of the main underlying concepts employed for the synthesis of feedback laws is Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
+In terms of computation, controller design problems are often translated in terms of optimization.
 

### 2016-12-16 R0V0.tex
Item 6

@@
 
-\mypara In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
+\mypara In terms of semidefinite programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
 Consequently, for nonlinear systems the problem is very challenging.

### 2016-12-16 R0V0.tex
item 7

@@
 Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure.
-The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to reduce the number of LMIs to be solved.
+The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to solve linear programs.
 

### 2016-12-16 R0V0.tex
Item 8

@@
 
-\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein).
-However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}.
+\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein).
+However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions).
 The case can be even worse, when structural constraints are considered.

### 2016-12-16 R0V0.tex
Item 12
Item 13

@@
 $\mathbb{R}^m$).
-The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by
-\begin{equation*}
-	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
+The matrix $A\in\mathbb{R}^{n\times n}$ has components given by
+\begin{equation*}
+	A_{jk}(x,u)=\dfrac{\partial}{\partial x_k}\left[f_j+\sum_{i=1}^{m_j} B_{ji}u_i\right]
 \end{equation*}
@@
 \mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows.
-Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively.
-If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta_u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
+Given a fixed two control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$.
+If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
 The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

### 2016-12-16 R0V0.tex
Item 14

@@
 \begin{definition}\label{def:}
-		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for fixed controls $u\equiv0$ and $\delta_u\equiv0$ for systems~\eqref{eq:general system} and \eqref{eq:general system:differential}, there exists a value $\lambda>0$ such that the inequality
+		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
 	 	 \begin{equation}
-	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,0,0))\leq -\lambda V(x,\delta_x)
- 	 	 \end{equation}
- 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
+	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
+ 	 	 \end{equation}
+ 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
 \end{definition}

### 2016-12-16 R0V0.tex
Item 15

@@
 \end{definition}
-\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the  exponential convergence of solutions.
+\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}.
 Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.

### 2016-12-16 R0V0.tex
Item 17
item 18

@@
 \mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
-This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.
-
-\mypara In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$.
+This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner.
+
+\mypara In this paper, these limitations are addressed by imposing a separable structure over $W$.
 

### 2016-12-16 R0V0.tex
Item 21

@@
 
-\mypara 	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
+\mypara Since $M$ has a block-diagonal structure, it can be split into $N$ separate optimization problems depending on
+different decision variables.
+Moreover, the positive definiteness of $M$ implies also that the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
 Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$.
@@
 	\begin{equation*}
-		\gamma_i=\arg\inf e(c_i)\Leftrightarrow\gamma=\arg\inf\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+		\gamma_i=\arg\min e(c_i)\Leftrightarrow\gamma=\arg\min\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
 	\end{equation*}
@@
 	\begin{align*}
-		\gamma_i=\arg\inf_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
+		\gamma_i=\arg\min_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
 	\end{align*}

### 2017-01-10 R0V0.tex
item I.5

@@
 \mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well.
-This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
+This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
+In general, the case is worse, for nonlinear systems.
 

### 2017-01-10 R0V0.tex
Item 10.

@@
 \begin{problem}\label{problem formulation}
-	\begin{enumerate}[{P}$_1$.]\hfill
-		\item For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
+ For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
 Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;
-
-		\item Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among the components of the controller, the set $\mathscr{K}(i)$ is composed of elements from $\mathscr{E}_c$.
-	\end{enumerate}
 \end{problem}
 
-\mypara In other words, item P$_1$ of Problem~\ref{problem formulation} states that the controller is decomposed into smaller components.
+\mypara In other words, Problem~\ref{problem formulation} states that the controller is decomposed into smaller components.
 Each of these depends on the states  prescribed by the set $\mathscr{K}$.
-Item P$_2$ of Problem~\ref{problem formulation} states that this set may not necessarily correspond to the states which system~\eqref{eq:subsystem} depends on.
-This item addresses the case in which there exists a difference between the communication topology of the network represented by Equation~\eqref{eq:general system} and the communication topology of the distributed controller.
+The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$.
+Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among different controllers, the set $\mathscr{K}$ can be defined as a subset of $\mathscr{V}_c$.
 

### 2017-01-10 R0V0.tex
Item 11. See paragraph I.23

@@
 \end{equation}
-As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to the number of variables.
+As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints.
 However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

### 2017-01-10 R0V0.tex
Minor typo
Item 22. See new paragraph# III.2

@@
 This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
-For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done parallel.
-To this end some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
+For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done in parallel.
+
+\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance.
+The first exploits the network topology to decompose it into smaller connected components.
+The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality below.
+Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling.
+Note that these methodologies can be used either separately or together.
+The latter would appropriate, when the smaller components of the network have high rank.
+Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
 

### 2017-01-10 R0V0.tex
Item 24

@@
 
-\mypara By applying the change of coordinates $\eta=M\delta$ and defining the matrix $W=M^{-1}$, inequality~\eqref{eq:Artstein-Sontag:inequality} is satisfied, whenever the matrix inequality
+\mypara Inequality~\eqref{eq:Artstein-Sontag:inequality} is satisfied, whenever the matrix inequality
 \begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
- 	-\dot{W}+AW + WA^\top+2\lambda W\prec0
-\end{equation} 
-holds.
+ 	\ker(B)^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)\ker(B)\prec0
+\end{equation} 
+holds, where $\ker(B)$ is a full-rank matrix satisfying $B^\top\ker(B)\equiv0$.
 
@@
 	p_W=&\ v^\top W v\;,\\
-	p_{MI}=&\ -v^\top(-\dot{W}+AW + WA^\top+2\lambda W)v\;.
+	p_{MI}=&\ -v^\top\ker(B)^\top(-\dot{W}+AW + WA^\top+2\lambda W)\\
+	&\ker(B)v\;.
 \end{align*}

### 2017-01-10 R0V0.tex
Item 25
change email for contact

@@
 \thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
-Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt humberto.shiromoto@ieee.org}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
+Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt h.stein.shiromoto@gmail.com}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
 }
@@
 The feasibility program consists of finding symmetric $Q_W\succeq0$ and $Q_{MI}\succeq0$, called \emph{Gramians}, with appropriate dimensions and such that $p_W=\bar{v}^\top Q_W\bar{v}$ and $p_{MI}=\bar{v}^\top Q_{MI}\bar{v}$ belong to $\mathbb{R}[x,v]$, where $\bar{v}$ is vector of monomials on the variables $x_i,\ldots,x_N$ and $v_1,\ldots,v_N$.
-
-\mypara Once $Q$ has been computed, employing Finsler's lemma \cite[Lemma~11.1]{CalafioreGhaoui2014} pointwisely, the existence of a function $Y:\mathbb{R}^n\to\mathbb{R}^{n\times m}$ satisfying MI~\eqref{eq:MI formulation} is ensured.
 

### 2017-01-12 TheoreticalExample2/ADMMCyclic.m
Create new files for the cyclic example

@@ -1,0 +1,568 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Git Branch: master                                        %
+% Description: In this branch, the gramian matrix is composed by monomials%
+% from the Ws                                                             %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function ADMM
+
+clear all
+clc
+close all
+dbstop if error
+
+%% Initialization =========================================================
+
+global Simulation SystemStates SystemInputs
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2; %Maximum value to avoid numerical problems
+% d = 0;
+NumberOfAgents = 4
+NumberOfStates = length(SystemStates);
+
+LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
+LaplacianMatrix = CyclicLaplacianGenerator(NumberOfAgents);
+% WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+% PreProcessedSys
+
+PolymialDegree = 2;
+NumberOfMonomials = nchoosek(2*NumberOfStates + PolymialDegree,PolymialDegree);
+
+MaxNumberOfIterations = 50;
+IterationCounter      = 1;
+ErrorTolerance = 1e-4;
+Error = Inf;
+ErrorVector = zeros(MaxNumberOfIterations,1);
+
+Gramian_MI1 = rand(NumberOfMonomials);
+Gramian_MI2 = rand(NumberOfMonomials);
+Gramian_MI3 = rand(NumberOfMonomials);
+Gramian_MI4 = rand(NumberOfMonomials);
[…]

### 2017-01-12 TheoreticalExample2/CyclicLaplacianGenerator.m

@@ -1,0 +1,40 @@
+function L=CyclicLaplacianGenerator(NAgents)
+
+L = zeros(NAgents,NAgents);
+
+for RowCounter = 1:NAgents
+    
+    for ColumnCounter = 1:NAgents
+        
+        if ColumnCounter >= RowCounter
+            
+            if ColumnCounter == RowCounter
+                    
+                    L(RowCounter,ColumnCounter) = 1;
+                
+            else
+                
+                if ColumnCounter == RowCounter - 1 || ColumnCounter == RowCounter + 1
+                    L(RowCounter,ColumnCounter) = -1;
+                end
+                
+                if RowCounter == 1 && ColumnCounter == NAgents
+                    L(RowCounter,ColumnCounter) = -1;
+                end
+                
+                if RowCounter == NAgents && ColumnCounter == 1
+                    L(RowCounter,ColumnCounter) = -1;
+                end
+                
+            end
+            
+        end
+        
+    end
+    
+end
+
+L = L + transpose(L);
+
+
+end

### 2017-01-12 TheoreticalExample2/CyclicTopology.m

@@ -1,0 +1,89 @@
+function CyclicTopology
+clear all
+close all
+clc
+warning off
+
+global Simulation SystemStates SystemInputs 
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2;
+lambda = 1e-1; % Max value for SOS feasibility
+Option       = 'Neighbor';
+
+NumberOfAgents = 4
+
+fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
+diary(fname)
+diary on
+
+if NumberOfAgents > 5 && strcmp(Option,'Diagonal') + strcmp(Option,'Neighbor') == 0
+    
+    disp('This option requires lots of RAM memory for more than 5 agents.')
+    disp('Chose Option = Diagonal or Neighbor to run with more than 5 agents or')
+    return
+    
+end
+
+if NumberOfAgents > 256 && strcmp(Option,'Neighbor')
+    disp('This option requires lots of RAM memory for more than 256 agents.')
+    disp('Chose Option = Diagonal and run it with more than 256 agents or')
+    return
+end
+
+if NumberOfAgents > 512 && strcmp(Option,'Diagonal')
+    disp('This option requires lots of RAM memory for more than 512 agents.')
+    return
+end
+
+LaplacianMatrix = CyclicLaplacianGenerator(NumberOfAgents);
+% LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
+Optimisation(LaplacianMatrix,Option,lambda)
+
+diary off
+
+end
+
+function Optimisation(LaplacianMatrix,Option,lambda)
+
+global Simulation SystemStates SystemInputs SystemParameters
+
+WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+PreProcessedSys
+
+Wdegree = 2;
+ScalingFactor = 1e-2;  % Max value for SOS feasibility
+WriterW(SystemStates,LaplacianMatrix,Wdegree,ScalingFactor)
+PreProcessedW
+
+Ydegree = 2;
+WriterY(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+PreProcessedY
+
+% WriterMI(SystemStates,LaplacianMatrix,ScalingFactor,lambda,Option)
[…]

### 2017-01-12 TheoreticalExample2/ADMM.m
Remove tic tac for solver time computation command.

@@ -129,7 +129,7 @@ B4  = jacobian(f4,input4);
 f = [f1;f2;f3;f4;];
 A = jacobian(f,q);
 B = jacobian(f,InputVector);
-
+tic
 while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance    
     %% W update ===============================================================
     
@@ -450,7 +450,7 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
     IterationCounter = IterationCounter + 1;
     
 end
-
+SolverTime = toc
 if IterationCounter >= MaxNumberOfIterations
    disp('Maximum number of iterations reached !')
 end

### 2017-01-12 TheoreticalExample2/WriterMI.m
[WriterMI.m] Remove the need for the scaling factor.

@@ -48,13 +48,13 @@ if strcmp(Option,'Diagonal') || strcmp(Option,'Neighbor')
     
     fprintf(fid, 'MIConstraints = [');
     for AgentsCounter = 1:NumberOfAgents - 1
-        fprintf(fid, 'sos(-Block%s + %f*eye(size(Block%s)));',num2str(AgentsCounter),ScalingFactor,num2str(AgentsCounter));
+        fprintf(fid, 'sos(-Block%s);',num2str(AgentsCounter));
     end
     fprintf(fid, '];');
     
 else
     
-    fprintf(fid, 'MIConstraints = sos(-MI + %f*eye(size(MI)));\n',ScalingFactor);
+    fprintf(fid, 'MIConstraints = sos(-MI);\n');
     
 end
 

### 2017-01-12 TheoreticalExample2/LMIOptmisation.m
[LMIOptimisation.m] Add a comment regarding the maximum admissible value for lambda and the scaling factor to ensure feasibility of the LMIs

@@ -12,10 +12,10 @@ SystemStates = ['x','y'];
 SystemInputs = ['u'];
 SystemParameters = ['d'];
 d = 1e-2;
-lambda = 1;
+lambda = 1e-1; % Max value for SOS feasibility
 Option       = 'Neighbor';
 
-NumberOfAgents = 2
+NumberOfAgents = 4
 
 fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
 diary(fname)
@@ -41,7 +41,7 @@ if NumberOfAgents > 512 && strcmp(Option,'Diagonal')
 end
 
 LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
-LMIOptimisation(LaplacianMatrix,Option,lambda)
+Optimisation(LaplacianMatrix,Option,lambda)
 
 diary off
 
@@ -49,7 +49,7 @@ pause(60)
 
 end
 
-function LMIOptimisation(LaplacianMatrix,Option,lambda)
+function Optimisation(LaplacianMatrix,Option,lambda)
 
 global Simulation SystemStates SystemInputs SystemParameters
 
@@ -57,7 +57,7 @@ WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
 PreProcessedSys
 
 Wdegree = 2;
-ScalingFactor = 1;
+ScalingFactor = 1e-2; % Max value for SOS feasibility
 WriterW(SystemStates,LaplacianMatrix,Wdegree,ScalingFactor)
 PreProcessedW
 
@@ -86,4 +86,5 @@ PostProcessedY
 NumberOfAgents = size(LaplacianMatrix,1);
 fname = sprintf('Output%s%dAgents',Option,NumberOfAgents);
 save(fname)
+
 end

### 2017-01-12 R0V0.tex
Item 25 (cont.): small change
Item 26. Start to implement the example.

@@
 
-\mypara Inequality~\eqref{eq:Artstein-Sontag:inequality} is satisfied, whenever the matrix inequality
+\mypara Condition~\eqref{eq:Arstein-Sontag} is satisfied, whenever the matrix inequality
 \begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
@@
 
-\mypara A case where structured controller design is relevant is on distributed design for network systems.
-Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
-\begin{figure}[htpb!]
-	\centering
-	\input{./imgs/GraphStructure.pdf_tex}
-	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
-	\label{fig:graph}
-\end{figure}
-For each index $i\in\mathbb{N}_{[1,N]}$, the agents dynamics is described by the system
+\mypara A case where structured controller design is relevant is on distributed design for network systems. For a given integer $N>0$, consider the system that describes the dynamics of each agent
 \begin{equation}\tag{\ref{eq:example}}
@@
 		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
-		\dot{y}_i&=&u_i,
+		\dot{y}_i&=&u_i\;,
 	\end{array}\right.$}
 \end{equation}
-where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.
+where $i\in\mathbb{N}_{[1,N]}$ and for convenience $x_0=x_1$ and $x_N=x_{N+1}$.
 
@@
 
-\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b.
+\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper.
+The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b
+
+\subsection{Circumference topology}
+
+\mypara The graph describing the network structure in provided in Figure~\ref{fig:cycle graph}.
+\begin{figure}[htpb!]
+	\centering
+	\input{./imgs/CyclicGraph.pdf_tex}
+	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
+	\label{fig:cycle graph}
+\end{figure}
+
+\subsection{Chain topology}
+
+\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
+\begin{figure}[htpb!]
+	\centering
+	\input{./imgs/GraphStructure.pdf_tex}
+	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
+	\label{fig:graph}
+\end{figure}
+
+\mypara The matrix $W$ obtained is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$.
+The matrix $Y$ is given by
+\begin{equation*}
+	Y(q)=\begin{bmatrix}
+		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
+		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
+		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
+		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
+	\end{bmatrix}\;,
+\end{equation*}
+where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
+$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
+
+\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.

### 2017-01-13 R0V0.tex
Item 26. Implementing new example
Item 26. Done implementing the chordal graph case for the new example

@@
 
-\section{Numerical Experiment}\label{sec:Illustration}
+\section{Numerical Experiments}\label{sec:Illustration}
 
@@
 
-\subsection{Circumference topology}
-
-\mypara The graph describing the network structure in provided in Figure~\ref{fig:cycle graph}.
-\begin{figure}[htpb!]
-	\centering
-	\input{./imgs/CyclicGraph.pdf_tex}
-	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
-	\label{fig:cycle graph}
-\end{figure}
-
 \subsection{Chain topology}
 
-\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
+\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$.
+
 \begin{figure}[htpb!]
@@
 \end{figure}
-
-\mypara The matrix $W$ obtained is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$.
-The matrix $Y$ is given by
-\begin{equation*}
-	Y(q)=\begin{bmatrix}
-		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
-		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
-		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
-		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
-	\end{bmatrix}\;,
-\end{equation*}
-where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
-$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
 
@@
 
+\subsection{Circumference topology}
+
+\mypara Consider the with four agents (i.e., $N=4$) network having the topology illustrated in Figure~\ref{fig:cycle graph}.
+
+\begin{figure}[htpb!]
+	\centering
+	\input{./imgs/CyclicGraph.pdf_tex}
+	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
+	\label{fig:cycle graph}
+\end{figure}
+
+\mypara In the ``neighbour'' case, the solver took 11.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$.
+The matrix $Y$ is given by
+\begin{equation*}
+	Y(q)=\begin{bmatrix}
+		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
+		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
+		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
+		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
+	\end{bmatrix}\;,
+\end{equation*}
+where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
+$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
+
+\mypara In the ``neighbour'' case, the solver took 5.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.74,1.05)$.
+The matrix $Y$ is given by
+\begin{equation*}
+	Y(q)=\begin{bmatrix}
+	\overline{Y}(q_1)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&\overline{Y}(q_2)&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&\overline{Y}(q_3)&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}(q_4)
+	\end{bmatrix}\;,
+\end{equation*}
+where $\overline{Y}(q_i)=-\begin{bmatrix}2.0125y_i,&3.2+2.3(x_i^2+y_i^2)\end{bmatrix}$.
+
+\mypara In the unconstrained case, the solver took 9.8s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.69,1.24)$.
+The matrix $Y$ is given by
+\begin{equation*}
+	Y(q)=\begin{bmatrix}
+	\overline{Y}_1(q)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&\overline{Y}_2(q)&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&\overline{Y}_3(q)&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}_4(q)
+	\end{bmatrix}\;,
+\end{equation*}
+where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$
+
 \section{Conclusion}\label{sec:Conclusion}

### 2017-01-16 R0V0.tex
Modify the paragraph about the ADMM

@@
 
-\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper.
+\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper.
 The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b
@@
 
-\mypara In all cases, the computed matrix $W$ has a block-diagonal structure as follows
-\begin{equation*}
- W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right)\;.
-\end{equation*}
-the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.
-
 \mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
@@
 The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.
-The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
-\begin{equation*}
-		W_a=\mathbin{\mathtt{diag}}\left(
- 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
+The matrix $W$ is given by
+\begin{equation*}
+		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
 \end{equation*}
@@
 \begin{align*}
- \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\;,\\
- \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2\;.
+ \overline{Y}_{ij}(q)=&-2y_i\;,\\
+ \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
 \end{align*}
@@
 \begin{equation}\label{eq:example:Y:general}
-		Y(q)=\scalebox{0.75}{$\begin{bmatrix}
-			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1-0.003x_3y_1,&0.005y_1y_3,&-0.006y_1+0.001x_4y_1,&0\\
-			-0.006y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.009y_2-0.001x_3y_21,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
-			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.001x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.006y_3,&0\\
-			-0.006y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
-		\end{bmatrix}$}
+		Y(q)=\begin{bmatrix}
+			\overline{Y}_{11}(q),&\underline{Y}_{12}(q),&0,&0,&-0.03y_1,&0,&0&0\\
+			0,&0,&\overline{Y}_{23}(q),&\underline{Y}_{24}(q),&0,&0,&-0.04y_2,&0\\
+			-0.04y_3,&0,&0,&0,&\overline{Y}_{35}(q),&\underline{Y}_{36}(q),&0,&0\\
+			0,&0,&-0.03y_4,&0,&0,&0,&\overline{Y}_{47}(q),&\underline{Y}_{48}(q)
+		\end{bmatrix}
 \end{equation}
@@
 
-\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds.
-The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
-\begin{equation*}
-		W_a=\mathbin{\mathtt{diag}}\left(
- 1.32,1.7\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
+\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
+\begin{equation*}
+		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
 \end{equation*}
 and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
-\begin{equation*}
-	Y_{ij}(q_i,\breve{q}_i)=-3.3y_i-0.09x_iy_i
-\end{equation*}
-for pair of indexes $(i,j)$ given as $(1,1)$, $(2,3)$, $(3,5)$ and $(4,6)$. Also, 
 \begin{align*}
-	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\;,\\	
-	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\;,\\	
-	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\;,\\	
-	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)\;.
+	Y_{12}(q_1,\breve{q}_1)=&-2.5(1+\sum_{j=1}^2x_j^2+y_j^2)\;,\\	
+	Y_{24}(q_2,\breve{q}_2)=&-2.3(1+\sum_{j=1}^3x_j^2+y_j^2)\;,\\	
+	Y_{36}(q_3,\breve{q}_3)=&-2.2(1+\sum_{j=2}^4x_j^2+y_j^2)\;,\\	
+	Y_{48}(q_4,\breve{q}_4)=&-1.7(1+\sum_{j=3}^4x_j^2+y_j^2)\;.\\	
 \end{align*}
@@
 \begin{equation}\label{eq:example:Y:neighbor}
-	Y(q)=\scalebox{0.85}{$\begin{bmatrix}
-	Y_{11}(q_1,\breve{q}_1),&Y_{12}(q_1,\breve{q}_1),&-0.001y_1,&0,&0,&0,&0,&0\\
-	-0.001(y_2+x_1y_2),&0,&Y_{23}(q_2,\breve{q}_2),&Y_{24}(q_2,\breve{q}_2),&-0.003y_2,&0,&0,&0\\
-	0,&0,&-0.002y_3,&0,&Y_{35}(q_3,\breve{q}_3),&Y_{36}(q_3,\breve{q}_3),&-0.002y_3,&0\\
-	0,&0,&0,&0,&-0.003y_4,&0,&Y_{47}(q_4,\breve{q}_4),&Y_{48}(q_4,\breve{q}_4)
-	\end{bmatrix}$}
+	Y(q)=\begin{bmatrix}
+	-1.8y_1,&Y_{12}(q_1,\breve{q}_1),&0,&0,&0,&0,&0,&0\\
+	0,&0,&-2y_2,&Y_{24}(q_2,\breve{q}_2),&0,&0,&0,&0\\
+	0,&0,&0,&0,&-2y_3,&Y_{36}(q_3,\breve{q}_3),&0,&0\\
+	0,&0,&0,&0,&0,&0,&-2y_4,&Y_{48}(q_4,\breve{q}_4)
+	\end{bmatrix}
 \end{equation}
@@
 \end{equation*}
-Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
+Solving the MI \eqref{eq:MI formulation} the following matrices $W$ and $Y$ were obtained
 \begin{align*}
- W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
- Y=&\begin{bmatrix}
- 	Y_{11}&Y_{12}&0&0&0&0&0&0\\
- 	0&0&Y_{23}&Y_{24}&0&0&0&0\\
- 	0&0&0&0&Y_{35}&Y_{36}&0&0\\
- 	0&0&0&0&0&0&Y_{47}&Y_{48}
+ W=&\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
+ Y(q)=&\begin{bmatrix}
+ 	\overline{Y}(q_1)&0&0&0\\
+ 	0&\overline{Y}(q_2)&0&0\\
+ 	0&0&\overline{Y}(q_3)&0\\
+ 	0&0&0&\overline{Y}(q_4)
  \end{bmatrix}
@@
 where
-\begin{equation*}
-		W_a=\mathbin{\mathtt{diag}}\left(
- 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
-\end{equation*}
-and
 \begin{align*}
- Y_{11}(q_i)=Y_{47}(q_i)=&\ -3.1y_i+0.06x_iy_i\;,\\
- Y_{12}(q_i)=Y_{48}(q_i)=&\ -3.6-0.02x_i-2.3y_i^2-2.4x_i^2\;,\\
- Y_{23}(q_i)=Y_{35}(q_i)=&\ -3.1y_i\;,\\
- Y_{24}(q_i)=Y_{26}(q_i)=&\ -3.8-2.1y_i^2-2.2x_i^2\;.
+ \overline{Y}(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
 \end{align*}
@@
 
-\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
+\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.
 

### 2017-01-16 R0V0.tex
Modify the paragraph about the ADMM (reverted from commit 1a3a8b77133ebd4ba55143aedd828da5421ce7e1)

@@
 
-\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper.
+\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper.
 The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b
@@
 
-\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.
+\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
 

### 2017-01-16 R0V0.tex
Modify the paragraph about ADMM

--- 2017-01-16 R0V0.tex
@@
 \begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
- 	\ker(B)^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)\ker(B)\prec0
-\end{equation} 
-holds, where $\ker(B)$ is a full-rank matrix satisfying $B^\top\ker(B)\equiv0$.
+ 	B_\perp^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)B_\perp\prec0
+\end{equation} 
+holds, where $B_\perp$ is a full-rank matrix satisfying $B B_\perp\equiv0$.
 
@@
 
-\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper.
+\mypara In the remainder of this section, two network topologies are considered to illustrate the results presented in this paper.
 The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b
@@
 
-\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.
+\mypara Note that the ADMM cannot be used to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual}. The reason is the fact that $B_\perp\equiv0$.
 

### 2017-01-18 R0V0.tex
Modify the notation of Bperp and rewrite some paragraphs of the conclusion

@@
 \end{equation} 
-holds, where $B_\perp$ is a full-rank matrix satisfying $B B_\perp\equiv0$.
+holds, where $B_\perp$ is any full-rank matrix satisfying $B^\top B_\perp\equiv0$ \cite[pp. 23]{Boyd1994}.
 
@@
 	p_W=&\ v^\top W v\;,\\
-	p_{MI}=&\ -v^\top\ker(B)^\top(-\dot{W}+AW + WA^\top+2\lambda W)\\
-	&\ker(B)v\;.
+	p_{MI}=&\ -v^\top B_\perp^\top(-\dot{W}+AW + WA^\top+2\lambda W)\\
+	&B_\perp v\;.
 \end{align*}
@@
 
-\mypara In this work, input-affine nonlinear systems were considered.
-The problem was the design of structured feedback laws.
-The methodology employed for synthesis was based on control-contraction metrics which provides a controller ensuring exponential convergence of pairs of solutions.
-
 \mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
@@
 
-\mypara For systems described by a non-fully connected graph, the approach presented in this paper exploits sparsity to design feedback laws with a prescribed structure.
-More precisely, by imposing a block-diagonal structure on the matrix describing the metric, a controller with a prescribed structure can be synthesized.
-Moreover, the on-line integration phase computation can be in parallel, because each block defines a metric to the corresponding component of the state space where the geodesic is computed by optimization.
+\mypara For large-scale systems, the approach presented in this paper exploits sparsity to design feedback laws with a prescribed structure.
+More precisely, during the off-line phase, by imposing a block-diagonal structure on the matrix describing the metric, a controller with a prescribed structure can be synthesized.
+Moreover, the on-line integration phase computation can be in parallel, because each block defines a metric to the corresponding component of the state space.
 

### 2017-01-19 TheoreticalExample2/ADMM.m
Back to the case in which the overall list of monomials is a compositions of the smaller monomials

@@ -244,10 +244,13 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
     
     v = [v1;v2];
     
-%     ListOfMonomials_MI = [ListOfMonomials1;ListOfMonomials2];
-    ListOfMonomials_MI = monolist([q1;q2;v1;v2],2);
+    ListOfMonomials_MI = [ListOfMonomials1;ListOfMonomials2];
+%     ListOfMonomials_MI = monolist([q1;q2;v1;v2],2);
 
-    Gramian_MI = sdpvar(length(ListOfMonomials_MI));
+    Gramian_MI1 = sdpvar(length(ListOfMonomials1));
+    Gramian_MI2 = sdpvar(length(ListOfMonomials2));
+%     Gramian_MI = sdpvar(length(ListOfMonomials_MI));
+    Gramian_MI  = blkdiag(Gramian_MI1,Gramian_MI2);
     
     p_MI = -v'*MI*v;
     p_SMI = ListOfMonomials_MI'*Gramian_MI*ListOfMonomials_MI;
@@ -255,11 +258,11 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
     Options = sdpsettings('solver','mosek','verbose',0);
     
     Constraints = [Gramian_MI>=0;coefficients(p_MI-p_SMI,[q;v])==0];
-%     Objective   = norm(Gramian_MI1 - Gramian_W1 - Lambda1,'fro')^2 ...
-%                   + norm(Gramian_MI2 - Gramian_W2 - Lambda2,'fro')^2;
-    Objective   = norm(blkdiag(Gramian_MI1,Gramian_MI2)...
-                   + blkdiag(Gramian_W1,Gramian_W2) -...
-                   + blkdiag(Lambda1,Lambda2),'fro')^2;
+    Objective   = norm(Gramian_MI1 - Gramian_W1 - Lambda1,'fro')^2 ...
+                  + norm(Gramian_MI2 - Gramian_W2 - Lambda2,'fro')^2;
+%     Objective   = norm(blkdiag(Gramian_MI1,Gramian_MI2)...
+%                    + blkdiag(Gramian_W1,Gramian_W2) -...
+%                    + blkdiag(Lambda1,Lambda2),'fro')^2;
     DiagnosticMI = optimize(Constraints,Objective,Options);
     
     % Checking for errors in the optimization ---------------------------------
[…]

### 2017-01-19 TheoreticalExample2/ADMM.m
Is working OK, in general, with some numerical errors

@@ -245,11 +245,9 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
     v = [v1;v2];
     
     ListOfMonomials_MI = [ListOfMonomials1;ListOfMonomials2];
-%     ListOfMonomials_MI = monolist([q1;q2;v1;v2],2);
 
     Gramian_MI1 = sdpvar(length(ListOfMonomials1));
     Gramian_MI2 = sdpvar(length(ListOfMonomials2));
-%     Gramian_MI = sdpvar(length(ListOfMonomials_MI));
     Gramian_MI  = blkdiag(Gramian_MI1,Gramian_MI2);
     
     p_MI = -v'*MI*v;
@@ -257,12 +255,11 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
     
     Options = sdpsettings('solver','mosek','verbose',0);
     
+    temp = length(ListOfMonomials1);
+    
     Constraints = [Gramian_MI>=0;coefficients(p_MI-p_SMI,[q;v])==0];
-    Objective   = norm(Gramian_MI1 - Gramian_W1 - Lambda1,'fro')^2 ...
-                  + norm(Gramian_MI2 - Gramian_W2 - Lambda2,'fro')^2;
-%     Objective   = norm(blkdiag(Gramian_MI1,Gramian_MI2)...
-%                    + blkdiag(Gramian_W1,Gramian_W2) -...
-%                    + blkdiag(Lambda1,Lambda2),'fro')^2;
+    Objective   = norm(Gramian_MI(1:temp,1:temp) - Gramian_W1 - Lambda1,'fro')^2 ...
+                  + norm(Gramian_MI(1+temp:2*temp,1+temp:2*temp) - Gramian_W2 - Lambda2,'fro')^2;
     DiagnosticMI = optimize(Constraints,Objective,Options);
     
     % Checking for errors in the optimization ---------------------------------
@@ -272,8 +269,8 @@ while IterationCounter <= MaxNumberOfIterations && Error >= ErrorTolerance
         keyboard;
     end
     
-%     Gramian_MI1 = Gramian_MI(1:15,1:15);
-%     Gramian_MI2 = Gramian_MI(16:30,16:30);
+    Gramian_MI1 = Gramian_MI(1:temp,1:temp);
+    Gramian_MI2 = Gramian_MI(1+temp:2*temp,1+temp:2*temp);
     
[…]

### 2017-01-20 R0V0.tex
Continue writing the components of W for the new example.
Finish typing the metric. Start the "new formulation" of the main result.
Propagate changes of the set Xi along the examples

@@
 \mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
-\begin{subequations}
-	\begin{align*}
-		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
-		\arg(Y_{ij}(\cdot,u))\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
-	\end{align*}
-\end{subequations}
-where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ indexed by the set $\mathscr{K}(k)$.
+\begin{align}
+		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
+		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
+		&i\in\mathbb{N}_{[1,N]}\}\;,
+\end{align}
+where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having components zero but those corresponding to the indices defined in $\mathscr{K}$.
 
 \mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
-Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.
+Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.
 
@@
 	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
+In particular, given a graph $\mathscr{G}_c$ describing the communication network among different controllers
 \end{theorem}
@@
 The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
-The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
-\begin{equation*}
-	\begin{array}{rl}
-		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}1, 1, 1, 0\end{bmatrix}^\top\right\},\\
-		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0, 1, 1, 1\end{bmatrix}^\top\right\},&		    \mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0, 0, 1, 1\end{bmatrix}^\top\right\}\;.
+The sets $\mathbf{C}$ are defined as
+\begin{equation*}
+	\begin{array}{rcl}
+		\mathbf{C}(1)&=&\{\begin{bmatrix}
+		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
+		\mathbf{C}(2)&=&\{\begin{bmatrix}
+		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
+		\mathbf{C}(3)&=&\{\begin{bmatrix}
+		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
+		\mathbf{C}(4)&=&\{\begin{bmatrix}
+		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
 	\end{array} 
@@
 
-\mypara The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.
+\mypara The sets $\mathbin{\mathtt{proj}}_{\mathscr{K}}(\mathbb{R}^8)$ are defined, for each index $i\in\mathbb{N}_{[1,4]}$, as
+\begin{equation*}
+	\begin{array}{rcl}
+		\mathbin{\mathtt{proj}}_{\mathscr{K}(1)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
+		q_1,&q_2\end{bmatrix}\}\;,\\
+		\mathbin{\mathtt{proj}}_{\mathscr{K}(2)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
+		q_1,&q_2,&q_3\end{bmatrix}\}\;,\\
+		\mathbin{\mathtt{proj}}_{\mathscr{K}(3)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
+		q_2,&q_3,&q_4\end{bmatrix}\}\;,\\
+		\mathbin{\mathtt{proj}}_{\mathscr{K}(4)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
+		q_3,&q_4\end{bmatrix}\}\;.
+	\end{array}
+\end{equation*}
 
@@
 \end{equation*}
-and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
-\begin{align*}
-	Y_{12}(q_1,\breve{q}_1)=&-2.5(1+\sum_{j=1}^2x_j^2+y_j^2)\;,\\	
-	Y_{24}(q_2,\breve{q}_2)=&-2.3(1+\sum_{j=1}^3x_j^2+y_j^2)\;,\\	
-	Y_{36}(q_3,\breve{q}_3)=&-2.2(1+\sum_{j=2}^4x_j^2+y_j^2)\;,\\	
-	Y_{48}(q_4,\breve{q}_4)=&-1.7(1+\sum_{j=3}^4x_j^2+y_j^2)\;.\\	
-\end{align*}
-
-\begin{figure*}
-\begin{equation}\label{eq:example:Y:neighbor}
+and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
+\begin{equation}\label{eq:example:Y:neighbor and decentralized}
 	 Y(q)=\begin{bmatrix}
-	-1.8y_1,&Y_{12}(q_1,\breve{q}_1),&0,&0,&0,&0,&0,&0\\
-	0,&0,&-2y_2,&Y_{24}(q_2,\breve{q}_2),&0,&0,&0,&0\\
-	0,&0,&0,&0,&-2y_3,&Y_{36}(q_3,\breve{q}_3),&0,&0\\
-	0,&0,&0,&0,&0,&0,&-2y_4,&Y_{48}(q_4,\breve{q}_4)
-	\end{bmatrix}
-\end{equation}
-\end{figure*}
+ 	\overline{Y}_1(\cdot)&0&0&0\\
+ 	0&\overline{Y}_2(\cdot)&0&0\\
+ 	0&0&\overline{Y}_3(\cdot)&0\\
+ 	0&0&0&\overline{Y}_4(\cdot)
+ \end{bmatrix}\;,
+\end{equation}
+with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
+\begin{equation*}
+	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
+	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}\;.
+\end{equation*}
 
@@
 The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds.
-In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$.
-Moreover,
-\begin{equation*}
-	\begin{array}{rl}
-		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
-		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
+In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$.
+Moreover, the sets $\mathbf{C}$ are defined as
+\begin{equation*}
+	\begin{array}{rcl}
+		\mathbf{C}(1)&=&\{\begin{bmatrix}
+		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
+		\mathbf{C}(2)&=&\{\begin{bmatrix}
+		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
+		\mathbf{C}(3)&=&\{\begin{bmatrix}
+		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
+		\mathbf{C}(4)&=&\{\begin{bmatrix}
+		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
 	\end{array} 
 \end{equation*}
-Solving the MI \eqref{eq:MI formulation} the following matrices $W$ and $Y$ were obtained
+Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
+\begin{equation*}
+ W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
+\end{equation*}
+and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
 \begin{align*}
- W=&\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
- Y(q)=&\begin{bmatrix}
- 	\overline{Y}(q_1)&0&0&0\\
- 	0&\overline{Y}(q_2)&0&0\\
- 	0&0&\overline{Y}(q_3)&0\\
- 	0&0&0&\overline{Y}(q_4)
- \end{bmatrix}
-\end{align*}
-where
-\begin{align*}
- \overline{Y}(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
+ \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
 \end{align*}
@@
 \end{equation*}
-where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$
+where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$.
+
+\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in
+
+\begin{figure*}
+	\begin{subequations}
+	\begin{equation}\label{eq:}
+		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
+		4+3x_1-1\times10^3y_1+1\times10^{5}y_1^2+5x_1^2-1\times10^{3}x_1y_1&2+6x_1-5\times10^2y_1-6\times10^{2}y_1^2+3x_1^2-8\times10^{2}x_1y_1\\
+		*&2+4x_1+3y_1+3y_1^2+5x_1^2+8x_1y_1
+		\end{bmatrix}\;,$}
+	\end{equation}
+	\begin{equation}\label{eq:}
+		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
+		5+9x_2-2\times10^3y_2+1\times10^{5}y_2^2+4x_2^2-1\times10^{3}x_2y_2&6+11x_2-1\times10^{3}y_2-7\times10^{2}y_2^2+5x_2^2-9\times10^{2}x_2y_2\\
+		*&7+12x_2+10y_2+4y_1^2+6x_1^2+9x_2y_2
+		\end{bmatrix}\;,$}
+	\end{equation}
+	\begin{equation}\label{eq:}
+		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
+		7+16x_3-2\times10^3y_3+1\times10^{5}y_3^2+12x_3^2-2\times10^{3}x_3y_3&10+20x_3-1\times10^{3}y_3+1\times10^{3}y_3^2+11x_1^2-11\times10^{3}x_3y_3\\
+		*&20+29x_3+29y_3+13y_3^2+13x_3^2+24x_3y_3
+		\end{bmatrix}\;,$}
+	\end{equation}
+	\begin{equation}\label{eq:}
+		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}
+		11+17x_4-2\times10^3y_4+1\times10^{5}y_4^2+9x_4^2-2\times10^{3}x_4y_4&13+21x_4-1\times10^{3}y_4+1\times10^{3}y_4^2+10x_4^2-1\times10^{3}x_4y_4\\
+		*&20+27x_4+24y_4+11y_4^2+12x_4^2+18x_4y_4
+		\end{bmatrix}\;,$}
+	\end{equation}
+	\end{subequations}
+\end{figure*}
 

### 2017-01-22 R0V0.tex
Changes in the ADMM paragraph

@@
 
-\mypara Note that the ADMM cannot be used to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual}. The reason is the fact that $B_\perp\equiv0$.
+\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in Equation~??
 
@@
 
+\begin{table}
+	\begin{tabular}{r|l}
+	Method&Time taken by the solver [s]\\ \hline
+	Chordal graph decomposition&2.6 to 98\\
+	ADMM&
+	\end{tabular}
+\end{table}
+
 \subsection{Circumference topology}

### 2017-01-22 R0V0.tex
Change the notation of the sets C and add the set proj

@@
 \mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
-More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$.
+More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $i\in\mathbb{N}_{[1,4]}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\mathbb{R}^8$, $\mathbf{C}(i)=\mathbb{R}^8$.
 The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.

### 2017-01-23 R0V0.tex
Finish to write about the ADMM on the chain topology case

@@
 
-\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in Equation~??
+\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}.
+A summary of the time taken by the solver employing chordal graph and ADMM approach is shown in Table~\ref{tab:chain case}.
 
 \begin{figure*}
-\begin{align*}
-	W_1(q_1)=1\times10^{-7}\begin{bmatrix}
-	18-15x_1-28y_1+11.2y_1^2+3.2x_1^2+1.2x_1y_2&9.3+35x_1-43y_1+28y_1^2-16x_1^2-16x_1y_1\\
-	*&4.9+40x_1-37y_1+72y_1^2+84x_1^2-155x_1y_1
-	\end{bmatrix}\;,\\
-	W_2(q_2)=1\times10^{-7}\begin{bmatrix}1-3.7x_2+2.3y_2+1.3y_2^2+3.5x_2^2-4.3x_2y_2&
-	-0.6-0.6x_2+y_2+2y_2^2+3.5x_2^2-5.5x_2y_2\\
-	*&0.4+2.3x_2-2.3y_2+3.3y_2^2+3.4x_2^2-6.7x_2y_2
-	\end{bmatrix}\;,\\
-	W_3(q_3)=1\times10^{-7}\begin{bmatrix}
-		127-248x_3+18y_3+y_3^2+122x_3^2-18x_3y_3&
-		-98+146x_3+19y_3+1.9y_3^2-50x_3^2-22x_3y_3\\
-		*&76-78x_3-42y_3+6.4y3^2+21x_3^2+20x_3y_3
-	\end{bmatrix}\;,\\
-	W_4(q_4)=1\times10^{-6}\begin{bmatrix}
-	22+4x_4-17y_4+8.8y_4^2+9.4x_4^2+12x_4y_4&
-	-8.6-5.9x_4+1.8y_4-4.2y_4^2-9.7x_4^2-12x_4y_4\\
-	*&4.3+7.5x_4+2.8y_4+3.2y_4^2+10x_4^2+11x_4y_4
-	\end{bmatrix}\;.
-\end{align*}
+\begin{subequations}\label{eq:ADMM:chain case}
+	\begin{equation}
+		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-6}\begin{bmatrix}
+		2-7x_1-10^3y_1+10^7y_1^2+10x_1^2-8.9\times10^2x_1y_1&
+		0.5+0.6x_1-5.6\times10^2y_1-3\times10^2y_1^2-9x_1^2-4.1\times10^2\\
+		*&0.4+4x_1-3y_1+6y_1^2+10x_1^2-16x_1y_1
+		\end{bmatrix}$}
+	\end{equation}
+	\begin{equation}
+		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-6}\begin{bmatrix}
+		4-2x_2-4\times10^3y_2+10^7y_2^2+x_2^2-5\times10^3x_2y_2&
+		2-5x_2-2.5\times10^3y_2-2.3\times10^3y_2^2+3.2x_2^2-2.5\times10^3x_2y_2\\
+		*&1-3x_2+3y_2+3y_2^2+9x_2^2-8x_2y_2
+		\end{bmatrix}$}
+	\end{equation}
+	\begin{equation}
+		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-6}\begin{bmatrix}
+		58-43x_3-6.1\times10^2y_3+10^8y_3^2+9x_3^2-4\times10^2x_3y_3&
+		-60-9x_3-2.4\times10^2y_3-4\times10^2y_3^2+11x_3^2-3.6\times10^2x_3y_3\\
+		*&60+60x_3-64y_3+18y_3^2+16x_3^2-34x_3y_3
+		\end{bmatrix}$}
+	\end{equation}
+	\begin{equation}
+		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-6}\begin{bmatrix}
+		18.5+44x_4-3.2\times10^3y_4+9.3\times10^6y_4^2+29x_4^2-3.7\times10^3x_4y_4&
+		-33-50x_4-2\times10^3y_4-2\times10^3y_4^2-9x_4^2-2.3\times10^3x_4y_4\\
+		*&64+31x_4-26y_4+4.4y_4^2+5x_4^2-7x_4y_4
+		\end{bmatrix}$}
+	\end{equation}
+\end{subequations}
 \end{figure*}
@@
 	\begin{tabular}{r|l}
-	Method&Time taken by the solver [s]\\ \hline
-	Chordal graph decomposition&2.6 to 98\\
-	ADMM&
+	Method&Time taken by the solver (4 agents)\\ \hline
+	Chordal graph decomposition&2.6s (decentralized)\\
+	&3.5s (neighbor)\\
+	&98s (unconstrained)\\
+	ADMM&300s\\\hline
 	\end{tabular}
+	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the case of the chain topology}
+	\label{tab:chain case}
 \end{table}
@@
 
-\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in
+\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in the set of Equations~\eqref{eq:ADMM:cyclic case}.
 
 \begin{figure*}
-	\begin{subequations}
-	\begin{equation}\label{eq:}
+	\begin{subequations}\label{eq:ADMM:cyclic case}
+	\begin{equation}
 		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
@@
 	\end{equation}
-	\begin{equation}\label{eq:}
+	\begin{equation}
 		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
@@
 	\end{equation}
-	\begin{equation}\label{eq:}
+	\begin{equation}
 		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
@@
 	\end{equation}
-	\begin{equation}\label{eq:}
+	\begin{equation}
 		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}

### 2017-01-23 R0V0.tex
Finish to edit the example. Add a comparison table.

@@
 \mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}.
-A summary of the time taken by the solver employing chordal graph and ADMM approach is shown in Table~\ref{tab:chain case}.
+A summary of the time taken by the solver employing chordal graph and ADMM approach is presented in Table~\ref{tab:chain case}.
 
@@
 	\end{tabular}
-	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the case of the chain topology}
+	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the topology illustrated by Fig.~\ref{fig:graph}.}
 	\label{tab:chain case}
@@
 
-\mypara In the ``neighbour'' case, the solver took 11.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$.
+\mypara In the ``unconstrained'' case, the solver took 7.4s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1.2)$.
+The matrix $Y$ is given by
+\begin{equation*}
+	Y(q)=\begin{bmatrix}
+	\overline{Y}(q_1)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&\overline{Y}(q_2)&0_{2\times1}&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&\overline{Y}(q_3)&0_{2\times1}\\
+	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}(q_4)
+	\end{bmatrix}\;,
+\end{equation*}
+where $\overline{Y}(q_i)=-\begin{bmatrix}2.4y_i,&2.9+2.9(x_i^2+y_i^2)\end{bmatrix}$.
+
+\mypara In the ``neighbor'' case, the solver took 7.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1.2)$.
 The matrix $Y$ is given by
@@
 \end{equation*}
-where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
+where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&1+\sum_{j=1}^4y_j^2+x_j^2\end{bmatrix}$,
 $\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
 
-\mypara In the ``neighbour'' case, the solver took 5.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.74,1.05)$.
-The matrix $Y$ is given by
-\begin{equation*}
-	Y(q)=\begin{bmatrix}
-	\overline{Y}(q_1)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&\overline{Y}(q_2)&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&\overline{Y}(q_3)&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}(q_4)
-	\end{bmatrix}\;,
-\end{equation*}
-where $\overline{Y}(q_i)=-\begin{bmatrix}2.0125y_i,&3.2+2.3(x_i^2+y_i^2)\end{bmatrix}$.
-
-\mypara In the unconstrained case, the solver took 9.8s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.69,1.24)$.
+\mypara In the decentralized case, the solver took 6.2s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1)$.
 The matrix $Y$ is given by
@@
 \end{equation*}
-where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$.
-
-\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in the set of Equations~\eqref{eq:ADMM:cyclic case}.
+where $\overline{Y}_i(q)=-\begin{bmatrix}3.1y_i,&2.3+2.3\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$.
+
+\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 114[s] and the obtained matrix $W$ has the components shown in the set of Equations~\eqref{eq:ADMM:cyclic case}.
+A summary of the time taken by the solver employing chordal graph and ADMM approach is presented in Table~\ref{tab:cyclic case}.
 
@@
 \end{figure*}
+
+\begin{table}
+	\begin{tabular}{r|l}
+	Method&Time taken by the solver (4 agents)\\ \hline
+	Chordal graph decomposition&7.4s (unconstrained)\\
+	&7.7s (neighbor)\\
+	&6.2s (decentralized)\\	
+	ADMM&114s\\\hline
+	\end{tabular}
+	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
+	\label{tab:cyclic case}
+\end{table}
 

### 2017-01-23 R0V0.tex
Finish reviwing the examples

@@
 \mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance.
-The first exploits the network topology to decompose it into smaller connected components.
-The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality below.
+The first exploits the network topology to decompose it into smaller complete components.
+The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
 Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling.
 Note that these methodologies can be used either separately or together.
-The latter would appropriate, when the smaller components of the network have high rank.
-Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
-
-\mypara Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
+The latter would appropriate, when the smaller components of the network have high rank and the computing platform where the solver runs has memory limitations.
+
+\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
+onsider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
@@
 
-\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$.
+\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
+Consider the case with $N=4$.
+Two different methods are employed to compute the matrix $W$, namely, chordal graphs and ADMM.
 
@@
 
-\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved.
+\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials and the MI \eqref{eq:MI formulation} could not be solved.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
@@
 
-\mypara To show the advantages of the method proposed in this paper, a benchmark was run for a network composes by $N=4$ systems and in three scenarios, according to the constraints imposed on the matrix $Y$.
-Namely, the unconstrained case, the ``neighbor case'', and the fully decentralized (diagonal) case.
-For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor case'' and up to $N=512$ systems for the fully decentralized (diagonal) case.
+\mypara To show the advantages of the method proposed in this paper, a benchmark composed of  three scenarios, according to the constraints imposed on the matrix $Y$, has been created.
+Namely, the unconstrained case, the ``neighbor'' case, and the fully decentralized case.
+For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor'' case and up to $N=512$ systems for the fully decentralized (diagonal) case.
+In these scenarios the techniques provided by chordal graphs have been employed.
 
@@
 \mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
-The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.
+To comply with this requirement, the set $\mathscr{K}$ is defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$.
 The sets $\mathbf{C}$ are defined as
@@
 	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
-	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}\;.
+	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
 \end{equation*}
@@
 \begin{align*}
- \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
+ \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
 \end{align*}
 
-\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this illustration: unconstrained, ``neighbor'' and fully decentralized.
+\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
+According to this graph shown, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} has the same order of magnitude for the three cases.
+However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralize case.
+The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case.
+In addition to this, in the former case, each element is defined as a polynomial of second degree on the variables $q_i$ and $\breve{q}_i$, while for the latter, they are defined on the variable $q_i$ only.
 
@@
 \end{figure}
-
-\mypara According to the graph shown in Figure \ref{fig:time graph}, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} was of the same order of magnitude for the three cases.
-However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor''-constrained case which, in turn, takes more time than the fully decentralized-constrained case.
-The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case.
-In addition to this, in the former case, each element is defined as a polynomial of second degree on the variables $q_i$ and $\breve{q}_i$, while for the latter, they are defined on the variable $q_i$ only.
-
-\mypara Regarding the on-line integration phase, since the matrices $W$ computed in each case is  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$.
-For each case, and for each index $i\in\mathbb{N}_{[1,4]}$, the feedback law is  given by the formula
-\begin{equation*}
-	k= \int_0^1Y(sq)W^{-1}q\,ds.
-\end{equation*}
-Given the structure of the matrices $Y$ and $W$, each line $i\in\mathbb{N}_{[1,4]}$ is given by
-\begin{equation*}
-k_i=\begin{cases}
-	\displaystyle\int_0^1Y_i(sq)W_i^{-1}q_i\,ds,&\text{if unconstrained}\\
-	\displaystyle\int_0^1Y_i(sq_i,s\breve{q}_i)W_i^{-1}q_i\,ds,&\text{if ``neighbor''}\\
-	\displaystyle\int_0^1Y_i(sq_i)W_i^{-1}q_i\,ds,&\text{if fully decentralized.}
-\end{cases}
-\end{equation*}
-Moreover, from Theorem~\ref{thm:main result}, the feedback law $k$ solves Problem~\ref{problem formulation} for the network resulting from the interconnection of systems \eqref{eq:example}.
 
@@
 
+\mypara Regarding the on-line integration phase, since the matrices $W$ computed in each case are  constant, for each index $i\in\mathbb{N}_{[1,4]}$, the geodesic curve connecting the origin to a point $q_i\in\mathbb{R}^2$ is a straight line: $\gamma_i(s)=sq_i$, where $s\in[0,1]$.
+For each index $i\in\mathbb{N}_{[1,4]}$ and assuming that $u^\ast\equiv0$, the feedback law is  given by the formula
+\begin{equation*}
+	k= \int_0^1Y(sq)W^{-1}q\,ds.
+\end{equation*}
+Given the structure of the matrices $Y$ and $W$, each line $i\in\mathbb{N}_{[1,4]}$ is given by
+\begin{equation*}
+k_i=\begin{cases}
+	\displaystyle\int_0^1Y_i(sq)W_i^{-1}q_i\,ds,&\text{if unconstrained}\\
+	\displaystyle\int_0^1Y_i(sq_i,s\breve{q}_i)W_i^{-1}q_i\,ds,&\text{if ``neighbor''}\\
+	\displaystyle\int_0^1Y_i(sq_i)W_i^{-1}q_i\,ds,&\text{if fully decentralized.}
+\end{cases}
+\end{equation*}
+Moreover, from Theorem~\ref{thm:main result}, the feedback law $k$ solves Problem~\ref{problem formulation} for the network resulting from the interconnection of systems \eqref{eq:example}.
+
 \subsection{Circumference topology}
 
-\mypara Consider the with four agents (i.e., $N=4$) network having the topology illustrated in Figure~\ref{fig:cycle graph}.
+\mypara Consider the with network with four agents (i.e., $N=4$) with the topology illustrated in Figure~\ref{fig:cycle graph}.
+Also in this topology, chordal graphs and ADMM are employed to solve the MIs~\eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual}, respectively.
 
@@
 
+\mypara The online computation of the feedback law for the network composed of subsystems of the form \eqref{eq:example} is analogous to what has been shown to the chain-topology case.
+
 \section{Conclusion}\label{sec:Conclusion}

### 2017-01-24 R0V0.tex
Finish to propagate the notation of the Xi set to the proof and add a statement in the proof regarding Gc

@@
 	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
-In particular, given a graph $\mathscr{G}_c$ describing the communication network among different controllers
+In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
 \end{theorem}
@@
 	\end{equation*}
-	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
-	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
+	where $\widetilde{\gamma}_i(\cdot)\in\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^n)$.
+	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
+
+	To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$.
+This concludes the proof of Theorem~\ref{thm:main result}.
 \end{proof}

### 2017-01-24 R0V0.tex
Changes on the introduction to focus more on the large-scale problem

@@
 
-\mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure.
-One of the main underlying concepts employed for the synthesis of feedback laws is Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}.
-In terms of computation, controller design problems are often translated in terms of optimization.
-
-\mypara For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
+\mypara Over the years, methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure.
+For linear systems, controller design problems are often translated in terms of optimization.
+
+\mypara Numerical methods to design linear controllers include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
 The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.
-In the case of nonlinear systems, design approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
+In the case of nonlinear systems, design approaches are generally analytic and include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
 These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.
-In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.
 
@@
 
-\mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well.
+\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it does not scale well.
 This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
@@
 
-\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein).
+\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein).
 However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions).
@@
 \mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
-Although this is one of its main advantages over the search of control-Lyapunov functions, it does not scale well.
+Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of systems, in general.
 

### 2017-01-25 R0V0.tex
Implement changes proposed on the ReviewHSS20170124

@@
 \begin{abstract}
-In this paper, input-affine nonlinear systems are considered.
-The problem is the design of structured (for instance, decentralized or distributed) controllers for this class of systems.
-Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, numerical methods employed to construct for these functions usually leads to a non-convex optimization problem.
+In this paper, large-scale input-affine nonlinear systems are considered.
+The problem is the design of distributed controllers for this class of network systems.
+Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, numerical methods employed to construct for these functions usually lead to a non-convex optimization problem.
 Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements.
-In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable topological (distributed) structures.
+In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures.
 By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
@@
 
-\mypara For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
+\mypara For systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
 However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}).
@@
 \mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
-One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered.
-The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed solution (see a precise definition below).
-In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system.
-This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.
-
-\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it does not scale well.
+One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}.
+
+\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it may require a large memory size.
 This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
@@
 However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions).
-The case can be even worse, when structural constraints are considered.
-
-\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work.
+The case can be even worse, when structural constraints are imposed.
+
+\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints.
 The systems under consideration are continuously differentiable and affine in the input.
@@
 The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).
+In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system.
+This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.
 
 \mypara At this point, the three contributions of this work can be highlighted.
-First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structure constraint, a feedback law with prescribed structure is obtained for nonlinear systems.
-Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is distributed.
-Third, when the system is described a non-strongly connected graph, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability.
-Note that the proposed method provides an explicit algorithm to design the controller which makes this approach constructive.
+First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structural constraint, a distributed feedback law is obtained.
+Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is also distributed.
+Third, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability.
+Note that the proposed method provides an explicit algorithm to design the controller.
 
@@
 A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$.
-Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
+Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
 A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct.
@@
 
-\mypara In other words, Problem~\ref{problem formulation} states that the controller is decomposed into smaller components.
-Each of these depends on the states  prescribed by the set $\mathscr{K}$.
-The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$.
-Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among different controllers, the set $\mathscr{K}$ can be defined as a subset of $\mathscr{V}_c$.
-
-\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology).
+\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$.
+The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$, for instance, it can be described by a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ that defined the communication network among different controllers.
+
+\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design of distributed feedback laws with a prescribed topology (described possibly by $\mathscr{G}_c$).
 Consider the network composed of systems described by the following equation.
@@
 As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints.
-However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.
+However, by exploring sparsity, up to 512 of theses systems can be connected and the distributed controller can be computed.
 
@@
 \mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows.
-Given a fixed two control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$.
-If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially.
+Given a fixed control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$.
+If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} under the input $u$ converge to each other exponentially.
 The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.
@@
 
-\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially.
+\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions to this system converge to each other exponentially.
 The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
@@
 Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
-\cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.
+\cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.
 
@@
 The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf.
-\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
+\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W(\cdot)=W(\cdot)^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
 \begin{equation}\label{eq:MI formulation}
-	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0\;.
-\end{equation}
+	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
+\end{equation}
+uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
 Note that \eqref{eq:MI formulation} is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
@@
 This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner.
-
-\mypara In this paper, these limitations are addressed by imposing a separable structure over $W$.
-
-\section{Design of Distributed Controllers}\label{sec:Design of Decentralized Controllers}
-
-\begin{definition}\label{def:SSCCM}
-	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if it can be decomposed into the following sum
-	\begin{equation*}
-		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
-	\end{equation*}
-	where, for each index $i\in\mathbb{N}_{[1,N]}$, and for every $(x_i,\delta_{x_i})\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$, the function $V_i(x_i,\delta_{x_i}):=\delta_{x_i}^\top M_i(x_i)\delta_{x_i}$ is a metric on $\mathbb{R}^{n_i}$.
-\end{definition}
-
-\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
-The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
-
-\mypara To address the constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation}, the structure of the feedback defined by Equation~\eqref{eq:contracting feedback law} is obtained by imposing a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
-
-\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
-\begin{align}
-		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
-		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
-		&i\in\mathbb{N}_{[1,N]}\}\;,
-\end{align}
-where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having components zero but those corresponding to the indices defined in $\mathscr{K}$.
-
-\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
-Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.
-
-\begin{theorem}\label{thm:main result}
-	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
-In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
-\end{theorem}
-
-\mypara The existence of a control contraction metric for system~\eqref{eq:general system} implies that there exist matrices $(W,Y)$ that are a solution to the MI~\eqref{eq:MI formulation} with structure prescribed by the set $\Xi$.
-
-\begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ are a solution to the MI \eqref{eq:MI formulation}.
-Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
-Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi$.
-
-\mypara	The MI \eqref{eq:MI formulation} implies that the inequality
-	\begin{equation*}
-		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
-	\end{equation*}
-	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$.
-Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
-Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
-
-\mypara 	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
-Because $M$ is a block-diagonal matrix, the energy of any curve $c:[0,1]\to\mathbb{R}^n$ satisfies the following equation
-	\begin{equation}\label{eq:geodesic sum}
-		e(c)=\int_0^1\sum_{i=1}^N V_i\left(c_i(s_i),\frac{\partial c_i}{\partial s_i}(s_i)\right)\,ds\;.
-	\end{equation}
-
-\mypara Since $M$ has a block-diagonal structure, it can be split into $N$ separate optimization problems depending on
-different decision variables.
-Moreover, the positive definiteness of $M$ implies also that the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
-Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$.
-Consequently,
-	\begin{equation*}
-		\gamma_i=\arg\min e(c_i)\Leftrightarrow\gamma=\arg\min\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
-	\end{equation*}
-	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
-
-\mypara 	From Hopf-Rinow theorem (cf.
-\cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
-	\begin{align*}
-		\gamma_i=\arg\min_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
-	\end{align*}
-	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.
-
-\mypara 	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system~\eqref{eq:general system} is given by Equation~\eqref{eq:contracting feedback law}.
-
-\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
-	\begin{equation}\label{eq:K ODE}
-		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
-	\end{equation}
-	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$.
-It remains to show that this interval of existence can be extended on $[0,1]$.
-In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.
-
-\mypara 	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
-This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
-
-\mypara 	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
-This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
-	\begin{equation*}
-		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
-	\end{equation*}
-	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
-Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
-
-\mypara 	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
-	\begin{equation*}
-		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
-	\end{equation*}
-	where $\widetilde{\gamma}_i(\cdot)\in\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^n)$.
-	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
-
-	To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$.
-This concludes the proof of Theorem~\ref{thm:main result}.
-\end{proof}
+In this paper, these limitations are addressed by imposing a separable structure over $W$.
 
@@
 
-\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}.
+\section{Design of Distributed Controllers}\label{sec:Design of Decentralized Controllers}
+
+\begin{definition}\label{def:SSCCM}
+	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if it can be decomposed into the following sum
+	\begin{equation*}
+		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
+	\end{equation*}
+	where, for each index $i\in\mathbb{N}_{[1,N]}$, and for every $(x_i,\delta_{x_i})\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$, the function $V_i(x_i,\delta_{x_i}):=\delta_{x_i}^\top M_i(x_i)\delta_{x_i}$ is a metric on $\mathbb{R}^{n_i}$.
+\end{definition}
+
+\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
+The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
+
+\mypara To address the constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation}, the structure of the feedback defined by Equation~\eqref{eq:contracting feedback law} is obtained by imposing a suitable constraint on the function $Y$ to be satisfied together with the MI \eqref{eq:MI formulation}.
+
+\mypara For each index $i\in\mathbb{N}_{[1,N]}$, define the set 
+\begin{align}
+		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
+		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
+		&i\in\mathbb{N}_{[1,N]}\}\;,
+\end{align}
+where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having all components zero but those corresponding to the indices defined in $\mathscr{K}$.
+
+\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables.
+Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.
+
+\begin{theorem}\label{thm:main result}
+	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
+In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
+\end{theorem}
+
+\begin{proof}[Proof of Theorem \ref{thm:main result}]
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ are a solution to the MI \eqref{eq:MI formulation}.
+Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
+Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi$.
+
+\mypara	The MI \eqref{eq:MI formulation} implies that the inequality
+	\begin{equation*}
+		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
+	\end{equation*}
+	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$.
+Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
+Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
+
+\mypara 	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}.
+Because $M$ is a block-diagonal matrix, the energy of any curve $c:[0,1]\to\mathbb{R}^n$ satisfies the following equation
+	\begin{equation}\label{eq:geodesic sum}
+		e(c)=\int_0^1\sum_{i=1}^N V_i\left(c_i(s_i),\frac{\partial c_i}{\partial s_i}(s_i)\right)\,ds\;.
+	\end{equation}
+
+\mypara Since $M$ has a block-diagonal structure, it can be split into $N$ separate optimization problems depending on
+different decision variables.
+Moreover, the positive definiteness of $M$ implies also that the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$.
+Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$.
+Consequently,
+	\begin{equation*}
+		\gamma_i=\arg\min e(c_i)\Leftrightarrow\gamma=\arg\min\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+	\end{equation*}
+	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
+
+\mypara 	From Hopf-Rinow theorem (cf.
+\cite[Theorem 7.7]{Boothby1986}), for every index $i\in\mathbb{N}_{[1,N]}$, and for every $x_i$ and $x_i^\ast\in\mathbb{R}^{n_i}$, there exists a solution to the optimization problem
+	\begin{align*}
+		\gamma_i=\arg\min_{c_i\in\Gamma(x_i^\ast,x_i)} e(c_i)\;.
+	\end{align*}
+	This solution is a geodesic smooth curve $\gamma_i:[0,1]\to\mathbb{R}^{n_i}$ connecting $x_i$ to $x_i^\ast\in\mathbb{R}^{n_i}$, because $e(\gamma)=\ell(\gamma)^2$.
+
+\mypara 	From the definition of the tangent vectors $\delta_x$ and $\delta_u$, given an input $u^\ast$ for system \eqref{eq:general system}, a feedback for system~\eqref{eq:general system} is given by Equation~\eqref{eq:contracting feedback law}.
+
+\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
+	\begin{equation}\label{eq:K ODE}
+		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
+	\end{equation}
+which has a unique solution defined on a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$.
+It remains to show that this interval of existence can be extended on $[0,1]$.
+In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.
+
+\mypara 	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
+This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
+
+\mypara 	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
+This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
+	\begin{equation*}
+		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
+	\end{equation*}
+	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
+Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
+
+\mypara 	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
+	\begin{equation*}
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
+	\end{equation*}
+	where $\widetilde{\gamma}_i(\cdot)\in\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^n)$. Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
+
+	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$.
+This concludes the proof of Theorem~\ref{thm:main result}.
+\end{proof}
+
+\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, nothing has been imposed to compute the MI~\eqref{eq:MI formulation} in a distributed manner.
 The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.
@@
 
-\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance.
+\mypara To that end three methodologies are recalled below: chordal graphs, scaled diagonal dominance and alternating direction of multipliers (ADMM).
 The first exploits the network topology to decompose it into smaller complete components.
-The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
-Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling.
+The second method exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling.
+Finally, the last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
 Note that these methodologies can be used either separately or together.
-The latter would appropriate, when the smaller components of the network have high rank and the computing platform where the solver runs has memory limitations.
+The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.
 
 \mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
-onsider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
+Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
 A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
@@
 A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
-The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.
+The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.
 
@@
 Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
+Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI formulation} is satisfied.
 \end{proposition}
@@
 \mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
-For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
+For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbin{\mathtt{proj}}_{\mathscr{C}_k)}(\mathbb{R}^n)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 
@@
 
-\mypara   	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
+\mypara Consequently, whenever the following matrix inequality holds 
   	\begin{equation}\label{eq:MIF}
-  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
-	\end{equation}
-	This concludes the proof.
+  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
+	\end{equation}
+	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI formulation} holds. This concludes the proof.
 \end{proof}
@@
 \mypara Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph.
-The obtained graph is said to be a \emph{chordal embedding}.
-The above procedure can be applied for the chordal embedded graphs.
+The obtained graph is said to be a \emph{chordal embedded} and the above procedure can be applied for this graph.
 
@@
 \end{subequations}
-Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.
-
-\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
+Note that, the requirement of $A$ to be diagonally dominant can be interpreted as the network having stable agents interconnected with a weak coupling.
+
+\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the sum-separable control contraction metrics in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
 To use this methodology, define the set of (resp.
@@
 \end{align*}
-The feasibility program consists of finding symmetric $Q_W\succeq0$ and $Q_{MI}\succeq0$, called \emph{Gramians}, with appropriate dimensions and such that $p_W=\bar{v}^\top Q_W\bar{v}$ and $p_{MI}=\bar{v}^\top Q_{MI}\bar{v}$ belong to $\mathbb{R}[x,v]$, where $\bar{v}$ is vector of monomials on the variables $x_i,\ldots,x_N$ and $v_1,\ldots,v_N$.
+The feasibility program consists of finding symmetric matrices $Q_W\succeq0$ and $Q_{MI}\succeq0$, called \emph{Gramians}, with appropriate dimensions and such that $p_W=\bar{v}^\top Q_W\bar{v}$ and $p_{MI}=\bar{v}^\top Q_{MI}\bar{v}$ belong to $\mathbb{R}[x,v]$, where $\bar{v}$ is vector of monomials on the variables $x_i,\ldots,x_N$ and $v_1,\ldots,v_N$.
 
@@
 
-\mypara The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
+\mypara The MI~\eqref{eq:Artstein-Sontag:inequality:dual} can be cast into the following optimization problem
 \begin{equation*}
@@
 
-\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stabilizability of the origin, for some classes of systems.
+\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
 
@@
 
-\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials and the MI \eqref{eq:MI formulation} could not be solved.
+\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved on a standard desktop computer.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
@@
 
-\mypara For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}.
+\mypara For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example} has been exploited.
 More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.
@@
 \mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
-According to this graph shown, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} has the same order of magnitude for the three cases.
-However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralize case.
+According to this graph, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} has the same order of magnitude for the three cases.
+However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralized case.
 The time difference between the two latter cases can be explained by fact that, for the ``neighbor'' case, the matrix $Y$ contains more non-identically zero elements than the fully decentralized case.
@@
 
-\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}.
+\mypara The solver took approximately 300s to computed the matrix $W$ satisfying the inequality~\eqref{eq:Artstein-Sontag:inequality:dual} employing ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}.
 A summary of the time taken by the solver employing chordal graph and ADMM approach is presented in Table~\ref{tab:chain case}.
@@
 
-\mypara Consider the with network with four agents (i.e., $N=4$) with the topology illustrated in Figure~\ref{fig:cycle graph}.
-Also in this topology, chordal graphs and ADMM are employed to solve the MIs~\eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual}, respectively.
+\mypara Consider the network with four agents (i.e., $N=4$) and the topology illustrated in Figure~\ref{fig:cycle graph}.
+Also here, chordal graphs and ADMM are employed to solve the MIs~\eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual}, respectively.
 
@@
 \end{equation*}
-where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&1+\sum_{j=1}^4y_j^2+x_j^2\end{bmatrix}$,
+where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&1+\sum_{j\in\mathscr{N}(i)\cup\{i\}}^4y_j^2+x_j^2\end{bmatrix}$,
 $\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
@@
 \end{equation*}
-where $\overline{Y}_i(q)=-\begin{bmatrix}3.1y_i,&2.3+2.3\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$.
+where $\overline{Y}_i(q)=-\begin{bmatrix}3.1y_i,&2.3+2.3(x_i^2+y_i^2)\end{bmatrix}$.
 
@@
 \mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
-Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of systems, in general.
+Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of states, in general.
 

### 2017-02-02 R0V0.tex
Start the first paragraph

@@
 
-\mypara Over the years, methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure.
+\mypara Over the years, the improvements on distance communication and cheaper computation platform have allowed the development of large-scale interconnected systems such as smart grids, smart sensor networks, smart manufacturing plants and intelligent transportation systems.
+One of the main characteristic of these systems is the capacity of being autonomous.
+Most of current controller algorithms written to render technologies automatic is based on the assumption that the system will operate ``near'' to a prescribed set point.
+In other words, the system will designed fixed behavior.
+This assumption imposes severe limitations for system, as large excursions are not allowed, in general.
+For instance, large variations on smart grids are not allowed and manufacturing plants tend to synthesize only a fixed range of goods.
+To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.
+
+\mypara In terms of mathematical systems theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equations that describes the system behavior.
+For the former, the system is described by linear equation while, for the latter, by a nonlinear one.
+\todo[inline]{Continue with difficulties to design nonlinear controller.}
+Methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure.
 For linear systems, controller design problems are often translated in terms of optimization.

### 2017-02-02 R0V0.tex
Remove the scaled diagonal dominance paragraphs

@@
 
-\mypara To that end three methodologies are recalled below: chordal graphs, scaled diagonal dominance and alternating direction of multipliers (ADMM).
+\mypara To that end two methodologies are recalled below: chordal graphs and alternating direction of multipliers (ADMM).
 The first exploits the network topology to decompose it into smaller complete components.
-The second method exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling.
-Finally, the last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
-Note that these methodologies can be used either separately or together.
+The last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
 The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.
@@
 The obtained graph is said to be a \emph{chordal embedded} and the above procedure can be applied for this graph.
-
-\mypara Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}.
-If the vector fields $f$ and $B$ are polynomials and the search for the matrix $F$ is restricted to have appropriate diagonal structure, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.
-
-\mypara A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds.
-It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
-
-\mypara The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
-		\begin{align*}
-			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=U^\top DU,\\
-			 D\in SDD_h\}
-		\end{align*}
-be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$.
-
-\mypara Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
-\begin{subequations}
-\begin{equation}\label{eq:DSOS}
-\begin{array}{rcl}
--F_l&\in&\mathbf{SDD}(U_l)\;,
-\end{array}
-\end{equation}
-where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
-\begin{equation}
-\begin{array}{rcl}
-	U_0&=&\ I_h\\
-	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
-\end{array}
-\end{equation}
-\end{subequations}
-Note that, the requirement of $A$ to be diagonally dominant can be interpreted as the network having stable agents interconnected with a weak coupling.
 

### 2017-02-03 R0V0.tex
Change statement of the main result.

@@
 \begin{theorem}\label{thm:main result}
-	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
+	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
 In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.

### 2017-02-03 R0V0.tex
Change notation of u

@@
 
-\mypara The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded.
+\mypara The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ that are locally essentially bounded.
 Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.

### 2017-02-03 R0V0.tex
Change statement of the main result (cont.)

@@
 \begin{theorem}\label{thm:main result}
+	If there exists a solution to the matrix inequalities
+	\begin{subequations}
+		\begin{equation}\label{eq:MI:SSCCM}
+			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
+		\end{equation}
+		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
+		\begin{equation}\label{eq:Ws:SSCCM}
+			W_1\succ0,\ldots,W_N\succ0
+		\end{equation}
+		and
+		\begin{equation}\label{eq:YinXi}
+			Y\in\Xi.
+		\end{equation}
+	\end{subequations}
 	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.

### 2017-02-03 R0V0.tex
Add the information that \Delta_x is computed along signals

@@
 
-\mypara Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
+\mypara Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, along signals $(x(t),u(t))\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
 

### 2017-02-03 R0V0.tex
Change from exploiting sparsity to utilizing separable structure
Change case in which u=0 and delta_u=0 to autonomous case

@@
 As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints.
-However, by exploring sparsity, up to 512 of theses systems can be connected and the distributed controller can be computed.
+However, by utilizing a separable structure (see definition below), up to 512 of theses systems can be connected and the distributed controller can be computed.
 
@@
 \mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions to this system converge to each other exponentially.
-The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
+The proof of this claim, for the autonomous case, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
 

### 2017-02-03 R0V0.tex
Change from "the main advantage" to "one of the main advantages"

@@
 
-\mypara As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
+\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system~\eqref{eq:general system} are recalled below.

### 2017-02-05 R0V0.tex
Change theorem statement and propagate changes

@@
 	If there exists a solution to the matrix inequalities
-	\begin{subequations}
+	\begin{subequations}\label{eq:main result}
 		\begin{equation}\label{eq:MI:SSCCM}
@@
 \begin{proof}[Proof of Theorem \ref{thm:main result}]
-	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ are a solution to the MI \eqref{eq:MI formulation}.
+	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfy the set of equations~\eqref{eq:main result}.
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
@@
 
-\mypara	The MI \eqref{eq:MI formulation} implies that the inequality
+\mypara	The MI~\eqref{eq:MI:SSCCM} implies that the inequality
 	\begin{equation*}
@@
 	\begin{equation}\label{eq:K ODE}
-		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
+		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s))k^\ast(t,s)\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
 	\end{equation}
@@
 
-\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, nothing has been imposed to compute the MI~\eqref{eq:MI formulation} in a distributed manner.
-The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.
+\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, nothing has been imposed to compute the set of equations~\eqref{eq:main result} in a distributed manner.
+The next section provides sufficient conditions to parallelize the search for a solution to the set of equations~\eqref{eq:main result}.
 
@@
 
-\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}.
+\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem to satisfy the set of equations~\eqref{eq:main result}.
 This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
-For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done in parallel.
+In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel.
 
@@
 	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
-Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
-Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI formulation} is satisfied.
+Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension.
+Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
 \end{proposition}
@@
 
-\mypara    Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$.
+\mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$.
 The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
@@
 	\end{equation}
-	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI formulation} holds. This concludes the proof.
+	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds. This concludes the proof.
 \end{proof}
@@
 
-\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved on a standard desktop computer.
+\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the MI~\eqref{eq:MI:SSCCM} could not be solved on a standard desktop computer.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
-Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite.
+Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite.
 For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
@@
 More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $i\in\mathbb{N}_{[1,4]}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\mathbb{R}^8$, $\mathbf{C}(i)=\mathbb{R}^8$.
-The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}.
+The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}.
 The matrix $W$ is given by
@@
 More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.
-Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into $N-1$ cliques  described by the matrix
+Consequently, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $N-1$ cliques  described by the matrix
 \begin{equation*}
@@
 \mypara In the last case, the fully decentralized scenario has been considered.
-The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds.
+The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds.
 In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$.
@@
 
-\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI formulation} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
-According to this graph, for $N=1,2$, the time taken by the parser to solve the MI \eqref{eq:MI formulation} has the same order of magnitude for the three cases.
+\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI:SSCCM} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
+According to this graph, for $N=1,2$, the time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} has the same order of magnitude for the three cases.
 However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralized case.
@@
 
-\mypara In the ``unconstrained'' case, the solver took 7.4s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
+\mypara In the ``unconstrained'' case, the solver took 7.4s to solve the MI~\eqref{eq:MI:SSCCM} using chordal graphs.
 The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1.2)$.

### 2017-02-05 R0V0.tex
Redefine set \Xi

@@
 
-\mypara For each index $i\in\mathbb{N}_{[1,N]}$, define the set 
-\begin{align}
-		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
-		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
-		&i\in\mathbb{N}_{[1,N]}\}\;,
-\end{align}
-where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having all components zero but those corresponding to the indices defined in $\mathscr{K}$.
+\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
+\begin{equation*}
+		Y_{ij}(\cdot)\begin{cases}
+		=Y_{ij}(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
+		\equiv0_{m_i\times n_i},&\text{otherwise},
+		\end{cases}
+\end{equation*}
+for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.
 

### 2017-02-06 R0V0.tex
Add definition of undirected and directed graphs
Change the location of the communication graph to before the problem formulation

@@
 A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$.
+A graph is said to be \emph{undirected} if, for every edge $(i,j)\in\mathscr{E}$, there exists $(j,i)\in\mathscr{E}$.
+It is said to be \emph{directed} if otherwise.
 Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
@@
 where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
+Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network, for each $i\in\mathscr{V}$, define the set $\mathscr{K}(i)=\{j\in\mathbb{N}_{[1,N]}:(i,j)\in\mathscr{E}_c\}$.
+One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{K}$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_k$ for which $k\in\mathscr{K}(i)$.
 
@@
 \mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$.
-The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$, for instance, it can be described by a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ that defined the communication network among different controllers.
 

### 2017-02-06 R0V0.tex
Propagate the change on the definition of the set \Xi in the proof of the main result
Change the definition of Y_ij to make it affine on u
Propagate the changes on the set \Xi in the proof of the main result (cont.)

@@
 		Y_{ij}(\cdot)\begin{cases}
-		=Y_{ij}(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
+		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
 		\equiv0_{m_i\times n_i},&\text{otherwise},
@@
 
-\mypara 	Since the vector field $\overline{K}$ is smooth, it is also Lipschitzian.
-This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
+\mypara Since the vector field $\overline{K}$ is affine on $u$. This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
 	\begin{equation*}
@@
 	\end{equation*}
-	where $\widetilde{\gamma}_i(\cdot)\in\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^n)$. Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
-
-	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$.
+	where $\widetilde{\gamma}_i(\cdot)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}$. Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
+
+	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the dependence of $K_i$ on the variables $x_i$ and $\vec{x}_i$.
 This concludes the proof of Theorem~\ref{thm:main result}.

### 2017-02-07 R0V0.tex
Propagate changes on notation to the example

@@
 
-\mypara Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
+\mypara Once a solution to MI~\eqref{eq:MI formulation} has been computed, the function defined, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, by
 	\begin{equation}\label{eq:differential feedback law}
@@
 \begin{equation*}
-		Y_{ij}(\cdot)\begin{cases}
+		Y_{ij}\begin{cases}
 		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
@@
 
-\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix).
-More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $i\in\mathbb{N}_{[1,4]}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\mathbb{R}^8$, $\mathbf{C}(i)=\mathbb{R}^8$.
-The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}.
-The matrix $W$ is given by
+\mypara In the first one, the graph $\mathscr{G}_c$ describing the communication network is fully connected, i.e., $\mathscr{E}_c=\mathbb{N}_{[1,4]}\times\mathbb{N}_{[1,4]}$ and no constraints were imposed on the matrix $Y$.
+Consequently, for each $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{1,2,3,4\}$, and for every $j\in\mathbb{N}_{[1,4]}$, $Y_{ij}=Y_{ij}(q_1,\ldots,q_4)\in\mathbb{R}^{1\times 2}$.
+
+The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}. The matrix $W$ is given by
 \begin{equation*}
@@
 \end{equation*}
-and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
+and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
 \begin{align*}
- \overline{Y}_{ij}(q)=&-2y_i\;,\\
- \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
+	\overline{Y}_i(q)=&-2\begin{bmatrix}
+	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
+	\end{bmatrix},\\
+	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},
 \end{align*}
-
-\begin{figure*}
+where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
 \begin{equation}\label{eq:example:Y:general}
-		Y(q)=\begin{bmatrix}
-			\overline{Y}_{11}(q),&\underline{Y}_{12}(q),&0,&0,&-0.03y_1,&0,&0&0\\
-			0,&0,&\overline{Y}_{23}(q),&\underline{Y}_{24}(q),&0,&0,&-0.04y_2,&0\\
-			-0.04y_3,&0,&0,&0,&\overline{Y}_{35}(q),&\underline{Y}_{36}(q),&0,&0\\
-			0,&0,&-0.03y_4,&0,&0,&0,&\overline{Y}_{47}(q),&\underline{Y}_{48}(q)
-		\end{bmatrix}
-\end{equation}
-\end{figure*}
+		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
+			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
+			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
+			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
+			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
+		\end{bmatrix}$}.
+\end{equation}
 
@@
 
-\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors.
-To comply with this requirement, the set $\mathscr{K}$ is defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$.
-The sets $\mathbf{C}$ are defined as
-\begin{equation*}
-	\begin{array}{rcl}
-		\mathbf{C}(1)&=&\{\begin{bmatrix}
-		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
-		\mathbf{C}(2)&=&\{\begin{bmatrix}
-		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
-		\mathbf{C}(3)&=&\{\begin{bmatrix}
-		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
-		\mathbf{C}(4)&=&\{\begin{bmatrix}
-		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
-	\end{array} 
-\end{equation*}
-
-\mypara The sets $\mathbin{\mathtt{proj}}_{\mathscr{K}}(\mathbb{R}^8)$ are defined, for each index $i\in\mathbb{N}_{[1,4]}$, as
-\begin{equation*}
-	\begin{array}{rcl}
-		\mathbin{\mathtt{proj}}_{\mathscr{K}(1)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
-		q_1,&q_2\end{bmatrix}\}\;,\\
-		\mathbin{\mathtt{proj}}_{\mathscr{K}(2)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
-		q_1,&q_2,&q_3\end{bmatrix}\}\;,\\
-		\mathbin{\mathtt{proj}}_{\mathscr{K}(3)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
-		q_2,&q_3,&q_4\end{bmatrix}\}\;,\\
-		\mathbin{\mathtt{proj}}_{\mathscr{K}(4)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
-		q_3,&q_4\end{bmatrix}\}\;.
-	\end{array}
-\end{equation*}
+\mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system.
+Consequently, the sets $\mathscr{K}$ are defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$.
 
@@
 	 Y(q)=\begin{bmatrix}
- 	\overline{Y}_1(\cdot)&0&0&0\\
- 	0&\overline{Y}_2(\cdot)&0&0\\
- 	0&0&\overline{Y}_3(\cdot)&0\\
- 	0&0&0&\overline{Y}_4(\cdot)
+ 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
+ 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
+ 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
+ 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
  \end{bmatrix}\;,
@@
 
-\mypara In the last case, the fully decentralized scenario has been considered.
-The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds.
-In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$.
-Moreover, the sets $\mathbf{C}$ are defined as
-\begin{equation*}
-	\begin{array}{rcl}
-		\mathbf{C}(1)&=&\{\begin{bmatrix}
-		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
-		\mathbf{C}(2)&=&\{\begin{bmatrix}
-		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
-		\mathbf{C}(3)&=&\{\begin{bmatrix}
-		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
-		\mathbf{C}(4)&=&\{\begin{bmatrix}
-		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
-	\end{array} 
-\end{equation*}
-Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
+\mypara In the fully decentralized case, also the communication network topology $\mathscr{G}_c$ has the same structure as the network system.
+However, the sets $\mathscr{K}$ are defined as proper subsets of $\mathscr{E}$.
+More precisely, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$.
+The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds, the matrix $W$ is given by
 \begin{equation*}

### 2017-02-09 R0V0.tex
Minor change
Remove ADMM paragraph from distributed synthesis of distributed controller

@@
 	\ell(\gamma)=&\ \int_0^1\left|c_s(s)\right|_{c(s)}\,ds\\
-	e(\gamma)=&\ \int_0^1V\left(c(s),c_s(s)\right)\,ds\;,
+	e(\gamma)=&\ \int_0^1 V(c(s),c_s(s))\,ds\;,
 \end{align*}
@@
 In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel.
-
-\mypara To that end two methodologies are recalled below: chordal graphs and alternating direction of multipliers (ADMM).
-The first exploits the network topology to decompose it into smaller complete components.
-The last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below).
-The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.
+To that end chordal graphs are employed.
+It utilizes the network topology to decompose it into smaller complete components.
 
@@
 The obtained graph is said to be a \emph{chordal embedded} and the above procedure can be applied for this graph.
-
-\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the sum-separable control contraction metrics in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}.
-To use this methodology, define the set of (resp.
-sum-of-squares (SOS)) polynomials $\mathbb{R}[x]$ (resp.
-$\mathbb{SOS}[x]$), and denote the degree of a polynomial $p\in\mathbb{R}[x]$ as $\deg(p)$.
-
-\mypara Condition~\eqref{eq:Arstein-Sontag} is satisfied, whenever the matrix inequality
-\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
- 	B_\perp^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)B_\perp\prec0
-\end{equation} 
-holds, where $B_\perp$ is any full-rank matrix satisfying $B^\top B_\perp\equiv0$ \cite[pp. 23]{Boyd1994}.
-
-\mypara The search the function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ can be relaxed to a semidefinite program.
-Whenever $f$ and $B$ are polynomials, this program is cast in terms of the sum-of-squares (SOS) feasibility program \cite{Parrilo2000}.
-To that end, introduce the vector $v\in\mathbb{R}^n$ and define the polynomials
-\begin{align*}
-	p_W=&\ v^\top W v\;,\\
-	p_{MI}=&\ -v^\top B_\perp^\top(-\dot{W}+AW + WA^\top+2\lambda W)\\
-	&B_\perp v\;.
-\end{align*}
-The feasibility program consists of finding symmetric matrices $Q_W\succeq0$ and $Q_{MI}\succeq0$, called \emph{Gramians}, with appropriate dimensions and such that $p_W=\bar{v}^\top Q_W\bar{v}$ and $p_{MI}=\bar{v}^\top Q_{MI}\bar{v}$ belong to $\mathbb{R}[x,v]$, where $\bar{v}$ is vector of monomials on the variables $x_i,\ldots,x_N$ and $v_1,\ldots,v_N$.
-
-\mypara Now that the computation of a positive definite $W$ satisfying inequality~\eqref{eq:Artstein-Sontag:inequality:dual} in terms of SOS polynomials has been explained, the next step is to solve the SOS feasibility using ADMM.
-
-\mypara Define the set $\mathbf{T}=\{Z_1,\ldots,Z_N:Z=\mathbin{\mathtt{diag}}(Z_1,\ldots,Z_N),p_{MI}=\bar{v}^\top Z\bar{v}\in\mathbb{R}[x,v]\}$.
-For a set $\mathbf{G}$ define the indicator (also known as barrier) function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
-\begin{equation*}
-	H(\mathbf{G},g)=\begin{cases}
-									0,&g\in \mathbf{G}\\
-									\infty,&\text{Otherwise.}
-								\end{cases}
-\end{equation*}
-
-\mypara The MI~\eqref{eq:Artstein-Sontag:inequality:dual} can be cast into the following optimization problem
-\begin{equation*}
-	\begin{array}{rl}
-		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succeq0}^{\alpha_i},Q_{W_i})\\
-		\text{subject to}&Q_{W_i}-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;,
-	\end{array}
-\end{equation*}
-where $\alpha_i=(2n_i+d_i)!/(d_i!(2n_i)!)$, $d_i=\deg(v_i^\top W_iv_i)$ and $v_i\in\mathbb{R}^{n_i}$.
-
-\mypara The ADMM algorithm can be written as
-\begin{enumerate}
-	\item For each $i\in\mathbb{N}_{[1,N]}$, update the matrix $W_i$ as follows.
-	\begin{equation*}
-	\begin{array}{rcl}
-		Q_{W_i}^{k+1}&=&\mathbin{\mathtt{argmin}}_{Q_{W_i}\in\mathbf{S}_{\succeq0}^{\alpha_i}}\left|\left|Q_{W_i}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
-	\end{array}
-\end{equation*}
-	where $||\cdot||_F$ stands for the Frobenius norm;
-
-	\item If the matrices $W_1,\ldots,W_N$ belong to $T$, then a solution has been found and the algorithm can be stopped. Otherwise, solve the global problem
-	\begin{equation*}
-		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i-\Lambda_i^k\right|\right|_F^2\;;
-	\end{equation*}
-	\item Update $\Lambda$ and return to step 1
-	\begin{equation*}
-		\Lambda_i^{k+1}=Q_{W_i}^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
-	\end{equation*}
-\end{enumerate}
-Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $Q_{W_i}$ and the values $\Lambda_i$.
-
-\mypara As $k\to\infty$, for each index $i\in\mathbb{N}_{[1,N]}$, the Gramians $Q_{W_i}$ will coincide with the matrices $Z_i$.
-Consequently, the block-diagonal matrix $Z$ is symmetric and positive semidefinite.
-Thus, $p_{MI}\in\mathbb{SOS}[x,v]$ and, for each index $i\in\mathbb{N}_{[1,N]}$, $v_i^\top W_iv_i\in\mathbb{SOS}[x_i,v_i]$.
-Hence, $M=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)^{-1}$ is a separable control contraction metric for system \eqref{eq:general system}.
 

### 2017-02-09 R0V0.tex
Remove ADMM paragraphs from the examples

@@
 
-\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
-Consider the case with $N=4$.
-Two different methods are employed to compute the matrix $W$, namely, chordal graphs and ADMM.
+\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. To compute the matrix $W$, chordal graphs are employed.
 
@@
 
-\mypara The solver took approximately 300s to computed the matrix $W$ satisfying the inequality~\eqref{eq:Artstein-Sontag:inequality:dual} employing ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}.
-A summary of the time taken by the solver employing chordal graph and ADMM approach is presented in Table~\ref{tab:chain case}.
-
-\begin{figure*}
-\begin{subequations}\label{eq:ADMM:chain case}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-6}\begin{bmatrix}
-		2-7x_1-10^3y_1+10^7y_1^2+10x_1^2-8.9\times10^2x_1y_1&
-		0.5+0.6x_1-5.6\times10^2y_1-3\times10^2y_1^2-9x_1^2-4.1\times10^2\\
-		*&0.4+4x_1-3y_1+6y_1^2+10x_1^2-16x_1y_1
-		\end{bmatrix}$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-6}\begin{bmatrix}
-		4-2x_2-4\times10^3y_2+10^7y_2^2+x_2^2-5\times10^3x_2y_2&
-		2-5x_2-2.5\times10^3y_2-2.3\times10^3y_2^2+3.2x_2^2-2.5\times10^3x_2y_2\\
-		*&1-3x_2+3y_2+3y_2^2+9x_2^2-8x_2y_2
-		\end{bmatrix}$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-6}\begin{bmatrix}
-		58-43x_3-6.1\times10^2y_3+10^8y_3^2+9x_3^2-4\times10^2x_3y_3&
-		-60-9x_3-2.4\times10^2y_3-4\times10^2y_3^2+11x_3^2-3.6\times10^2x_3y_3\\
-		*&60+60x_3-64y_3+18y_3^2+16x_3^2-34x_3y_3
-		\end{bmatrix}$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-6}\begin{bmatrix}
-		18.5+44x_4-3.2\times10^3y_4+9.3\times10^6y_4^2+29x_4^2-3.7\times10^3x_4y_4&
-		-33-50x_4-2\times10^3y_4-2\times10^3y_4^2-9x_4^2-2.3\times10^3x_4y_4\\
-		*&64+31x_4-26y_4+4.4y_4^2+5x_4^2-7x_4y_4
-		\end{bmatrix}$}
-	\end{equation}
-\end{subequations}
-\end{figure*}
-
 \begin{table}
@@
 	&3.5s (neighbor)\\
-	&98s (unconstrained)\\
-	ADMM&300s\\\hline
+	&98s (unconstrained)\\\hline
 	\end{tabular}
-	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the topology illustrated by Fig.~\ref{fig:graph}.}
+	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
 	\label{tab:chain case}
@@
 \mypara Consider the network with four agents (i.e., $N=4$) and the topology illustrated in Figure~\ref{fig:cycle graph}.
-Also here, chordal graphs and ADMM are employed to solve the MIs~\eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual}, respectively.
+Also here, chordal graphs are employed to solve the MIs\eqref{eq:MI formulation}.
 
@@
 where $\overline{Y}_i(q)=-\begin{bmatrix}3.1y_i,&2.3+2.3(x_i^2+y_i^2)\end{bmatrix}$.
-
-\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 114[s] and the obtained matrix $W$ has the components shown in the set of Equations~\eqref{eq:ADMM:cyclic case}.
-A summary of the time taken by the solver employing chordal graph and ADMM approach is presented in Table~\ref{tab:cyclic case}.
-
-\begin{figure*}
-	\begin{subequations}\label{eq:ADMM:cyclic case}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
-		4+3x_1-1\times10^3y_1+1\times10^{5}y_1^2+5x_1^2-1\times10^{3}x_1y_1&2+6x_1-5\times10^2y_1-6\times10^{2}y_1^2+3x_1^2-8\times10^{2}x_1y_1\\
-		*&2+4x_1+3y_1+3y_1^2+5x_1^2+8x_1y_1
-		\end{bmatrix}\;,$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
-		5+9x_2-2\times10^3y_2+1\times10^{5}y_2^2+4x_2^2-1\times10^{3}x_2y_2&6+11x_2-1\times10^{3}y_2-7\times10^{2}y_2^2+5x_2^2-9\times10^{2}x_2y_2\\
-		*&7+12x_2+10y_2+4y_1^2+6x_1^2+9x_2y_2
-		\end{bmatrix}\;,$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
-		7+16x_3-2\times10^3y_3+1\times10^{5}y_3^2+12x_3^2-2\times10^{3}x_3y_3&10+20x_3-1\times10^{3}y_3+1\times10^{3}y_3^2+11x_1^2-11\times10^{3}x_3y_3\\
-		*&20+29x_3+29y_3+13y_3^2+13x_3^2+24x_3y_3
-		\end{bmatrix}\;,$}
-	\end{equation}
-	\begin{equation}
-		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}
-		11+17x_4-2\times10^3y_4+1\times10^{5}y_4^2+9x_4^2-2\times10^{3}x_4y_4&13+21x_4-1\times10^{3}y_4+1\times10^{3}y_4^2+10x_4^2-1\times10^{3}x_4y_4\\
-		*&20+27x_4+24y_4+11y_4^2+12x_4^2+18x_4y_4
-		\end{bmatrix}\;,$}
-	\end{equation}
-	\end{subequations}
-\end{figure*}
 
@@
 	\end{tabular}
-	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
+	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
 	\label{tab:cyclic case}

### 2017-02-12 R0V0.tex
Put clique tree into the notation paragraph

@@
 A \emph{leaf} is a node that is adjacent to only one node.
+The following concepts are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
+A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
+A \emph{chord} of a path is any edge joining two nonconsecutive nodes.
+A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
+The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.
 
@@
 It utilizes the network topology to decompose it into smaller complete components.
-
-\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
-Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}.
-A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
-A \emph{chord} of a path is any edge joining two nonconsecutive nodes.
-A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
-The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.
 
@@
 	&7.7s (neighbor)\\
-	&6.2s (decentralized)\\	
-	ADMM&114s\\\hline
+	&6.2s (decentralized)\\\hline
 	\end{tabular}

### 2017-02-12 R0V0.tex
Propagate changes on the statement of the main result to the example and delete the circle topology case

@@
 
-\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the MI~\eqref{eq:MI:SSCCM} could not be solved on a standard desktop computer.
+\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
@@
 
-The parser took 98  seconds to solve the MI~\eqref{eq:MI:SSCCM}. The matrix $W$ is given by
+The parser took 98  seconds to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
 \begin{equation*}
@@
 
-\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
+\mypara The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3.5 seconds. The matrix $W$ is given by
 \begin{equation*}
@@
 
-\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the MI \eqref{eq:MI:SSCCM} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
-According to this graph, for $N=1,2$, the time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} has the same order of magnitude for the three cases.
+\mypara Figure \ref{fig:time graph} shows a plot of the time taken by parser to the set of matrix inequalities~\eqref{eq:main result} for the three cases considered in this topology: unconstrained, ``neighbor'' and fully decentralized.
+According to this graph, for $N=1,2$, the time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} has the same order of magnitude for the three cases.
 However, as the number of systems increases, the unconstrained case takes more time to be solved than the ``neighbor'' case which, in turn, takes more time than the fully decentralized case.
@@
 	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
-	\caption{Time take by the parser to solve the MI \eqref{eq:MI formulation} for the three cases under consideration.
+	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
 The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).
@@
 
-\subsection{Circumference topology}
-
-\mypara Consider the network with four agents (i.e., $N=4$) and the topology illustrated in Figure~\ref{fig:cycle graph}.
-Also here, chordal graphs are employed to solve the MIs\eqref{eq:MI formulation}.
-
-\begin{figure}[htpb!]
-	\centering
-	\input{./imgs/CyclicGraph.pdf_tex}
-	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
-	\label{fig:cycle graph}
-\end{figure}
-
-\mypara In the ``unconstrained'' case, the solver took 7.4s to solve the MI~\eqref{eq:MI:SSCCM} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1.2)$.
-The matrix $Y$ is given by
-\begin{equation*}
-	Y(q)=\begin{bmatrix}
-	\overline{Y}(q_1)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&\overline{Y}(q_2)&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&\overline{Y}(q_3)&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}(q_4)
-	\end{bmatrix}\;,
-\end{equation*}
-where $\overline{Y}(q_i)=-\begin{bmatrix}2.4y_i,&2.9+2.9(x_i^2+y_i^2)\end{bmatrix}$.
-
-\mypara In the ``neighbor'' case, the solver took 7.7s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1.2)$.
-The matrix $Y$ is given by
-\begin{equation*}
-	Y(q)=\begin{bmatrix}
-		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
-		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
-		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
-		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
-	\end{bmatrix}\;,
-\end{equation*}
-where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&1+\sum_{j\in\mathscr{N}(i)\cup\{i\}}^4y_j^2+x_j^2\end{bmatrix}$,
-$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.
-
-\mypara In the decentralized case, the solver took 6.2s to solve the MI~\eqref{eq:MI formulation} using chordal graphs.
-The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.7,1)$.
-The matrix $Y$ is given by
-\begin{equation*}
-	Y(q)=\begin{bmatrix}
-	\overline{Y}_1(q)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&\overline{Y}_2(q)&0_{2\times1}&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&\overline{Y}_3(q)&0_{2\times1}\\
-	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}_4(q)
-	\end{bmatrix}\;,
-\end{equation*}
-where $\overline{Y}_i(q)=-\begin{bmatrix}3.1y_i,&2.3+2.3(x_i^2+y_i^2)\end{bmatrix}$.
-
-\begin{table}
-	\begin{tabular}{r|l}
-	Method&Time taken by the solver (4 agents)\\ \hline
-	Chordal graph decomposition&7.4s (unconstrained)\\
-	&7.7s (neighbor)\\
-	&6.2s (decentralized)\\\hline
-	\end{tabular}
-	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
-	\label{tab:cyclic case}
-\end{table}
-
-\mypara The online computation of the feedback law for the network composed of subsystems of the form \eqref{eq:example} is analogous to what has been shown to the chain-topology case.
+\subsection{Topology with a cycle}
 

### 2017-02-13 R0V0.tex
Add CDC as a corollary

@@
 	\end{subequations}
-	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
+	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
 In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
@@
 \end{proof}
+
+\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
+	Assume that the matrix $A$ depends only on the system state $x$, the matrix $B$ satisfies the identity
+	\begin{equation*}
+		\partial_BW-\tfrac{\partial B}{\partial x}W+W\tfrac{\partial B}{\partial x}^\top\equiv0
+	\end{equation*}
+	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
+	\begin{equation}\label{eq:with R}
+		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
+	\end{equation}
+	holds uniformly with respect to $x\in\mathbb{R}^n$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$.
+Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
+In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
+\end{corollary}
+
+\mypara To see that Corollary~\ref{cor:main result} is a particular case of Theorem~\ref{thm:main result}, note that imposing $Y$ to be $Y=-RB^\top/2$ on the set $\Xi$ (cf.
+\eqref{eq:YinXi}), the matrix inequality~\eqref{eq:MI:SSCCM} yields \eqref{eq:with R}.
 
@@
 
-\subsection{Topology with a cycle}
+\subsection{A topology with a cycle}
 

### 2017-02-14 R0V0.tex
Modify abstract and introduction

@@
 The problem is the design of distributed controllers for this class of network systems.
-Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, numerical methods employed to construct for these functions usually lead to a non-convex optimization problem.
+Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, the construction of these functions is a non-convex optimization problem.
 Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements.
 In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures.
-By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
+By utilizing a separable structure, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
 An example illustrates the approach for a network system.
@@
 
-\mypara Over the years, the improvements on distance communication and cheaper computation platform have allowed the development of large-scale interconnected systems such as smart grids, smart sensor networks, smart manufacturing plants and intelligent transportation systems.
+\mypara Over the years, improvements on distance communication and cheaper computation platforms have allowed the development of large-scale interconnected systems such as smart grids, sensor networks \cite{Pajic2011}, smart manufacturing plants and traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}.
 One of the main characteristic of these systems is the capacity of being autonomous.
-Most of current controller algorithms written to render technologies automatic is based on the assumption that the system will operate ``near'' to a prescribed set point.
-In other words, the system will designed fixed behavior.
+Most of current control algorithms are based on the assumption that the system will operate ``near'' to a prescribed set point.
+Consequently, the system is designed to have fixed behavior.
 This assumption imposes severe limitations for system, as large excursions are not allowed, in general.
-For instance, large variations on smart grids are not allowed and manufacturing plants tend to synthesize only a fixed range of goods.
+For instance, large power variations on smart grids (e.g., when renewable sources of energy are taken into account) are not allowed and manufacturing plants tend to synthesize only a fixed range of goods.
 To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.
 
-\mypara In terms of mathematical systems theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equations that describes the system behavior.
-For the former, the system is described by linear equation while, for the latter, by a nonlinear one.
-\todo[inline]{Continue with difficulties to design nonlinear controller.}
-Methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure.
-For linear systems, controller design problems are often translated in terms of optimization.
-
-\mypara Numerical methods to design linear controllers include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}.
-The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.
-In the case of nonlinear systems, design approaches are generally analytic and include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}.
-These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.
-
-\mypara For systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}.
-However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}).
-In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.
-
-\mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs).
-One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}.
-
-\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it may require a large memory size.
-This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
-In general, the case is worse, for nonlinear systems.
-
-\mypara Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}.
-For such systems, a property often desired is the ability to synthetize controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).
-
-\mypara In terms of semidefinite programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems.
-Consequently, for nonlinear systems the problem is very challenging.
-
-\mypara In the case of linear systems whose solutions evolve in the positive orthant (positive systems), the problem of design a structured stabilizing feedback law has been addressed in \cite{Tanaka2011}.
-Also, the authors show that the existence of such a controller is equivalent to the existence of Lyapunov function with a diagonal structure.
-The importance of this result for large-scale systems is highlighted in \cite{Rantzer2015}, where sparsity is explored to solve linear programs.
-
-\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein).
-However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions).
-The case can be even worse, when structural constraints are imposed.
-
-\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints.
-The systems under consideration are continuously differentiable and affine in the input.
-One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions.
-Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.
+\mypara In terms of control theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equation that describes the system behavior.
+In the former, the system is described by linear equation while, in the latter, by a nonlinear one.
+In general, controller design methods for nonlinear systems require the knowledge of a \emph{Lyapunov function}.
+The search of Lyapunov functions for this class of systems is a non-trivial problem by itself, as no general methodology exists.
+Another drawback of Lyapunov functions is the fact that they are defined with respect to a particular set point.
+In case of large excursions, it is more appropriate to define a function depending of the distance between set points.
+Even if a Lyapunov function is known, no general methodology is known to design distributed feedback laws for nonlinear systems.
+Thus, existing approaches are, in general, \emph{ad-hoc}.
+When the design of distributed controllers is considered, the situation is even worse as the problem is known to be, at least, NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}.
+
+\mypara  An alternative method, called control contraction method (CCM), provides an algorithm in which nonlinear feedback laws are designed based on solving a convex optimization problem  \cite{Manchester2014a}.
+The main challenge with this methodology is that, when the system under consideration has a large number of states, it may require a large memory amount.
+This is due to the fact that the stability verification of a linear system with $n$ states may require a function with, at least, $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
+
+\mypara One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions to each other.
+Employing CCMs that can be decomposed into the sum of smaller elements, the design of a distributed feedback law allowing exponential convergence of solutions is obtained in two steps.
 
@@
 This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained.
+A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}.
+In contrast to this paper, more general conditions to design the distributed controller (cf.
+Corollary~\ref{cor:main result}) and a methodology to distribute the computation of the feedback law are given.
 

### 2017-03-07 R0V0.tex
Small change on the matrix of the example
Start new example. Add figure illustrating the topology
several modifications

@@
 where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
-Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network, for each $i\in\mathscr{V}$, define the set $\mathscr{K}(i)=\{j\in\mathbb{N}_{[1,N]}:(i,j)\in\mathscr{E}_c\}$.
-One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{K}$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_k$ for which $k\in\mathscr{K}(i)$.
+Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network, for each $i\in\mathscr{V}$.
+One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$.
 
@@
  For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}.
-Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;
+Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ described by the graph $\mathscr{G}_c$.
 \end{problem}
 
-\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$.
+\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the graph $\mathscr{G}_c$.
 
@@
 
-	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the dependence of $K_i$ on the variables $x_i$ and $\vec{x}_i$.
+	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the dependence of $K_i$ on the variables $x_i$ and $\vec{x}_i$.
 This concludes the proof of Theorem~\ref{thm:main result}.
@@
 
-\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
-For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbin{\mathtt{proj}}_{\mathscr{C}_k)}(\mathbb{R}^n)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
+\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
+For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 
 \mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$.
-The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
+The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
    \begin{equation*}
@@
 
-\subsection{Chain topology}
-
-\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. To compute the matrix $W$, chordal graphs are employed.
+\subsection{Chain topology}\label{sec:chain topology}
+
+\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. To compute the matrix $W$, chordal graphs are employed.
 
@@
 \mypara In the first one, the graph $\mathscr{G}_c$ describing the communication network is fully connected, i.e., $\mathscr{E}_c=\mathbb{N}_{[1,4]}\times\mathbb{N}_{[1,4]}$ and no constraints were imposed on the matrix $Y$.
-Consequently, for each $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{1,2,3,4\}$, and for every $j\in\mathbb{N}_{[1,4]}$, $Y_{ij}=Y_{ij}(q_1,\ldots,q_4)\in\mathbb{R}^{1\times 2}$.
+Consequently, for each $i\in\mathbb{N}_{[1,4]}$, for every $j\in\mathbb{N}_{[1,4]}$, $Y_{ij}=Y_{ij}(q_1,\ldots,q_4)\in\mathbb{R}^{1\times 2}$.
 
@@
 	\end{bmatrix},\\
-	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},
+	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
+	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
 \end{align*}
@@
 \mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system.
-Consequently, the sets $\mathscr{K}$ are defined as $\mathscr{K}(1)=\{1,2\}$, $\mathscr{K}(4)=\{3,4\}$ and $\mathscr{K}(i)=\{i-1,i,i+1\}$, for each index $i=2,3$.
+Consequently, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\mathscr{E}$.
 
@@
 
-\mypara In the fully decentralized case, also the communication network topology $\mathscr{G}_c$ has the same structure as the network system.
-However, the sets $\mathscr{K}$ are defined as proper subsets of $\mathscr{E}$.
-More precisely, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$.
-The time taken by the parser to solve the MI~\eqref{eq:MI:SSCCM} was 2.6 seconds, the matrix $W$ is given by
+\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$.
+The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 2.6 seconds, the matrix $W$ is given by
 \begin{equation*}
@@
 	&98s (unconstrained)\\\hline
-	\end{tabular}
+	\end{tabular}\vspace{1em}
 	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
@@
 \subsection{A topology with a cycle}
+
+\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}.
+As in the Section~\ref{sec:chain topology}, here same three scenarios are considered.
+Namely, the unconstrained case, the ``neighbor'' case and the fully decentralized case.
+
+\begin{figure}[htpb!]
+	\centering
+	\input{./imgs/NewExample.pdf_tex}
+	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
+	\label{fig:graph}
+\end{figure}
+
+\mypara In the first scenario, the unconstrained case, the graph $\mathscr{G}_c$ describing the communication network is fully connected, i.e., $\mathscr{E}_c=\mathbb{N}_{[1,6]}\times\mathbb{N}_{[1,6]}$ and no constrained were imposed on the matrix $Y$.
+Consequently, the matrix $Y$ have elements given by $Y_{ij}=Y_{ij}(q_1,q_2,q_3,q_4)$, for each $i,j\in\mathbb{N}_{[1,4]}$, for each $(q_1,q_2,q_3,q_4)\in\mathbb{R}^8$.
+
+\mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$.
+The solver took 43s to solve the set of matrix inequalities~\eqref{eq:main result}.
+
+\mypara The matrix $W$ obtained is given by
+\begin{equation*}
+	W=\mathbin{\mathtt{diag}}(0.6,1,0.8,1,0.6,1,0.4,1,0.7,1,1,1)
+\end{equation*}
+
+\mypara The matrix $Y$ have elements given by $Y_{ij}=Y_{ij}(q_i)\delta_{ij}\in\mathbb{R}^{2\times 1}$, for each $i,j\in\mathbb{N}_{[1,4]}$, and for each $q_i\in\mathbb{R}^{2}$, where $\delta_{ij}$ is the Kronecker's delta.
 

### 2017-03-08 R0V0.tex
Remove cholesky decomposition from notation
Finish example and other minor modifications

@@
 The problem is the design of distributed controllers for this class of network systems.
-Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, the construction of these functions is a non-convex optimization problem.
+Although control-Lyapunov functions are the natural candidates to design feedback laws, the computation of these functions is a non-convex optimization problem.
 Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements.
-In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures.
-By utilizing a separable structure, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
+In this paper, control-contraction metrics (CCMs) are employed to design controllers with prescribed distributed structures.
+By using a separable structure, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
 An example illustrates the approach for a network system.
@@
 
-\mypara Over the years, improvements on distance communication and cheaper computation platforms have allowed the development of large-scale interconnected systems such as smart grids, sensor networks \cite{Pajic2011}, smart manufacturing plants and traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}.
+\mypara Over the years, improvements on distance communication and cheaper computation platforms have allowed the development of large-scale interconnected systems such as smart grids, sensor networks \cite{Pajic2011}, smart manufacturing plants, traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}.
 One of the main characteristic of these systems is the capacity of being autonomous.
@@
 Consequently, the system is designed to have fixed behavior.
-This assumption imposes severe limitations for system, as large excursions are not allowed, in general.
-For instance, large power variations on smart grids (e.g., when renewable sources of energy are taken into account) are not allowed and manufacturing plants tend to synthesize only a fixed range of goods.
-To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account a more complex behavior is needed.
+This assumption imposes severe limitations for systems, as large excursions are not allowed, in general.
+For instance, large power variations in smart grids (e.g., when renewable sources of energy are taken into account) are not allowed and manufacturing plants tend to synthesize only a fixed range of goods.
+To render these systems more flexible, i.e., allowing large excursions a controller algorithm that takes into account the behavior far from the set point is needed.
 
@@
 Another drawback of Lyapunov functions is the fact that they are defined with respect to a particular set point.
-In case of large excursions, it is more appropriate to define a function depending of the distance between set points.
+In case of large excursions, it is more appropriate to define a function depending on the distance between points.
 Even if a Lyapunov function is known, no general methodology is known to design distributed feedback laws for nonlinear systems.
@@
 For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
-This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained.
+This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit algorithm of the distributed controller is provided.
 A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}.
@@
 semi)definite such a class of matrices is denoted as $\mathbf{S}_{\star0}^n=\{M\in\mathbb{R}^{n\times n}:M\star0,M=M^\top\}$, where $\star\in\{\succ,\succeq,\prec,\preceq\}$.
-For a matrix $M\succ0$, the notation $\mathbin{\mathtt{chol}}(M)$ stands for the \emph{upper-triangular Cholesky factor $U$} satisfying $A=U^\top U$.
 
@@
 where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
-Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network, for each $i\in\mathscr{V}$.
-One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$.
+Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network.
+One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$.
 
@@
 
-\mypara Since the vector field $\overline{K}$ is affine on $u$. This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
+\mypara Since the vector field $\overline{K}$ is affine on $k^\ast$.
+This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
 	\begin{equation*}
@@
 	\begin{equation*}
-		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma),k_i^\ast(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma))k_i^\ast(t,\sigma)\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
 	\end{equation*}
@@
 
+\mypara Table~\ref{tab:chain case} shows a summary of the time taken by the solver to compute the matrices $W$ and $Y$ satisfying the set of matrix inequalities~\eqref{eq:main result}, according to the unrestricted, ``neighbor'' and fully decentralized cases.
+
 \begin{figure}[htpb!]
@@
 \begin{table}
-	\begin{tabular}{r|l}
-	Method&Time taken by the solver (4 agents)\\ \hline
-	Chordal graph decomposition&2.6s (decentralized)\\
-	&3.5s (neighbor)\\
-	&98s (unconstrained)\\\hline
+	\begin{tabular}{r|c}
+	Case&Time taken by the solver (4 agents)\\ \hline
+	Unconstrained&98s\\
+	Neighbor&3.5s\\
+	Fully decentralized&2.6s\\\hline
 	\end{tabular}\vspace{1em}
-	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
+	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
 	\label{tab:chain case}
@@
 
+\mypara The solver took 48s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
+\begin{equation*}
+	W=\mathbin{\mathtt{diag}}(0.1,1,0.1,1,0.1,1,0.1,1,0.1,1,0.3,1).
+\end{equation*}
+The matrix $Y$ is given by
+\begin{equation*}
+	\begin{bmatrix}
+		\overline{Y}_{11}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
+		0_{1\times2}&\underline{Y}_{22}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
+		0_{1\times2}&0_{1\times2}&\overline{Y}_{33}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
+		0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{44}(q)&0_{1\times2}&0_{1\times2}\\
+		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{55}(q)&0_{1\times2}\\
+		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\underline{Y}_{66}(q)
+	\end{bmatrix},
+\end{equation*}
+for every $q\in\mathbb{R}^{12}$, where 
+\begin{align*}
+ \overline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&4+4\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},\\
+ \underline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&2+2\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},
+\end{align*}
+for each index $i,j\in\mathbb{N}_{[1,6]}$.
+
+\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network.
+More precisely, $\mathscr{G}_c=\mathscr{G}$.
+The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.
+
+\mypara The matrix $W$ obtained is given by
+\begin{equation*}
+	W=\mathbin{\mathtt{diag}}(1,1,1,1,1,1,1,1,1,1,2,1).
+\end{equation*} 
+The matrix $Y$ is given by Equation~\eqref{eq:Y mixed case:neighbor}.
+
+\setcounter{MaxMatrixCols}{20}
+\begin{figure*}
+\begin{equation}\label{eq:Y mixed case:neighbor}
+	\resizebox{.9\textwidth}{!}{
+$-\begin{bmatrix}
+		2y_1&4+3(|q_1|^2+|\breve{q}_1|^2)&0&0&0&0&0&0&0&0&0&0\\
+		0&0&2y_2&2+2(|q_2|^2+|\breve{q}_2|^2)&0&0&0&0&0&0&0&0\\
+		0&0&0&0&2y_3&4+3(|q_3|^2+|\breve{q}_3|^2)&0&0&0&0&0&0\\
+		0&0&0&0&0&0&2y_4&3+3(|q_4|^2+|\breve{q}_4|^2)&0&0&0&0\\
+		0&0&0&0&0&0&0&0&2y_5&4+3(|q_5|^2+|\breve{q}_5|^2)&0&0\\
+		0&0&0&0&0&0&0&0&0&0&2y_6&4+3(|q_6|^2+|\breve{q}_6|^2)
+	\end{bmatrix}$}
+\end{equation}
+\end{figure*}
+
 \mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$.
@@
 
-\mypara The matrix $Y$ have elements given by $Y_{ij}=Y_{ij}(q_i)\delta_{ij}\in\mathbb{R}^{2\times 1}$, for each $i,j\in\mathbb{N}_{[1,4]}$, and for each $q_i\in\mathbb{R}^{2}$, where $\delta_{ij}$ is the Kronecker's delta.
+\mypara The matrix $Y$ have elements given by $Y_{ij}=Y_{ij}(q_i)\delta_{ij}\in\mathbb{R}^{2\times 1}$, for each $i,j\in\mathbb{N}_{[1,6]}$, and for each $q_i\in\mathbb{R}^{2}$, where $\delta_{ij}$ is the Kronecker's delta.
+More specifically, the matrix $Y$ is presented in Equation~\eqref{Y for mixed case}.
+
+\begin{figure*}
+\begin{equation}\label{Y for mixed case}
+	Y=-\begin{bmatrix}
+	2y_1&5+3|q_1|^2&0&0&0&0&0&0\\
+ 	0&0&2y_2&3+2|q_2|^2&0&0&0&0\\
+ 	0&0&0&0&2y_3&5+3|q_3|^2&0&0\\
+ 	0&0&0&0&0&0&2y_4&4+2|q_4|^2
+	\end{bmatrix}
+\end{equation}
+\end{figure*}
+
+\begin{table}
+	\begin{tabular}{r|c}
+	Case&Time taken by the solver (4 agents)\\ \hline
+	Unconstrained&48s\\
+	Neighbor&57s\\
+	Fully decentralized&43s\\\hline
+	\end{tabular}\vspace{1em}
+	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
+	\label{tab:mixed example}
+\end{table}
 

### 2017-05-25 R0V0.tex
Minor changes
Add 3D simulation without input and other minor changes

@@
 
+\mypara Figure~\ref{fig:3dsim} shows the $x$-component of a simulation of network~\eqref{eq:example} composed of three systems with the network structure as represented by the graph in Figure~\ref{fig:graph} and with input $u\equiv0$.
+Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.
+
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=\linewidth]{./imgs/3dsim.eps}
+	\caption{Simulation of network~\eqref{eq:example} for 1s with input $u\equiv0$, $N=3$ and starting from random initial conditions.}
+	\label{fig:3dsim}
+\end{figure}
+
 \mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
+	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
 	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
@@
 
-\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}.
+\mypara The graph describing the network structure is provided in Figure~\ref{fig:cycle graph}.
 As in the Section~\ref{sec:chain topology}, here same three scenarios are considered.
@@
 	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
-	\label{fig:graph}
+	\label{fig:cycle graph}
 \end{figure}
@@
 	\end{tabular}\vspace{1em}
-	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
+	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
 	\label{tab:mixed example}

### 2017-05-31 R0V0.tex
Modifications to make clear the dependence of the metric on each component i of x

@@
 Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.
+For each index $i\in\mathbb{N}_{[1,N]}$, define $\Pi_i$ as the set of functions $W_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ such that, for each $j\in\mathbb{N}_{[1,N]}\setminus\{i\}$, $\tfrac{\partial W_i}{\partial x_j}\equiv 0$.
 
@@
 		\begin{equation}\label{eq:Ws:SSCCM}
-			W_1\succ0,\ldots,W_N\succ0
+			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
 		\end{equation}
@@
 	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
-	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
+	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
 The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).

### 2017-05-31 R0V0.tex
Change notation of the plant graph by adding a subscript p

@@
 
-\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$.
+\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}_p$ defined by the set of vertices $\mathscr{V}_p=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}_p\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$.
 For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
@@
 \mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system.
-Consequently, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\mathscr{E}$.
+Consequently, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\mathscr{E}_p$.
 
@@
 \mypara In the ``neighbor'' case, the topology of the controller is the same as of the network.
-More precisely, $\mathscr{G}_c=\mathscr{G}$.
+More precisely, $\mathscr{G}_c=\mathscr{G}_p$.
 The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.

### 2017-05-31 R0V0.tex
Add a figure explaining the difference between the plant and the communication network graph
Add figure with simulations

@@
 One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$.
+The difference between both graphs is illustrated in Figure~\ref{fig:graph different illustration}.
+
+\begin{figure}[htbp!]
+	\centering
+%	\includegraphics[]{}
+	\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
+	\caption{Illustration of the graphs $\mathscr{G}_p$ and $\mathscr{G}_c$. The solid lines represent the edges defining $\mathscr{G}_p$ while the dashed lines represent edges defining $\mathscr{G}_c$.}
+	\label{fig:graph different illustration}
+\end{figure}
 
@@
 
-\mypara Figure~\ref{fig:3dsim} shows the $x$-component of a simulation of network~\eqref{eq:example} composed of three systems with the network structure as represented by the graph in Figure~\ref{fig:graph} and with input $u\equiv0$.
+\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs, and the Riemannian metric $V$.
 Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.
@@
 	\centering
-	\includegraphics[width=\linewidth]{./imgs/3dsim.eps}
-	\caption{Simulation of network~\eqref{eq:example} for 1s with input $u\equiv0$, $N=3$ and starting from random initial conditions.}
+	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
+	\vspace{-2em}
+	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained.
+In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.
+The bottom graph shows the variation of the Riemannian metric along the solutions of each case.}
 	\label{fig:3dsim}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
+	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
 	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.

### 2017-05-31 R0V0.tex
Changes regarding the maximum number of nodes simulated in Wolfram's computer

@@
 \mypara In the remainder of this section, two network topologies are considered to illustrate the results presented in this paper.
-The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b
+The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 32GB RAM, Ubuntu and on Matlab 2015b
 
@@
 
-\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer.
+\mypara When $N>8$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer.
 A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$.
@@
 	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
-The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).
+The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).
 Axes are on log scale.}

### 2017-05-31 4agents.py
Initial commit

@@ -1,0 +1,291 @@
+"""
+Notes:
+    
+    1) Known numerical errors. Choosing the initial condition [-9.44500792, 2.92172601] for the trajectory generator and
+    the initial condition [-9.06892831, -9.7230096 ] for the closed-loop system leads to a trajectory error, when the
+    odeint is executed with the option mxstep<1500
+
+"""
+
+import logging
+import inspect
+import numpy as np
+from pylab import *
+from scipy.integrate import odeint
+from scipy.integrate import quad
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import random
+import itertools
+
+def trajectory_plot(t, trajectory, case, title, linestyle, ax1 = None, ax2 = None):
+
+    fig = plt.figure(title, figsize=(6, 8), dpi=80)
+    fig.subplots_adjust(left=0.2, wspace=0.4, hspace = 0.5)
+    # st = fig.suptitle(title)
+    # st.set_y(0.95)
+    labelx = -0.15
+    components = itertools.cycle([r'$x(t)$', r'$y(t)$'])
+    color_vector = itertools.cycle(['red', 'blue', 'green', 'black'])
+    for counter in range(trajectory.shape[1]):
+        if (counter % 2) == 0:
+            if (case is 'diagonal') & (counter == 0) & (ax1 == None):
+                ax1 = plt.subplot2grid((5, 2), ((counter % 2), 0))
+            elif (case is 'neighbour') & (counter == 0) & (ax1 == None):
+                ax1 = plt.subplot2grid((5, 2), ((counter % 2) + 2, 0))
+            elif (case is 'unconstrained') & (counter == 0) & (ax1 == None):
+                ax1 = plt.subplot2grid((5, 2), ((counter % 2), 1))
+            elif (counter == 0) & (ax1 == None):
+                ax1 = plt.subplot2grid((5, 2), ((counter % 2) + 2, 1))
+            color = color_vector.next()
+            ax1.plot(t, trajectory[:, counter], label=r'x' + str(counter / 2 + 1), linestyle=linestyle, c=color)
+            ax1.set_xticklabels([])
[…]

### 2017-05-31 single_agent.py

@@ -1,0 +1,164 @@
+"""
+Notes:
+    
+    1) Known numerical errors. Choosing the initial condition [-9.44500792, 2.92172601] for the trajectory generator and
+    the initial condition [-9.06892831, -9.7230096 ] for the closed-loop system leads to a trajectory error, when the
+    odeint is executed with the option mxstep<1500
+
+"""
+
+import logging
+import inspect
+import numpy as np
+from pylab import *
+from scipy.integrate import odeint
+from scipy.integrate import quad
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import random
+import itertools
+
+def trajectory_plot(t, trajectory, label, title, linestyle, color):
+
+    fig = figure(title)
+    st = fig.suptitle(title)
+    st.set_y(0.95)
+    components = [r'$x(t)$', r'$y(t)$']
+    for counter, y_label in zip(range(trajectory.shape[1]), components):
+        if counter == 0:
+            ax1 = plt.subplot(3, 1, counter + 1)
+            plt.plot(t, trajectory[:, counter], label=label, linestyle=linestyle, c=color)
+        else:
+            ax2 = plt.subplot(3, 1, counter + 1)
+            plt.plot(t, trajectory[:, counter], label=label, linestyle=linestyle, c=color)
+
+        plt.legend(loc='best')
+        plt.ylabel(y_label)
+        plt.grid(True)
+    ax1.get_shared_x_axes().join(ax1, ax2)
+    ax1.set_xticklabels([])
+    ax2.set_xticklabels([])
+    #plt.xlabel(r'time $t$')
+
+
+    return
+
+def initial_condition_generator(n_agents, zero = False):
+    logging.info('Starting')
+    logging.debug('input = %s' %n_agents)
+    if zero is False:
+        ic = []
+        for counter in range(2 * n_agents):
+            ic.append(random.random() * (-1) ** random.randrange(1, 10))
+    else:
+        ic = np.zeros(2)
+    ic = np.array(ic).reshape(2, 1) * 10
+    logging.debug('output = %s' % ic)
+    logging.info('End\n\n')
+    return ic
+
+def load_system(states, t, open_loop, M = np.eye(2), target_trajectory = None):
+    logging.info('\n Starting')
[…]

### 2017-05-31 TheoreticalExample2/mat_reader.py
Add Python script to generate the time taken by the solver to compute the controller, as the number of agents increases

@@ -1,0 +1,62 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue May 02 11:20:13 2017
+
+@author: humberto
+"""
+
+import scipy.io as sio
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+number_of_neighbors = [2**i for i in range(0, 10)]
+
+l_constraint = []
+l_nn = []
+l_st = []
+l_solver = []
+
+for solver in ['mosek', 'CDCS']:
+    for nn in number_of_neighbors:
+        for constraint in ['General', 'Neighbor', 'Diagonal']:
+            
+            filename = 'Output' + constraint + str(nn) + 'Agents' + '-Solver_' + solver
+            filename = filename + '.mat'
+            l_constraint.append(constraint)
+            l_nn.append(nn)
+            l_solver.append(solver)
+            try:
+                mat = sio.loadmat(filename)
+                l_st.append(float(mat['SolverTime']))
+            except IOError:
+                l_st.append('na')
+
+df = pd.DataFrame(zip(l_constraint, l_nn, l_st, l_solver), 
+                  columns=['Constraint', 'NNeigh', 'SolverTime', 'Solver'])
+
+df[['SolverTime']] = pd.to_numeric(df['SolverTime'], errors='coerce')
+print df.head()
+print df[(df.Constraint == 'Neighbor') & (df.Solver == 'mosek')]
+
+fig = plt.figure()
+ax = plt.gca()
+mosek_diagonal = ax.scatter(df[(df.Constraint == 'Diagonal') & (df.Solver == 'mosek')].NNeigh, df[(df.Constraint == 'Diagonal') & (df.Solver == 'mosek')].SolverTime, c='blue', marker='o', label='Diagonal', alpha=0.33, lw=1)
+mosek_neighbor = ax.scatter(df[(df.Constraint == 'Neighbor') & (df.Solver == 'mosek')].NNeigh, df[(df.Constraint == 'Neighbor') & (df.Solver == 'mosek')].SolverTime, c='blue', marker='s', label='Neighbor', alpha=0.33, lw=1)
[…]

### 2017-05-31 TheoreticalExample2/MixedExample.m
Computation of the matrix inequalities for the second example

@@ -1,0 +1,80 @@
+function MixedExample
+clear all
+close all
+clc
+warning off
+
+global Simulation SystemStates SystemInputs 
+global SystemParameters d
+
+Simulation   = 0;
+SystemStates = ['x','y'];
+SystemInputs = ['u'];
+SystemParameters = ['d'];
+d = 1e-2;
+lambda = 1e-1; % Max value for SOS feasibility
+Option       = 'Unconstrained';
+
+LaplacianMatrix = LaplacianMatrixGenerator;
+NumberOfAgents  = length(LaplacianMatrix);
+
+fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
+diary(fname)
+diary on
+
+Optimisation(LaplacianMatrix,Option,lambda)
+
+diary off
+
+end
+
+function out = LaplacianMatrixGenerator
+
+out = [ 2, -1,  0, -1,  0,  0;
+       -1,  2, -1,  0,  0,  0;
+        0, -1,  2, -1,  0,  0;
+       -1,  0, -1,  3, -1,  0;
+        0,  0,  0, -1,  2, -1;
+        0,  0,  0,  0, -1, -1];
+    
+end
+
+function Optimisation(LaplacianMatrix,Option,lambda)
+
+global Simulation SystemStates SystemInputs SystemParameters
+
+WriterSys(SystemStates,SystemInputs,SystemParameters,Simulation,LaplacianMatrix)
+PreProcessedSys
+
+Wdegree = 2;
+ScalingFactor = 1e-2;  % Max value for SOS feasibility
+WriterW(SystemStates,LaplacianMatrix,Wdegree,ScalingFactor)
+PreProcessedW
+
+Ydegree = 2;
+WriterY(SystemStates,SystemInputs,LaplacianMatrix,Option,Ydegree)
+PreProcessedY
+
+% WriterMI(SystemStates,LaplacianMatrix,ScalingFactor,lambda,Option)
+PreProcessedMixedMI
+
+Constraints = [WConstraints;MIConstraints];
+checkset(Constraints)
+coefList = [Wc;Yc];
+options = sdpsettings('solver','mosek','verbose',1);
+tic
+[sol, q, Q, res] = solvesos(Constraints,[],options,coefList);
+SolverTime = toc;
+
+Precision = 1e-3;
+AnalysisW(SystemStates,LaplacianMatrix,Precision)
+PostProcessedW
+
[…]

### 2017-05-31 TheoreticalExample2/TimerPlot.m
Minor modification in the file TimerPlot.m

@@ -9,45 +9,54 @@ set(groot, 'defaultLegendInterpreter','latex');
     
     TimeDiagonal(1) = 1.224428609719290;
     TimeDiagonal(2) = 1.561498248693083;
-    TimeDiagonal(3) = 2.754560839016742;
-    TimeDiagonal(4) = 5.57600135162288;
-    TimeDiagonal(5) = 10.910490511994272;
-    TimeDiagonal(6) = 22.1421868579150;
-    TimeDiagonal(7) = 47.584998880884680;
-    TimeDiagonal(8) = 1.074516828633032e+02;
-    TimeDiagonal(9) = 2.677553198628477e+02;
-    TimeDiagonal(10) = 8.784112856174025e+02;
+    TimeDiagonal(3) = 0;
+    TimeDiagonal(4) = 2.754560839016742;
+    TimeDiagonal(5) = 5.57600135162288;
+    TimeDiagonal(6) = 10.910490511994272;
+    TimeDiagonal(7) = 22.1421868579150;
+    TimeDiagonal(8) = 47.584998880884680;
+    TimeDiagonal(9) = 1.074516828633032e+02;
+    TimeDiagonal(10) = 2.677553198628477e+02;
+    TimeDiagonal(11) = 8.784112856174025e+02;
     
     
     TimeNeighbor(1) = 1.4669574118103108;
     TimeNeighbor(2) = 1.534924490309093;
-    TimeNeighbor(3) = 3.531500826408437;
-    TimeNeighbor(4) = 8.130443844688111;
-    TimeNeighbor(5) = 17.69292659906184;
-    TimeNeighbor(6) = 37.699186934101675;
-    TimeNeighbor(7) = 81.59612608462406;
-    TimeNeighbor(8) = 159.61856998294263;
-    TimeNeighbor(9) = 444.1379786425903;
-    TimeNeighbor(10) = 0;
+    TimeNeighbor(3) = 0;
+    TimeNeighbor(4) = 3.531500826408437;
+    TimeNeighbor(5) = 8.130443844688111;
+    TimeNeighbor(6) = 17.69292659906184;
+    TimeNeighbor(7) = 37.699186934101675;
+    TimeNeighbor(8) = 81.59612608462406;
+    TimeNeighbor(9) = 159.61856998294263;
+    TimeNeighbor(10) = 444.1379786425903;
+    TimeNeighbor(11) = 0;
     
     TimeGeneral(1) = 1.37392396598692;
     TimeGeneral(2) = 1.5140840205569028;
[…]

### 2017-05-31 TheoreticalExample2/LMIOptmisation.m
Modify the LMIOptimisation.m to include the CDCS solver option

@@ -1,4 +1,6 @@
 function caller
+
+
 clear all
 close all
 clc
@@ -6,18 +8,22 @@ warning off
 
 global Simulation SystemStates SystemInputs 
 global SystemParameters d
+global solver
 
 Simulation   = 0;
 SystemStates = ['x','y'];
 SystemInputs = ['u'];
 SystemParameters = ['d'];
-d = 1e-2;
-lambda = 1e-1; % Max value for SOS feasibility
-Option       = 'Neighbor';
+% d = 1e-2;
+d = 0
+lambda = 1e-1; % Max value for SOS feasibilityprofile on
+Option       = 'General';
+solver = 'CDCS';
+solver = 'mosek'
 
-NumberOfAgents = 4
+NumberOfAgents = 1
 
-fname = sprintf('Diary%s%dAgents',Option,NumberOfAgents);
+fname = sprintf('Diary%s%dAgents-Solver_%s',Option,NumberOfAgents,solver);
 diary(fname)
 diary on
 
@@ -25,19 +31,19 @@ if NumberOfAgents > 5 && strcmp(Option,'Diagonal') + strcmp(Option,'Neighbor') =
     
     disp('This option requires lots of RAM memory for more than 5 agents.')
     disp('Chose Option = Diagonal or Neighbor to run with more than 5 agents or')
-    return
+%     return
     
 end
 
 if NumberOfAgents > 256 && strcmp(Option,'Neighbor')
     disp('This option requires lots of RAM memory for more than 256 agents.')
     disp('Chose Option = Diagonal and run it with more than 256 agents or')
-    return
+   % return
 end
 
 if NumberOfAgents > 512 && strcmp(Option,'Diagonal')
     disp('This option requires lots of RAM memory for more than 512 agents.')
-    return
+    %return
 end
 
 LaplacianMatrix = LinearLaplacianGenerator(NumberOfAgents);
@@ -45,13 +51,21 @@ Optimisation(LaplacianMatrix,Option,lambda)
 
 diary off
 
-pause(60)
+p = profile('info');
+profile_name = sprintf('Profile%s%dAgents-Solver_%s',Option,NumberOfAgents,solver);
+save(profile_name,'p')
+
+clear p
+
+load(profile_name)
+
+profview(0,p)
 
 end
 
 function Optimisation(LaplacianMatrix,Option,lambda)
 
[…]

### 2017-05-31 TheoreticalExample2/CyclicTopology.m
Minor change to "CyclicTopology.m"

@@ -13,7 +13,7 @@ SystemInputs = ['u'];
 SystemParameters = ['d'];
 d = 1e-2;
 lambda = 1e-1; % Max value for SOS feasibility
-Option       = 'Neighbor';
+Option       = 'Unrestricted';
 
 NumberOfAgents = 4
 

### 2017-05-31 R0V0.tex
Remove the dependence of Y on u

@@
 		Y_{ij}\begin{cases}
-		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
+		=Y_{ij}(x_i,\vec{x}_i)\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
 		\equiv0_{m_i\times n_i},&\text{otherwise},
@@
 \end{equation*}
-for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.
+for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}$.
 
@@
 
-\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
-	\begin{equation}\label{eq:K ODE}
-		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s))k^\ast(t,s)\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
-	\end{equation}
-which has a unique solution defined on a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$.
-It remains to show that this interval of existence can be extended on $[0,1]$.
-In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.
-
-\mypara 	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed.
-This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.
-
-\mypara Since the vector field $\overline{K}$ is affine on $k^\ast$.
-This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
-	\begin{equation*}
-		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
-	\end{equation*}
-	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$.
-Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.
-
-\mypara Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
-	\begin{equation*}
-		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma))k_i^\ast(t,\sigma)\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
+\mypara Note that, due to the constraint $Y\in\Xi$, the independence of $Y$ with respect to the input variable $u$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
+	\begin{equation*}
+		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
 	\end{equation*}

### 2017-05-31 R0V0.tex
Merge Ian's changes on preamble and biblio

@@
 
-\usepackage[natbib=true,backend=biber,style=ieee,
-firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
-\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
-\AtBeginBibliography{\small}
+%\usepackage[natbib=true,backend=biber,style=ieee,
+%firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
+%\addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1} 
+%\AtBeginBibliography{\small}
 
@@
 % Do not put math or special symbols in the title.
-\title{Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics}
+\title{Distributed Nonlinear Control Design using Separable Control Contraction Metrics}
 %
@@
         Ian~R. Manchester,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
-\thanks{Both authors are with the Department of Aerospace, Mechanical, and Mechatronic Engineering and The Australian Centre for Field Robotics. Address: The
+\thanks{Both authors are with the Australian Centre for Field Robotics, Department of Aerospace, Mechanical, and Mechatronic Engineering,
 Rose Street Building J04, The University of Sydney, NSW 2006, Australia. Corresponding author: {\tt h.stein.shiromoto@gmail.com}, {\tt orcid.org/0000-0002-0883-0231}}% <-this % stops a space
@@
 % (used to reserve space for the reference number labels box)
-\printbibliography
+%\printbibliography
+
+\bibliographystyle{ieeetr}
+\bibliography{Library,Distributed}
 

### 2017-06-01 R0V0.tex
Merge Ian's changes in the introduction

@@
 \begin{abstract}
-In this paper, large-scale input-affine nonlinear systems are considered.
-The problem is the design of distributed controllers for this class of network systems.
-Although control-Lyapunov functions are the natural candidates to design feedback laws, the computation of these functions is a non-convex optimization problem.
-Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements.
-In this paper, control-contraction metrics (CCMs) are employed to design controllers with prescribed distributed structures.
-By using a separable structure, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program.
-An example illustrates the approach for a network system.
+This paper gives convex conditions for synthesis of a distributed  control system control for a class of large-scale networked nonlinear dynamic systems.
+It is shown that the technique of control contraction metrics (CCMs) can be extended to this problem by utilizing {\em separable} metric structures, resulting in controllers that only depend on information from local sensors and communications from immediate neighbours.
+The conditions given are pointwise linear matrix inequalities, and are necessary and sufficient for linear positive systems.
+Distributed synthesis methods based on chordal graphs are also proposed.
+A simple example demonstrates feasibility for network  of nonlinear dynamic systems with up to 512 nodes.
 \end{abstract}
@@
 
-\mypara Over the years, improvements on distance communication and cheaper computation platforms have allowed the development of large-scale interconnected systems such as smart grids, sensor networks \cite{Pajic2011}, smart manufacturing plants, traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}.
-One of the main characteristic of these systems is the capacity of being autonomous.
-Most of current control algorithms are based on the assumption that the system will operate ``near'' to a prescribed set point.
+\mypara In recent years, rapid advances in communication and  computation technology have enabled the development of large-scale engineered systems such as smart grids \cite{hill_smart_2012}, sensor networks \cite{Pajic2011}, smart manufacturing plants \cite{wang_implementing_2016}, traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015} and pipe networks \cite{Persis2011a}.
+Despite these advances, the design of feedback controllers for such large systems remains challenging.
+
+\mypara When it is assumed that a system  has linear dynamics and that all sensor information can be collected in a single location for control computation, well-developed synthesis methods such as LQG and $H^\infty$ can be applied \cite{anderson1990optimal, dullerud2000course}.
+However, emerging applications motivate going beyond these assumptions:
+\begin{enumerate}[i)]
+	\item For geographically distributed systems with thousands or millions of nodes, such as transportation and power networks, it is not practical to collect all sensor information in one location for control.
+In this case there is a need for {\em distributed} methods that rely only on local information or information communicated from nearby nodes.
+ \item Most real systems exhibit {\em nonlinear} dynamics.
+The use of linear dynamic models is usually based on the premise that the system always operates near a prescribed set-point.
+When large excursions in operating conditions are expected, e.g.
+due to changing production demands in a flexible manufacturing system, or recovery from a fault in a smart electrical grid, one must take into account the system nonlinearity.
+\end{enumerate}
+
+%Most of current control algorithms are based on the assumption that the system will operate ``near'' to a prescribed set point.
 Consequently, the system is designed to have fixed behavior.
@@
 
-\mypara In terms of control theory, the difference between a system operating in a set point and operating in a much larger region lies in the type of equation that describes the system behavior.
-In the former, the system is described by linear equation while, in the latter, by a nonlinear one.
-In general, controller design methods for nonlinear systems require the knowledge of a \emph{Lyapunov function}.
-The search of Lyapunov functions for this class of systems is a non-trivial problem by itself, as no general methodology exists.
-Another drawback of Lyapunov functions is the fact that they are defined with respect to a particular set point.
-In case of large excursions, it is more appropriate to define a function depending on the distance between points.
-Even if a Lyapunov function is known, no general methodology is known to design distributed feedback laws for nonlinear systems.
-Thus, existing approaches are, in general, \emph{ad-hoc}.
-When the design of distributed controllers is considered, the situation is even worse as the problem is known to be, at least, NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}.
-
-\mypara  An alternative method, called control contraction method (CCM), provides an algorithm in which nonlinear feedback laws are designed based on solving a convex optimization problem  \cite{Manchester2014a}.
-The main challenge with this methodology is that, when the system under consideration has a large number of states, it may require a large memory amount.
-This is due to the fact that the stability verification of a linear system with $n$ states may require a function with, at least, $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).
-
-\mypara One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions to each other.
+\mypara Decentralised and distributed control are long-standing problems in control theory, with important early work surveyed in \cite{sandell_survey_1978}.
+Terminology is not completely uniform in the literature, but
+in this paper we take ``decentralised'' to mean that at each node there is a controller that uses {\em only} local information, and  ``distributed'' to mean that {\em some} communication is allowed between nearby nodes.
+In either case, there is a desire to impose a {\em structure} on information flow, and this turns out to be the main source of difficulty.
+
+\mypara Even for linear systems, it has long been known that apparently simple problems with decentralized information flow can be surprisingly challenging \cite{witsenhausen_counterexample_1968}.
+A recent breakthrough was the discovery that a property called {\em quadratic invariance} characterises a convex subclass of problems in which, roughly speaking, communication is faster than the propagation of dynamical effects \cite{rotkowitz_characterization_2006}.
+%
+%\begin{align}
+%M(A+BK)+(A+BK)'M<0\\
+%\Updownarrow\\
+%AW+WA'+BY+Y'B'<0	
+%\end{align}
+
+\mypara More directly related to this paper is a large body of work on linear matrix inequality (LMI) methods.
+For linear state feedback, information flow can be encoded by a sparsity structure on the feedback gain matrix, however in general the problem of finding such a gain which is stabilizing is NP-Hard \cite{BlondelTsitsiklis1997}.
+It has been recognized by many authors that if the search is restricted to {\em diagonal} (or {\em block diagonal}) Lyapunov matrices, then the problem is convex (see, e.g., \cite{zecevic_control_2010, Tanaka2011, Rantzer2015} and references therein).
+The main benefit is that sparsity structure in the gain matrix is preserved under the standard change of variables for LMI-based design.
+
+\mypara In general, restricting the set of Lyapunov functions is conservative: it produces sufficient conditions for stabilizability, but not necessary.
+However, for the important sub-class of systems for which internal states are always  non-negative, known as {\em positive systems}, existence of a diagonal Lyapunov function is actually necessary and sufficient
+(see, e.g., \cite{berman_nonnegative_1994} and references therein).
+This result has been extended to $H^\infty$ design \cite{Tanaka2011}, robust stability \cite{colombino_convex_2016}, and scalable algorithms for control design \cite{Rantzer2015} and identification \cite{umenberger_scalable_2016} of networked positive systems.
+
+\mypara Design of controllers for nonlinear systems has also been a major topic of research for many years, see e.g. \cite{Slotine1991,Krstic1995, Sontag1998, Khalil:2001} for established approaches.
+Most methods require (at least implicitly) the construction of a \emph{control Lyapunov function}.
+While for certain structured systems, constructive methods such as backstepping and energy-based control can be used \cite{Slotine1991, Krstic1995}, no general methodology exists.
+Indeed, the set of control Lyapunov functions can be non-convex and disconnected \cite{Rantzer:2001}.
+
+Separable Lyapunov functions
+\cite{Dirr2015} and references therein. \cite{liu_nonlinear_2014}.
+
+\mypara Another drawback of Lyapunov functions is the fact that they are defined with respect to a particular set point or trajectory, which must be known {\em a priori}.
+In many cases, e.g.
+robotics or flexible manufacturing, it is more appropriate to define a function depending on the distance {\em between} pairs of points.
+Tools such as contraction metrics \cite{Lohmiller1998} and incremental Lyapunov functions \cite{Angeli2002} provide such a capability for stability analysis, but the problem of going from analysis to synthesis remains.
+
+\mypara  An alternative approach is to construct a control contraction metric (CCM), introduced in \cite{Manchester2014a, manchester_control_2017}.
+The main advantages this method offers over the Lyapunov approach are that the synthesis conditions are convex, and that provides a stabilizing controller for {\em all} solutions, not just a single set point.
+It was shown in \cite{manchester_control_2017} that the CCM conditions are necessary and sufficient for feedback-linearizable nonlinear systems.
+
+%mypara One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions to each other.
 Employing CCMs that can be decomposed into the sum of smaller elements, the design of a distributed feedback law allowing exponential convergence of solutions is obtained in two steps.
 
-\mypara The first step consists of an off-line computation.
+%\mypara The first step consists of an off-line computation.
 The original system is extended with its \emph{differential / variational} formulation.
@@
 
+Contraction analysis of networked systems
+\cite{Russo2013}
+\cite{Aminzare2014a} 
+\cite{manchester_existence_2018}
+
 \mypara At this point, the three contributions of this work can be highlighted.
-First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structural constraint, a distributed feedback law is obtained.
+First, using the methodology for synthesis of CCMs introduced in \cite{manchester_control_2017} and imposing a (block-)diagonal structural constraint, a distributed feedback law is obtained.
 Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is also distributed.
@@
 
-\mypara Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature.
-For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis.
-This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit algorithm of the distributed controller is provided.
-A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}.
-In contrast to this paper, more general conditions to design the distributed controller (cf.
-Corollary~\ref{cor:main result}) and a methodology to distribute the computation of the feedback law are given.
-
-\paragraph{Overview} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}.
-The background needed for this paper is stated in Section \ref{sec:background}.
+A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}
+
+\paragraph{Overview} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}, with technical background in Section \ref{sec:background}.
+Sections \ref{sec:Design of Decentralized Controllers} and \ref{sec:distributed_design} present the proposed method and main theoretical results.
 Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}.
 Section \ref{sec:Conclusion} collects final remarks.
+
+\section{Preliminaries and Problem Formulation}
 

### 2017-06-01 R0V0.tex
Merge Ian's changes in the problem formulation section

@@
 It is said to be \emph{directed} if otherwise.
-Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}.
-A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct.
+Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from node $i$ to the node $j$}.
+A path is said to be \emph{cycle} if node $i$ equals node $j$, no edges are repeated, and the nodes $i$ and $j-1$  are distinct.
 A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them.
@@
 The following concepts are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
-A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
+A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is a maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.
 A \emph{chord} of a path is any edge joining two nonconsecutive nodes.
-A graph is said to be \emph{chordal} if every cycle greater than three has a chord.
+A graph is said to be \emph{chordal} if every cycle of length greater than three has a chord.
 The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.

### 2017-06-01 R0V0.tex
Merge Ian's change in the control-contraction metric section

@@
 
-\subsection{Background}\label{sec:background}
+\subsection{Control Contraction Metrics}\label{sec:background}
 
@@
 \begin{definition}[{\cite{Manchester2014a}}]\label{def:}
-	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
+	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
 	\begin{subequations}\label{eq:Arstein-Sontag}
@@
 \mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}.
-Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
+Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
 \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.
@@
 \begin{theorem}\label{prop:CCM Existence}
-	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a differential feedback law for system~\eqref{eq:general system:differential} rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
+	If there exists a control contraction metric for system \eqref{eq:general system}, then there exists a differential feedback law for system~\eqref{eq:general system:differential} rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
 Moreover, a stabilizing feedback law for system~\eqref{eq:general system} is obtained by integrating the differential feedback law for system~\eqref{eq:general system:differential} along geodesics.

### 2017-06-01 R0V0.tex
Merge Ian's changes regarding the main result

@@
 
-\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control-contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
+\mypara As remarked in \cite{Manchester2014a}, one of the main advantages to look for control contraction metric over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the latter is non-convex \cite{Rantzer:2001}.
 The steps to obtain a control to system~\eqref{eq:general system} are recalled below.
@@
 
-\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
+\mypara From the above steps, even if the problem of imposing a particular structure on $K$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints.
 This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner.
@@
 
+Inspired by the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}), we introduce the following class of control contraction metrics:
+
 \begin{definition}\label{def:SSCCM}
-	A control-contraction metric $V$ for system \eqref{eq:general system} receives the adjective \emph{sum-separable} if it can be decomposed into the following sum
-	\begin{equation*}
+	A control contraction metric $V$ for system \eqref{eq:general system} is called \emph{sum-separable} if it can be decomposed like so:	\begin{equation*}
 		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}\;,
@@
 
-\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components.
-The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).
+\mypara In other words, Definition~\ref{def:SSCCM} states that the metric $V$ on $\mathbb{R}^n$ can be  decomposed into a sum of smaller components, each of which depends only on the {\em local} information $x_i, \delta_{x_i}$.
 
@@
 		\begin{equation}\label{eq:MI:SSCCM}
-			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
+			-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
 		\end{equation}
@@
 Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds.
-Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
+Thus, $M$ is a sum-separable control contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.
 
@@
 	\begin{equation*}
-		\gamma_i=\arg\min e(c_i)\Leftrightarrow\gamma=\arg\min\ell(c),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
+		\gamma_i=\arg\min e(c_i),\forall i\in\mathbb{N}_{[1,N]}\,\Leftrightarrow\,\gamma=\arg\min\ell(c).
 	\end{equation*}

### 2017-06-01 R0V0.tex
Merge Ian's changes regarding the distributed design

@@
 
-\section{Distributed Design of Distributed Controllers}
+\section{Distributed Design of Distributed Controllers}\label{sec:distributed_design}
 
@@
 
-\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{Tanaka2011}.
+\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}.
 Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
+
+\mypara Further conditions are discussed in \cite{manchester_existence_2018}.
 

### 2017-06-01 R0V0.tex
Merge Ian's change in the example and conclusion

@@
 \mypara Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open.
-As mentioned before, the main advantage to look for control-contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems.
+As mentioned before, the main advantage to look for control contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems.
 This is illustrated in the next section.
@@
 
-\mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
+\mypara In terms of semidefinite programming, employing control contraction metrics allows one to formulate the search for the controller as a convex optimization problem.
 Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of states, in general.

### 2017-06-02 R0V0.tex
Separate the Riemannian energy and add a log-scale figure

@@
 
-\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs, and the Riemannian metric $V$.
+\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs.
+Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}.
 Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.
@@
 	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
-	\vspace{-2em}
+
 	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained.
-In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.
-The bottom graph shows the variation of the Riemannian metric along the solutions of each case.}
+In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.}
 	\label{fig:3dsim}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+%	\includegraphics[]{}
+	\includegraphics[width=\linewidth]{./imgs/Riemannian_energy.eps}
+	\caption{Computation of the Riemannian energy along solutions to \eqref{eq:example}, according to each of each case. The bottom graph is the logarithm of the Riemannian energy.}
+	\label{fig:Riemannian energy}
 \end{figure}

### 2017-06-05 4agents.py
Change the graphs. Plot the Riemannian energy separately, plot it also using log scale

@@ -30,13 +30,13 @@ def trajectory_plot(t, trajectory, case, title, linestyle, ax1 = None, ax2 = Non
     for counter in range(trajectory.shape[1]):
         if (counter % 2) == 0:
             if (case is 'diagonal') & (counter == 0) & (ax1 == None):
-                ax1 = plt.subplot2grid((5, 2), ((counter % 2), 0))
+                ax1 = plt.subplot2grid((4, 2), ((counter % 2), 0))
             elif (case is 'neighbour') & (counter == 0) & (ax1 == None):
-                ax1 = plt.subplot2grid((5, 2), ((counter % 2) + 2, 0))
+                ax1 = plt.subplot2grid((4, 2), ((counter % 2) + 2, 0))
             elif (case is 'unconstrained') & (counter == 0) & (ax1 == None):
-                ax1 = plt.subplot2grid((5, 2), ((counter % 2), 1))
+                ax1 = plt.subplot2grid((4, 2), ((counter % 2), 1))
             elif (counter == 0) & (ax1 == None):
-                ax1 = plt.subplot2grid((5, 2), ((counter % 2) + 2, 1))
+                ax1 = plt.subplot2grid((4, 2), ((counter % 2) + 2, 1))
             color = color_vector.next()
             ax1.plot(t, trajectory[:, counter], label=r'x' + str(counter / 2 + 1), linestyle=linestyle, c=color)
             ax1.set_xticklabels([])
@@ -44,16 +44,16 @@ def trajectory_plot(t, trajectory, case, title, linestyle, ax1 = None, ax2 = Non
             #ax1.yaxis.set_label_coords(labelx, 0.5)
         else:
             if (case is 'diagonal') & (counter == 1) & (ax2 == None):
-                ax2 = plt.subplot2grid((5, 2), ((counter % 2), 0))
+                ax2 = plt.subplot2grid((4, 2), ((counter % 2), 0))
                 ax2.set_xticklabels([])
             elif (case is 'neighbour') & (counter == 1) & (ax2 == None):
-                ax2 = plt.subplot2grid((5, 2), ((counter % 2) + 2, 0))
+                ax2 = plt.subplot2grid((4, 2), ((counter % 2) + 2, 0))
                 ax2.set_xlabel(r'time $t$')
             elif (case is 'unconstrained') & (counter == 1) & (ax2 == None):
[…]

### 2017-06-05 R0V0.tex
Change Corollary 1: formulation considering also the input variable u and the sign of the identity

@@
 \begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
-	Assume that the matrix $A$ depends only on the system state $x$, the matrix $B$ satisfies the identity
-	\begin{equation*}
-		\partial_BW-\tfrac{\partial B}{\partial x}W+W\tfrac{\partial B}{\partial x}^\top\equiv0
+	Assume that the matrix $B$ satisfies the identity
+	\begin{equation*}
+		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
 	\end{equation*}
@@
 	\end{equation}
-	holds uniformly with respect to $x\in\mathbb{R}^n$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$.
+	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$.
 Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.

### 2017-06-05 R0V0.tex
Remove phrases from the introduction, and change wording of paragraph II.8

@@
 
-Separable Lyapunov functions
-\cite{Dirr2015} and references therein. \cite{liu_nonlinear_2014}.
+%Separable Lyapunov functions \cite{Dirr2015} and references therein. \cite{liu_nonlinear_2014}.
 
@@
 
-Contraction analysis of networked systems
-\cite{Russo2013}
-\cite{Aminzare2014a} 
-\cite{manchester_existence_2018}
+%Contraction analysis of networked systems \cite{Russo2013} \cite{Aminzare2014a}  \cite{manchester_existence_2018}
 
@@
 Note that the proposed method provides an explicit algorithm to design the controller.
-
-A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}
+A particular case of this paper has also been published in \cite{SteinShiromotoManchester2016}.
 
@@
 
-\mypara At this point, the problem under consideration in this paper can be stated as follows.
+\mypara At this point, the problem under consideration in this paper can be formulated as follows.
 
@@
 \end{equation}
-As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints.
+As explained in Section \ref{sec:Illustration}, when more than eight of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints.
 However, by utilizing a separable structure (see definition below), up to 512 of theses systems can be connected and the distributed controller can be computed.

### 2017-06-05 R0V0.tex
Minor corrections

@@
 Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
-
-\mypara Further conditions are discussed in \cite{manchester_existence_2018}.
+Further conditions are discussed in \cite{manchester_existence_2018}.
 
@@
 
-\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. To compute the matrix $W$, chordal graphs are employed.
+\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. Consider the case with $N=4$ to compute the matrix $W$, chordal graphs are employed.
 
@@
 
-\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs.
-Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}.
-Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.
-
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
-
-	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained.
-In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.}
-	\label{fig:3dsim}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-%	\includegraphics[]{}
-	\includegraphics[width=\linewidth]{./imgs/Riemannian_energy.eps}
-	\caption{Computation of the Riemannian energy along solutions to \eqref{eq:example}, according to each of each case. The bottom graph is the logarithm of the Riemannian energy.}
-	\label{fig:Riemannian energy}
-\end{figure}
-
 \mypara When $N>8$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer.
@@
 Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite.
-For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
+For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position of the matrix $T$ is
 \begin{equation*}
@@
 
-The parser took 98  seconds to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
+\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
 \begin{equation*}
@@
 \mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$.
-The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 2.6 seconds, the matrix $W$ is given by
+The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
 \begin{equation*}
@@
 \end{align*}
+
+\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph}, according to each constraint imposed on the controller.
+Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}.
+Note that, when random initial random initial conditions are considered and the input is zero to be identically zero, the system may diverge from the neighborhood of the origin.
+
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
+
+	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained.
+In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin.}
+	\label{fig:3dsim}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+%	\includegraphics[]{}
+	\includegraphics[width=\linewidth]{./imgs/Riemannian_energy.eps}
+	\caption{Computation of the Riemannian energy along solutions to \eqref{eq:example}, according to each of each case. The bottom graph is the logarithm of the Riemannian energy.}
+	\label{fig:Riemannian energy}
+\end{figure}
 
@@
 	Neighbor&3.5s\\
-	Fully decentralized&2.6s\\\hline
+	Fully decentralized&4.4s\\\hline
 	\end{tabular}\vspace{1em}

### 2017-06-22 R0V0.tex
Change the proof Proposition 1 to explain the dependence of F on nodes x_i, \breve{x_i}, \hat{x}_i. Change the times on the tables for the examples

@@
 This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
-In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel.
-To that end chordal graphs are employed.
-It utilizes the network topology to decompose it into smaller complete components.
+Thus, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be scalable, in the sense that adding more agents to the network will make the time taken to compute the controller linearly.
+To that end chordal graphs are employed to decompose the network topology into smaller complete components.
 
 \begin{proposition}\label{prop:clique tree decomposition}
-	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
+	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
 Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension.
@@
 	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$.
-Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$.
+Let the integer $l>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$.
 The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.
 
-\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
-For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
+\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_l$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,l]}$.
+For each index $k\in\mathbb{N}_{[1,l]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 
 \mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$.
-The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
+The existence of $l$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,l]}$, satisfying the equation
    \begin{equation*}
@@
 
-\mypara Consequently, whenever the following matrix inequality holds 
+\mypara Without loss of generality, assume that the node $i\in\mathscr{V}_c$ is contained in the clique $\mathscr{C}_k$. Whenever the following matrix inequality 
   	\begin{equation}\label{eq:MIF}
-  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
-	\end{equation}
-	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds. This concludes the proof.
+  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,l]},
+	\end{equation}
+	holds uniformly, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds.
+
+	For each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in the clique $\mathscr{C}_k$.
+The corresponding matrix $F_k$ has arguments $x_i, \breve{x}_i$ and $\vec{x}_i$.
+In other words, $F_k$ depends on how strongly the nodes of the of the system (defined by $\mathscr{G}_c$) and communication network (defined by $\mathscr{G}_p$) are connected among each other.
+This concludes the proof.
 \end{proof}
@@
 Namely, the unconstrained case, the ``neighbor'' case, and the fully decentralized case.
-For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor'' case and up to $N=512$ systems for the fully decentralized (diagonal) case.
+For the two latter cases, it was possible to consider up to $N=512$ systems.
 In these scenarios the techniques provided by chordal graphs have been employed.
@@
 
-\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
+\mypara The solver took 31 seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
 \begin{equation*}
@@
 
-\mypara The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3.5 seconds. The matrix $W$ is given by
+\mypara The time taken by solver to find a solution to the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3 seconds. The matrix $W$ is given by
 \begin{equation*}
@@
 \mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$.
-The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
+The time taken by the solver to find a solution to the set of matrix inequalities~\eqref{eq:main result} was 2.5 seconds, the matrix $W$ is given by
 \begin{equation*}
@@
 	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration.
-The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case).
+The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 512 for the other cases).
 Axes are on log scale.}
@@
 	Case&Time taken by the solver (4 agents)\\ \hline
-	Unconstrained&98s\\
-	Neighbor&3.5s\\
-	Fully decentralized&4.4s\\\hline
+	Unconstrained&31s\\
+	Neighbor&3s\\
+	Fully decentralized&2.5s\\\hline
 	\end{tabular}\vspace{1em}
@@
 
-\mypara The solver took 48s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
+\mypara The solver took 32s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
 \begin{equation*}
@@
 More precisely, $\mathscr{G}_c=\mathscr{G}_p$.
-The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.
+The solver took 17s to solve the set of matrix inequalities~\eqref{eq:main result}.
 
@@
 \mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$.
-The solver took 43s to solve the set of matrix inequalities~\eqref{eq:main result}.
+The solver took 12s to solve the set of matrix inequalities~\eqref{eq:main result}.
 
@@
 	Case&Time taken by the solver (4 agents)\\ \hline
-	Unconstrained&48s\\
-	Neighbor&57s\\
-	Fully decentralized&43s\\\hline
+	Unconstrained&32s\\
+	Neighbor&17s\\
+	Fully decentralized&12s\\\hline
 	\end{tabular}\vspace{1em}

### 2017-06-23 R0V0.tex
Change title of the distribued optimisation section
Add Ian's changes on the paper

@@
 \newcounter{para}
-\newcommand\mypara{\par \thesection.\refstepcounter{para}\thepara.\space}
+%\newcommand\mypara{\par \thesection.\refstepcounter{para}\thepara.\space}
+\newcommand\mypara{\par}
 
@@
 
-\mypara A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\times\{X^\ast\}\times\{u^\ast\}\to\mathbb{R}^m$, denoted as $k^\ast$, such that the inequality
+\mypara A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}^n\times\{X^\ast\}\times\{u^\ast\}\to\mathbb{R}^m$, denoted as $k^\ast$, such that the inequality
 \begin{equation}\label{eq:global exponential uniform stabilizability}
@@
 
-\begin{figure}[htbp!]
+\begin{figure}
 	\centering
 %	\includegraphics[]{}
-	\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
-	\caption{Illustration of the graphs $\mathscr{G}_p$ and $\mathscr{G}_c$. The solid lines represent the edges defining $\mathscr{G}_p$ while the dashed lines represent edges defining $\mathscr{G}_c$.}
+	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
+	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
 	\label{fig:graph different illustration}
@@
 \mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows.
-Given a fixed control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$.
+Given a particular control signal $u(\cdot)$ for system \eqref{eq:general system}, $\delta_u\equiv0$.
 If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} under the input $u$ converge to each other exponentially.
@@
 Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf.
-\cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.
+\cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\to\mathbb{R}^{n\times m}$.
 
@@
 The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf.
-\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W(\cdot)=W(\cdot)^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
+\cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W(\cdot)=W(\cdot)^\top\succ0$ and a function $Y:\mathbb{R}^n\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
 \begin{equation}\label{eq:MI formulation}
@@
 	\begin{equation}\label{eq:differential feedback law}
-		\delta_k=Y(x,u)W^{-1}(x)\delta_x:=K(x,u)\delta_x
+		\delta_k=Y(x)W^{-1}(x)\delta_x:=K(x)\delta_x
 	\end{equation}
@@
 \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them.
-This implies that the solution $k^\ast$ to the integral equation
+Then the differential feedback law $K(x)$ can be integrated along $\gamma$:
 \begin{equation}\label{eq:contracting feedback law}
-	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)\,ds\;,
+	k(x,=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
 \end{equation}
 where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.
+
+Note about existence a.e.
+
+Note about constant metric/constant Y case.
 
@@
 
+This was used in \cite{wang_distributed_2017} to guarantee stability in distributed economic model predictive control.
+
 \section{Design of Distributed Controllers}\label{sec:Design of Decentralized Controllers}
 
-Inspired by the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}), we introduce the following class of control contraction metrics:
+Inspired by the notion of sum-separable Lyapunov functions (see e.g. \cite{Dirr2015}), we introduce the following class of control contraction metrics:
 
@@
 	\end{subequations}
-	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
+	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
 In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
@@
 Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$.
-Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi$.
+Since $W$ is separable, the sparsity pattern and local dependence of $Y$ is preserved and, consequently, $K\in\Xi$.
 
@@
 
-\section{Distributed Design of Distributed Controllers}\label{sec:distributed_design}
+\section{Scalable Design of Distributed Controllers}\label{sec:distributed_design}
 

### 2017-06-26 R0V0.tex
Minor updates

@@
 	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
+	\includegraphics[width=\columnwidth]{./imgs/physical_network_graphs}
 	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
@@
 
-\begin{definition}\label{def:}
+\begin{definition}
 		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
@@
 
-\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
+\begin{definition}[{\cite{Manchester2014a}}]
 	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
@@
 \begin{equation}\label{eq:contracting feedback law}
-	k(x,=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
+	k(t)=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
 \end{equation}
@@
 Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
-Further conditions are discussed in \cite{manchester_existence_2018}.
 

### 2017-06-26 R0V0.tex
Update the statement of Proposition 1

@@
 	Then, $W$ is a separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
+Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, each function $W_i$ depends only on the state of system $i$.
 In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
@@
 Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}.
-In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
+Also, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
 \end{corollary}
@@
 	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
-Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension.
-Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
+Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $l$ matrix inequalities with smaller dimension.
+Furthermore, each of the matrix inequality correspond to a clique, and for each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in it, the matrix inequality depends on $x_i, \breve{x}_i$ and $\vec{x}_i$.
+Finally, whenever each matrix inequality holds uniformly over its argument, the set of Equations~\eqref{eq:MI:SSCCM} is satisfied.
 \end{proposition}

### 2017-10-18 R0V0_ian.tex
Add / change files

--- 2017-06-23 R0V0.tex
@@
 	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
+	\includegraphics[width=\columnwidth]{./imgs/physical_network_graphs}
+
 	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
@@
 
-\section{Scalable Design of Distributed Controllers}\label{sec:distributed_design}
+\section{Distributed Design of Distributed Controllers}\label{sec:distributed_design}
 
@@
 This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}.
-Thus, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be scalable, in the sense that adding more agents to the network will make the time taken to compute the controller linearly.
-To that end chordal graphs are employed to decompose the network topology into smaller complete components.
+In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel.
+To that end chordal graphs are employed.
+It utilizes the network topology to decompose it into smaller complete components.
 
 \begin{proposition}\label{prop:clique tree decomposition}
-	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
+	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$.
 Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension.
@@
 	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$.
-Let the integer $l>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$.
+Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$.
 The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.
 
-\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_l$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,l]}$.
-For each index $k\in\mathbb{N}_{[1,l]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
+\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$.
+For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
 
 \mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$.
-The existence of $l$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,l]}$, satisfying the equation
+The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
    \begin{equation*}
@@
 
-\mypara Without loss of generality, assume that the node $i\in\mathscr{V}_c$ is contained in the clique $\mathscr{C}_k$. Whenever the following matrix inequality 
+\mypara Consequently, whenever the following matrix inequality holds 
   	\begin{equation}\label{eq:MIF}
-  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,l]},
-	\end{equation}
-	holds uniformly, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds.
-
-	For each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in the clique $\mathscr{C}_k$.
-The corresponding matrix $F_k$ has arguments $x_i, \breve{x}_i$ and $\vec{x}_i$.
-In other words, $F_k$ depends on how strongly the nodes of the of the system (defined by $\mathscr{G}_c$) and communication network (defined by $\mathscr{G}_p$) are connected among each other.
-This concludes the proof.
+  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
+	\end{equation}
+	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds. This concludes the proof.
 \end{proof}
@@
 
-\mypara The solver took 31 seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
+\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
 \begin{equation*}
@@
 
-\mypara The time taken by solver to find a solution to the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3 seconds. The matrix $W$ is given by
+\mypara The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3.5 seconds. The matrix $W$ is given by
 \begin{equation*}
@@
 \mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$.
-The time taken by the solver to find a solution to the set of matrix inequalities~\eqref{eq:main result} was 2.5 seconds, the matrix $W$ is given by
+The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
 \begin{equation*}
@@
 	Case&Time taken by the solver (4 agents)\\ \hline
-	Unconstrained&31s\\
-	Neighbor&3s\\
-	Fully decentralized&2.5s\\\hline
+	Unconstrained&98s\\
+	Neighbor&3.5s\\
+	Fully decentralized&4.4s\\\hline
 	\end{tabular}\vspace{1em}
@@
 
-\mypara The solver took 32s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
+\mypara The solver took 48s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
 \begin{equation*}
@@
 More precisely, $\mathscr{G}_c=\mathscr{G}_p$.
-The solver took 17s to solve the set of matrix inequalities~\eqref{eq:main result}.
+The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.
 
@@
 \mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$.
-The solver took 12s to solve the set of matrix inequalities~\eqref{eq:main result}.
+The solver took 43s to solve the set of matrix inequalities~\eqref{eq:main result}.
 
@@
 	Case&Time taken by the solver (4 agents)\\ \hline
-	Unconstrained&32s\\
-	Neighbor&17s\\
-	Fully decentralized&12s\\\hline
+	Unconstrained&48s\\
+	Neighbor&57s\\
+	Fully decentralized&43s\\\hline
 	\end{tabular}\vspace{1em}

### 2017-10-30 TheoreticalExample2/LMIOptmisation.m
Improvements

@@ -14,14 +14,14 @@ Simulation   = 0;
 SystemStates = ['x','y'];
 SystemInputs = ['u'];
 SystemParameters = ['d'];
-% d = 1e-2;
-d = 0
+d = 1e-2;
+% d = 0
 lambda = 1e-1; % Max value for SOS feasibilityprofile on
-Option       = 'General';
-solver = 'CDCS';
+Option       = 'Neighbor';
+% solver = 'CDCS';
 solver = 'mosek'
 
-NumberOfAgents = 1
+NumberOfAgents = 512
 
 fname = sprintf('Diary%s%dAgents-Solver_%s',Option,NumberOfAgents,solver);
 diary(fname)
@@ -93,11 +93,11 @@ tic
 SolverTime = toc;
 
 Precision = 1e-3;
-AnalysisW(SystemStates,LaplacianMatrix,Precision)
-PostProcessedW
+%AnalysisW(SystemStates,LaplacianMatrix,Precision)
+%PostProcessedW
 
-AnalysisY(SystemInputs,LaplacianMatrix,Precision)
-PostProcessedY
+%AnalysisY(SystemInputs,LaplacianMatrix,Precision)
+%PostProcessedY
 
 NumberOfAgents = size(LaplacianMatrix,1);
 fname = sprintf('Output%s%dAgents-Solver_%s',Option,NumberOfAgents,solver);

### 2017-10-30 TheoreticalExample2/MixedExample.m

@@ -13,7 +13,7 @@ SystemInputs = ['u'];
 SystemParameters = ['d'];
 d = 1e-2;
 lambda = 1e-1; % Max value for SOS feasibility
-Option       = 'Unconstrained';
+Option       = 'Diagonal';
 
 LaplacianMatrix = LaplacianMatrixGenerator;
 NumberOfAgents  = length(LaplacianMatrix);

### 2017-10-30 TheoreticalExample2/mat_reader.py

@@ -49,13 +49,13 @@ mosek_general = ax.scatter(df[(df.Constraint == 'General') & (df.Solver == 'mose
 #CDCS_general = ax.scatter(df[(df.Constraint == 'General') & (df.Solver == 'CDCS')].NNeigh, df[(df.Constraint == 'General') & (df.Solver == 'CDCS')].SolverTime, c='red', marker='d', label='General & CDCS', alpha=0.33, lw=1)
 ax.set_yscale('log')
 plt.ylabel('Time [s]')
-ax.set_xscale('log')
+ax.set_xscale('log', basex=2)
 plt.xlabel('Number of nodes (N)')
 plt.xticks(number_of_neighbors, number_of_neighbors)
 plt.title('Time taken to solve the set of matrix inequalities')
 # lgd = plt.legend(handles=[mosek_diagonal, mosek_neighbor, mosek_general, CDCS_diagonal, CDCS_neighbor, CDCS_general], loc='upper right', bbox_to_anchor=(1,-0.15), ncol=2)
 lgd = plt.legend(handles=[mosek_diagonal, mosek_neighbor, mosek_general], loc='best')
-plt.grid(True)
+plt.grid(True, which="both", linewidth=0.25, linestyle=':')
 plt.savefig('ParserTimes.eps', format='eps', dpi=1200, bbox_inches='tight')
 plt.show()
 # print sio.whosmat('OutputGeneral1Agents-Solver_CDCS.mat')

### 2018-04-09 response_letter.tex
Add response letter

\documentclass[11pt,a4]{article}

%%%%%%%%%%%%
% Language %
%%%%%%%%%%%%
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[english]{babel}

%% For graphics
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf} % Must be loaded right after graphicx

\usepackage[normalem]{ulem} % to use the \sout command

\usepackage[natbib=true,backend=biber,style=alphabetic,
firstinits=true,doi=false,eprint=false,isbn=false,url=false,texencoding=utf8,bibencoding=utf8]{biblatex}
%\AtBeginBibliography{\footnotesize} % To make bibliography smaller

  %Must be used with biber as backend
  %Execute with "biber filename"
  \addbibresource[location=remote]{https://www.dropbox.com/s/r00o9lw76cksxvj/Library.bib?dl=1}

% Fonts and symbols
\usepackage{amsfonts,amssymb,amsmath} % AMS fonts and symbols package

\begin{document}

\title{Response to the Associate Editor and Reviewers' comments on the 
paper ''Distributed Nonlinear Control Design using Separable Control 
Contraction Metrics''}

\author{Humberto Stein Shiromoto, and Ian R. Manchester}

\date{\today}

\maketitle

\printbibliography

\end{document}

### 2018-04-09 response_letter.tex
Start response_letter

@@
 
+\section*{Associate Editor} % (fold)
+\label{sec:ae}
+All the reviewers found the paper clear and well written. However, the
+main concerns that have been raised involve:
+
+\begin{enumerate}
+	\item novelty nature of the results - the authors should better 
+	clarify the novelties of their work and better relate their results 
+	with the literature;
+
+	\item Effectiveness of the results - the authors
+should provide some sufficient conditions for the existence of the
+sum-separable metric. How this relates to the structure of the graph?
+It seems that the matrix inequalities should be satisfied along any
+possible $(x,u)$. If this is the case, then this seems to make the
+resolution of the inequalities extremely challenging. The authors
+should discuss this point;
+
+	\item The results of this paper seem to provide a natural extension to
+previous works by the authors. What are the benefits of this extension?
+Are there cases that cannot be studied with the previous work by the
+authors but can be studied with the approach of this paper?
+
+\item Related to the items above, the authors should also include in the
+paper a revised application section for e.g. a large scale network
+system arising in engineering applications. Platooning of autonomous
+vehicles would be, for example, an interesting application. This would
+allow the authors to comment on the items raised above.
+\end{enumerate}
+% section  (end)
+
+\section{Reviewer\# 6}\label{r:6}
+
+\section{Reviewer\# 9}\label{r:9}
+
+\section{Reviewer\# 11}\label{r:11}
+
+\section{Reviewer\# 13}\label{r:13}
+
 \printbibliography
